### 2023-04-03 manuscript/manuscript.tex
manuscript LaTeX backmatter, packages, commands

\documentclass[11pt, 5p]{elsarticle}

\journal{TBA}

\bibliographystyle{elsarticle-num}
\biboptions{numbers,sort&compress}

% format hacks
\usepackage{libertine}
\usepackage{libertinust1math}
\usepackage{amsmath}                 % Provides advanced math typesetting and environments
\usepackage{bbold}                   % Provides blackboard bold font for numbers
\usepackage{graphicx}                % Handles the inclusion of graphics files
\usepackage{eurosym}                 % Provides the Euro currency symbol
\usepackage{mathtools}               % Enhances amsmath package, adding new symbols and tools
\usepackage{url}                     % Handles the formatting of URLs
\usepackage{booktabs}                % Improves the quality of tables in LaTeX
\usepackage{epstopdf}                % Automatically converts EPS files to PDF
\usepackage{xfrac}                   % Provides a consistent way to typeset fractions
\usepackage{tabularx}                % Enhances the standard LaTeX tables
\usepackage{bm}                      % Provides access to bold math symbols
\usepackage{subcaption}              % Provides support for subfigures and subtables
\usepackage{longtable}               % Allows the creation of multi-page tables
\usepackage{multirow}                % Enables cells spanning multiple rows in tables
\usepackage{threeparttable}          % Provides additional functionality for tables
\usepackage{pdflscape}               % Allows landscape pages in PDF output
\usepackage[svgnames]{xcolor}    	 % Load xcolor packages
\usepackage[export]{adjustbox}       % Provides tools for resizing and trimming images
\usepackage[version=4]{mhchem}       % Provides typesetting for chemical equations
\usepackage[colorlinks]{hyperref}    % Creates hyperlinks in the document
\usepackage[parfill]{parskip}        % Adjusts paragraph spacing
\usepackage[nameinlink,sort&compress,capitalise,noabbrev]{cleveref} % Enhanced cross-referencing
\usepackage[leftcaption,raggedright]{sidecap} % Provides side captions for figures and tables
\usepackage[prependcaption,textsize=footnotesize]{todonotes} % Allows inline and margin notes
\usepackage{siunitx}                 % Provides consistent formatting for units and numbers
\usepackage[acronym, automake, nonumberlist]{glossaries-extra}

\usepackage{lipsum}
\usepackage{mdframed}
\usepackage[resetlabels,labeled]{multibib} % Allows multiple bibliographies with own styles/numbering
\newcites{S}{Supplementary References}
\bibliographystyleS{elsarticle-num}

\sisetup{
	range-units = single,
	per-mode = symbol
}
\DeclareSIUnit\year{a}
\DeclareSIUnit{\tco}{t_{\ce{CO2}}}
\DeclareSIUnit{\sieuro}{\mbox{\euro}}

\graphicspath{{../results/graphics/},}

\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\set}[1]{\left\{#1\right\} }
\DeclareMathOperator*{\argmin}{\arg\!\min}
\newcommand{\R}{\mathbb{R} }
\newcommand{\B}{\mathbb{B} }
\newcommand{\N}{\mathbb{N} }
\newcommand{\co}{\ce{CO2}~}
\def\el{${}_{\textrm{el}}$}
\def\th{${}_{\textrm{th}}$}
\def\deg{${}^\circ$}

\newdefinition{rmk}{Remark}
\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newmdtheoremenv[
  backgroundcolor=Wheat, % Background color
  linewidth=0.5pt, % Width of the line around the box
  frametitlefont=\normalfont\bfseries, % Font for the box title
]{res}[thm]{Result}

% acronyms
\makeglossaries
\newacronym{tes}{TES}{Thermal energy storage (in form of water tanks)}
\newacronym{chp}{CHP}{Combined heat and power plant}
\newacronym{cop}{COP}{Coefficient of Performance}
\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
\newacronym{PV}{PV}{Solar photovoltaics}
\newacronym{ghg}{GHG}{Greenhouse gas}
\newacronym{EU}{EU}{European Union}
\newacronym{dea}{DEA}{Danish Energy Agency}
\newacronym{helmeth}{HELMETH}{Integrated High-Temperature Electrolysis and Methanation for Effective Power to Gas Conversion}
\newacronym{jrc}{JRC}{Joint Research Center}
\newacronym{ocgt}{OCGT}{Open cyclic gas turbine}
\newacronym{v2g}{V2G}{Vehicle to Grid}
\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
\newacronym{tyndp}{TYNDP}{Ten-year network development plan}
\newacronym{entso-e}{ENTSO-E}{European network for transmission system operators electricity}
\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
\newacronym{covid}{COVID-19}{Coronavirus disease 2019}
\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}
\newacronym{dsm}{DSM}{Demand side management}
\newacronym{hvdc}{HVDC}{High voltage direct current}
\newacronym{phs}{PHS}{Pumped hydro storage}
\newacronym{dac}{DAC}{Direct air capture}
\newacronym{sng}{SNG}{Synthetic natural gas}
\newacronym{fom}{FOM}{Fixed operation and maintenance costs}
\newacronym{vom}{VOM}{Variable operation and maintenance costs}
\newacronym{ppa}{PPA}{Power Purchase Agreement}
\newacronym{ptc}{PTC}{Production Tax Credit}
\newacronym{res}{RES}{Renewable energy sources}
\newacronym{necp}{NECP}{National energy climate plan}
\newacronym{ets}{ETS}{Emissions Trading System}
\newacronym{capex}{CAPEX}{Capital expenditures}
\newacronym{cfd}{CfD}{Contract for Difference}
\newacronym{cfe}{CFE}{Carbon-free electricity}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

	\title{ new paper}

	\author[affil]{ iegor } % \corref{correspondingauthor}
	\ead{ name@box }

	\address[affil]{ affiliation }

	\begin{abstract}
		\input{sections/abstract.tex}
	\end{abstract}

	\begin{keyword}
		TODO
	\end{keyword}

	% \begin{graphicalabstract}
	% \end{graphicalabstract}

\end{frontmatter}

%\listoftodos[TODOs]
%\tableofcontents

\section{Introduction}
\label{sec:intro}
\input{sections/introduction.tex}

\section{Methods}
\label{sec:methods}

\input{sections/methods.tex}

\section{Results}
\label{sec:results}

\input{sections/results.tex}

\section{Discussion}
\label{sec:discussion}

\input{sections/discussion.tex}

\section{Conclusion}
\label{sec:conclusion}

\input{sections/conclusion.tex}

\section*{Acknowledgements}

% XY gratefully acknowledge funding from XY under grant no. 00000.

\section*{License}
% \doclicenseLongText
% \doclicenseIcon

\section*{Author Contributions}

% following https://casrai.org/credit/

\textbf{Author XY}:
Conceptualization --
Data curation --
Formal Analysis --
Funding acquisition --
Investigation --
Methodology --
Project administration --
Resources --
Software --
Supervision --
Validation --
Visualization --
Writing - original draft --
Writing - review \& editing

\section*{Data and Code Availability}

A dataset of the model results is available at \href{zenodoTBA}{doi:zenodoTBA}.
The code to reproduce the experiments is available at \href{https://github.com/repository}{GITHUB}.

\section*{Abbreviations}
\printglossary[type=\acronymtype]

% tidy with https://flamingtempura.github.io/bibtex-tidy/
\addcontentsline{toc}{section}{References}
\renewcommand{\ttdefault}{\sfdefault}
\bibliography{references}

% supplementary information

\newpage

\makeatletter
\renewcommand \thesection{S\@arabic\c@section}
\renewcommand\thetable{S\@arabic\c@table}
\renewcommand \thefigure{S\@arabic\c@figure}
\makeatother
\renewcommand{\citenumfont}[1]{S#1}
\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{section}{0}

\section{Supplementary Information}
\label{sec:si}

\input{sections/supplementary.tex}

\addcontentsline{toc}{section}{Supplementary References}
\renewcommand{\ttdefault}{\sfdefault}
\bibliographyS{references}

\end{document}

### 2023-04-04 manuscript/manuscript.tex
final LaTeX configs, move auxiliaries to gitignore
manuscript skeleton

@@
-\documentclass[11pt, 5p]{elsarticle}
+\documentclass[11pt, 5p, nopreprintline]{elsarticle}
 
@@
 
-\graphicspath{{../results/graphics/},}
+\graphicspath{{../results/paper/},}
 
@@
 \makeglossaries
-\newacronym{tes}{TES}{Thermal energy storage (in form of water tanks)}
-\newacronym{chp}{CHP}{Combined heat and power plant}
+\newacronym{tes}{TES}{Thermal Energy Storage (in form of water tanks)}
+\newacronym{chp}{CHP}{Combined Heat and Power plant}
 \newacronym{cop}{COP}{Coefficient of Performance}
@@
 \newacronym{jrc}{JRC}{Joint Research Center}
-\newacronym{ocgt}{OCGT}{Open cyclic gas turbine}
+\newacronym{ocgt}{OCGT}{Open Cycle Gas Turbine}
 \newacronym{v2g}{V2G}{Vehicle to Grid}
 \newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
-\newacronym{tyndp}{TYNDP}{Ten-year network development plan}
-\newacronym{entso-e}{ENTSO-E}{European network for transmission system operators electricity}
+\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
+\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
+\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}
 \newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
-\newacronym{covid}{COVID-19}{Coronavirus disease 2019}
-\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}
-\newacronym{dsm}{DSM}{Demand side management}
-\newacronym{hvdc}{HVDC}{High voltage direct current}
-\newacronym{phs}{PHS}{Pumped hydro storage}
-\newacronym{dac}{DAC}{Direct air capture}
-\newacronym{sng}{SNG}{Synthetic natural gas}
-\newacronym{fom}{FOM}{Fixed operation and maintenance costs}
-\newacronym{vom}{VOM}{Variable operation and maintenance costs}
+\newacronym{dsm}{DSM}{Demand Side Management}
+\newacronym{hvdc}{HVDC}{High Voltage Direct Current}
+\newacronym{phs}{PHS}{Pumped Hydro Storage}
+\newacronym{dac}{DAC}{Direct Air Capture}
+\newacronym{sng}{SNG}{Synthetic Natural Gas}
+\newacronym{fom}{FOM}{Fixed Operation and Maintenance costs}
+\newacronym{vom}{VOM}{Variable Operation and Maintenance costs}
 \newacronym{ppa}{PPA}{Power Purchase Agreement}
 \newacronym{ptc}{PTC}{Production Tax Credit}
-\newacronym{res}{RES}{Renewable energy sources}
-\newacronym{necp}{NECP}{National energy climate plan}
+\newacronym{res}{RES}{Renewable Energy Sources}
+\newacronym{necp}{NECP}{National Energy and Climate Plan}
 \newacronym{ets}{ETS}{Emissions Trading System}
@@
 \newacronym{cfd}{CfD}{Contract for Difference}
-\newacronym{cfe}{CFE}{Carbon-free electricity}
+\newacronym{cfe}{CFE}{Carbon-Free Electricity}
+\newacronym{ci}{CI}{Corporate and Industry sectors}
 
@@
 
-	\title{ new paper}
+	\title{Navigating to a Greener Europe through Clean Electricity Procurement}
 
-	\author[affil]{ iegor } % \corref{correspondingauthor}
-	\ead{ name@box }
+	\author[tubaddress]{Iegor Riepin}
+	\ead{iegor.riepin@tu-berlin.de}
+	\author[tubaddress]{Tom Brown} 
+	\ead{t.brown@tu-berlin.de}
 
-	\address[affil]{ affiliation }
+	\address[tubaddress]{Department of Digital Transformation in Energy Systems, TU Berlin, Germany}
 
@@
 \label{sec:methods}
-
 \input{sections/methods.tex}
@@
 \label{sec:results}
-
 \input{sections/results.tex}
@@
 \label{sec:discussion}
-
 \input{sections/discussion.tex}
@@
 \label{sec:conclusion}
-
 \input{sections/conclusion.tex}
@@
 
-% XY gratefully acknowledge funding from XY under grant no. 00000.
-
-\section*{License}
-% \doclicenseLongText
-% \doclicenseIcon
+This paper is an independent project, which is based on the third-party funded 
+research work \cite{Riepin-report-2022}. This research work was supported by a grant from Google Inc.
 
@@
 
-\textbf{Author XY}:
+\textbf{Iegor Riepin}:
 Conceptualization --
@@
 Formal Analysis --
-Funding acquisition --
 Investigation --
 Methodology --
-Project administration --
-Resources --
+Software --
+Validation --
+Visualization --
+Writing - original draft
+
+\textbf{Tom Brown}:
+Conceptualization --
+Methodology --
 Software --
 Supervision --
-Validation --
-Visualization --
-Writing - original draft --
 Writing - review \& editing
@@
 
-\section*{Abbreviations}
 \printglossary[type=\acronymtype]

### 2023-04-04 manuscript/sections/abstract.tex
manuscript skeleton

Traditional power purchase agreements for renewable energy have seen rapid growth in recent years, but they only match supply and demand on average over a longer period such as a year.
There is increasing interest from leaders in voluntary clean electricity procurement to cover their consumption with clean energy supply on truly 24/7 basis. 
Achieving 24/7 carbon-free energy means that every kilowatt-hour of electricity consumption is met with carbon-free electricity sources, every hour of every day.
In this study, we investigate both the means and costs of pursuing different clean electricity procurement strategies for companies in a selection of European countries.
We also explore how the 24/7 clean energy procurement affects the rest of the European electricity system.

\bf{Dummy abstract - to refine}

### 2023-04-04 manuscript/sections/conclusion.tex
manuscript skeleton

Taken together, we show that 24/7-CFE commitment by corporate sector stakeholders is a step above and beyond the 100\% annual renewable matching in paving the path toward the carbon net-zero energy systems. 
This voluntary commitment also delivers a range of benefits to the society by 
(i) triggering innovation, availability and earlier utilisation of advanced clean firm generation needed for the transformation of energy systems to a complete carbon net-zero state, 
(ii) reducing system emissions, and (iii) reducing system flexibility needs.

### 2023-04-04 manuscript/sections/introduction.tex
manuscript skeleton

\textbf{Dummy abstract from ECEMP - to refine}

Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
Many public and private energy buyers have joined this effort and highlight their sustainable credentials by procuring renewable energy with the Power Purchase Agreements (\gls{ppa}s).
\gls{ppa}s typically allow for renewable energy to match supply and demand on average over a long period of time. 
For example, more than 360 members of the there100.org group\footnote{\url{https://www.there100.org/}} have committed to purchasing enough renewable energy to match 100\% of their electricity consumption on an annual basis. 
Such voluntary commitments accelerate the deployment of wind and solar capacity above the policy requirements in the countries and jurisdictions these companies operate.

However, the energy buyers that commit to 100\% annual matching from Renewable Energy Sources (\gls{res}) still face times when generation from wind and solar generators is not sufficient to match the companies' electricity demand.
During those hours, the energy buyers often have to rely on carbon-emitting power generating technologies available on the local market, such as coal and gas. 
The energy demand supplied by the annual matching approach is thus not \textit{entirely} carbon-free. 
Furthermore, 100\% annual matching approach keeps electricity buyers exposed to price volatility. 
Finally, it requires the energy system to maintain backup and flexibility options for hours with low renewable generation.

For this reason, there is growing interest from corporations such as Google to match their demand with clean energy supply on a truly 24/7 basis. 
Achieving 24/7 Carbon-Free Energy (CFE) means that every kilowatt-hour of electricity consumption is met with carbon-free electricity sources, every hour of every day. 
Thus, this approach has the potential to eliminate all carbon emissions associated with Google's electricity use completely. 
In 2020 Google committed to the ambitious goal of operating entirely on a 24/7-CFE approach at all its data centres and campuses worldwide by 2030 \cite{Google-1}. 
Shortly after, Google published a policy roadmap on achieving the 24/7-CFE goal \cite{Google-2}.

In this study, we model 24/7-CFE procurement in Europe up to 2030. 
We explore different designs, costs, benefits and impacts of the 24/7 approach, both for Google and for the power systems in which the data centres are located. 
In sum, we want to find out:

\begin{enumerate}
    \item How can we achieve hourly clean energy matching? 
    \item What is the 24/7-CFE cost premium versus the 100\% annual matching with renewables? 
    \item To which extent can technologies, such as long-duration storage or new dispatchable clean technologies, help to achieve the 24/7-CFE goal? 
    \item If many companies follow the 24/7-CFE approach, how does this effect the rest of the energy system?
\end{enumerate}

### 2023-04-04 manuscript/sections/methods.tex
manuscript skeleton

\textbf{Dummy methods - to refine}

Methodologically, our modelling workflow is based on the PyPSA (Python for Power System Analysis)\footnote{PyPSA is available at \url{https://github.com/PyPSA/PyPSA}}—an open-source software toolbox for simulating and optimising modern energy systems at high resolution maintained by TU Berlin \cite{Brown-PyPSA,HORSCH-PyPSAEUR}. 
The model developed for this study optimises investment and operational decisions to meet projected electricity demand for the consumers performing clean energy procurement, as well as the demand for other consumers in the European electricity system, while meeting all relevant engineering, reliability, and policy constraints. 
This project is also developed as open-source.\footnote{247-CFE code is available at  \url{https://github.com/PyPSA/247-cfe}}

In this study, we implement a set of new constraints to model a situation when a fraction of corporate and industry (C\&I) demand commit to the 24/7-CFE goal. 
These constraints ensure that a portfolio of carbon-free generation located in the same market as the participating C\&I consumers covers their electricity demand profiles every hour of every day. 
The mathematical implementation allows for examining a scenario space when different shares of demand pursue the 24/7 approach with varying thresholds for meeting the hourly clean energy requirement (e.g. 90\%, 95\%, 100\%) using the definitions provided in Google's paper on methodologies and metrics \cite{Google-methods}.

For comparison, we also model a benchmark scenario where the C\&I consumers meet their annual energy demand on a volumetric basis with renewable energy procurement (the 100\% annual matching), as well as the scenario with no voluntary procurement of carbon-free energy.

Finally, we model scenarios where C\&I consumers are located in different national markets across Europe. 
Thus, we aim to generalise the impacts of 24/7-CFE procurement, accounting for the different patterns of electricity demand, weather, availability of renewable resources, existing electricity generation capacity, and national climate- and energy policies, among other factors.

### 2023-04-04 manuscript/sections/results.tex
manuscript skeleton

We explore how the 247-CFE and the 100\% annual renewable matching procurement approaches affect both the participating consumers (driving the average costs of procured electricity and carbon emissions associated with the consumers' electricity usage) and the electricity system as a whole. 
Regarding the latter one, we examine both the short-term impacts (market dispatch, revenue streams for electricity generators, system emissions, curtailment) and the long-term impacts (exit of fossil-fueled generators from the market, improved market conditions for storage and new clean dispatchable technologies like geothermal power or advanced nuclear technologies).

\subsection{title}

text

\vspace*{5pt}
\begin{res}
    24/7-CFE procurement reduces emissions both for the participating electricity consumer and within the rest of the electricity system.
\end{res}

\vspace*{5pt}
\begin{res}
    24/7-CFE procurement comes with a cost premium. However, the 80-90\% hourly CFE target has only a small cost premium over 100\% annual renewable matching. 100\% hourly CFE target increases costs by 0-60\%, depending on technologies available.
\end{res}

\vspace*{5pt}
\begin{res}
    24/7-CFE procurement triggers investment in new technologies the system will need later: long-duration storage and new clean firm generation.
\end{res}

\subsection{title}

text

### 2023-04-07 manuscript/manuscript.tex
manuscript results chapter

@@
 
+\usepackage{float}
 \usepackage{lipsum}
@@
 
-\graphicspath{{../results/paper/},}
+\setlength{\abovecaptionskip}{1pt} 	% Adjust the space above the caption
+\graphicspath{ 						% Allows for multiple directories
+	{../results/paper/},
+	}
 
@@
 \newacronym{cfe}{CFE}{Carbon-Free Electricity}
-\newacronym{ci}{CI}{Corporate and Industry sectors}
+\newacronym{ci}{C\&I}{Corporate and Industry (sectors)}
 
@@
 
-	\title{Navigating to a Greener Europe through Clean Electricity Procurement}
+	\title{Navigating to a greener Europe with 24/7 hourly clean electricity procurement}
 
@@
 %\listoftodos[TODOs]
-%\tableofcontents
+\tableofcontents
 
@@
 \section*{Data and Code Availability}
+\label{sec:code}
 
-A dataset of the model results is available at \href{zenodoTBA}{doi:zenodoTBA}.
-The code to reproduce the experiments is available at \href{https://github.com/repository}{GITHUB}.
+The data and code to reproduce the experiments is available at \href{https://github.com/repository}{GITHUB}.
+
+The online dashboard with the results for this study is available at \url{dashboard}.
 

### 2023-04-07 manuscript/sections/results.tex
manuscript results chapter

@@
-We explore how the 247-CFE and the 100\% annual renewable matching procurement approaches affect both the participating consumers (driving the average costs of procured electricity and carbon emissions associated with the consumers' electricity usage) and the electricity system as a whole.
-Regarding the latter one, we examine both the short-term impacts (market dispatch, revenue streams for electricity generators, system emissions, curtailment) and the long-term impacts (exit of fossil-fueled generators from the market, improved market conditions for storage and new clean dispatchable technologies like geothermal power or advanced nuclear technologies).
+In this section, we present modelling results and related analysis. 
+In the analysis, we explore how the 247-CFE and the 100\% annual renewable matching procurement approaches affect both the participating electricity buyers and the electricity system as a whole. 
+Focusing on the electricity buyers' perspective, we analyse procurement strategies (i.e.
+the optimal mix of locally procured capacities of energy generation \& storage assets and electricity imports from the grid), the average costs of procured electricity and carbon emissions associated with the consumers' electricity usage.
+When our focus switches to the system perspective, we describe the impact of the \gls{cfe} procurement approaches on \co emissions on the local grids, as well as the impact on back up flexibility needs.
 
-\subsection{title}
+As described in \cref{subsec:scenarios}, we aim to generalize our findings void individual assumptions by incorporating a large scenario space into the study design. 
+For convenience, we start with a \textit{base scenario} presented in \cref{subsec:base}.
+Afterwards, we explore the scenario space further by presenting selected results that answer the following questions:
+\begin{enumerate}[(i)]
+\item What if clean electricity buyers have an access to a wider palette of carbon-free technologies that are expected to be available for a commercial scale up in the near future (\cref{subsec:palette})?
+\item What if electricity buyers are located in parts of the European electricity grid that are much different to the base scenario? (\cref{subsec:location})?
+\item What if electricity procurement takes place in 2030 instead of 2025 (\cref{subsec:time})? 
+\item Finally, in \cref{subsec:mechanisms}, we explore how exactly 24/7 CFE commitments help to decarbonize local grids and reveal the individual mechanisms behind this effect that are present across the scenario space.
+\end{enumerate}
 
-text
+In the Annex \ref{sec:si}, we summarise findings from sensitivity analyses regarding higher 24/7 procurement participations rates and various consumption profiles of electricity buyers.
 
-\vspace*{5pt}
+Given the large scenario space, the manuscript presents results for selected scenario branches that generalise system impacts of 24/7 hourly clean electricity procurement.
+For interested reader, we provide results for the entire scenario space in a dashboard that is published online alongside this study, see \nameref{sec:code}.
+
+\subsection{Base scenario}
+\label{subsec:base}
+
+\vspace{10pt}
 \begin{res}
-    24/7-CFE procurement reduces emissions both for the participating electricity consumer and within the rest of the electricity system.
+    24/7 carbon-free electricity (CFE) procurement can eliminate carbon emissiosns of a buyer's electricity consumption and helps to decarbonise the whole electricity system.
 \end{res}
 
-\vspace*{5pt}
+\vspace{5pt}
 \begin{res}
-    24/7-CFE procurement comes with a cost premium.
-However, the 80-90\% hourly CFE target has only a small cost premium over 100\% annual renewable matching.
-100\% hourly CFE target increases costs by 0-60\%, depending on technologies available.
+    24/7 CFE procurement comes with a cost premium. 
+    However, the 90\%--95\% CFE targets have only a small cost premium over 100\% annual renewable matching. 
+    With solar, wind and batteries, 100\% CFE target comes at much higher costs.
 \end{res}
+
+The base scenario reflects a case when \textbf{10\%} (on volumetric basis) of commertial \& industrial consumers in \textbf{Ireland} in \textbf{2025} voluntrary commits to 24/7 clean electricity procurement goal.
+This assumption yields 220~MW of \textbf{base load} that has to be matched with clean electricity. 
+The participating consumers can achieve the \gls{cfe} procurement goal by co-optimizing local procurement with the \textbf{palette 1} of technologies (i.e., mature technologies available on the market now: onshore wind, solar, and battery storage), as well as by importing electrcity from the local grid.
+
+%some parts of this paragraph may go to methods
+\cref{fig:10-2025-IE-p1-used} shows the fraction of the fraction of hourly demand met with carbon-free electricity depending on the procurement policy that \gls{ci} consumers follow.
+We contrast two main cases, one where participating consumers commit to 100\% annual renewable matching policy (100\% RES) and another case where the consumers commit to 24/7 hourly matching policy with various \gls{cfe} scores in a range from 80\% to 100\%.
+A \textit{reference case} depicts a case when the consumers cover their load purely with grid purchases without any policy regarding the origin of electricity.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{plots/10/2025/IE/p1/used.pdf}
+    \caption{Fraction of hourly demand met with carbon-free electricity.}
+    \label{fig:10-2025-IE-p1-used}
+\end{figure}
+
+In the reference case, where \gls{ci} consumers do not procure any resources, relying purely on grid purchases, only 54\% of demand is met with clean electricity.
+100\% RES -- the best case for the annual renewable matching policy -- results in 83\% fraction. 
+Consequently, 24/7~CFE targets beyond 85\% yield higher share of hourly demand met with clean electricity than 100\% annual matching policy.
+A notable trend in \cref{fig:10-2025-IE-p1-used} is that \gls{ci} participants rely more on procured resources and less on grid imports with CFE target approaching 100\%,
+
+\cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of \gls{ci} consumers.
+Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 178~g\co/kWh in the reference case. 
+If \gls{ci} consumers follow 100\% RES goal and procure enough renewable recourses, the emission rate is reduced to 60~g\co/kWh.
+This yields a considerable emission rate reduction compared to the reference case.
+The 24/7 procurement policy with CFE targets above 85\% can help the participating consumers to reduce emissions further, or eliminate them competely in the case of 100\% 24/7~CFE.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \caption{Average emissions rate of participating consumers.}
+    \label{fig:10-2025-IE-p1-ci_emisrate}
+\end{figure}
+
+Voluntary procurement of clean electricity also helps decarbonise electricity system as a whole.
+We explore this effect by plotting \co emissions in the local region of the participating consumers, i.e. Ireland.
+Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2~Mt\co -- see a reference case in \cref{fig:10-2025-IE-p1-zone_emissions}.
+\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021.
+A strong decreasing trend is expected, since Irish government has set ambitious targets to achieve a low-carbon energy system \cite{SEAI}.}
+The modelling results show that if only 10\% of \gls{ci} electricity demand commits to 100\% 24/7 carbon-free electricity in 2025, it would reduce Irish emissions by 0.6~Mt\co per year compared to the scenario with no voluntary procurement.
+This reduction is equivalent to 14\% of Irish power sector emissions.
+100\% annual renewable matching policy can also deliver system-level \co emissions reductions (left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, beyond 85\% CFE target, 24/7 hourly matching achieves greater emissions reductions than 100\% annual mathing policy.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \caption{CO2 emissions in the local region -- Ireland.}
+    \label{fig:10-2025-IE-p1-zone_emissions}
+\end{figure}
+
+The following analysis reveals the \gls{cfe} procurement strategies by participating consumers for each procurement policy.
+\cref{fig:10-2025-IE-p1-ci_capacity} shows that for 10\% of \gls{ci} load in Ireland (220 MW), the 100\% RES policy is cost-optimally met with 1.3~GW of onshore wind and solar generators.
+Matching demand with clean generation on 24/7 hourly basis requires a much bigger portfolio of wind and solar than the 100\% RES policy.
+Also, for CFE target above 85\% the cost-optimal procurement sees battery storage enter the portfolio mix.
+Note that for 80\% CFE target, 24/7 participating consumers procure less capacity than for 100\% annual matching policy, as it relies more on grid imports.
+
+The breakdown of costs associated with a procurement policy that participating consumers choose is shown in \cref{fig:10-2025-IE-p1-ci_costandrev}.
+Note that revenues from selling the excess electricity to the regional grid at market prices can be treated as ”negative costs” and subtracted from the net procurement cost.
+The results show that a CFE targets of 80\%--95\% can be achieved at a small cost premium to 100\% annual renewable matching with solar, wind and batteries.
+However, what stands out in the plot is the rapid increase of procurement costs for high 24/7 CFE targets. 
+For example, 98\% CFE target has cost premium of 54\% over 100\% the RES policy; while the last 2\% of hourly CFE matching more than doubles the costs.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[t]{\columnwidth}
+        \centering
+        \caption{Portfolio capacity procured by participating consumers.}
+        \includegraphics[width=\columnwidth]{plots/10/2025/IE/p1/ci_capacity.pdf}
+        \label{fig:10-2025-IE-p1-ci_capacity}
+    \end{subfigure}
+    \begin{subfigure}[t]{\columnwidth}
+        \centering
+        \vspace{-0.5cm}
+        \caption{Costs of a procurement policy.}
+        \includegraphics[width=\columnwidth]{plots/10/2025/IE/p1/ci_costandrev.pdf}
+        \label{fig:10-2025-IE-p1-ci_costandrev}
+    \end{subfigure}
+    \caption{Procurement of clean resources and energy storage by \gls{ci} consumerts participating in voluntary clean electricity procurement. 
+    \cref{fig:10-2025-IE-p1-ci_capacity} shows power capacity portfolio for each procurement policy [GW].
+    \cref{fig:10-2025-IE-p1-ci_costandrev} shows the breakdown of costs associated with a procurement [\euro/MWh].}
+    \label{fig:10-2025-IE-p1-ci_procurement}
+\end{figure}
+
+\subsection{Technology access}
+\label{subsec:palette}
 
@@
 
+text
+
+\subsection{Diverse grid locations}
+\label{subsec:location}
+
+text
+
+\subsection{Moving five years more ahead}
+\label{subsec:time}
+
+text
+
+\subsection{Uncovering mechanisms how 24/7 CFE commitments decarnonise local grids}
+\label{subsec:mechanisms}
+
+text
+
 \subsection{title}

### 2023-04-08 scripts/plot_summary.py
minor plot touches for manuscript

@@ -211,7 +211,7 @@ def ci_emisrate():
     fig, ax = plt.subplots()
     fig.set_size_inches((6,4.5))
 
-    ldf = df.loc['ci_emission_rate_true']
+    ldf = df.loc['ci_emission_rate_true']*1e3
     ldf.index = ldf.index.map(rename_scen)
    
     yl_ref = ldf.loc['no\npolicy']
@@ -219,7 +219,7 @@ def ci_emisrate():
     plt.axhline(y = yl_ref, color = 'gray', linestyle="-", linewidth=1.5)
     plt.axhline(y = yl_100RES, color = 'gray', linestyle="--", linewidth=0.8)
     plt.axvline(x = 0.5, color = 'gray', linestyle="--")
-    plt.text(1.5, yl_ref-0.06*yl_ref,f'Reference case, C&I emission rate {round(yl_ref,3)} [t/MWh]', 
+    plt.text(3, yl_ref-0.06*yl_ref,f'Reference case: {int(yl_ref)} gCO\u2082/kWh', 
             horizontalalignment='left', bbox=dict(facecolor='w', alpha=0.5)) 
     
     #Drop reference scenario before plotting
@@ -232,7 +232,7 @@ def ci_emisrate():
     ax.grid(alpha=0.3)
     ax.set_axisbelow(True)
     #ax.set_xlabel("CFE target")
-    ax.set_ylabel("C&I emission rate [t/MWh]")
+    ax.set_ylabel("C&I emission rate [gCO\u2082/kWh]")
     #ax.yaxis.label.set_size(6)
 
     fig.tight_layout()
@@ -553,7 +553,7 @@ def system_emisrate():
     fig, ax = plt.subplots()
     fig.set_size_inches((6,4.5))
 
-    ldf = df.loc['system_emission_rate']
+    ldf = df.loc['system_emission_rate']*1e3
     ldf.index = ldf.index.map(rename_scen)
 
     #Drop reference scenario before plotting
@@ -566,7 +566,7 @@ def system_emisrate():
     ax.grid(alpha=0.3)
     ax.set_axisbelow(True)
     #ax.set_xlabel("CFE target")
-    ax.set_ylabel("System emission rate [t/MWh]")
+    ax.set_ylabel("System emission rate [gCO\u2082/kWh]")
     #ax.yaxis.label.set_size(6)
 
     fig.tight_layout()

### 2023-04-08 manuscript/sections/results.tex
results results, technology access

@@
 Consequently, 24/7~CFE targets beyond 85\% yield higher share of hourly demand met with clean electricity than 100\% annual matching policy.
-A notable trend in \cref{fig:10-2025-IE-p1-used} is that \gls{ci} participants rely more on procured resources and less on grid imports with CFE target approaching 100\%,
+
+Another notable trend in \cref{fig:10-2025-IE-p1-used} is that \gls{ci} participants rely more on procured resources and less on grid imports with higher CFE target.
+When CFE target approaches 100\%, \gls{ci} consumers cannot rely on electricity imports from the grid, since the grid supply mix contains some carbon content in almost all hours.
 
 \cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of \gls{ci} consumers.
-Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 178~g\co/kWh in the reference case. 
+Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case. 
 If \gls{ci} consumers follow 100\% RES goal and procure enough renewable recourses, the emission rate is reduced to 60~g\co/kWh.
@@
     \end{subfigure}
-    \caption{Procurement of clean resources and energy storage by \gls{ci} consumerts participating in voluntary clean electricity procurement. 
-    \cref{fig:10-2025-IE-p1-ci_capacity} shows power capacity portfolio for each procurement policy [GW].
-    \cref{fig:10-2025-IE-p1-ci_costandrev} shows the breakdown of costs associated with a procurement [\euro/MWh].}
+    \caption{Procurement of clean resources and energy storage by \gls{ci} consumers participating in voluntary clean electricity procurement. 
+    \cref{fig:10-2025-IE-p1-ci_capacity} shows power capacity portfolio for each procurement policy.
+    \cref{fig:10-2025-IE-p1-ci_costandrev} shows the breakdown of costs associated with a procurement.}
     \label{fig:10-2025-IE-p1-ci_procurement}
@@
 
-\vspace*{5pt}
+\vspace{10pt}
 \begin{res}
@@
 
-text
+\vspace*{5pt}
+\begin{res}
+    High targets for 24/7 CFE procurement could have a much smaller cost premium if long duration energy storage or advanced clean firm technologies are available for a commercial scale up.
+\end{res}
+
+The cost premium of 24/7 hourly clean electricity procurement presented in \cref{subsec:base} is driven by the variability of renewable power supply.
+Indeed, in the periods when not much wind or solar is available, matching every kilowatt-hour of electricity consumption with carbon-free electricity on hourly basis is not an easy task.
+Battery storage technology is cost-optimal for shifting surplus a power supply by a couple of hours. 
+However, bridging extended periods of low wind and sun with battery storage is expensive.
+Results above also illustrate that for CFE targets of 98\%--100\%, 24/7 participating consumers rely little on the grid supply, since electricity mix in the local grids contain some carbon content.
+
+The results in \cref{fig:10-2025-IE-p23-ci_procurement} reflect a case when 24/7~CFE participants have an access to a wider palette of technologies: 
+long-duration energy storage (\gls{ldes}) and advanced clean firm generators, such as advanced geothermal systems, advanced nuclear or Allam cycle generators with carbon capture and sequestration.
+
+The top row shows the power capacity portfolio (\cref{fig:10-2025-IE-p2-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p2-ci_costandrev}) for a case when \gls{ci} consumers have an access to \textbf{palette~2} technologies, i.e., the \gls{ldes} system is also available on a market.%
+\footnote{Here we assume 2.5~\euro/kWh underground hydrogen storage in salt caverns.}
+The \gls{ldes} helps to align the load with the generation of procured variable renewable resources. 
+As a result, the cost-optimal portfolio of renewable capacity for the 100\% 24/7 CFE target is not much larger than for the 100\% annual matching policy. 
+This also significantly decreases procurement costs at high CFE targets: 100\% 24/7~CFE has a cost premium of 42\% above 100\% annual renewable mathing policy.
+
+The bottom row shows the results for technological \textbf{palette 3} scenario (\cref{fig:10-2025-IE-p3-ci_capacity} and \cref{fig:10-2025-IE-p3-ci_costandrev}). 
+The procurement strategy now includes the Allam cycle generator.
+The clean firm technology can be operated any time of the year and thus helps to fill in the gaps in variable renewable generation to match demand and clean generation on hourly basis.
+Inclusion of clean firm generation also reduces renewable capacity and storage requirements. 
+This, in turn, further limits the 24/7 CFE cost premium.
+In this scenario, 100\% 24/7~CFE costs only 15\% above 100\% annual renewable mathing.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Portfolio capacity with LDES.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p2/ci_capacity.pdf}
+        \label{fig:10-2025-IE-p2-ci_capacity}
+    \end{subfigure}% 
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Costs of a procurement policy with LDES.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p2/ci_costandrev.pdf}
+        \label{fig:10-2025-IE-p2-ci_costandrev}
+    \end{subfigure}
+
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \vspace{-0.5cm}
+        \caption{Portfolio capacity with LDES and clean firm generators.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p3/ci_capacity.pdf}
+        \label{fig:10-2025-IE-p3-ci_capacity}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \vspace{-0.5cm}
+        \caption{Costs of a procurement policy LDES and clean firm generators.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p3/ci_costandrev.pdf}
+        \label{fig:10-2025-IE-p3-ci_costandrev}
+    \end{subfigure}
+    \caption{Procurement of clean resources and energy storage if \gls{ci} consumerts have an access to a wider palette of technologies. 
+    The top row shows the power capacity portfolio (\cref{fig:10-2025-IE-p2-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p2-ci_costandrev}) 
+    if \gls{ldes} is available on the market.
+    The bottom row shows the power capacity portfolio (\cref{fig:10-2025-IE-p3-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p3-ci_costandrev}) 
+    for a case when both \gls{ldes} and clean firm dispatchable generators are available.}
+    \label{fig:10-2025-IE-p23-ci_procurement}
+\end{figure*}
 
@@
 text
-
-\subsection{title}
-
-text

### 2023-04-09 manuscript/sections/results.tex
results results, diverse grid locations

@@
     \includegraphics[width=\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \caption{CO2 emissions in the local region -- Ireland.}
+    \caption{\co emissions in the local region (Ireland).}
     \label{fig:10-2025-IE-p1-zone_emissions}
@@
     \centering
-    \begin{subfigure}[t]{\columnwidth}
+    \begin{subfigure}[t]{0.95\columnwidth}
         \centering
         \caption{Portfolio capacity procured by participating consumers.}
-        \includegraphics[width=\columnwidth]{plots/10/2025/IE/p1/ci_capacity.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_capacity.pdf}
         \label{fig:10-2025-IE-p1-ci_capacity}
     \end{subfigure}
-    \begin{subfigure}[t]{\columnwidth}
+    \begin{subfigure}[t]{0.95\columnwidth}
         \centering
@@
         \caption{Costs of a procurement policy.}
-        \includegraphics[width=\columnwidth]{plots/10/2025/IE/p1/ci_costandrev.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_costandrev.pdf}
         \label{fig:10-2025-IE-p1-ci_costandrev}
@@
     \end{subfigure}
-
     \begin{subfigure}{0.5\textwidth}
         \centering
-        \vspace{-0.5cm}
         \caption{Portfolio capacity with LDES and clean firm generators.}
@@
         \centering
-        \vspace{-0.5cm}
-        \caption{Costs of a procurement policy LDES and clean firm generators.}
+        \caption{Costs of a procurement policy with LDES and clean firm generators.}
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p3/ci_costandrev.pdf}
@@
     \end{subfigure}
-    \caption{Procurement of clean resources and energy storage if \gls{ci} consumerts have an access to a wider palette of technologies. 
+    \caption{Procurement of clean resources and energy storage if \gls{ci} consumers located in Ireland have an access to a wider palette of technologies.
     The top row shows the power capacity portfolio (\cref{fig:10-2025-IE-p2-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p2-ci_costandrev}) 
@@
 
-text
+While we have focused on base scenario reflecting the case of Ireland, exactly the same modelling exercise can be repeated for other regions of the European electricity grid.
+Since each region has a unique set of characteristics that depend on local resources, renewable potentials, national energy and climate policies, and degree of interconnections, such sensitivity can allow for generalising the impact of 24/7 CFE procurement void regional differences.
+
+\cref{fig:10-2025-DEPL-p3-4plots} shows results for the two selected regions: Germany and Poland.
+Germany is selected as it the largest electricity consumer in Europe and it is well interconnected to regions with clean electrcity grids, such as France and Denmark.
+Poland -- a country with  historic dependency on domestic coal resources, resistance from the coal industry and lack of governmental support for renewable energy -- is selected for a contrast.
+To keep other factors constant, the same 10\% share of \gls{ci} consumers is set to participate in voluntary clean electricity procurement.\footnote{10\% participation rate of \gls{ci} sector yields load of 3.8~GW in Germany and 1.1~GW in Poland.}
+
+Despite regional differences, the dynamics of 24/7 CFE procurement, observed in the example of Ireland, show similar trends.
+
+As can be expected, the cleaner grid in the German case results in a lower value of the average emissions rate of participating consumers than in the case of Poland.
+The values in the reference case are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.\footnote{For reference, 2021 estimates for emission intensity of electricity generation are 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}
+
+Similar to the Irish results, \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} show that in both cases, \gls{ci} participants achieve lower emissions rates with 24/7 hourly CFE procurement than with 100\% annual matching once CFE target is tight enough.
+As expected at 100\% CFE target, participating consumers achieve a zero emission rate associated to their electricity consumption, since they perfectly match demand and clean generation on hourly basis.
+
+% Another result that stands out in the cases of Germany and Poland is the impact of the 24\7 procurement on the system-level \co emissions.
+
+% Without any CFE procurement stategy, the German power sector carbon emissions are at the level of 40.6 MtCO2 in 2025.
+
+% With just 10\% participation rate, ca. 3.8 GW of C&I load follows voluntary procurement.
+
+% With this participation, the 100\% RES can reduce system-level CO2 emissions by 6 MtCO2 per year.
+With the 24/7 hourly matching, C&I consumers achieve greater impact on emissions, up to 8 MtCO2 per year with CFE 100\% target.
+
+% NB this impact can be achieved with just a 10\% cost premium on top of the 100\% annual renewable matching (see C&I cost analysis above).
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Average emissions rate of participating consumers (Germany).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/ci_emisrate.pdf}
+        \label{fig:10-2025-DE-p3-ci_emisrate}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Average emissions rate of participating consumers (Poland).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/ci_emisrate.pdf}
+        \label{fig:10-2025-PL-p3-ci_emisrate}
+    \end{subfigure}
+
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{\co emissions in the local region (Germany).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/zone_emissions.pdf}
+        \label{fig:10-2025-DE-p3-zone_emissions}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{\co emissions in the local region (Poland).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/zone_emissions.pdf}
+        \label{fig:10-2025-PL-p3-zone_emissions}
+    \end{subfigure}%
+
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Costs of a procurement policy (Germany).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/ci_costandrev.pdf}
+        \label{fig:10-2025-DE-p3-ci_costandrev}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Costs of a procurement policy (Poland).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/ci_costandrev.pdf}
+        \label{fig:10-2025-PL-p3-ci_costandrev}
+    \end{subfigure}
+
+    \caption{Results for cases when 10\% of \gls{ci} load in Germany \textbf{(left panel)} and Poland \textbf{(right panel)} follows 24/7 hourly clean electricity procurement.
+Selected scenario with technological palette~3.}
+    \label{fig:10-2025-DEPL-p3-4plots}
+\end{figure*}
 
@@
 
-text
+Note that for lower CFE targets, constraint (2) is not binding, what makes the same cost-optimal shares of procured portfolio and grid imports repeat until the CFE target becomes tight enough.
 

### 2023-04-09 scripts/plot_summary.py

@@ -29,7 +29,7 @@ def used():
     plt.axhline(y = yl_ref, color = 'gray', linestyle="--", linewidth=0.8)
     plt.axhline(y = yl_100RES, color = 'gray', linestyle="--", linewidth=0.8)
     plt.axvline(x = 0.5, color = 'gray', linestyle="--")
-    plt.text(3.5,yl_ref-6,f'Reference case, fraction CFE={int(round(yl_ref,0))}'+'%', 
+    plt.text(4, yl_ref-6,f'Reference case: {int(round(yl_ref,0))}'+'%', 
             horizontalalignment='left', bbox=dict(facecolor='w', alpha=0.5)) 
     
     #Drop reference scenario before plotting
@@ -186,7 +186,7 @@ def zone_emissions():
     plt.axhline(y = yl_100RES, color = 'gray', linestyle="--", linewidth=0.8)
     plt.axhline(y = yl_end, color = 'gray', linestyle="--", linewidth=0.8)
     plt.axvline(x = 0.5, color = 'gray', linestyle="--")
-    plt.text(3.3, yl_ref-0.02*yl_ref,f'Reference case, emissions {round(yl_ref,1)} [Mt]', 
+    plt.text(3.5, yl_ref-0.02*yl_ref,f'Reference case: {round(yl_ref,1)} Mt', 
             horizontalalignment='left', bbox=dict(facecolor='w', alpha=0.5)) 
     
     #Drop reference scenario before plotting
@@ -339,7 +339,7 @@ def ci_costandrev():
     #ax.set_xlabel("CFE target")
     ax.set_ylabel("24x7 C&I cost and revenue [€/MWh]")
     ax.legend(loc="upper left", ncol = 3, prop={"size":8})
-    ax.set_ylim(top=yl_end*1.5)
+    ax.set_ylim(top=yl_end*1.7)
 
     fig.tight_layout()
     fig.savefig(snakemake.output.used.replace("used.pdf","ci_costandrev.pdf"),

### 2023-04-10 manuscript/sections/results.tex
Finish section on diverse grid locations

@@
 
+\vspace{10pt}
+\begin{res}
+    Each region of the European electricity system has unique characteristics, such as renewable resources, national policies, degree of interconnection, etc.
+    Despite these differences, the model results for 24/7 clean energy procurement show similar trends. 
+\end{res}
+
 While we have focused on base scenario reflecting the case of Ireland, exactly the same modelling exercise can be repeated for other regions of the European electricity grid.
@@
 Poland -- a country with  historic dependency on domestic coal resources, resistance from the coal industry and lack of governmental support for renewable energy -- is selected for a contrast.
-To keep other factors constant, the same 10\% share of \gls{ci} consumers is set to participate in voluntary clean electricity procurement.\footnote{10\% participation rate of \gls{ci} sector yields load of 3.8~GW in Germany and 1.1~GW in Poland.}
+To keep other factors constant, the same 10\% share of \gls{ci} consumers is set to participate in voluntary clean electricity procurement.%
+\footnote{10\% participation rate of \gls{ci} sector yields load of 3.8~GW in Germany and 1.1~GW in Poland.}
 
@@
 As can be expected, the cleaner grid in the German case results in a lower value of the average emissions rate of participating consumers than in the case of Poland. 
-The values in the reference case are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.\footnote{For reference, 2021 estimates for emission intensity of electricity generation are 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}
+The values in the reference case are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.%
+\footnote{For reference, 2021 estimates for emission intensity of electricity generation are 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}
 
@@
 
-% Another result that stands out in the cases of Germany and Poland is the impact of the 24\7 procurement on the system-level \co emissions.
+A result that stands out in the cases of Germany and Poland is the impact of the 24/7 hourly CFE procurement on the system-level \co emissions, as shown in \cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions}.
+Without any CFE procurement stategy, the German and Polish power sector carbon emissions are at 118.8~Mt\co and 83.8~Mt\co in 2025, respectively.%
+\footnote{Germany is a larger electricity consumer, while Polish electricity mix has much a higher emission intensity; thus, power sector carbon emissions are on a similar scale for these regions.} 
+If only 10\% of C\&I load joins efforts of voluntary \gls{cfe} procurement, a significant decarbonisation impact is achieved. 
+For example in Germany, with this participation, the 100\% annual matching with renewable electricity can reduce system-level \co emissions by 11.1~Mt\co per year. 
+With the 24/7 hourly matching, C\&I consumers achieve even greater impact on emissions, up to 14~Mt\co per year with CFE 100\% target.
 
-% Without any CFE procurement stategy, the German power sector carbon emissions are at the level of 40.6 MtCO2 in 2025.
-
-% With just 10\% participation rate, ca. 3.8 GW of C&I load follows voluntary procurement.
-
-% With this participation, the 100\% RES can reduce system-level CO2 emissions by 6 MtCO2 per year.
-With the 24/7 hourly matching, C&I consumers achieve greater impact on emissions, up to 8 MtCO2 per year with CFE 100\% target.
-
-% NB this impact can be achieved with just a 10\% cost premium on top of the 100\% annual renewable matching (see C&I cost analysis above).
+\cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions} show also similar trends to the base scenario. 
+For lower CFE targets, participating consumers can complement portfolio with electricity imports from grid.
+To achieve higher CFE targets, an clean firm generatorion is added to the portfolio, which greatly reduces the need for renewable generation capacity to match load on an hourly basis.
+In the case of Germany and Poland, both the Allam cycle generator with CCS and advanced dispatchable generator enter the optimal procurement strategy. 
+This is likely due to a case that these regions are better interconnected with the rest of the European electrcity grid than Ireland. 
+A better interconnection makes possible to exhaust all arbitrage opportunities across time and space and maximise the dispatch value from an advanced dispatchable generator with low variable costs.
 

### 2023-04-10 manuscript/sections/results.tex
Finish section on moving to 2030

@@
 \begin{res}
-    24/7 CFE procurement comes with a cost premium. 
-    However, the 90\%--95\% CFE targets have only a small cost premium over 100\% annual renewable matching. 
-    With solar, wind and batteries, 100\% CFE target comes at much higher costs.
+    90\%--95\% 24/7 CFE targets have only a small cost premium over 100\% annual renewable matching. 100\% 24/7 CFE can be achieved with solar, wind and battery storage, but at a high cost premium.
 \end{res}
@@
 \begin{res}
-    24/7-CFE procurement triggers investment in new technologies the system will need later: long-duration storage and new clean firm generation.
+    24/7 CFE procurement triggers investment in new technologies the system will need later: long-duration storage and advanced clean firm generators.
 \end{res}
@@
 \footnote{For reference, 2021 estimates for emission intensity of electricity generation are 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}
-
 Similar to the Irish results, \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} show that in both cases, \gls{ci} participants achieve lower emissions rates with 24/7 hourly CFE procurement than with 100\% annual matching once CFE target is tight enough.
@@
 
-\cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions} show also similar trends to the base scenario. 
+\cref{fig:10-2025-DE-p3-ci_costandrev} and \cref{fig:10-2025-PL-p3-ci_costandrev} also show similar trends to the base scenario. 
 For lower CFE targets, participating consumers can complement portfolio with electricity imports from grid.
@@
 
-Note that for lower CFE targets, constraint (2) is not binding, what makes the same cost-optimal shares of procured portfolio and grid imports repeat until the CFE target becomes tight enough.
+\vspace{10pt}
+\begin{res}
+    In 2030, participating consumers benefit from decreasing costs of clean technologies and cleaner state of the electricity grids.
+\end{res}
+
+\vspace{5pt}
+\begin{res}
+    Voluntary commitments to clean electricity procurement bring system value even in
+    cleaner grids. Similarly to the base scenario, 24/7 hourly matching results in deeper decarbonisation than 100\% annual renewable matching if CFE targets are above certain treshhold.
+\end{res}
+
+In the scenarios above, we have been exploring 24/7 clean electricity procurement within the European electricity system, with a focus on the year 2025. 
+In this section, we shift our attention to the results and implications of these procurement strategies for the year 2030. 
+This will provide a deeper understanding of the long-term effects and the potential evolution of clean energy procurement across Europe, as companies continue to adapt their procurement strategies to achieve carbon-free energy goals.
+
+From the modelling perspective, many system parameters change with a five year step to 2030. 
+In particular, the technology costs decline due to economics of scale and incremental innovation, national energy- and climate policies become more tight, and some legacy power plants leave the market.
+An overarching feature of the five-year step is a cleaner state of the electricity grids.
+
+\cref{fig:10-2030-IE-6plots} illustrates the results for the "base scenario" moved five years into the future to 2030, with all other factors held constant.
+
+\cref{fig:10-2030-IE-p1-used} shows the fraction of hourly demand met with clean electricity for each procurement policy -- now in 2030. 
+There two observations from comparing these results with a base scenario.
+First, in the reference case, 72\% of demand is met with CFE, which is 18\% more than in 2025, which is a result of a cleaner electricity grid on a background. 
+Thus, lower CFE targets (such as 80\%) are met with a larger share of grid imports. 
+Second, higher CFE targets still require a independency from grid imports for the perfect match of clean electricity with \gls{ci} load on hourly basis. 
+At 100\% 24/7 CFE, participating consumers rely only on procured resources.
+
+The average emissions rate of 24/7 participating consumers is intuitively lower with a cleaner regional network. 
+As shown in \cref{fig:10-2030-IE-p1-ci_emisrate}, the reference case value is reduced from 240~g\co/kWh in 2025 to 107~g\co/kWh in 2030.
+The dynamics of 24/7 CFE procurement remains also in 2030.
+An hourly 24/7 matching allows for net-zero emissions associated with the \gls{ci} buyers' consumption, with a lower emission rate than 100\% annual matching already at 90\% CFE target.
+An interesting result is that a CFE target of 90\% yields lower \gls{ci} emission rate, although costs the same as the 100\% annual matching for all three technological palettes (see \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p1-ci_costandrev}).
+
+\cref{fig:10-2030-IE-p1-zone_emissions} show that both 100\% annual matching with renewable energy and the 24/7 hourly matching with \gls{cfe} keep positive effect on system-level emissions even in cleaner system.
+Similarly to 2025, if CFE target is high enough, a diverse resource portfolio procured by 24/7 participating consumers has a larger impact on net system emissions in a local zone than 100\% annual matching.
+Interestingly, in the case of 2030, 100\% 24/7 CFE nearly doubles the decarbonisation effect of 100\% annual matching: 100\% RES reduces emissions in the local zone by 0.2~Mt\co/a (8\% of Irish power section emissions), while 100\% 24/7 CFE yields reduction of 0.4~Mt\co/a.
+The nature of this effect is explained in \cref{subsec:mechanisms}.
+
+The \gls{ci} cost breakdown for Ireland 2030 scenario shows that net costs for 24/7 CFE matching fall for all technological palettes.
+Participating consumers benefit from decreasing costs of clean technologies and cleaner state of the electricity grids.
+\cref{fig:10-2030-IE-p2-ci_costandrev} and \cref{fig:10-2030-IE-p1-ci_costandrev} show that in 2030, cost-optimal portfolio mix procured by the \gls{ci} participants for CFE 100\% target has a very limited cost premium to 100\% annual renewable matching with LDES and clean firm technologies.
+At the same time, participanting consumers achieve a zero emission rate associated to their electricity consumption and have a bigger impact on \co emissions in the rest of the system.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Fraction of hourly demand met with carbon-free electricity.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/used.pdf}
+        \label{fig:10-2030-IE-p1-used}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Average emissions rate of participating consumers.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_emisrate.pdf}
+        \label{fig:10-2030-IE-p1-ci_emisrate}
+    \end{subfigure}
+
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{\co emissions in the local region (Ireland).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/zone_emissions.pdf}
+        \label{fig:10-2030-IE-p1-zone_emissions}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}138
+        \caption{Costs of a procurement policy: technological palette~1.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_costandrev.pdf}
+        \label{fig:10-2030-IE-p1-ci_costandrev}
+    \end{subfigure}%
+
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Costs of a procurement policy: technological palette~2.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p2/ci_costandrev.pdf}
+        \label{fig:10-2030-IE-p2-ci_costandrev}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Costs of a procurement policy: technological palette~3.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p3/ci_costandrev.pdf}
+        \label{fig:10-2030-IE-p3-ci_costandrev}
+    \end{subfigure}
+
+    \caption{Results for the case of Ireland 2030. 10\% participation rate. 
+    Data for the Figures \ref{fig:10-2030-IE-p1-used}--\ref{fig:10-2030-IE-p1-zone_emissions} is for the technological palette~1 scenario.}
+    \label{fig:10-2030-IE-6plots}
+\end{figure*}
 
@@
 
-text
+result: reducing peaker and flex needs
+result: two effects, one stay also in clean grids
+
+plot with e.g. germany system capacity differences
+new plot in profile and volume.

### 2023-04-14 manuscript/sections/results.tex
add results for profile/volume effects

@@
 
-result: reducing peaker and flex needs
-result: two effects, one stay also in clean grids
+\vspace{10pt}
+\begin{res}
+    24/7 CFE procurement reduces system-level \co emissions via two mechanisms that can be isolated as profile and volume effects.
+\end{res}
 
-plot with e.g. germany system capacity differences
-new plot in profile and volume.
+\vspace{5pt}
+\begin{res}
+    The difference in impact that 24/7 CFE procurement and 100\% annual matching policies have on system decarbonisation amplifies between 2025 and 2030 with a cleaner state of local grids.
+\end{res}
+
+\vspace{5pt}
+\begin{res}
+    24/7 procurement reduces the needs for flexibility in the rest of the system.
+\end{res}
+
+text on results 8 and 9
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[t]{0.95\columnwidth}
+        \centering
+        \caption{Emissions reduction in a local zone by 24/7 hourly matching with 100\% target -- profile and volume effects isolated.}
+        \includegraphics[width=0.95\columnwidth]{profile-volume.pdf}
+        \label{fig:10-profile-volume.pdf}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.95\columnwidth}
+        \centering
+        \caption{Additional emissions reduction in local zone by 100\% hourly over annual matching as percentage points of reference zone emissions.}
+        \includegraphics[width=0.95\columnwidth]{hourly-annual.pdf}
+        \label{fig:10-hourly-annual.pdf}
+    \end{subfigure}
+    \caption{
+        System-level emission reduction: benchmark of procument policies and isolation of decarbonisation mechanisms. 
+    \cref{fig:10-profile-volume.pdf} shows breakdown of emissions reduction in a local zone if 10\% of \gls{ci} load follows 24/7 hourly CFE procurement with 100\% target.
+The profile are volume effects are isolated.
+    \cref{fig:10-hourly-annual.pdf} shows additional emissions reduction in a local zone by 100\% hourly over annual matching.}
+    \label{fig:decarbonisation_story}
+\end{figure}
+
+text on result 10
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{plots/10/2030/DE/p1/system_capacity_diff.pdf}
+    \caption{
+    Difference in generation capacity expansion in the whole European electricity system (including \gls{ci} resources) with and without clean energy procurement. 
+    Selected scenario of Germany, 2030, technological palette~1.}
+    \label{fig:10-2030-DE-p1-system_capacity_diff.pdf}
+\end{figure}

### 2023-04-16 manuscript/sections/results.tex
add uncovering mechanisms section

@@
 Germany is selected as it the largest electricity consumer in Europe and it is well interconnected to regions with clean electrcity grids, such as France and Denmark.
-Poland -- a country with  historic dependency on domestic coal resources, resistance from the coal industry and lack of governmental support for renewable energy -- is selected for a contrast.
+Poland—a country with  historic dependency on domestic coal resources, resistance from the coal industry and lack of governmental support for renewable energy—is selected for a contrast.
 To keep other factors constant, the same 10\% share of \gls{ci} consumers is set to participate in voluntary clean electricity procurement.%
@@
 \begin{res}
-    The difference in impact that 24/7 CFE procurement and 100\% annual matching policies have on system decarbonisation amplifies between 2025 and 2030 with a cleaner state of local grids.
+    The difference in impact that 24/7 CFE procurement and 100\% annual matching policies have on system decarbonisation amplifies with a cleaner state of local grids.
 \end{res}
@@
 \begin{res}
-    24/7 procurement reduces the needs for flexibility in the rest of the system.
+    24/7 CFE procurement reduces the needs for flexibility in the rest of the system.
 \end{res}
 
-text on results 8 and 9
+As illustrated in Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions}, voluntary commitments to 24/7 clean energy procurement result in a considerable reduction of \co emissions in local electricity grids.
+In this section, we delve deeper into the underlying mechanisms responsible for these observed reductions aiming to enhance our understanding of the complex interplay between clean energy procurement and emissions reduction at the system level.
+
+The reduction of system-wide emissions can be attributed to two primary mechanism driven by the dynamics of clean energy procurement and grid-supplied generation.
+
+First, the timing mechanism, concerns the alignment of clean electricity supply with electricity demand of participating consumers.
+When a share of electricity consumption in a given region is closely alligned with CFE supply, the need for backup dispatchable generation is reduced.
+This effect can reduce utilization of fossil-based peak generators, such as \gls{ocgt} power plants, particularly during periods when wind and solar resources are scarce.
+
+Second, the volume mechanism, pertains to the overall quantity of clean electricity generated by procured resources. 
+The excess clean electricity sold to the grid can displace the emitting grid generators or reduce the need of electricity imports from the neighbouring regions.
+The decarbonisation effect depends on the composition of the 24/7 portfolio, the volume of excess generation that is sold to the grid and the generation (and import) mix in the local zone when the excess electricity is sold.
+
+In the following, we do an experiment to isolate the volume from the profile mechanism. 
+We aim to attribute the reduction of \co emissions in a local zone either to the excess electricity or to the better alignment of procured generation with \gls{ci} consumers' demand.
+In the experiment, we rerun the optimization with setting the rigt-hand side of the constraint \textit{TODO CORRECT REF} to zero, so that only the profile mechanism is present.
+The difference in emissions to the case with excess allowed, we assign to the volume mechanism.
+
+\cref{fig:10-profile-volume.pdf} shows the results of the experiment -- the reduction of emissions in a local zone in Mt\co per year if 10\% of \gls{ci} consumers commit to 24/7 hourly procurement with 100\% CFE target with isolated contributions of the profile and volume mechanisms.
+In other words, \cref{fig:10-profile-volume.pdf} attributes the difference between emissions in the \textit{reference} and the \textit{100\%} 24/7 CFE cases presented  Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions} (right columns) to the two decarbonisation mechanisms.
+The x-axis of the \cref{fig:10-profile-volume.pdf} lists different states of electricity grids where consumers following 24/7 approach can be located: a combination of four zones and two modelled years yields eight 'background' systems.
+
+Two observations in (\cref{fig:10-profile-volume.pdf}) follow intuition: (i) the impact on local zone emissions of 24/7 hourly CFE procurement policy is notably different in absolute numbers (Mt\co per year) depending on \gls{ci} consumers' location, and (ii) the decarbonisation effect of voluntary clean electricity procurement reduces over time since electricity mix in all modelled zones becomes cleaner due to tightening of \gls{necp}s and decomissioning of old emitting power plant fleet.
+Isolation of the profile and volume mechanisms offers news insights.
+First, both mechanisms contribute to the system decarbonisation.
+Second, the cases of Germany and Poland 2030 show that the impact of both mechanisms is also present with the cleaner states of the grid in 2030.
+
+The economic intuition suggests that self-cannibalisation effect of non-dispatchable generators, such as wind and solar, can decrease the impact of clean energy procurement on system-level decarbonisation.
+\cref{fig:10-hourly-annual.pdf} provides a nuanced view on this point.
+The figure presents the \textit{additional} reduction of \co emissions in a local zone driven by the 100\% 24/7 hourly matching with clean electricity over the 100\% annual (volumetric) matching policy.
+In other words, \cref{fig:10-hourly-annual.pdf} illustrates proportional impact of the emissions reduction acvieved by the \textit{RES100\%} and the \textit{100\%} 24/7 CFE policies presented in Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions} (left and right columns), and gives an intuition how the impact changes between 2025 and 2030.
+
+A prominent observation in \cref{fig:10-hourly-annual.pdf} is that 100\% annual matching (or any other volumetric-based matching policy) has a proportionally smaller effect on a system decarbonisation than 24/7 hourly matching in 2030 compared to 2025.
+This result is driven by the diminishing value of each additional megawatt of capacity of non-dispatchable generators, i.e., self-cannibalisation of solar and wind generators. 
+The 24/7 hourly CFE matching have a stronger decarbonisation impact in a cleaner systems due to (i) the profile mechanism, (ii) the volume mechanism, since the procured resources have a more diverse portfolio including battery storage, long-duration energy storage or advanced clean firm technologies that allow for having clean electricity available in periods when system-wide wind and solar generation is scarce.
 
@@
 
-text on result 10
-
 \begin{figure}

### 2023-04-16 manuscript/sections/results.tex
finish results section

@@
 
-A prominent observation in \cref{fig:10-hourly-annual.pdf} is that 100\% annual matching (or any other volumetric-based matching policy) has a proportionally smaller effect on a system decarbonisation than 24/7 hourly matching in 2030 compared to 2025.
+A prominent observation in \cref{fig:10-hourly-annual.pdf} is that 100\% annual matching has a proportionally smaller effect on a system decarbonisation than 24/7 hourly matching in 2030 compared to 2025.
 This result is driven by the diminishing value of each additional megawatt of capacity of non-dispatchable generators, i.e., self-cannibalisation of solar and wind generators. 
 The 24/7 hourly CFE matching have a stronger decarbonisation impact in a cleaner systems due to (i) the profile mechanism, (ii) the volume mechanism, since the procured resources have a more diverse portfolio including battery storage, long-duration energy storage or advanced clean firm technologies that allow for having clean electricity available in periods when system-wide wind and solar generation is scarce.
+
+The decarbonisation mechanisms discussed above suggest a displacement of fossil-fueled generators in the rest of the system in presense of voluntary clean electricity procurement.
+We illustrate this effect in \cref{fig:10-2030-DE-p1-system_capacity_diff.pdf}, which shows the difference in the generation capacity expansion of the whole European electricity system (excluding resources procured by participating customers) with and without commitments to clean electrity procurement (an illustraive scenario for Germany, 2030, technological palette~1).
+Hourly CFE procurement benefits the system by having a pronounced effect of flexibility needs reduction -- the system requires less battery storage and less peaker capacity in a form of \gls{ocgt}. 
+In the selected example, 3.8~GW of load (10\% of \gls{ci} sectors in Germany) participate in the procurement.
+In a case of hourly matching with 100\% CFE target, this reduces \gls{ocgt} investments by 4.6~GW and battery storage by 2.6~GW in the rest of the system.
+The substitution of gas-fired capacity with clean resources procured by \gls{ci} consumers facilitates decarbonization of the entire system, as shown above.
 

### 2023-09-21 manuscript/sections/results.tex
typo fix
revise 3.1 after long break

@@
 Focusing on the electricity buyers' perspective, we analyse procurement strategies (i.e.
-the optimal mix of locally procured capacities of energy generation \& storage assets and electricity imports from the grid), the average costs of procured electricity and carbon emissions associated with the consumers' electricity usage.
+the optimal mix of locally procured capacities of energy generation and storage assets, and electricity imports from the grid), the average costs of procured electricity and carbon emissions associated with the consumers' electricity usage.
 When our focus switches to the system perspective, we describe the impact of the \gls{cfe} procurement approaches on \co emissions on the local grids, as well as the impact on back up flexibility needs.
 
-As described in \cref{subsec:scenarios}, we aim to generalize our findings void individual assumptions by incorporating a large scenario space into the study design. 
+We aim to generalize our findings on 24/7 procurement void individual assumptions by incorporating a large scenario space into the study design.
 For convenience, we start with a \textit{base scenario} presented in \cref{subsec:base}.
@@
 
-In the Annex \ref{sec:si}, we summarise findings from sensitivity analyses regarding higher 24/7 procurement participations rates and various consumption profiles of electricity buyers.
+In the \nameref{sec:discussion}, we summarise our findings for the four questions above and have a look beyond the focus of the model scenarios discussed in the main part of the paper by integrating observations from sensitivity analyses relating to the participation rates of electricity buyers and their diverse consumption profiles, providing an overarching look at the 24/7 procurement and impacts on the electrcity systems.
 
@@
 
-The base scenario reflects a case when \textbf{10\%} (on volumetric basis) of commertial \& industrial consumers in \textbf{Ireland} in \textbf{2025} voluntrary commits to 24/7 clean electricity procurement goal.
+The base scenario reflects a case when \textbf{10\%} (on volumetric basis) of \gls{ci} consumers in \textbf{Ireland} in \textbf{2025} voluntrary commits to 24/7 clean electricity procurement goal.
 This assumption yields 220~MW of \textbf{base load} that has to be matched with clean electricity. 
-The participating consumers can achieve the \gls{cfe} procurement goal by co-optimizing local procurement with the \textbf{palette 1} of technologies (i.e., mature technologies available on the market now: onshore wind, solar, and battery storage), as well as by importing electrcity from the local grid.
+The participating consumers can achieve the \gls{cfe} procurement goal by co-optimizing local procurement with of mature technologies (designated as \textbf{palette~1}), i.e., technologies available on a market for commercial use as of now, such as onshore wind, utility-scale solar PV, and battery storage, as well as by importing electricity from the local grid.
 
@@
 
-In the reference case, where \gls{ci} consumers do not procure any resources, relying purely on grid purchases, only 54\% of demand is met with clean electricity.
-100\% RES -- the best case for the annual renewable matching policy -- results in 83\% fraction. 
+In the reference case, where \gls{ci} consumers do not procure any resources, relying on grid purchases, only 54\% of demand is met with clean electricity.
+100\% RES---the best case for the annual renewable matching policy---results in 83\% fraction. 
 Consequently, 24/7~CFE targets beyond 85\% yield higher share of hourly demand met with clean electricity than 100\% annual matching policy.
@@
 We explore this effect by plotting \co emissions in the local region of the participating consumers, i.e. Ireland.
-Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2~Mt\co -- see a reference case in \cref{fig:10-2025-IE-p1-zone_emissions}.
-\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021.
+Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2~Mt\co -- see a reference case in \cref{fig:10-2025-IE-p1-zone_emissions}.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021.
 A strong decreasing trend is expected, since Irish government has set ambitious targets to achieve a low-carbon energy system \cite{SEAI}.}
@@
 This reduction is equivalent to 14\% of Irish power sector emissions.
-100\% annual renewable matching policy can also deliver system-level \co emissions reductions (left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, beyond 85\% CFE target, 24/7 hourly matching achieves greater emissions reductions than 100\% annual mathing policy.
+100\% annual renewable matching policy can also deliver system-level \co emissions reductions (left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, beyond 85\% CFE target, 24/7 hourly matching achieves greater emissions reductions than 100\% annual mathing.
 
@@
 
-The following analysis reveals the \gls{cfe} procurement strategies by participating consumers for each procurement policy.
-\cref{fig:10-2025-IE-p1-ci_capacity} shows that for 10\% of \gls{ci} load in Ireland (220 MW), the 100\% RES policy is cost-optimally met with 1.3~GW of onshore wind and solar generators.
-Matching demand with clean generation on 24/7 hourly basis requires a much bigger portfolio of wind and solar than the 100\% RES policy.
-Also, for CFE target above 85\% the cost-optimal procurement sees battery storage enter the portfolio mix.
-Note that for 80\% CFE target, 24/7 participating consumers procure less capacity than for 100\% annual matching policy, as it relies more on grid imports.
+The following analysis reveals the modelled cost-optimal procurement strategies for each \gls{cfe} policy.
+\cref{fig:10-2025-IE-p1-ci_capacity} shows that for 10\% of \gls{ci} load in Ireland (220 MW), the 100\% annual matching policy is met by onshore wind and solar PV generators with combined capacity of 1.3~GW.
+Matching demand with clean generation on hourly basis requires a much bigger portfolio of wind and solar than the annual matching policy, up to 4.0~GW of combined capacity to reach the 100\%~CFE.
+Batteries are included in the cost-optimal portfolio mix when CFE targets are above 85\%.
+Note that for 80\% CFE target, 24/7 participating consumers procure less capacity than for 100\% annual matching policy, as they rely more on grid imports.
 
@@
 \cref{fig:10-2025-DEPL-p3-4plots} shows results for the two selected regions: Germany and Poland. 
-Germany is selected as it the largest electricity consumer in Europe and it is well interconnected to regions with clean electrcity grids, such as France and Denmark.
-Poland—a country with  historic dependency on domestic coal resources, resistance from the coal industry and lack of governmental support for renewable energy—is selected for a contrast.
+Germany is selected as it the largest electricity consumer in Europe that is well interconnected to regions with relatively clean grids, such as France and Denmark.
+Poland---a country with  historic dependency on domestic coal resources, resistance from the coal industry and lack of governmental support for renewable energy---is selected for a contrast.
 To keep other factors constant, the same 10\% share of \gls{ci} consumers is set to participate in voluntary clean electricity procurement.%
@@
 
-\subsection{Uncovering mechanisms how 24/7 CFE commitments decarnonise local grids}
+\subsection{Uncovering mechanisms how 24/7 CFE commitments decarbonise local grids}
 \label{subsec:mechanisms}

### 2023-09-25 manuscript/manuscript.tex
results results, technology access
results results, diverse grid locations
suppress minor overfull hbox warnings
format: result w/o box env

@@
 \biboptions{numbers,sort&compress}
+
+\hfuzz=5.002pt %https://tex.stackexchange.com/questions/13715/how-to-suppress-overfull-hbox-warnings-up-to-some-maximum
 
@@
 \newtheorem{lem}[thm]{Lemma}
-\newmdtheoremenv[
-  backgroundcolor=Wheat, % Background color
-  linewidth=0.5pt, % Width of the line around the box
-  frametitlefont=\normalfont\bfseries, % Font for the box title
-]{res}[thm]{Result}
+\newtheorem{res}[thm]{Result}  % Result w/o box env
+%\newmdtheoremenv[
+%  backgroundcolor=Wheat, % Background color
+%  linewidth=0.5pt, % Width of the line around the box
+%  frametitlefont=\normalfont\bfseries, % Font for the box title
+%]{res}[thm]{Result}
 
@@
 \newacronym{ci}{C\&I}{Corporate and Industry (sectors)}
+\newacronym{ldes}{LDES}{Long Duration Energy Storage}
 
@@
 \input{sections/methods.tex}
+
+\newpage
 

### 2023-09-26 manuscript/sections/results.tex
results: revise section 3.2 to 3.4

@@
     \centering
-    \includegraphics[width=\columnwidth]{plots/10/2025/IE/p1/used.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/used.pdf}
     \caption{Fraction of hourly demand met with carbon-free electricity.}
@@
 Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case. 
-If \gls{ci} consumers follow 100\% RES goal and procure enough renewable recourses, the emission rate is reduced to 60~g\co/kWh.
+If \gls{ci} consumers follow 100\% annual matching policy and procure enough renewable energy, the emission rate is reduced to 60~g\co/kWh.
 This yields a considerable emission rate reduction compared to the reference case.
-The 24/7 procurement policy with CFE targets above 85\% can help the participating consumers to reduce emissions further, or eliminate them competely in the case of 100\% 24/7~CFE.
+The 24/7 procurement policy with CFE targets above 85\% helps the participating consumers to reduce emissions further beyond the treshhold set by the 100\% annual matching with renewable energy. 
+At the 100\% CFE target, participating consumers attain a zero emission rate associated with their electricity consumption, as they perfectly align demand and clean generation on an hourly basis.
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
     \caption{Average emissions rate of participating consumers.}
@@
     \centering
-    \includegraphics[width=\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
     \caption{\co emissions in the local region (Ireland).}
@@
 
+%TODO CCS has to be defined first above
 The results in \cref{fig:10-2025-IE-p23-ci_procurement} reflect a case when 24/7~CFE participants have an access to a wider palette of technologies: 
-long-duration energy storage (\gls{ldes}) and advanced clean firm generators, such as advanced geothermal systems, advanced nuclear or Allam cycle generators with carbon capture and sequestration.
+long-duration energy storage (\gls{ldes}) and advanced clean firm generators, such as advanced geothermal systems, advanced nuclear or Allam cycle generators with \gls{ccs}.
 
-The top row shows the power capacity portfolio (\cref{fig:10-2025-IE-p2-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p2-ci_costandrev}) for a case when \gls{ci} consumers have an access to \textbf{palette~2} technologies, i.e., the \gls{ldes} system is also available on a market.%
+%TODO maybe remove footnote when tech cost table is there
+The top row shows the power capacity portfolio (\cref{fig:10-2025-IE-p2-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p2-ci_costandrev}) for a case when \gls{ci} consumers have an access to \textbf{palette~2} technologies, i.e., the \gls{ldes} complements onshore wind, solar PV and battery storage.%
 \footnote{Here we assume 2.5~\euro/kWh underground hydrogen storage in salt caverns.}
@@
 As a result, the cost-optimal portfolio of renewable capacity for the 100\% 24/7 CFE target is not much larger than for the 100\% annual matching policy. 
-This also significantly decreases procurement costs at high CFE targets: 100\% 24/7~CFE has a cost premium of 42\% above 100\% annual renewable mathing policy.
+This also significantly decreases procurement costs at high CFE targets: with \gls{ldes}, 100\% 24/7~CFE has a cost premium of 42\% above 100\% annual mathing with renewable energy.
 
-The bottom row shows the results for technological \textbf{palette 3} scenario (\cref{fig:10-2025-IE-p3-ci_capacity} and \cref{fig:10-2025-IE-p3-ci_costandrev}). 
-The procurement strategy now includes the Allam cycle generator.
-The clean firm technology can be operated any time of the year and thus helps to fill in the gaps in variable renewable generation to match demand and clean generation on hourly basis.
-Inclusion of clean firm generation also reduces renewable capacity and storage requirements. 
+The bottom row shows the results for the \textbf{palette~3} scenario (\cref{fig:10-2025-IE-p3-ci_capacity} and \cref{fig:10-2025-IE-p3-ci_costandrev}). 
+In this scenario, 24/7~CFE participants have an access to the palette~2 technologies, as well as the clean firm generators, such as advanced geothermal and Allam cycle generators.
+In the case of Ireland, the procurement strategy now includes the Allam cycle technology in the optimal mix.
+The clean firm technology helps to fill in the gaps in variable renewable generation to match demand and clean generation on hourly basis.
+Inclusion of clean firm generation reduces renewable capacity and storage requirements. 
 This, in turn, further limits the 24/7 CFE cost premium.
-In this scenario, 100\% 24/7~CFE costs only 15\% above 100\% annual renewable mathing.
+In this scenario, 100\% 24/7~CFE costs only 15\% above 100\% annual renewable matching.
 
+%TODO remove two capacity figs for space reduction? adjust text
 \begin{figure*}
@@
 
-While we have focused on base scenario reflecting the case of Ireland, exactly the same modelling exercise can be repeated for other regions of the European electricity grid.
+While we have focused on base scenario reflecting the case of Ireland, the same modelling exercise can be repeated for other regions of the European electricity grid.
 Since each region has a unique set of characteristics that depend on local resources, renewable potentials, national energy and climate policies, and degree of interconnections, such sensitivity can allow for generalising the impact of 24/7 CFE procurement void regional differences.
 
-\cref{fig:10-2025-DEPL-p3-4plots} shows results for the two selected regions: Germany and Poland. 
-Germany is selected as it the largest electricity consumer in Europe that is well interconnected to regions with relatively clean grids, such as France and Denmark.
-Poland---a country with  historic dependency on domestic coal resources, resistance from the coal industry and lack of governmental support for renewable energy---is selected for a contrast.
-To keep other factors constant, the same 10\% share of \gls{ci} consumers is set to participate in voluntary clean electricity procurement.%
+\cref{fig:10-2025-DEPL-p3-4plots} shows the results for the two selected regions: Germany and Poland. 
+Germany is selected because it is the largest electricity consumer in Europe and has a good connection to regions with relatively clean grids, like France and Denmark. 
+As an example of the contrast, Poland is chosen because of its historical reliance on coal resources, resistance from the coal industry, and lack of government support for renewable energy.
+The participation rate of 24/7~CFE consumers is set at 10\% of the \gls{ci} sector in each country, as in the base scenario.%
 \footnote{10\% participation rate of \gls{ci} sector yields load of 3.8~GW in Germany and 1.1~GW in Poland.}
 
-Despite regional differences, the dynamics of 24/7 CFE procurement, observed in the example of Ireland, show similar trends.
+The dynamics of 24/7 CFE procurement, observed above, appear similar despite regional differences.
 
-As can be expected, the cleaner grid in the German case results in a lower value of the average emissions rate of participating consumers than in the case of Poland. 
-The values in the reference case are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.%
-\footnote{For reference, 2021 estimates for emission intensity of electricity generation are 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}
-Similar to the Irish results, \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} show that in both cases, \gls{ci} participants achieve lower emissions rates with 24/7 hourly CFE procurement than with 100\% annual matching once CFE target is tight enough.
-As expected at 100\% CFE target, participating consumers achieve a zero emission rate associated to their electricity consumption, since they perfectly match demand and clean generation on hourly basis.
+German consumers have lower average emissions rates due to a cleaner grid than Polish consumers, as one would expect.
+In the reference case of grid electricity procurement, the values are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.%
+\footnote{For reference, 2021 data for emission intensity of electricity generation was at 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}
+Similar to the Irish results, \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} show that in both cases, \gls{ci} participants achieve lower emissions rates with 24/7 hourly CFE procurement than with 100\% annual matching with renewable energy once their CFE targets are tight enough.
 
@@
 Without any CFE procurement stategy, the German and Polish power sector carbon emissions are at 118.8~Mt\co and 83.8~Mt\co in 2025, respectively.%
-\footnote{Germany is a larger electricity consumer, while Polish electricity mix has much a higher emission intensity; thus, power sector carbon emissions are on a similar scale for these regions.} 
-If only 10\% of C\&I load joins efforts of voluntary \gls{cfe} procurement, a significant decarbonisation impact is achieved. 
-For example in Germany, with this participation, the 100\% annual matching with renewable electricity can reduce system-level \co emissions by 11.1~Mt\co per year. 
-With the 24/7 hourly matching, C\&I consumers achieve even greater impact on emissions, up to 14~Mt\co per year with CFE 100\% target.
+\footnote{Germany is a larger electricity consumer, while Polish electricity mix has much a higher emission intensity; thus, power sector carbon emissions are on a similar scale for these countries.} 
+If C\&I load commits to voluntary clean energy procurement beyond \gls{necp}s, a significant decarbonisation impact is achieved. 
+The modelling results provides insightful data.
+For example, in Germany, with just 10\% \gls{ci} participation rate, the 100\% annual matching with renewable energy can reduce national emissions by 11.1~Mt\co/a; the 24/7 hourly matching policy yields even greater impact, up to 14~Mt\co/a with CFE 100\% target.
 
-\cref{fig:10-2025-DE-p3-ci_costandrev} and \cref{fig:10-2025-PL-p3-ci_costandrev} also show similar trends to the base scenario. 
-For lower CFE targets, participating consumers can complement portfolio with electricity imports from grid.
-To achieve higher CFE targets, an clean firm generatorion is added to the portfolio, which greatly reduces the need for renewable generation capacity to match load on an hourly basis.
-In the case of Germany and Poland, both the Allam cycle generator with CCS and advanced dispatchable generator enter the optimal procurement strategy. 
-This is likely due to a case that these regions are better interconnected with the rest of the European electrcity grid than Ireland. 
+The results for the required portfolio capacity-/costs are shown in \cref{fig:10-2025-DE-p3-ci_costandrev} and \cref{fig:10-2025-PL-p3-ci_costandrev}.
+24/7 consumers in Germany and Poland complement procurement of renewable energy with electricity imports from grid for low CFE targets. 
+To achieve higher CFE targets, Allam cycle with \gls{ccs} and advanced clean firm generators enter the technology mix. 
+The fact that both advanced technologies enter the optimal solution space is different to Irish results, where only the Allam cycle is cost-optimal. 
+This likely due to a case that Germany and Poland are better interconnected with the rest of the European electrcity grid than Ireland. 
 A better interconnection makes possible to exhaust all arbitrage opportunities across time and space and maximise the dispatch value from an advanced dispatchable generator with low variable costs.
+Similarly to Irish results though, the cost premium of 24/7 hourly matching is small when the advanced technologies are available.
 
@@
 
-\subsection{Moving five years more ahead}
+\subsection{Advancing five years forward}
 \label{subsec:time}
@@
 
-In the scenarios above, we have been exploring 24/7 clean electricity procurement within the European electricity system, with a focus on the year 2025. 
-In this section, we shift our attention to the results and implications of these procurement strategies for the year 2030. 
-This will provide a deeper understanding of the long-term effects and the potential evolution of clean energy procurement across Europe, as companies continue to adapt their procurement strategies to achieve carbon-free energy goals.
+We explored the means, costs, and impacts of clean electricity procurement in the European electricity system for the year 2025 in the sections above.
+In this section, we examine the results and implications of these procurement strategies for 2030.
+Ultimately, this will allow us to better understand the long-term effects and the potential evolution of clean energy procurement in Europe, as companies continue to adapt their procurement strategies.
 
-From the modelling perspective, many system parameters change with a five year step to 2030. 
-In particular, the technology costs decline due to economics of scale and incremental innovation, national energy- and climate policies become more tight, and some legacy power plants leave the market.
-An overarching feature of the five-year step is a cleaner state of the electricity grids.
+A five-year step to 2030 changes many system parameters from a modelling perspective.
+In partcular, technology costs decline as a result of economies of scale and incremental innovation, energy- and climate policies become tighter, and some legacy power plants go out of business.
+The two key trends of advancing five years forward are cleaner electricity grids and lower costs for energy technologies.
 
-\cref{fig:10-2030-IE-6plots} illustrates the results for the "base scenario" moved five years into the future to 2030, with all other factors held constant.
+\cref{fig:10-2030-IE-6plots} illustrates the results for \textit{base scenario} moved five years to 2030, with all other factors held constant.
 
-\cref{fig:10-2030-IE-p1-used} shows the fraction of hourly demand met with clean electricity for each procurement policy -- now in 2030. 
-There two observations from comparing these results with a base scenario.
-First, in the reference case, 72\% of demand is met with CFE, which is 18\% more than in 2025, which is a result of a cleaner electricity grid on a background. 
-Thus, lower CFE targets (such as 80\%) are met with a larger share of grid imports. 
-Second, higher CFE targets still require a independency from grid imports for the perfect match of clean electricity with \gls{ci} load on hourly basis. 
-At 100\% 24/7 CFE, participating consumers rely only on procured resources.
+\cref{fig:10-2030-IE-p1-used} shows the fraction of hourly demand met by clean electricity under each procurement policy in 2030.
+Two observations can be drawn from comparing these results with a base scenario.
+The first is that 72\% of demand is met by CFE in the reference case, which is 18\% greater than in 2025, i.e., there is a cleaner electricity grid on a background.
+Therefore, lower CFE targets (such as 80\%) are achieved by importing more electricity.
+Second, 24/7 participants continue to rely primarily on their own procurement of \gls{cfe} resources and storage, without importing much from the background grid to reach higher CFE targets.
 
-The average emissions rate of 24/7 participating consumers is intuitively lower with a cleaner regional network. 
+A cleaner background grid results in lower average emissions rates for 24/7 participants. 
 As shown in \cref{fig:10-2030-IE-p1-ci_emisrate}, the reference case value is reduced from 240~g\co/kWh in 2025 to 107~g\co/kWh in 2030.
-The dynamics of 24/7 CFE procurement remains also in 2030.
-An hourly 24/7 matching allows for net-zero emissions associated with the \gls{ci} buyers' consumption, with a lower emission rate than 100\% annual matching already at 90\% CFE target.
-An interesting result is that a CFE target of 90\% yields lower \gls{ci} emission rate, although costs the same as the 100\% annual matching for all three technological palettes (see \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p1-ci_costandrev}).
+The hourly matching policy allows achieving zero emissions associated with \gls{ci} participants consumption.
+It is interesting to note that a CFE target of 90\% yields lower average emissions than a 100\% annual matching policy, even though these policies are both equally costly (see \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p3-ci_costandrev}).
 
-\cref{fig:10-2030-IE-p1-zone_emissions} show that both 100\% annual matching with renewable energy and the 24/7 hourly matching with \gls{cfe} keep positive effect on system-level emissions even in cleaner system.
-Similarly to 2025, if CFE target is high enough, a diverse resource portfolio procured by 24/7 participating consumers has a larger impact on net system emissions in a local zone than 100\% annual matching.
-Interestingly, in the case of 2030, 100\% 24/7 CFE nearly doubles the decarbonisation effect of 100\% annual matching: 100\% RES reduces emissions in the local zone by 0.2~Mt\co/a (8\% of Irish power section emissions), while 100\% 24/7 CFE yields reduction of 0.4~Mt\co/a.
+In even cleaner systems, both 100\% annual matching with renewable energy and 24/7 hourly matching with \gls{cfe} keep their positive effect on system-level emissions.
+Similar to 2025, when a CFE target is high enough, a diverse portfolio of energy resources procured by 24/7 participating consumers impacts system-level emissions more than the annual matching policy, see \cref{fig:10-2030-IE-p1-zone_emissions}.
+The hourly matching policy nearly doubles the decarbonisation effect of renewable matching in 2030: with a 10\% participation rate, annual matching reduces local emissions by 0.2~Mt\co/a (approximately 8\% of Irish power section emissions).
+Hourly matching results in a reduction of 0.4~Mt\co/a at 100\% CFE target.
 The nature of this effect is explained in \cref{subsec:mechanisms}.
 
-The \gls{ci} cost breakdown for Ireland 2030 scenario shows that net costs for 24/7 CFE matching fall for all technological palettes.
-Participating consumers benefit from decreasing costs of clean technologies and cleaner state of the electricity grids.
-\cref{fig:10-2030-IE-p2-ci_costandrev} and \cref{fig:10-2030-IE-p1-ci_costandrev} show that in 2030, cost-optimal portfolio mix procured by the \gls{ci} participants for CFE 100\% target has a very limited cost premium to 100\% annual renewable matching with LDES and clean firm technologies.
-At the same time, participanting consumers achieve a zero emission rate associated to their electricity consumption and have a bigger impact on \co emissions in the rest of the system.
+The cost breakdown for Ireland 2030 shows that 24/7 hourly matching costs are decreasing for all technological pallets compared to 2025, see \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p3-ci_costandrev}.
+The reason is that 24/7 participating consumers benefit from lower prices for clean energy technologies and cleaner electricity grids. 
+The results show that cost-optimal portfolios procured by \gls{ci} participants for the 100\% hourly matching with CFE policy have a very limited premium over the 100\% annual renewable matching, for scenarios when \gls{ldes} and advanced clean firm technologies are available.
+Through these low cost premiums, participating consumers achieve zero emissions associated with their electricity consumption and have a great impact on system-level \co emissions.
 
@@
     \caption{Results for the case of Ireland 2030. 10\% participation rate. 
-    Data for the Figures \ref{fig:10-2030-IE-p1-used}--\ref{fig:10-2030-IE-p1-zone_emissions} is for the technological palette~1 scenario.}
+    Figures \ref{fig:10-2030-IE-p1-used}--\ref{fig:10-2030-IE-p1-ci_costandrev} display the technological palette~1 scenario.}
     \label{fig:10-2030-IE-6plots}
@@
     \centering
-    \includegraphics[width=\columnwidth]{plots/10/2030/DE/p1/system_capacity_diff.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2030/DE/p1/system_capacity_diff.pdf}
     \caption{

### 2023-09-26 manuscript/sections/results.tex
results: remove redundant plots from main text

@@
 
-The cost premium of 24/7 hourly clean electricity procurement presented in \cref{subsec:base} is driven by the variability of renewable power supply.
-Indeed, in the periods when not much wind or solar is available, matching every kilowatt-hour of electricity consumption with carbon-free electricity on hourly basis is not an easy task.
+The cost premium of 24/7 hourly \gls{cfe} procurement presented in \cref{subsec:base} is driven by the variability of renewable power supply.
+Indeed, in the periods when not much wind or solar is available, matching every kWh of electricity consumption with carbon-free electricity on hourly basis is not an easy task.
 Battery storage technology is cost-optimal for shifting surplus a power supply by a couple of hours.
 However, bridging extended periods of low wind and sun with battery storage is expensive.
-Results above also illustrate that for CFE targets of 98\%--100\%, 24/7 participating consumers rely little on the grid supply, since electricity mix in the local grids contain some carbon content.
+Also, the results above show that 24/7 participating consumers rely little on grid supply to reach CFE targets of 98\%--100\%, since a local grid's electricity mix almost always includes some fossil-fueled generation.
 
-%TODO CCS has to be defined first above
-The results in \cref{fig:10-2025-IE-p23-ci_procurement} reflect a case when 24/7~CFE participants have an access to a wider palette of technologies: 
-long-duration energy storage (\gls{ldes}) and advanced clean firm generators, such as advanced geothermal systems, advanced nuclear or Allam cycle generators with \gls{ccs}.
+The results in \cref{fig:10-2025-IE-p23-ci_procurement} reflect a case when 24/7~CFE participants have an access to a wider palette of technologies, including \gls{ldes} and advanced clean firm generators, such as advanced geothermal systems, advanced nuclear or Allam cycle generators with \gls{ccs}.
 
-%TODO maybe remove footnote when tech cost table is there
-The top row shows the power capacity portfolio (\cref{fig:10-2025-IE-p2-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p2-ci_costandrev}) for a case when \gls{ci} consumers have an access to \textbf{palette~2} technologies, i.e., the \gls{ldes} complements onshore wind, solar PV and battery storage.%
-\footnote{Here we assume 2.5~\euro/kWh underground hydrogen storage in salt caverns.}
-The \gls{ldes} helps to align the load with the generation of procured variable renewable resources. 
-As a result, the cost-optimal portfolio of renewable capacity for the 100\% 24/7 CFE target is not much larger than for the 100\% annual matching policy. 
-This also significantly decreases procurement costs at high CFE targets: with \gls{ldes}, 100\% 24/7~CFE has a cost premium of 42\% above 100\% annual mathing with renewable energy.
+\cref{fig:10-2025-IE-p2-ci_costandrev} (left panel) shows the breakdown of costs for a case when \gls{ci} consumers have an access to \textbf{palette~2} technologies, i.e., \gls{ldes} complements onshore wind, solar PV and battery storage.
+A \gls{ldes} system\footnote{Here we assume 2.5~\euro/kWh underground hydrogen storage in salt caverns.} helps to bridge hours with no renewable feed-in. 
+As a result, the required portfolio of renewable capacity and procurement costs are reduced, especially for high CFE targets.
+Thus, 100\% 24/7 hourly matching has a cost premium of 42\% above annual matching policy, which is significantly lower than w/o \gls{ldes}.
 
-The bottom row shows the results for the \textbf{palette~3} scenario (\cref{fig:10-2025-IE-p3-ci_capacity} and \cref{fig:10-2025-IE-p3-ci_costandrev}). 
-In this scenario, 24/7~CFE participants have an access to the palette~2 technologies, as well as the clean firm generators, such as advanced geothermal and Allam cycle generators.
-In the case of Ireland, the procurement strategy now includes the Allam cycle technology in the optimal mix.
-The clean firm technology helps to fill in the gaps in variable renewable generation to match demand and clean generation on hourly basis.
-Inclusion of clean firm generation reduces renewable capacity and storage requirements. 
-This, in turn, further limits the 24/7 CFE cost premium.
-In this scenario, 100\% 24/7~CFE costs only 15\% above 100\% annual renewable matching.
+\cref{fig:10-2025-IE-p3-ci_costandrev} (right panel) illustrates \textbf{palette~3} scenario, i.e., 24/7 participants have an access to all palette~2 technologies, as well as to clean firm generation technologies.
+Allam cycle generator with \gls{ccs} is now part of the optimal procurement strategy.
+As CFE targets increase, the cost-optimal share of clean firm technology increases.
+The clean firm technology helps to fill in the gaps in variable renewable generation to match demand and clean generation on an hourly basis.
+The cost premium for 24/7 CFE is further reduced in this case: the 100\% 24/7 CFE costs only 15\% over 100\% annual renewable matching.
 
-%TODO remove two capacity figs for space reduction? adjust text
 \begin{figure*}
     \centering
-    \begin{subfigure}{0.5\textwidth}
-        \centering
-        \caption{Portfolio capacity with LDES.}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p2/ci_capacity.pdf}
-        \label{fig:10-2025-IE-p2-ci_capacity}
-    \end{subfigure}% 
     \begin{subfigure}{0.5\textwidth}
@@
         \label{fig:10-2025-IE-p2-ci_costandrev}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-        \centering
-        \caption{Portfolio capacity with LDES and clean firm generators.}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p3/ci_capacity.pdf}
-        \label{fig:10-2025-IE-p3-ci_capacity}
     \end{subfigure}%
@@
     \end{subfigure}
-    \caption{Procurement of clean resources and energy storage if \gls{ci} consumers located in Ireland have an access to a wider palette of technologies.
-    The top row shows the power capacity portfolio (\cref{fig:10-2025-IE-p2-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p2-ci_costandrev}) 
-    if \gls{ldes} is available on the market.
-    The bottom row shows the power capacity portfolio (\cref{fig:10-2025-IE-p3-ci_capacity}) and the breakdown of costs (\cref{fig:10-2025-IE-p3-ci_costandrev}) 
-    for a case when both \gls{ldes} and clean firm dispatchable generators are available.}
+    \caption{The breakdown of costs per procurement policy if \gls{ci} consumers located in Ireland have an access to a wider palette of technologies:
+    w/ \gls{ldes} (\cref{fig:10-2025-IE-p2-ci_costandrev});
+    w/ \gls{ldes} and clean firm generation technologies (\cref{fig:10-2025-IE-p3-ci_costandrev}).
+    }
     \label{fig:10-2025-IE-p23-ci_procurement}
@@
 
-    \caption{Results for cases when 10\% of \gls{ci} load in Germany \textbf{(left panel)} and Poland \textbf{(right panel)} follows 24/7 hourly clean electricity procurement.
+    \caption{Results for cases when 10\% of \gls{ci} load in Germany \textbf{(left)} and Poland \textbf{(right)} follows 24/7 hourly clean electricity procurement.
 Selected scenario with technological palette~3.}
@@
 The reason is that 24/7 participating consumers benefit from lower prices for clean energy technologies and cleaner electricity grids. 
-The results show that cost-optimal portfolios procured by \gls{ci} participants for the 100\% hourly matching with CFE policy have a very limited premium over the 100\% annual renewable matching, for scenarios when \gls{ldes} and advanced clean firm technologies are available.
-Through these low cost premiums, participating consumers achieve zero emissions associated with their electricity consumption and have a great impact on system-level \co emissions.
+The results show that cost-optimal portfolios procured by 24/7 participants for the 100\% hourly matching policy have a minor cost premium over the annual renewable matching, for scenarios when \gls{ldes} and advanced clean firm technologies are available.
+Through these low cost premiums, participating consumers achieve zero emissions associated with their consumption and have a great impact on system-level \co emissions.
 
@@
     \end{subfigure}%
-    \begin{subfigure}{0.5\textwidth}138
+    \begin{subfigure}{0.5\textwidth}
         \caption{Costs of a procurement policy: technological palette~1.}

### 2023-10-02 manuscript/sections/results.tex
results: complete section 3.5

@@
 
-\subsection{Uncovering mechanisms how 24/7 CFE commitments decarbonise local grids}
+\subsection{Exploring mechanisms: how 24/7 CFE procurement decarbonises local grids}
 \label{subsec:mechanisms}
@@
 \begin{res}
-    24/7 CFE procurement reduces system-level \co emissions via two mechanisms that can be isolated as profile and volume effects.
+    24/7 CFE procurement reduces system-level \co \newline
+    emissions through "profile" and "volume" mechanisms. 
 \end{res}
@@
 \begin{res}
-    The difference in impact that 24/7 CFE procurement and 100\% annual matching policies have on system decarbonisation amplifies with a cleaner state of local grids.
+    The difference in impact that 24/7 CFE procurement and 100\% annual matching policies have on system decarbonisation amplifies with a cleaner state of local grids. %TODO REFINE
 \end{res}
 
-\vspace{5pt}
-\begin{res}
-    24/7 CFE procurement reduces the needs for flexibility in the rest of the system.
-\end{res}
+In the previous sections, we demonstrated that 24/7 clean energy procurement results in a substantial reduction of \co emissions in local electricity grids (Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions}).
+In this section, we examine the underlying mechanisms that drive these observed reductions, so as to better understand how clean energy procurement and emissions reduction interrelate.
 
-As illustrated in Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions}, voluntary commitments to 24/7 clean energy procurement result in a considerable reduction of \co emissions in local electricity grids.
-In this section, we delve deeper into the underlying mechanisms responsible for these observed reductions aiming to enhance our understanding of the complex interplay between clean energy procurement and emissions reduction at the system level.
+Two mechanisms are responsible for reducing system-wide emissions:
 
-The reduction of system-wide emissions can be attributed to two primary mechanism driven by the dynamics of clean energy procurement and grid-supplied generation.
+First, a \textit{profile} mechanism: participants doing 24/7 hourly matching procure clean energy resources that better match their demand patterns. 
+As certain consumers timely align their demand with \gls{cfe} supply, the need for dispatchable generation that can firm intermittent renewable supply is lower in the rest of the system. 
+This mechanism can reduce the utilisation of fossil-based generators, such as \gls{ocgt} power plants, which typically ramp up when wind and solar resources are scarce.
 
-First, the timing mechanism, concerns the alignment of clean electricity supply with electricity demand of participating consumers.
-When a share of electricity consumption in a given region is closely alligned with CFE supply, the need for backup dispatchable generation is reduced.
-This effect can reduce utilization of fossil-based peak generators, such as \gls{ocgt} power plants, particularly during periods when wind and solar resources are scarce.
+Second, a \textit{volume} mechanism: even the cost-optimal procurement strategy for 24/7 hourly matching might include some amount of excess clean energy.
+If total \gls{cfe} generation of assets procured by 24/7 participants exceeds demand in a given hour and region, the “excess CFE” is not counted toward a CFE score; however, it is clean electricity that can potentially be stored (using batteries or LDES), or sold to the regional grid.
+As for the latter, "excess CFE" might displace emitting grid generators or reduce the need to import electricity from neighbouring areas.
 
-Second, the volume mechanism, pertains to the overall quantity of clean electricity generated by procured resources. 
-The excess clean electricity sold to the grid can displace the emitting grid generators or reduce the need of electricity imports from the neighbouring regions.
-The decarbonisation effect depends on the composition of the 24/7 portfolio, the volume of excess generation that is sold to the grid and the generation (and import) mix in the local zone when the excess electricity is sold.
+Several factors influence the degree to which profile and volume mechanisms contribute to decarbonising the local grids, such as the composition of the 24/7 portfolio, the volume of excess generation sold to the grid, and the electricity generation (and import) mix in the local zone.
 
-In the following, we do an experiment to isolate the volume from the profile mechanism. 
-We aim to attribute the reduction of \co emissions in a local zone either to the excess electricity or to the better alignment of procured generation with \gls{ci} consumers' demand.
-In the experiment, we rerun the optimization with setting the rigt-hand side of the constraint \textit{TODO CORRECT REF} to zero, so that only the profile mechanism is present.
-The difference in emissions to the case with excess allowed, we assign to the volume mechanism.
+In the following, we conduct an experiment to isolate the decarbonisation effects of the volume and profile mechanisms.
+In the experiment, we reran the optimization with fixing an excess electricity sold to the grid to zero (NB excess is still possible, but can either be stored or curtailed). 
+Such a model setup includes only a profile decarbonisation mechanism. 
+We attribute the difference between emissions reduction in the experiment model setup and the base scenario to the volume mechanism.
+As a result, the reduction of \co emissions in a local zone can be attributed either to excess electricity sold to the grid (volume effect) or to better alignment of CFE generation with demand (profile effect).
 
-\cref{fig:10-profile-volume.pdf} shows the results of the experiment -- the reduction of emissions in a local zone in Mt\co per year if 10\% of \gls{ci} consumers commit to 24/7 hourly procurement with 100\% CFE target with isolated contributions of the profile and volume mechanisms.
-In other words, \cref{fig:10-profile-volume.pdf} attributes the difference between emissions in the \textit{reference} and the \textit{100\%} 24/7 CFE cases presented  Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions} (right columns) to the two decarbonisation mechanisms.
-The x-axis of the \cref{fig:10-profile-volume.pdf} lists different states of electricity grids where consumers following 24/7 approach can be located: a combination of four zones and two modelled years yields eight 'background' systems.
+\cref{fig:10-profile-volume.pdf} illustrates the reduction in local zone emissions attributed to each of the two decarbonisation mechanisms.
+In the plot, the x-axis shows the different states of electricity grids in which \gls{ci} consumers participate in 24/7 procurement.
+The eight 'background grids' are generated from the combination of modelled wildcards: four zones and two years.
 
-Two observations in (\cref{fig:10-profile-volume.pdf}) follow intuition: (i) the impact on local zone emissions of 24/7 hourly CFE procurement policy is notably different in absolute numbers (Mt\co per year) depending on \gls{ci} consumers' location, and (ii) the decarbonisation effect of voluntary clean electricity procurement reduces over time since electricity mix in all modelled zones becomes cleaner due to tightening of \gls{necp}s and decomissioning of old emitting power plant fleet.
-Isolation of the profile and volume mechanisms offers news insights.
-First, both mechanisms contribute to the system decarbonisation.
-Second, the cases of Germany and Poland 2030 show that the impact of both mechanisms is also present with the cleaner states of the grid in 2030.
+It can be seen in \cref{fig:10-profile-volume.pdf} that the overall impact of 24/7 CFE procurement is proportional to how clean the background grid on average is.
+Thus, the largest impact is at 571.6~kgCO$_2$/a·MWh$^{-1}$ takes place in the Poland 2025 zone, and the lowest one is 3.7~kgCO$_2$/a·MWh$^{-1}$ in Denmark 2030 (NB 10\% of \gls{ci} sector participation rate with CFE 100\% score).
+It is noteworthy that from 2025 to 2030, the decarbonisation effect of voluntary clean electricity procurement decreases over time in all zones since electricity grids become cleaner as a result of national climate policy programs and decomissioning of emitting power plants.
+A comparison of the volume and profile mechanisms reveals that both contribute to the decarbonization of the local grids.
+In particular, the profile mechanism contributes significantly to overall emissions reductions, with a major share across all zones regardless of their configuration.
 
-The economic intuition suggests that self-cannibalisation effect of non-dispatchable generators, such as wind and solar, can decrease the impact of clean energy procurement on system-level decarbonisation.
-\cref{fig:10-hourly-annual.pdf} provides a nuanced view on this point.
-The figure presents the \textit{additional} reduction of \co emissions in a local zone driven by the 100\% 24/7 hourly matching with clean electricity over the 100\% annual (volumetric) matching policy.
-In other words, \cref{fig:10-hourly-annual.pdf} illustrates proportional impact of the emissions reduction acvieved by the \textit{RES100\%} and the \textit{100\%} 24/7 CFE policies presented in Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions} (left and right columns), and gives an intuition how the impact changes between 2025 and 2030.
-
-A prominent observation in \cref{fig:10-hourly-annual.pdf} is that 100\% annual matching has a proportionally smaller effect on a system decarbonisation than 24/7 hourly matching in 2030 compared to 2025.
-This result is driven by the diminishing value of each additional megawatt of capacity of non-dispatchable generators, i.e., self-cannibalisation of solar and wind generators. 
-The 24/7 hourly CFE matching have a stronger decarbonisation impact in a cleaner systems due to (i) the profile mechanism, (ii) the volume mechanism, since the procured resources have a more diverse portfolio including battery storage, long-duration energy storage or advanced clean firm technologies that allow for having clean electricity available in periods when system-wide wind and solar generation is scarce.
-
-The decarbonisation mechanisms discussed above suggest a displacement of fossil-fueled generators in the rest of the system in presense of voluntary clean electricity procurement.
-We illustrate this effect in \cref{fig:10-2030-DE-p1-system_capacity_diff.pdf}, which shows the difference in the generation capacity expansion of the whole European electricity system (excluding resources procured by participating customers) with and without commitments to clean electrity procurement (an illustraive scenario for Germany, 2030, technological palette~1).
-Hourly CFE procurement benefits the system by having a pronounced effect of flexibility needs reduction -- the system requires less battery storage and less peaker capacity in a form of \gls{ocgt}. 
-In the selected example, 3.8~GW of load (10\% of \gls{ci} sectors in Germany) participate in the procurement.
-In a case of hourly matching with 100\% CFE target, this reduces \gls{ocgt} investments by 4.6~GW and battery storage by 2.6~GW in the rest of the system.
-The substitution of gas-fired capacity with clean resources procured by \gls{ci} consumers facilitates decarbonization of the entire system, as shown above.
+Additional insights into decarbonisation mechanisms can be gained by examining the emission reductions achieved by 100\% renewables matching and 100\% 24/7 CFE matching policies.
+\cref{fig:10-hourly-annual.pdf} compares the decarbonisation impact in a local zone of the two procurement policies in relative terms (percent point p.a.); the counterfactual scenario is a case when no \gls{ci} consumers participate in voluntary clean electricity procurement.
+The figure shows that the relative impact of 24/7 CFE matching on system-level emissions \textit{increases over time}; this is despite the fact that the impact of procurement policies in absolute terms decreases over time, as shown above.
+Furthermore, the self-cannibalisation effect of non-dispatchable generators, such as wind and solar, decreases the value of additional renewable capacity.
+Thus, in the countries where governments commit to ambitious \gls{necp} targets, such as Ireland and Germany, 24/7 CFE matching has a stronger decarbonisation impact than 100\% annual matching with renewable energy.
+It is because the profile mechanism remains relevant even when renewable energy generators are self-cannibalizing; whereas the volume mechanism is amplified due to the diverse portfolio of procured resources, including batteries, long-term energy storage, and advanced clean firm technologies.
+As a result, clean electricity can be available during times when wind and solar generation is scarce system-wide.
 
@@
         \centering
-        \caption{Emissions reduction in a local zone by 24/7 hourly matching with 100\% target -- profile and volume effects isolated.}
-        \includegraphics[width=0.95\columnwidth]{profile-volume.pdf}
+        \caption{Emissions reduction in a local zone with profile and volume mechanisms isolated. Data is normalised per MWh of demand participating in 24/7 procurement.}
+        \includegraphics[width=0.95\columnwidth]{normalized_effects.pdf}
         \label{fig:10-profile-volume.pdf}
@@
         \centering
-        \caption{Additional emissions reduction in local zone by 100\% hourly over annual matching as percentage points of reference zone emissions.}
-        \includegraphics[width=0.95\columnwidth]{hourly-annual.pdf}
+        \caption{Percentage of emissions reductions in a local zone as a result of a procurement policy compared with the no procurement policy case.}
+        \includegraphics[width=0.95\columnwidth]{emissions_reduction_comparison.pdf}
         \label{fig:10-hourly-annual.pdf}
@@
     \caption{
-        System-level emission reduction: benchmark of procument policies and isolation of decarbonisation mechanisms. 
-    \cref{fig:10-profile-volume.pdf} shows breakdown of emissions reduction in a local zone if 10\% of \gls{ci} load follows 24/7 hourly CFE procurement with 100\% target.
-The profile are volume effects are isolated.
-    \cref{fig:10-hourly-annual.pdf} shows additional emissions reduction in a local zone by 100\% hourly over annual matching.}
+        System-level emission reduction: comparison of procurement policies and isolation of decarbonisation mechanisms.
+        \cref{fig:10-profile-volume.pdf} shows breakdown of emissions reduction in a local zone if 10\% of \gls{ci} load follows 24/7 hourly procurement with CFE 100\% target.
+The profile are volume mechanisms are isolated.
+        \cref{fig:10-hourly-annual.pdf} compares reductions in annual zone emissions in percent points achieved through 100\% annual renewable matching and 100\% 24/7 CFE matching; no procurement policy is assumed in the counterfactual scenario.}
     \label{fig:decarbonisation_story}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.95\columnwidth]{plots/10/2030/DE/p1/system_capacity_diff.pdf}
-    \caption{
-    Difference in generation capacity expansion in the whole European electricity system (including \gls{ci} resources) with and without clean energy procurement. 
-    Selected scenario of Germany, 2030, technological palette~1.}
-    \label{fig:10-2030-DE-p1-system_capacity_diff.pdf}
-\end{figure}
+% \subsection{System flexibility need reduction}
+% \label{subsec:flexibility}
+
+% \vspace{5pt}
+% \begin{res}
+%     24/7 CFE procurement reduces the needs for flexibility in the rest of the system.
+% \end{res}
+
+% The decarbonisation mechanisms discussed above suggest a displacement of fossil-fueled generators in the rest of the system in presense of voluntary clean electricity procurement.
+% We illustrate this effect in \cref{fig:10-2030-DE-p1-system_capacity_diff.pdf}, which shows the difference in the generation capacity expansion of the whole European electricity system (excluding resources procured by participating customers) with and without commitments to clean electrity procurement (an illustraive scenario for Germany, 2030, technological palette~1).
+% Hourly CFE procurement benefits the system by having a pronounced effect of flexibility needs reduction -- the system requires less battery storage and less peaker capacity in a form of \gls{ocgt}. 
+% In the selected example, 3.8~GW of load (10\% of \gls{ci} sectors in Germany) participate in the procurement.
+% In a case of hourly matching with 100\% CFE target, this reduces \gls{ocgt} investments by 4.6~GW and battery storage by 2.6~GW in the rest of the system.
+% The substitution of gas-fired capacity with clean resources procured by \gls{ci} consumers facilitates decarbonization of the entire system, as shown above.
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.95\columnwidth]{plots/10/2030/DE/p1/system_capacity_diff.pdf}
+%     \caption{
+%     Difference in generation capacity expansion in the whole European electricity system (including \gls{ci} resources) with and without clean energy procurement. 
+%     Selected scenario of Germany, 2030, technological palette~1.}
+%     \label{fig:10-2030-DE-p1-system_capacity_diff.pdf}
+% \end{figure}

### 2023-10-02 manuscript/manuscript.tex
backmatter: generalise abbrev list
references: connect zotero export to project .bib

@@
 
-\hfuzz=5.002pt %https://tex.stackexchange.com/questions/13715/how-to-suppress-overfull-hbox-warnings-up-to-some-maximum
+\hfuzz=6.002pt %https://tex.stackexchange.com/questions/13715/how-to-suppress-overfull-hbox-warnings-up-to-some-maximum
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 % acronyms
 \makeglossaries
+
+% Proper nouns
+\newacronym{EU}{EU}{European Union}
+\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
+\newacronym{dea}{DEA}{Danish Energy Agency}
+\newacronym{jrc}{JRC}{Joint Research Center}
+\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
+\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
+\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}
+
+% Enegy tech concepts
 \newacronym{tes}{TES}{Thermal Energy Storage (in form of water tanks)}
@@
 \newacronym{cop}{COP}{Coefficient of Performance}
-\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
 \newacronym{PV}{PV}{Solar photovoltaics}
 \newacronym{ghg}{GHG}{Greenhouse gas}
-\newacronym{EU}{EU}{European Union}
-\newacronym{dea}{DEA}{Danish Energy Agency}
 \newacronym{helmeth}{HELMETH}{Integrated High-Temperature Electrolysis and Methanation for Effective Power to Gas Conversion}
-\newacronym{jrc}{JRC}{Joint Research Center}
 \newacronym{ocgt}{OCGT}{Open Cycle Gas Turbine}
 \newacronym{v2g}{V2G}{Vehicle to Grid}
-\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
-\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
-\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
-\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}
-\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
 \newacronym{dsm}{DSM}{Demand Side Management}
@@
 \newacronym{sng}{SNG}{Synthetic Natural Gas}
+\newacronym{res}{RES}{Renewable Energy Sources}
+\newacronym{cfe}{CFE}{Carbon-Free Electricity}
+\newacronym{ldes}{LDES}{Long Duration Energy Storage}
+\newacronym{ccs}{CCS}{Carbon Capture and Sequestration}
+
+% Energy economics and finance concepts
 \newacronym{fom}{FOM}{Fixed Operation and Maintenance costs}
 \newacronym{vom}{VOM}{Variable Operation and Maintenance costs}
+\newacronym{capex}{CAPEX}{Capital expenditures}
+\newacronym{opex}{OPEX}{Operational expenditures}
 \newacronym{ppa}{PPA}{Power Purchase Agreement}
 \newacronym{ptc}{PTC}{Production Tax Credit}
-\newacronym{res}{RES}{Renewable Energy Sources}
 \newacronym{necp}{NECP}{National Energy and Climate Plan}
 \newacronym{ets}{ETS}{Emissions Trading System}
-\newacronym{capex}{CAPEX}{Capital expenditures}
 \newacronym{cfd}{CfD}{Contract for Difference}
-\newacronym{cfe}{CFE}{Carbon-Free Electricity}
+
+% Other
+\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
+\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
 \newacronym{ci}{C\&I}{Corporate and Industry (sectors)}
-\newacronym{ldes}{LDES}{Long Duration Energy Storage}
 
@@
 
-This paper is an independent project, which is based on the third-party funded 
-research work \cite{Riepin-report-2022}. This research work was supported by a grant from Google Inc.
+This paper is an independent project, which is based on the third-party funded research work \cite{riepin-zenodo-systemlevel247}.
+This research work was supported by a grant from Google Inc.
 
@@
 \renewcommand{\ttdefault}{\sfdefault}
-\bibliography{references}
+\bibliography{paper_247CFE}
 

### 2023-10-02 manuscript/sections/introduction.tex
finish results section
references: connect zotero export to project .bib

@@
-\textbf{Dummy abstract from ECEMP - to refine}
+\textbf{Sketch introduction - to refine}
 
@@
 Thus, this approach has the potential to eliminate all carbon emissions associated with Google's electricity use completely. 
-In 2020 Google committed to the ambitious goal of operating entirely on a 24/7-CFE approach at all its data centres and campuses worldwide by 2030 \cite{Google-1}. 
-Shortly after, Google published a policy roadmap on achieving the 24/7-CFE goal \cite{Google-2}.
+In 2020 Google committed to the ambitious goal of operating entirely on a 24/7-CFE approach at all its data centres and campuses worldwide by 2030 \cite{google-247by2030}. 
+Shortly after, Google published a policy roadmap on achieving the 24/7-CFE goal \cite{google-PolicyRoadmap}.
 

### 2023-10-02 manuscript/sections/methods.tex
manuscript results chapter
finish results section
references: connect zotero export to project .bib

@@
-\textbf{Dummy methods - to refine}
+\textbf{Sketch methods - to refine}
 
-Methodologically, our modelling workflow is based on the PyPSA (Python for Power System Analysis)\footnote{PyPSA is available at \url{https://github.com/PyPSA/PyPSA}}—an open-source software toolbox for simulating and optimising modern energy systems at high resolution maintained by TU Berlin \cite{Brown-PyPSA,HORSCH-PyPSAEUR}.
+Methodologically, our modelling workflow is based on the PyPSA (Python for Power System Analysis)\footnote{PyPSA is available at \url{https://github.com/PyPSA/PyPSA}}—an open-source software toolbox for simulating and optimising modern energy systems at high resolution maintained by TU Berlin \cite{brownPyPSAPythonPower2018,horschPyPSAEurOpenOptimisation2018}.
 The model developed for this study optimises investment and operational decisions to meet projected electricity demand for the consumers performing clean energy procurement, as well as the demand for other consumers in the European electricity system, while meeting all relevant engineering, reliability, and policy constraints.
@@
 The mathematical implementation allows for examining a scenario space when different shares of demand pursue the 24/7 approach with varying thresholds for meeting the hourly clean energy requirement (e.g.
-90\%, 95\%, 100\%) using the definitions provided in Google's paper on methodologies and metrics \cite{Google-methods}.
+90\%, 95\%, 100\%) using the definitions provided in Google's paper on methodologies and metrics \cite{google-methodologies}.
 
@@
 Thus, we aim to generalise the impacts of 24/7-CFE procurement, accounting for the different patterns of electricity demand, weather, availability of renewable resources, existing electricity generation capacity, and national climate- and energy policies, among other factors.
+
+\subsection{Scenario space}
+\label{subsec:scenarios}
+
+%TODO tech abbrev have to be defined here
+% CCS and LDES

### 2023-10-02 manuscript/sections/results.tex
references: connect zotero export to project .bib

@@
 Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2~Mt\co -- see a reference case in \cref{fig:10-2025-IE-p1-zone_emissions}.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021.
-A strong decreasing trend is expected, since Irish government has set ambitious targets to achieve a low-carbon energy system \cite{SEAI}.}
+A strong decreasing trend is expected, since Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
 The modelling results show that if only 10\% of \gls{ci} electricity demand commits to 100\% 24/7 carbon-free electricity in 2025, it would reduce Irish emissions by 0.6~Mt\co per year compared to the scenario with no voluntary procurement.
@@
 In the reference case of grid electricity procurement, the values are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.%
-\footnote{For reference, 2021 data for emission intensity of electricity generation was at 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-europa-web}.}
+\footnote{For reference, 2021 data for emission intensity of electricity generation was at 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-GNGEmissionsEU}.}
 Similar to the Irish results, \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} show that in both cases, \gls{ci} participants achieve lower emissions rates with 24/7 hourly CFE procurement than with 100\% annual matching with renewable energy once their CFE targets are tight enough.

### 2023-10-03 manuscript/sections/introduction.tex
intro: outline section

--- 2023-04-04 manuscript/sections/introduction.tex
@@
-\textbf{Dummy abstract from ECEMP - to refine}
+% Introduction Structure
+
+% 1. **Opening & Introduce the global momentum towards renewable energy adoption.**
 
 Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
-Many public and private energy buyers have joined this effort and highlight their sustainable credentials by procuring renewable energy with the Power Purchase Agreements (\gls{ppa}s).
-\gls{ppa}s typically allow for renewable energy to match supply and demand on average over a long period of time. 
-For example, more than 360 members of the there100.org group\footnote{\url{https://www.there100.org/}} have committed to purchasing enough renewable energy to match 100\% of their electricity consumption on an annual basis.
-Such voluntary commitments accelerate the deployment of wind and solar capacity above the policy requirements in the countries and jurisdictions these companies operate.
+The European Union (\gls{eu}) has committed to achieve net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}.
+National climate initiatives span the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to "have \co emissions peak before 2030 and achieve carbon neutrality before 2060” \cite{ChinaNetZero-IEA}.
 
-However, the energy buyers that commit to 100\% annual matching from Renewable Energy Sources (\gls{res}) still face times when generation from wind and solar generators is not sufficient to match the companies' electricity demand.
-During those hours, the energy buyers often have to rely on carbon-emitting power generating technologies available on the local market, such as coal and gas. 
-The energy demand supplied by the annual matching approach is thus not \textit{entirely} carbon-free. 
-Furthermore, 100\% annual matching approach keeps electricity buyers exposed to price volatility. 
-Finally, it requires the energy system to maintain backup and flexibility options for hours with low renewable generation.
+% 2. **Evolution, approaches and challenges of voluntary clean energy procurement**
 
-For this reason, there is growing interest from corporations such as Google to match their demand with clean energy supply on a truly 24/7 basis. 
-Achieving 24/7 Carbon-Free Energy (CFE) means that every kilowatt-hour of electricity consumption is met with carbon-free electricity sources, every hour of every day. 
-Thus, this approach has the potential to eliminate all carbon emissions associated with Google's electricity use completely. 
-In 2020 Google committed to the ambitious goal of operating entirely on a 24/7-CFE approach at all its data centres and campuses worldwide by 2030 \cite{Google-1}. 
-Shortly after, Google published a policy roadmap on achieving the 24/7-CFE goal \cite{Google-2}.
+Many public and private energy buyers join this effort by purchasing clean energy to demonstrate their sustainability credentials, which, in the best case scenario, can result in additional renewable energy capacity deployment and a reduction in energy buyers' carbon footprints.
+
+The established schemes for voluntary clean energy procurement that have been in use for decades are the Guarantees of Origin (\gls{go}s) in Europe and the Renewable Energy Certificates (also known as Renewable Energy Credits) (\gls{rec}s) in the United States.
+A common feature of these schemes is that renewable energy credits are "unbundled" from megawatt-hours of energy and can be traded numerous times on specialized markets before being retired.
+The owner gets to claim environmental benefits when "retiring" (i.e. using) the certificate.
+The unbundled renewable energy credits, however, have been criticized by researchers and non-governmental organisations (\gls{ngo}s) for not ensuring a physical match between renewable energy generation and consumption, and for absence of evidence that such schemes drive build-out of additional renewable energy capacity \cite{bjorn-RECSnatcom-2022, gillenwater-2014, re100report-2020, spglobal-recs, bock-icelandGOproblem}.
+
+Some corporate and industrial (\gls{ci}) buyers recongnised the problems associated with the unbundled certificates and turned towards Power Purchase Agreements (\gls{ppa}s). 
+When signing a \gls{ppa}, energy buyers pledge to buy both the energy and the environmental credits ("bundled") to megawatt-hours.
+Market-driven procurement of renewable energy has become one of the major drivers of the energy transition: \gls{ppa}s are expected to account for one-fifth of utility solar PV and wind capacity expansion in 2023--2024, and almost twice as much (36\%) when China is excluded \cite{iea-REppa2023}.
+In some countries, such as Spain and Sweden, market-driven procurement of renewable energy capacity has already surpassed policy-driven capacity expansion \cite{iea-REppa2023}.
+
+\textbf{The key problem --} In most cases, \gls{ppa}s enable renewable energy to match supply and demand over a long period of time.
+As an example, more than 400 members of the there100.org group\footnote{\url{https://www.there100.org/}} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
+In spite of such ambitious targets, these buyers still face periods when wind and solar generators signed with \gls{ppa}s cannot supply enough electricity to meet their needs.
+During those hours, energy buyers often have to depend on carbon-emitting technologies, like coal and gas, available on local markets.
+As a result, the 100\% annual renewable matching approach does not entirely eliminate carbon emissions from the energy buyers portfolio.
+Furthermore, 100\% annual matching approach keeps electricity buyers exposed to price volatility, as the price of electricity on the wholesale markets can vary significantly from hour to hour.
+
+% 3. **24/7 Carbon-free Energy Procurement**
+% Introduce the 24/7 CFE idea
+% Initiatives corporate and NGO interest in 24/7 Carbon-free Energy Procurement
+
+\textbf{Proposed solution --} There is growing interest from the leaders in the clean energy procurement to move beyond the 100\% annual matching approach.
+The next frontier in the clean energy procurement is the 24/7 Carbon-Free Energy (\gls{cfe}) procurement, which aims to match clean energy supply with electricity demand on an hourly basis.
+Thus, 24/7-CFE procurement has the potential to eliminate \textit{all greenhouse gas emissions} associated with electricity use of the parciticpating companies.
+Furthermore, 24/7-CFE procurement is focused on \textit{carbon-free} rather than renewable energy, which opens up opportunities for a broad range of advanced energy technologies, such as long-duration energy storage (\gls{ldes}) or new clean firm power generators that are needed for deep decarbonisation of the energy systems.
+
+Google broke the 24/7 ground in 2020 by announcing its commitment to entirely on the 24/7-CFE approach at all its data centres and campuses worldwide by 2030 \cite{google-247by2030}.
+Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.
+Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. "100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases") \cite{Microsoft-vision}. 
+The list of entities that have committed to 24/7-CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}.
+
+In 2021, an international group of energy suppliers, buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact.\footnote{\url{https://gocarbonfree247.com/}}
+With over 135 signatories, the group aims to "develop and scale high-impact technologies, energy policies, procurement practices, aand solutions to make 24/7 Carbon-Free Energy achievable for all.".
+
+% 5. **24/7 model-based studies review**
+\textbf{State of research --}
+
+\cite{chalendar-2019}
+
+% 6. **Relevance of this paper**
 
@@
 \end{enumerate}
+
+% 7. **Prologue**

### 2023-10-06 manuscript/sections/introduction.tex
intro: complete section

--- 2023-04-04 manuscript/sections/introduction.tex
@@
-\textbf{Dummy abstract from ECEMP - to refine}
+% Introduction Structure
+
+% 1. **Opening & Introduce the global momentum towards renewable energy adoption.**
 
 Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
-Many public and private energy buyers have joined this effort and highlight their sustainable credentials by procuring renewable energy with the Power Purchase Agreements (\gls{ppa}s).
-\gls{ppa}s typically allow for renewable energy to match supply and demand on average over a long period of time. 
-For example, more than 360 members of the there100.org group\footnote{\url{https://www.there100.org/}} have committed to purchasing enough renewable energy to match 100\% of their electricity consumption on an annual basis.
-Such voluntary commitments accelerate the deployment of wind and solar capacity above the policy requirements in the countries and jurisdictions these companies operate.
+The European Union (\gls{eu}) has committed to achieve net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}.
+National climate initiatives span the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to \enquote{have \co emissions peak before 2030 and achieve carbon neutrality before 2060} \cite{ChinaNetZero-IEA}.
 
-However, the energy buyers that commit to 100\% annual matching from Renewable Energy Sources (\gls{res}) still face times when generation from wind and solar generators is not sufficient to match the companies' electricity demand.
-During those hours, the energy buyers often have to rely on carbon-emitting power generating technologies available on the local market, such as coal and gas. 
-The energy demand supplied by the annual matching approach is thus not \textit{entirely} carbon-free. 
-Furthermore, 100\% annual matching approach keeps electricity buyers exposed to price volatility. 
-Finally, it requires the energy system to maintain backup and flexibility options for hours with low renewable generation.
+% 2. **Evolution, approaches and challenges of voluntary clean energy procurement**
 
-For this reason, there is growing interest from corporations such as Google to match their demand with clean energy supply on a truly 24/7 basis. 
-Achieving 24/7 Carbon-Free Energy (CFE) means that every kilowatt-hour of electricity consumption is met with carbon-free electricity sources, every hour of every day. 
-Thus, this approach has the potential to eliminate all carbon emissions associated with Google's electricity use completely. 
-In 2020 Google committed to the ambitious goal of operating entirely on a 24/7-CFE approach at all its data centres and campuses worldwide by 2030 \cite{Google-1}. 
-Shortly after, Google published a policy roadmap on achieving the 24/7-CFE goal \cite{Google-2}.
+Many public and private energy buyers join this effort by purchasing clean energy to demonstrate their sustainability credentials.
+The established schemes for voluntary clean energy procurement are the Guarantees of Origin (\gls{go}s) in Europe and the Renewable Energy Certificates (also known as Renewable Energy Credits) (\gls{rec}s) in the United States.
+A common feature of these schemes is that renewable energy credits are \enquote{unbundled} from megawatt-hours of energy and can be traded numerous times on specialized markets before being retired.
+The owner gets to claim environmental benefits when \enquote{retiring} (i.e. using) the certificate.
+The unbundled renewable energy credits, however, have been criticized for not ensuring a physical match between renewable energy generation and consumption, and for absence of evidence that such schemes drive build-out of additional renewable energy capacity \cite{bjorn-RECSnatcom-2022, gillenwater-2014, re100report-2020, spglobal-recs, bock-icelandGOproblem}.
 
-In this study, we model 24/7-CFE procurement in Europe up to 2030. 
+Some corporate and industrial (\gls{ci}) buyers recongnised the problems associated with the unbundled certificates and turned towards Power Purchase Agreements (\gls{ppa}s). 
+When signing a \gls{ppa}, energy buyers pledge to buy both the energy and the environmental credits \enquote{bundled} to megawatt-hours.
+Market-driven procurement of renewable energy has become one of the major drivers of the energy transition: \gls{ppa}s are expected to account for one-fifth of utility solar PV and wind capacity expansion in 2023--2024, and almost twice as much (36\%) when China is excluded \cite{iea-REppa2023}.
+In some countries, such as Spain and Sweden, market-driven procurement of renewable energy capacity surpasses policy-driven capacity expansion \cite{iea-REppa2023}.
+
+\textbf{The key problem --} When \gls{ci} consumers purchase renewable credits, either via unbundled schemes or via bundled \gls{ppa}s, renewable energy supply is typically matched over a long period of time with buyers' energy demands.
+As an example, more than 400 members of the RE100 group\footnote{\url{https://www.there100.org/}} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
+Even the \enquote{best case} of the 100\% annual matching commitments, where energy buyers sign \gls{ppa}s with renewable energy generators located within a local grid, has a major problem -- the temporal mismatch between renewable energy supply and electricity demand.
+In hours when wind and solar generation is low, energy buyers have to depend on carbon-emitting technologies, like coal and gas, available on local markets.
+As a result, the 100\% annual renewable matching approach does not entirely eliminate carbon emissions from the energy buyers portfolio.
+Furthermore, 100\% annual matching approach keeps electricity buyers exposed to price volatility, as the price of electricity on the wholesale markets can vary significantly from hour to hour.
+
+% 3. **24/7 Carbon-free Energy Procurement**
+% Introduce the 24/7 CFE idea
+% Initiatives corporate and NGO interest in 24/7 Carbon-free Energy Procurement
+
+\textbf{Proposed solution: 24/7 CFE --} There is growing interest from the leaders in the clean energy procurement to move beyond the 100\% annual matching approach.
+The next frontier in the clean energy procurement is the 24/7 Carbon-Free Energy (\gls{cfe}) procurement, which aims to match clean energy supply with electricity demand on an \textit{hourly basis}.
+Thus, 24/7~CFE procurement has the potential to eliminate all greenhouse gas emissions associated with electricity use of the parciticpating companies.
+Furthermore, 24/7~CFE procurement is focused on \textit{carbon-free} rather than renewable energy, which opens up opportunities for a broad range of advanced energy technologies, such as long-duration energy storage (\gls{ldes}) or new clean firm power generators that are needed for deep decarbonisation of the energy systems.
+
+Google broke the 24/7 ground in 2020 by announcing its commitment to entirely on the 24/7~CFE approach at all its data centres and campuses worldwide by 2030 \cite{google-247by2030}.
+Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.
+Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. \enquote{100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases} \cite{Microsoft-vision}. 
+The list of entities that have committed to 24/7~CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}.
+In 2021, an international group of energy suppliers, buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact.\footnote{\url{https://gocarbonfree247.com/}}
+With over 135 signatories, the group aims to \enquote{develop and scale high-impact technologies, energy policies, procurement practices, aand solutions to make 24/7 Carbon-Free Energy achievable for all}.
+
+% 5. **24/7 model-based studies review**
+
+\textbf{Existing literature on 24/7 CFE --} The growing interest in the means, costs and the system-level impacts of hourly \gls{cfe} procurement created a need for a quantitative analysis of the approach.
+The existing model-based studies on 24/7~CFE approach are very recent.
+The first to incorporate it into the electricity system planning model were Xu et al.
+(Oct 2022) \cite{xu-247CFE-SSRN}.\footnote{A working paper updates a prior public technical report (Nov 2021, \cite{xu-247CFE-report}) investigating the system-level impacts of 24/7~CFE in two regions of the U.S.
+-- California and PJM.}
+The authors study the system-level impacts of 24/7~CFE procurement based on an example of California in the year 2030.
+In Nov 2022, IEA also released a model-based study on the 24/7~CFE, focusing on India and Indonesia \cite{ieaAdvancingDecarbonisationClean2022}.
+In early 2023, Peninsula Clean Energy published an own white paper introducing their modeling tool---MATCH (Matching Around-the-Clock Hourly energy)---and the results of the modeling indicating feasibility of the company's \enquote{24/7 renewable energy by 2025} goal \cite{peninsula-report247}.
+
+The first studies indicate that 24/7 CFE matching results in emission reduction for both energy buyers and the entire energy system, and has a potential to create demand pull for new clean energy technologies.
+What has been missing is a comprehensive analysis of 24/7 procurement over multiple regions and years, since electricity system characteristics, National Climate and Energy Plans (\gls{necp}s), renewable resource quality, and the cost of clean energy vary significantly across regions and over time.
+Furthermore, it is unclear whether decarbonisation effect of 24/7 CFE procurement remains relevant when electricity grids are progressively decarbonised, as is the case in many countries and jurisdictions, or if the 24/7~CFE procurement is only impactful in the early stages of the energy transition.
+
+% 6. **Relevance of this paper**
+
+% would be good to generalize 
+as provided in this paper.
+
+In this study, we model 24/7~CFE procurement in Europe up to 2030. 
 We explore different designs, costs, benefits and impacts of the 24/7 approach, both for Google and for the power systems in which the data centres are located. 
@@
     \item How can we achieve hourly clean energy matching? 
-    \item What is the 24/7-CFE cost premium versus the 100\% annual matching with renewables? 
-    \item To which extent can technologies, such as long-duration storage or new dispatchable clean technologies, help to achieve the 24/7-CFE goal? 
-    \item If many companies follow the 24/7-CFE approach, how does this effect the rest of the energy system?
+    \item What is the 24/7~CFE cost premium versus the 100\% annual matching with renewables? 
+    \item To which extent can technologies, such as long-duration storage or new dispatchable clean technologies, help to achieve the 24/7~CFE goal? 
+    \item If many companies follow the 24/7~CFE approach, how does this effect the rest of the energy system?
 \end{enumerate}
+
+% 7. **Prologue**

### 2023-10-06 manuscript/sections/results.tex
results: trim text

@@
-In this section, we present modelling results and related analysis. 
-In the analysis, we explore how the 247-CFE and the 100\% annual renewable matching procurement approaches affect both the participating electricity buyers and the electricity system as a whole. 
-Focusing on the electricity buyers' perspective, we analyse procurement strategies (i.e.
-the optimal mix of locally procured capacities of energy generation and storage assets, and electricity imports from the grid), the average costs of procured electricity and carbon emissions associated with the consumers' electricity usage.
-When our focus switches to the system perspective, we describe the impact of the \gls{cfe} procurement approaches on \co emissions on the local grids, as well as the impact on back up flexibility needs.
+% TODO refine and shorten the results section
+% Maybe move some of the graphs to the annex
+% and all other graphs to a dashboard
 
-We aim to generalize our findings on 24/7 procurement void individual assumptions by incorporating a large scenario space into the study design.
+Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
+From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage (also known as Scope 2 emissions).
+From a system perspective, we analyze how voluntary clean energy procurement impacts \co emissions in the region and the \enquote{demand pull} for advanced energy technologies.
+
+Our experimental setup incorporates a large scenario space so that we can generalize our results void of individual assumptions.
 For convenience, we start with a \textit{base scenario} presented in \cref{subsec:base}.
-Afterwards, we explore the scenario space further by presenting selected results that answer the following questions:
-\begin{enumerate}[(i)]
-\item What if clean electricity buyers have an access to a wider palette of carbon-free technologies that are expected to be available for a commercial scale up in the near future (\cref{subsec:palette})?
-\item What if electricity buyers are located in parts of the European electricity grid that are much different to the base scenario? (\cref{subsec:location})?
-\item What if electricity procurement takes place in 2030 instead of 2025 (\cref{subsec:time})? 
-\item Finally, in \cref{subsec:mechanisms}, we explore how exactly 24/7 CFE commitments help to decarbonize local grids and reveal the individual mechanisms behind this effect that are present across the scenario space.
+Afterwards, we explore scenario space further to answer the following questions:
+
+\begin{enumerate}[-]
+\item \cref{subsec:palette}: What if a wider palette of carbon-free technologies were available to participating buyers?
+\item \cref{subsec:location}: What if participating buyers are located in areas of the European electricity grid that differ significantly from the base scenario?
+\item \cref{subsec:time}: What are the implications if we move the timeframe ahead five years to 2030?
+\item Finally, in \cref{subsec:mechanisms}, we get a closer look at how 24/7 CFE commitments can help decarbonize local grids and reveal the individual mechanisms involved.
 \end{enumerate}
 
-In the \nameref{sec:discussion}, we summarise our findings for the four questions above and have a look beyond the focus of the model scenarios discussed in the main part of the paper by integrating observations from sensitivity analyses relating to the participation rates of electricity buyers and their diverse consumption profiles, providing an overarching look at the 24/7 procurement and impacts on the electrcity systems.
-
-Given the large scenario space, the manuscript presents results for selected scenario branches that generalise system impacts of 24/7 hourly clean electricity procurement.
-For interested reader, we provide results for the entire scenario space in a dashboard that is published online alongside this study, see \nameref{sec:code}.
+Given the large scenario space, the manuscript presents results for selected scenario branches that generalise system impacts of the 24/7~CFE procurement.
+For interested readers, we have published an online dashboard with results for the entire scenario space, see \nameref{sec:code}.
 
@@
 
-\begin{figure}
+\begin{figure}[H]
     \centering
-    \begin{subfigure}[t]{0.95\columnwidth}
+
+    \begin{subfigure}[t]{\columnwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}[t]{0.95\columnwidth}
+
+    \begin{subfigure}[t]{\columnwidth}
         \centering
@@
     \end{subfigure}
+
     \caption{
@@
         \label{fig:decarbonisation_story}
+
 \end{figure}

### 2023-10-06 manuscript/sections/introduction.tex
intro: contribution and prologue

@@
 \textbf{The key problem --} When \gls{ci} consumers purchase renewable credits, either via unbundled schemes or via bundled \gls{ppa}s, renewable energy supply is typically matched over a long period of time with buyers' energy demands.
-As an example, more than 400 members of the RE100 group\footnote{\url{https://www.there100.org/}} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
+As an example, more than 400 members of the RE100 group \cite{re100report-2020} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
 Even the \enquote{best case} of the 100\% annual matching commitments, where energy buyers sign \gls{ppa}s with renewable energy generators located within a local grid, has a major problem -- the temporal mismatch between renewable energy supply and electricity demand.
@@
 The list of entities that have committed to 24/7~CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}.
-In 2021, an international group of energy suppliers, buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact.\footnote{\url{https://gocarbonfree247.com/}}
+In 2021, an international group of energy suppliers, buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact \cite{gocarbonfree247}.
 With over 135 signatories, the group aims to \enquote{develop and scale high-impact technologies, energy policies, procurement practices, aand solutions to make 24/7 Carbon-Free Energy achievable for all}.
@@
 The first to incorporate it into the electricity system planning model were Xu et al.
-(Oct 2022) \cite{xu-247CFE-SSRN}.\footnote{A working paper updates a prior public technical report (Nov 2021, \cite{xu-247CFE-report}) investigating the system-level impacts of 24/7~CFE in two regions of the U.S.
--- California and PJM.}
+(2022) \cite{xu-247CFE-SSRN}.\footnote{A working paper updates a prior public technical report published in November 2021 investigating the system-level impacts of 24/7~CFE in two regions of the U.S.
+-- California and PJM \cite{xu-247CFE-report}.}
 The authors study the system-level impacts of 24/7~CFE procurement based on an example of California in the year 2030.
-In Nov 2022, IEA also released a model-based study on the 24/7~CFE, focusing on India and Indonesia \cite{ieaAdvancingDecarbonisationClean2022}.
+In November 2022, IEA also released a model-based study on the 24/7~CFE, focusing on India and Indonesia \cite{ieaAdvancingDecarbonisationClean2022}.
 In early 2023, Peninsula Clean Energy published an own white paper introducing their modeling tool---MATCH (Matching Around-the-Clock Hourly energy)---and the results of the modeling indicating feasibility of the company's \enquote{24/7 renewable energy by 2025} goal \cite{peninsula-report247}.
 
-The first studies indicate that 24/7 CFE matching results in emission reduction for both energy buyers and the entire energy system, and has a potential to create demand pull for new clean energy technologies.
-What has been missing is a comprehensive analysis of 24/7 procurement over multiple regions and years, since electricity system characteristics, National Climate and Energy Plans (\gls{necp}s), renewable resource quality, and the cost of clean energy vary significantly across regions and over time.
+The first studies indicate that voluntary 24/7~CFE commitments reduce the emissions of participating buyers as well as emissions in the electricity grids they operate.
+What has been missing is a comprehensive analysis of 24/7~CFE procurement over multiple regions and years, since electricity system characteristics, National Climate and Energy Plans (\gls{necp}s), renewable resource quality, and the cost of clean energy vary significantly across regions and over time.
 Furthermore, it is unclear whether decarbonisation effect of 24/7 CFE procurement remains relevant when electricity grids are progressively decarbonised, as is the case in many countries and jurisdictions, or if the 24/7~CFE procurement is only impactful in the early stages of the energy transition.
@@
 
-% would be good to generalize 
-as provided in this paper.
-
-In this study, we model 24/7~CFE procurement in Europe up to 2030. 
-We explore different designs, costs, benefits and impacts of the 24/7 approach, both for Google and for the power systems in which the data centres are located. 
-In sum, we want to find out:
-
-\begin{enumerate}
-    \item How can we achieve hourly clean energy matching? 
-    \item What is the 24/7~CFE cost premium versus the 100\% annual matching with renewables? 
-    \item To which extent can technologies, such as long-duration storage or new dispatchable clean technologies, help to achieve the 24/7~CFE goal? 
-    \item If many companies follow the 24/7~CFE approach, how does this effect the rest of the energy system?
-\end{enumerate}
+\textbf{Contribution --} The goal of this work is to systematically explore different designs, optimal procurement strategies, costs, benefits and impacts of the 24/7~CFE matching approach, both for participating buyers and for regions where voluntary procurement occurs.
+Our analysis focuses on four regions within the European energy system with unique characteristics, and we vary the analysis years to track the evolution of the energy system.
+Additionally, we examine the underlying mechanisms that drive the system-level reduction of \co emissions, and examine how they perform over time and across regions.
 
 % 7. **Prologue**
+
+The remainder of the paper is structured as follows: Section \cref{sec:methods} gives a brief summary of methodology, sources of model input data, and the experimental setup.
+The results are presented and discussed in Section \cref{sec:results} and put in perspective in Section \cref{sec:discussion}.
+The work is concluded in Section \cref{sec:conclusion}.

### 2023-10-08 manuscript/sections/methods.tex
methods: outline section

--- 2023-04-04 manuscript/sections/methods.tex
@@
-\textbf{Dummy methods - to refine}
+The modelling workflow is based on the PyPSA --- an open-source software framework for simulating and optimising modern energy systems \cite{brownPyPSAPythonPower2018}.
 
-Methodologically, our modelling workflow is based on the PyPSA (Python for Power System Analysis)\footnote{PyPSA is available at \url{https://github.com/PyPSA/PyPSA}}—an open-source software toolbox for simulating and optimising modern energy systems at high resolution maintained by TU Berlin \cite{Brown-PyPSA,HORSCH-PyPSAEUR}.
-The model developed for this study optimises investment and operational decisions to meet projected electricity demand for the consumers performing clean energy procurement, as well as the demand for other consumers in the European electricity system, while meeting all relevant engineering, reliability, and policy constraints.
-This project is also developed as open-source.\footnote{247-CFE code is available at  \url{https://github.com/PyPSA/247-cfe}}
+\textbf{Optimisation model --} The simulations were carried out with the modified version of the PyPSA-Eur model \cite{PyPSA-Eur-github}. 
+The objective of the model is to minimise the annualised system-wide costs of meeting electricity demand within the modelled system, while adhering to all relevant engineering, reliability, and policy constraints.
+The optimal solution of the model includes the location and capacity of new power generation and storage assets, as well as the hourly dispatch of all existing and new assets, including the linear optimal power flow on the transmission network for the planning year.
+This is standard for the PyPSA-Eur model \cite{horschPyPSAEurOpenOptimisation2018} and the long-term energy planning models of this class \cite{jenkinsGenX2022, howellsOSeMOSYSOpenSource2011}.
 
-In this study, we implement a set of new constraints to model a situation when a fraction of corporate and industry (C\&I) demand commit to the 24/7-CFE goal. 
-These constraints ensure that a portfolio of carbon-free generation located in the same market as the participating C\&I consumers covers their electricity demand profiles every hour of every day. 
-The mathematical implementation allows for examining a scenario space when different shares of demand pursue the 24/7 approach with varying thresholds for meeting the hourly clean energy requirement (e.g.
-90\%, 95\%, 100\%) using the definitions provided in Google's paper on methodologies and metrics \cite{Google-methods}.
+\textbf{Clean energy procurement --} We introduce a set of new constraints to model the situation when a fraction of corporate and industry demand commits to voluntary clean energy procurement.
+%continue here
 
-For comparison, we also model a benchmark scenario where the C\&I consumers meet their annual energy demand on a volumetric basis with renewable energy procurement (the 100\% annual matching), as well as the scenario with no voluntary procurement of carbon-free energy.
+The 24/7~CFE procurement framework is based on the methodologies and metrics paper by Google (2021) \cite{google-methodologies}.
+The framework considers various \gls{cfe} supply options, including procured generation resources, operation of storage assets, and electricity imports from the local grid. 
+The framework also allows for controlling the quality score of the 24/7~CFE procurement by setting the threshold for the minimum share of hours when the hourly \gls{cfe} supply meets the hourly electricity demand.
+The complete mathematical formulation of the 24/7~CFE procurement is provided in the \nameref{sec:si}.
 
+\textbf{Model scope --} text
+% European electricity system
+% Only electricity sector
+% 4 regions
+% etc.
+
+\textbf{Model inputs --} text
+% Technology assumptions
+
+\textbf{Procurement strategies in scope --} We model and compare two procurement strategies:
+
+\begin{itemize}[-]
+    \item 100\% annual matching, where participating buyers meet their annual energy demand on volumetric basis with additional renewable energy procurement;
+    \item 24/7 hourly matching, where participating buyers optimise their investment and operational decisions mixing \gls{cfe}procurement of additional resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality score;
+    \item For benchmarking, we also model a reference case, where participating buyers have no voluntary environmental commitments and get all their electricity from the local grid.
+\end{itemize}
+
+We setup the study design so that both procurement strategies are modelled under the same conditions.
+In both cases (i) procurement is possible with generators from the same bidding zone only (i.e., we model the \enquote{best case} of the annual matching strategy); (ii) the same set of consumers participate; (iii) the same set of constraints is applied to the rest of the electricity system.
+
+\textbf{Carbon-free energy technologies in scope --} text
+
+\textbf{Other scenarios --}
 Finally, we model scenarios where C\&I consumers are located in different national markets across Europe. 
 Thus, we aim to generalise the impacts of 24/7-CFE procurement, accounting for the different patterns of electricity demand, weather, availability of renewable resources, existing electricity generation capacity, and national climate- and energy policies, among other factors.
+
+\subsection{Scenario space}
+\label{subsec:scenarios}

### 2023-10-09 manuscript/sections/methods.tex
methods: main part of the section

@@
 \textbf{Optimisation model --} The simulations were carried out with the modified version of the PyPSA-Eur model \cite{PyPSA-Eur-github}. 
-The objective of the model is to minimise the annualised system-wide costs of meeting electricity demand within the modelled system, while adhering to all relevant engineering, reliability, and policy constraints.
+The objective of the model is to minimise the annualised system-wide costs of meeting energy demand within the modelled system, while adhering to all relevant engineering, reliability, and policy constraints.
 The optimal solution of the model includes the location and capacity of new power generation and storage assets, as well as the hourly dispatch of all existing and new assets, including the linear optimal power flow on the transmission network for the planning year.
@@
 
-\textbf{Clean energy procurement --} We introduce a set of new constraints to model the situation when a fraction of corporate and industry demand commits to voluntary clean energy procurement.
-%continue here
+\textbf{Clean energy procurement --} We introduce new model components (parameters, variables, constraints) to model voluntary clean energy procurement.
+By incorporating these into the mathematical problem, we model a situation when a fraction of electricity demand in a particular bidding zone is committed to procuring additional clean energy with a desired strategy.
+The fraction is set at 10\% of the total \gls{ci} electricity demand in a particular bidding zone, unless otherwise stated (hereinafter referred to as \enquote{participating consumers}).
+Accordingly, the model co-optimises the procurement and operational decisions of the participating consumers to meet their electricity demand in accordance with the procurement strategy they have chosen.
+The mathematical formulation of the clean energy procurement model is provided in the \nameref{sec:si}.
 
 The 24/7~CFE procurement framework is based on the methodologies and metrics paper by Google (2021) \cite{google-methodologies}.
-The framework considers various \gls{cfe} supply options, including procured generation resources, operation of storage assets, and electricity imports from the local grid. 
-The framework also allows for controlling the quality score of the 24/7~CFE procurement by setting the threshold for the minimum share of hours when the hourly \gls{cfe} supply meets the hourly electricity demand.
-The complete mathematical formulation of the 24/7~CFE procurement is provided in the \nameref{sec:si}.
+The framework considers various \gls{cfe} supply options for the participating consumers, including procurement of own generation resources and storage assets, and electricity imports from the local grid.
+The framework also allows for controlling \textit{the quality score} of the 24/7~CFE procurement by setting the threshold for the minimum share of hours when the hourly \gls{cfe} supply meets the hourly electricity demand.
 
-\textbf{Model scope --} text
-% European electricity system
-% Only electricity sector
-% 4 regions
-% etc.
+\textbf{Model scope --} Geographically, the model encompasses the entire \gls{entsoe} area, which covers the entire European electricity system.\footnote{Islands that are not connected to the main European system, such as Malta, Crete and Cyprus, are excluded from the model.}
+In this study, electricity demand, supply and power transmission infrastructure\footnote{Alternating current lines at and above 220kV voltage level and all high voltage direct current lines.} are clustered to 37 individual bidding zones \cite{PyPSAEur-docs-spatialresolution}.
+Thus, each zone represents a country; some countries straddling different synchronous areas are split into individual bidding zones, such as DK1 (West) and DK2 (East).
+The participating consumers can be located in either of the four selected zones: Ireland, Denmark (zone DK1), Germany, or Poland.
+The comparison of results across these zones allows us to generalize the implications of of voluntary clean energy procurement, taking into account factors such as electricity demand, weather, availability of renewable resources, existing electricity generation capacity mix, and national energy policies, among other factors.
 
-\textbf{Model inputs --} text
-% Technology assumptions
+We model two individual years: 2025 and 2030. 
+From a modelling perspective, a five-year step changes many system parameters.
+In particular, technology costs decline as a result of economies of scale and incremental innovation, \gls{necp}s become tighter, and some legacy power plants go out of business.
+The problem is solved with a temporal resolution of 2920 snapshots, representing a 3-hourly average of the hourly time-series data.
 
@@
 \begin{itemize}[-]
-    \item 100\% annual matching, where participating buyers meet their annual energy demand on volumetric basis with additional renewable energy procurement;
-    \item 24/7 hourly matching, where participating buyers optimise their investment and operational decisions mixing \gls{cfe}procurement of additional resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality score;
-    \item For benchmarking, we also model a reference case, where participating buyers have no voluntary environmental commitments and get all their electricity from the local grid.
+    \item \textit{100\% annual matching}: participating buyers meet their annual energy demand on volumetric basis with additional renewable energy procurement;
+    \item \textit{24/7 hourly matching}: participating buyers optimise their investment and operational decisions mixing procurement of additional generation and storage resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality score;
+    \item For benchmarking, we also model \textit{a reference case}: participating buyers have no voluntary environmental commitments and get all their electricity from the local grid.
 \end{itemize}
@@
 
-\textbf{Carbon-free energy technologies in scope --} text
+\textbf{Carbon-free energy technologies in scope --} Depending on the scenario, participating consumers can choose from a variety of energy technologies available on the European market.
+By grouping technologies according to their maturity levels and availability on the market, we formulate three scenarios:
 
-\textbf{Other scenarios --}
-Finally, we model scenarios where C\&I consumers are located in different national markets across Europe. 
-Thus, we aim to generalise the impacts of 24/7-CFE procurement, accounting for the different patterns of electricity demand, weather, availability of renewable resources, existing electricity generation capacity, and national climate- and energy policies, among other factors.
+\begin{itemize}[-]
+    \item \textit{Palette 1} -- technologies that are commercially available today: onshore wind, utility scale solar photovoltaics (\gls{PV}), and battery storage;
+    \item \textit{Palette 2} -- all above plus a long-duration energy storage (\gls{ldes}) that is expected to be commercially available in the near future; 
+    \item \textit{Palette 3} -- all above plus promising advanced technologies that are in prototype stage today, but are expected to be commercially available in the future: Allam cycle power plant with \gls{ccs}\footnote{Allam cycle is a natural gas power plant with up to 100\% of carbon capture and sequestration}, and advanced dispatchable generators---a stand-in for clean firm technologies, such as advanced geothermal (closed-loop) or advanced nuclear systems.
+\end{itemize}
 
-\subsection{Scenario space}
-\label{subsec:scenarios}
+\textbf{Technology assumptions --}
+
+Cost and other assumptions for energy technologies available for participating consumers were taken primarily from the Danish Energy Agency \cite{DEA-technologydata} for the respective years and are provided in Table S1.
+For a full list of technology assumptions, see the GitHub repository [TODO]. 
+For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion. 
+Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience. 
+We use the cost assumptions from the available literature and own indicative assumptions (see Table S1).
+
+\textbf{Other assumptions --}
+
+In all the modelled countries, renewable generation must meet the political targets as defined in the NECPs or by more recent national policy targets (such as the Easter
+package in Germany), see Table 1.

### 2023-10-10 manuscript/manuscript.tex
references: solve URL brake issue with xurl
intro: outline section
intro: complete section
manuscript: coordinate all chapters, complete methods

@@
 \usepackage[version=4]{mhchem}       % Provides typesetting for chemical equations
+\usepackage{xurl} 				     % Allows line breaks in URLs
 \usepackage[colorlinks]{hyperref}    % Creates hyperlinks in the document
@@
 \usepackage{siunitx}                 % Provides consistent formatting for units and numbers
+\usepackage{csquotes} 				 % For handling inline and display quotations
 \usepackage[acronym, automake, nonumberlist]{glossaries-extra}
@@
 % Proper nouns
-\newacronym{EU}{EU}{European Union}
+\newacronym{eu}{EU}{European Union}
 \newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
@@
 \newacronym{cfd}{CfD}{Contract for Difference}
+\newacronym{go}{GO}{Guarantees of Origin}
+\newacronym{rec}{REC}{Renewable Energy Certificate}
 
@@
 \newacronym{ci}{C\&I}{Corporate and Industry (sectors)}
+\newacronym{ngo}{NGO}{Non-Governmental Organization}
 
@@
 
-	\title{Navigating to a greener Europe with 24/7 hourly clean electricity procurement}
+	\title{Navigating to a greener Europe with 24/7 hourly carbon-free electricity procurement}
 
@@
 
-\section{Methods}
+\section{Methods and experimental design}
 \label{sec:methods}
 \input{sections/methods.tex}
-
-\newpage
 
@@
 
+This project is also developed as open-source. \url{https://github.com/PyPSA/247-cfe}
+
 The data and code to reproduce the experiments is available at \href{https://github.com/repository}{GITHUB}.
@@
 
-\section{Supplementary Information}
+\section*{Supplementary Information}
 \label{sec:si}
 
-\input{sections/supplementary.tex}
+\section{Technology assumptions}
+\label{sec:si_1}
+\input{sections/supplementary_1.tex}
 
-\addcontentsline{toc}{section}{Supplementary References}
-\renewcommand{\ttdefault}{\sfdefault}
-\bibliographyS{references}
+\section{Background system assumptions}
+\label{sec:si_2}
+\input{sections/supplementary_2.tex}
+
+\section{Mathematical formulation of clean energy procurement}
+\label{sec:si_3}
+\input{sections/supplementary_3.tex}
+
+% \addcontentsline{toc}{section}{Supplementary References}
+% \renewcommand{\ttdefault}{\sfdefault}
+% \bibliographyS{paper_247CFE}
 

### 2023-10-10 manuscript/sections/introduction.tex
manuscript: coordinate all chapters, complete methods

@@
 The European Union (\gls{eu}) has committed to achieve net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}.
-National climate initiatives span the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to \enquote{have \co emissions peak before 2030 and achieve carbon neutrality before 2060} \cite{ChinaNetZero-IEA}.
+National climate initiatives span the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have \co emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.
 
@@
 
-The remainder of the paper is structured as follows: Section \cref{sec:methods} gives a brief summary of methodology, sources of model input data, and the experimental setup.
-The results are presented and discussed in Section \cref{sec:results} and put in perspective in Section \cref{sec:discussion}.
-The work is concluded in Section \cref{sec:conclusion}.
+The remainder of the paper is structured as follows: \cref{sec:methods} gives a brief summary of methodology, sources of model input data, and the experimental setup. 
+The results are presented and discussed in \cref{sec:results} and put in perspective in \cref{sec:discussion}. 
+The work is concluded in \cref{sec:conclusion}. 
+\nameref{sec:si} provides further details about model assumptions, background energy system parametrisation, and the clean energy procurement mathematical model.

### 2023-10-10 manuscript/sections/methods.tex
manuscript: coordinate all chapters, complete methods

@@
 Accordingly, the model co-optimises the procurement and operational decisions of the participating consumers to meet their electricity demand in accordance with the procurement strategy they have chosen.
-The mathematical formulation of the clean energy procurement model is provided in the \nameref{sec:si}.
+The mathematical formulation of the clean energy procurement model is provided in supplementary material [\labelcref{sec:si_3}].
 
@@
 
-\textbf{Technology assumptions --}
-
-Cost and other assumptions for energy technologies available for participating consumers were taken primarily from the Danish Energy Agency \cite{DEA-technologydata} for the respective years and are provided in Table S1.
-For a full list of technology assumptions, see the GitHub repository [TODO]. 
+\textbf{Technology assumptions --} Cost and other assumptions for energy technologies available for participating consumers were collected primarily from the Danish Energy Agency \cite{DEA-technologydata} for the respective years and are provided in Table S1.
 For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion. 
 Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience. 
-We use the cost assumptions from the available literature and own indicative assumptions (see Table S1).
+We use the cost estimates from the available literature and own indicative assumptions (see Table S1).
 
-\textbf{Other assumptions --}
-
-In all the modelled countries, renewable generation must meet the political targets as defined in the NECPs or by more recent national policy targets (such as the Easter
-package in Germany), see Table 1.
+\textbf{Other assumptions --} Other model inputs and key background system assumptions are provided in [\labelcref{sec:si_2}].
+For a full list of technology assumptions, see the GitHub repository \cite{github-247CFEpaper}.

### 2023-10-10 manuscript/sections/results.tex
manuscript: coordinate all chapters, complete methods

@@
-% TODO refine and shorten the results section
-% Maybe move some of the graphs to the annex
-% and all other graphs to a dashboard
-
 Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
-From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage (also known as Scope 2 emissions).
+From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
 From a system perspective, we analyze how voluntary clean energy procurement impacts \co emissions in the region and the \enquote{demand pull} for advanced energy technologies.
@@
 In this section, we examine the results and implications of these procurement strategies for 2030.
-Ultimately, this will allow us to better understand the long-term effects and the potential evolution of clean energy procurement in Europe, as companies continue to adapt their procurement strategies.
-
-A five-year step to 2030 changes many system parameters from a modelling perspective.
-In partcular, technology costs decline as a result of economies of scale and incremental innovation, energy- and climate policies become tighter, and some legacy power plants go out of business.
-The two key trends of advancing five years forward are cleaner electricity grids and lower costs for energy technologies.
+To recall the \nameref{sec:methods} section, the key trends of advancing five years forward are cleaner electricity grids and lower costs for energy technologies.
 
@@
 
-\begin{figure}[H]
+\begin{figure}
     \centering

### 2023-10-10 manuscript/sections/supplementary_2.tex
manuscript: coordinate all chapters, complete methods

%S2: Background system assumptions
In all the modelled countries, renewable generation must meet the political targets as defined in the NECPs or by more recent national policy targets (such as the Easter package in Germany), see Table 1.

### 2023-10-10 manuscript/sections/supplementary_3.tex
manuscript: coordinate all chapters, complete methods

%S3: Mathematical formulation of clean energy procurement
\cite{srivastavCarbonCaptureUtilisation} %test supplementary references

### 2023-10-10 manuscript/sections/methods.tex
SI: complete S1

@@
 Accordingly, the model co-optimises the procurement and operational decisions of the participating consumers to meet their electricity demand in accordance with the procurement strategy they have chosen.
-The mathematical formulation of the clean energy procurement model is provided in supplementary material [\labelcref{sec:si_3}].
+The mathematical formulation of the clean energy procurement strategies is provided in the supplementary material [\labelcref{sec:si_3}].
 
@@
 
-We setup the study design so that both procurement strategies are modelled under the same conditions.
+We setup the study design so that the procurement strategies are modelled under the same conditions.
 In both cases (i) procurement is possible with generators from the same bidding zone only (i.e., we model the \enquote{best case} of the annual matching strategy); (ii) the same set of consumers participate; (iii) the same set of constraints is applied to the rest of the electricity system.
@@
     \item \textit{Palette 2} -- all above plus a long-duration energy storage (\gls{ldes}) that is expected to be commercially available in the near future; 
-    \item \textit{Palette 3} -- all above plus promising advanced technologies that are in prototype stage today, but are expected to be commercially available in the future: Allam cycle power plant with \gls{ccs}\footnote{Allam cycle is a natural gas power plant with up to 100\% of carbon capture and sequestration}, and advanced dispatchable generators---a stand-in for clean firm technologies, such as advanced geothermal (closed-loop) or advanced nuclear systems.
+    \item \textit{Palette 3} -- all above plus promising advanced technologies that are in prototype stage today, but are expected to be commercially available in the future: Allam cycle power plant with \gls{ccs}\footnote{Allam cycle is a natural gas power plant with up to 100\% of carbon capture and sequestration}, and advanced dispatchable generators -- a stand-in for clean firm technologies, such as advanced geothermal or advanced nuclear systems.
 \end{itemize}
@@
 For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion. 
-Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience. 
-We use the cost estimates from the available literature and own indicative assumptions (see Table S1).
+Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, use own indicative assumptions.
 

### 2023-10-10 manuscript/sections/supplementary_1.tex
SI: complete S1

%S1: Technology assumptions
Cost and other assumptions for energy technologies available for participating consumers were collected primarily from the Danish Energy Agency \cite{DEA-technologydata}. These assumptions are listed in \cref{tab:tech_costs}. 
A full list of technology assumptions, including the data for energy technologies in the background energy system, is available via the reproducible scientific workflow in the GitHub repository \cite{github-247CFEpaper}.

\begin{table*}[]
    \centering
    \resizebox{0.95\textwidth}{!}{%
        \begin{tabular}{lccccccc}
            \hline\hline
            \textbf{Technology} &
            \textbf{Year} &
            \textbf{\begin{tabular}[c]{@{}c@{}}CAPEX\\ (overnight cost)\end{tabular}} &
            \textbf{\begin{tabular}[c]{@{}c@{}}FOM\\ {[}\%/year{]}\end{tabular}} &
            \textbf{\begin{tabular}[c]{@{}c@{}}VOM\\ {[}Eur/MWh{]}\end{tabular}} &
            \textbf{\begin{tabular}[c]{@{}c@{}}Efficiency\\ {[}per unit{]}\end{tabular}} &
            \textbf{\begin{tabular}[c]{@{}c@{}}Lifetime\\ {[}years{]}\end{tabular}} &
            \textbf{Source} \\ \hline\hline
            Utility solar PV & 2025 & 612 \officialeuro/kW & 1.7 & 0.01 & - & 37.5 & \cite{DEA-technologydata} \\  
            & 2030 & 492 \officialeuro/kW & 2.0 & 0.01 & - & 40.0 & \cite{DEA-technologydata}  \\ \hline
            Onshore wind & 2025 & 1077 \officialeuro/kW & 1.2 & 0.015 & - & 28.5 & \cite{DEA-technologydata} \\  
            & 2030 & 1035 \officialeuro/kW & 1.2 & 0.015 & - & 30 & \cite{DEA-technologydata} \\ \hline
            Battery storage & 2025 & 187 \officialeuro/kWh & - & - & - & 22.5 & \cite{DEA-technologydata}  \\  
            & 2030 & 142 \officialeuro/kWh & - & - & - & 25 & \cite{DEA-technologydata} \\ \hline
            Battery inverter & 2025 & 215 \officialeuro/kW & 0.3 & - & 0.96 & 10 & \cite{DEA-technologydata} \\  
            & 2030 & 160 \officialeuro/kW & 0.3 & - & 0.96 & 10 & \cite{DEA-technologydata} \\ \hline
            Hydrogen storage$^1$ & 2025 & 2.5 \officialeuro/kWh$_{\text{H}_2}$ & - & - & - & 100 & \cite{DEA-technologydata}  \\  
            & 2030 & 2.0 \officialeuro/kWh$_{\text{H}_2}$ & - & - & - & 100 & \cite{DEA-technologydata} \\ \hline
            Hydrogen electrolysis & 2025 & 550 \officialeuro/kW$_{\text{el}}$ & 2.0 & - & 0.67 & 27.5 & \cite{DEA-technologydata} \\
            & 2030 & 450 \officialeuro/kW$_{\text{el}}$ & 2.0 & - & 0.68 & 30 & \cite{DEA-technologydata} \\ \hline
            Hydrogen fuel cell & 2025 & 1200 \officialeuro/kW  & 5.0 & - & 0.50 & 10.0 & \cite{DEA-technologydata} \\ 
            & 2030 & 1100 \officialeuro/kW & 5.0 & - & 0.50 & 10.0 & \cite{DEA-technologydata} \\ \hline
            Allam cycle generator$^2$ & 2025 & 2760 \officialeuro/kW  & 14.8 & 3.2 & 0.54 & 30 & \cite{navigant-report, NetZeroAmerica-report} \\ 
            & 2030 & 2600 \officialeuro/kW & 14.8 & 3.2 & 0.54 & 30 & \cite{navigant-report, NetZeroAmerica-report} \\ \hline
            Clean firm generator$^3$ & 2025 & 10000 \officialeuro/kW & 0 & 0 & 1.00 & 30.0 & [-]\\ 
            & 2030 & 10000 \officialeuro/kW & 0 & 0 & 1.00 & 30.0 & [-]\\ \hline \hline
        \end{tabular}%
    }
\begin{tablenotes}
    {\footnotesize
    \item[] Notes: All costs are in 2020 euros; $^1$assumed to be underground hydrogen storage in salt caverns; $^2$costs also include estimate of 40 \officialeuro/t\co for carbon transport and sequestration; $^3$a stand-in for clean dispatchable technologies, such as advanced geothermal or advanced nuclear systems; own indicative assumptions. \item[] CAPEX = capital expenditure; FOM = fixed operations and maintenance costs; VOM = variable operations and maintenance costs.
    }
\end{tablenotes}
    \vspace{0.2cm}
    \caption{Technology assumptions.}
    \label{tab:tech_costs}
\end{table*}

### 2023-10-10 manuscript/sections/results.tex
results: refine highlights for clarity

@@
 
-\vspace{10pt}
 \begin{res}
-    24/7 carbon-free electricity (CFE) procurement can eliminate carbon emissiosns of a buyer's electricity consumption and helps to decarbonise the whole electricity system.
+    Through 24/7 CFE procurement, participating consumers can eliminate carbon emissions associated with their electricity consumption and help to decarbonise the entire electricity system.
 \end{res}
 
-\vspace{5pt}
 \begin{res}
-    90\%--95\% 24/7 CFE targets have only a small cost premium over 100\% annual renewable matching. 100\% 24/7 CFE can be achieved with solar, wind and battery storage, but at a high cost premium.
+    90\%--95\% 24/7 CFE targets have only a small cost premium over 100\% annual renewable matching.
+100\%~CFE target can be achieved with solar PV, wind and battery storage, but at a high cost premium for participating consumers.
 \end{res}
 
+%move this up
 The base scenario reflects a case when \textbf{10\%} (on volumetric basis) of \gls{ci} consumers in \textbf{Ireland} in \textbf{2025} voluntrary commits to 24/7 clean electricity procurement goal.
@@
 \cref{fig:10-2025-IE-p1-used} shows the fraction of the fraction of hourly demand met with carbon-free electricity depending on the procurement policy that \gls{ci} consumers follow.
-We contrast two main cases, one where participating consumers commit to 100\% annual renewable matching policy (100\% RES) and another case where the consumers commit to 24/7 hourly matching policy with various \gls{cfe} scores in a range from 80\% to 100\%.
+We contrast two main cases, one where participating consumers commit to 100\% annual renewable matching policy (100\% RES) and another case where the consumers commit to 24/7 hourly matching policy with various \gls{cfe} targets in a range from 80\% to 100\%.
 A \textit{reference case} depicts a case when the consumers cover their load purely with grid purchases without any policy regarding the origin of electricity.
@@
 
-\vspace{10pt}
 \begin{res}
-    24/7 CFE procurement triggers investment in new technologies the system will need later: long-duration storage and advanced clean firm generators.
+    24/7 CFE procurement creates an early market for advanced energy technologies the system will need later: long-duration energy storage and clean firm generators.
 \end{res}
 
-\vspace*{5pt}
 \begin{res}
-    High targets for 24/7 CFE procurement could have a much smaller cost premium if long duration energy storage or advanced clean firm technologies are available for a commercial scale up.
+    The cost premium of 24/7 procurement with high CFE targets may substantially decrease if advanced energy technologies available for commercial scale-up. 
 \end{res}
@@
 
-\vspace{10pt}
 \begin{res}
-    Each region of the European electricity system has unique characteristics, such as renewable resources, national policies, degree of interconnection, etc.
-    Despite these differences, the model results for 24/7 clean energy procurement show similar trends. 
+    Despite the inherent variability in regional charac\-teristics---ranging from renewable resources and national policies to degrees of interconnection---the model shows a consistent effects of 24/7 clean energy procurement on both participating buyers and overarching system-level impacts across all analyzed regions.
 \end{res}
@@
 
-\vspace{10pt}
 \begin{res}
-    In 2030, participating consumers benefit from decreasing costs of clean technologies and cleaner state of the electricity grids.
+    Over time, participating consumers reap benefits from the gradual decline in clean technology costs and a progressively cleaner state of the electricity grids, enhancing the affordability of 24/7 CFE procurement.
 \end{res}
 
-\vspace{5pt}
 \begin{res}
-    Voluntary commitments to clean electricity procurement bring system value even in
-    cleaner grids. Similarly to the base scenario, 24/7 hourly matching results in deeper decarbonisation than 100\% annual renewable matching if CFE targets are above certain treshhold.
+    Voluntary commitments to 24/7 CFE procurement retain their significance in enhancing system value, even as grids become cleaner.
+Analogous to the base scenario, hourly matching commitments facilitate a more profound decarbonisation compared to 100\% annual renewable matching, provided that CFE targets surpass a particular threshold.
 \end{res}
@@
 
-\subsection{Exploring mechanisms: how 24/7 CFE procurement decarbonises local grids}
+\subsection{Unpacking 24/7 CFE procurement's role in grid decarbonisation}
 \label{subsec:mechanisms}
 
-\vspace{10pt}
 \begin{res}
-    24/7 CFE procurement reduces system-level \co \newline
-    emissions through "profile" and "volume" mechanisms. 
+    24/7 CFE procurement mitigates system-level \co \newline 
+    emissions through two distinct mechanisms: "profile" and "volume".
+The mechanisms origin from distinct aspects of the interplay between the 24/7 CFE procurement and the background electricity grids.
 \end{res}
 
-\vspace{5pt}
 \begin{res}
-    The difference in impact that 24/7 CFE procurement and 100\% annual matching policies have on system decarbonisation amplifies with a cleaner state of local grids. %TODO REFINE
+    The disparity in decarbonisation outcomes between 24/7 CFE hourly and 100\% annual renewable matching policies becomes increasingly pronounced as local grids transition to cleaner states.
+This phenomenon underscores the effectiveness of 24/7 CFE procurement in supporting system decarbonisation in the context of evolving national energy and climate policies.
 \end{res}
@@
 Second, a \textit{volume} mechanism: even the cost-optimal procurement strategy for 24/7 hourly matching might include some amount of excess clean energy.
-If total \gls{cfe} generation of assets procured by 24/7 participants exceeds demand in a given hour and region, the “excess CFE” is not counted toward a CFE score; however, it is clean electricity that can potentially be stored (using batteries or LDES), or sold to the regional grid.
+If total \gls{cfe} generation of assets procured by 24/7 participants exceeds demand in a given hour and region, the “excess CFE” is not counted toward a CFE target; however, it is clean electricity that can potentially be stored (using batteries or LDES), or sold to the regional grid.
 As for the latter, "excess CFE" might displace emitting grid generators or reduce the need to import electricity from neighbouring areas.
@@
 It can be seen in \cref{fig:10-profile-volume.pdf} that the overall impact of 24/7 CFE procurement is proportional to how clean the background grid on average is.
-Thus, the largest impact is at 571.6~kgCO$_2$/a·MWh$^{-1}$ takes place in the Poland 2025 zone, and the lowest one is 3.7~kgCO$_2$/a·MWh$^{-1}$ in Denmark 2030 (NB 10\% of \gls{ci} sector participation rate with CFE 100\% score).
+Thus, the largest impact is at 571.6~kgCO$_2$/a·MWh$^{-1}$ takes place in the Poland 2025 zone, and the lowest one is 3.7~kgCO$_2$/a·MWh$^{-1}$ in Denmark 2030 (NB 10\% of \gls{ci} sector participation rate with CFE 100\% target).
 It is noteworthy that from 2025 to 2030, the decarbonisation effect of voluntary clean electricity procurement decreases over time in all zones since electricity grids become cleaner as a result of national climate policy programs and decomissioning of emitting power plants.

### 2023-10-11 manuscript/sections/results.tex
results: merge figures, finalise text, align captures

@@
 
-Our experimental setup incorporates a large scenario space so that we can generalize our results void of individual assumptions.
+Our experimental setup incorporates a wide range of scenarios, allowing us to generalise our results beyond individual assumptions.
 For convenience, we start with a \textit{base scenario} presented in \cref{subsec:base}.
-Afterwards, we explore scenario space further to answer the following questions:
+The base scenario reflects a case when 10\% (on volumetric basis) of \gls{ci} consumers in \textit{Ireland} in \textit{2025} are committed to procuring additional clean energy with a desired strategy.
+The participating consumers can attain the 24/7~CFE procurement targets by co-optimizing local procurement using mature technologies, designated as \textit{palette~1}, and by importing electricity from the local grid.
+
+Afterward, we delve deeper into the scenario space, altering highlighted parameters to explore various alternatives and address the following questions:
 
@@
 
-Given the large scenario space, the manuscript presents results for selected scenario branches that generalise system impacts of the 24/7~CFE procurement.
-For interested readers, we have published an online dashboard with results for the entire scenario space, see \nameref{sec:code}.
+Considering the large scenario space, this work presents results for a selection of scenario branches that generalise the system impacts of 24/7 CFE procurements.
+For interested readers, we publish an online dashboard with results for the entire scenario space, see \nameref{sec:code}.
 
@@
 
-%move this up
-The base scenario reflects a case when \textbf{10\%} (on volumetric basis) of \gls{ci} consumers in \textbf{Ireland} in \textbf{2025} voluntrary commits to 24/7 clean electricity procurement goal.
-This assumption yields 220~MW of \textbf{base load} that has to be matched with clean electricity. 
-The participating consumers can achieve the \gls{cfe} procurement goal by co-optimizing local procurement with of mature technologies (designated as \textbf{palette~1}), i.e., technologies available on a market for commercial use as of now, such as onshore wind, utility-scale solar PV, and battery storage, as well as by importing electricity from the local grid.
-
 %some parts of this paragraph may go to methods
-\cref{fig:10-2025-IE-p1-used} shows the fraction of the fraction of hourly demand met with carbon-free electricity depending on the procurement policy that \gls{ci} consumers follow.
-We contrast two main cases, one where participating consumers commit to 100\% annual renewable matching policy (100\% RES) and another case where the consumers commit to 24/7 hourly matching policy with various \gls{cfe} targets in a range from 80\% to 100\%.
-A \textit{reference case} depicts a case when the consumers cover their load purely with grid purchases without any policy regarding the origin of electricity.
+\cref{fig:10-2025-IE-p1-used} shows the fraction of the fraction of hourly demand met with carbon-free electricity depending on the procurement policy that participating consumers follow.
+We contrast two main cases, one where participating consumers commit to 100\% annual renewable matching policy (hereinafter -- \enquote{100\% RES}) and another case where the consumers commit to 24/7~CFE hourly matching policy (hereinafter -- \enquote{24/7~CFE}) with various \gls{cfe} targets in a range from 80\% to 100\%.
+In the \textit{reference case}, participating consumers cover their load purely with grid purchases without any policy regarding the origin of electricity.
 
@@
 
-In the reference case, where \gls{ci} consumers do not procure any resources, relying on grid purchases, only 54\% of demand is met with clean electricity.
+In the reference case, only 54\% of demand is met with \gls{cfe} electricity.
 100\% RES---the best case for the annual renewable matching policy---results in 83\% fraction. 
-Consequently, 24/7~CFE targets beyond 85\% yield higher share of hourly demand met with clean electricity than 100\% annual matching policy.
+Consequently, CFE targets beyond 85\% yield higher share of hourly demand met with \gls{cfe} than 100\%~RES.
+Another notable trend in \cref{fig:10-2025-IE-p1-used} is that participanting consumers rely more on procured resources and less on grid imports with higher CFE targets.
+When targets approach 100\%, participanting consumers cannot rely on electricity imports from the grid, since the grid supply mix contains some carbon content in almost all hours.
 
-Another notable trend in \cref{fig:10-2025-IE-p1-used} is that \gls{ci} participants rely more on procured resources and less on grid imports with higher CFE target.
-When CFE target approaches 100\%, \gls{ci} consumers cannot rely on electricity imports from the grid, since the grid supply mix contains some carbon content in almost all hours.
+\cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of participating consumers.
+Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case.
+If participating consumers follow 100\%~RES policy, the emission rate is reduced to 60~g\co/kWh.
+This yields a considerable emission rate reduction compared to the reference case.
+The 24/7~CFE procurement with targets above 85\% helps the participating consumers to reduce emissions further beyond the treshhold set by the 100\%~RES. 
+At the 100\% CFE target, participating consumers attain a zero emission rate associated with their electricity consumption, as they perfectly align demand and \gls{cfe} supply on an hourly basis.
 
-\cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of \gls{ci} consumers.
-Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case. 
-If \gls{ci} consumers follow 100\% annual matching policy and procure enough renewable energy, the emission rate is reduced to 60~g\co/kWh.
-This yields a considerable emission rate reduction compared to the reference case.
-The 24/7 procurement policy with CFE targets above 85\% helps the participating consumers to reduce emissions further beyond the treshhold set by the 100\% annual matching with renewable energy. 
-At the 100\% CFE target, participating consumers attain a zero emission rate associated with their electricity consumption, as they perfectly align demand and clean generation on an hourly basis.
+Voluntary procurement of clean electricity also helps decarbonise electricity system as a whole.
+We explore this effect by plotting \co emissions in the local region of the participating consumers, i.e. Ireland (\cref{fig:10-2025-IE-p1-zone_emissions}).
+Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2~Mt\co.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021.
+A strong decreasing trend is expected, since Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
+The modelling results indicate that a commitment to 100\% 24/7~CFE in 2025 from 10\% of the \gls{ci} electricity demand could yield a reduction in Irish emissions by 0.6~MtCO$_2$ annually, in contrast to a scenario absent voluntary procurement.
+This reduction equates to 14\% of the total emissions from the Irish power sector.
+100\%~RES can also facilitate system-level \co emissions reductions (as depicted by the left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, 24/7~CFE attains superior emissions reductions when the CFE target surpasses 85\%.
 
@@
     \centering
+    \begin{subfigure}[t]{0.95\columnwidth}
+        \centering
+        \caption{Average emissions rate of participating consumers.}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \caption{Average emissions rate of participating consumers.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \caption{Average emissions rate of participating consumers.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \caption{Average emissions rate of participating consumers.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \caption{Average emissions rate of participating consumers.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \caption{Average emissions rate of participating consumers.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \caption{Average emissions rate of participating consumers.}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
+    \caption{Average emissions rate of participating consumers.}
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
@@
         \label{fig:10-2025-IE-p1-ci_emisrate}
-\end{figure}
-
-Voluntary procurement of clean electricity also helps decarbonise electricity system as a whole.
-We explore this effect by plotting \co emissions in the local region of the participating consumers, i.e. Ireland.
-Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2~Mt\co -- see a reference case in \cref{fig:10-2025-IE-p1-zone_emissions}.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021.
-A strong decreasing trend is expected, since Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
-The modelling results show that if only 10\% of \gls{ci} electricity demand commits to 100\% 24/7 carbon-free electricity in 2025, it would reduce Irish emissions by 0.6~Mt\co per year compared to the scenario with no voluntary procurement.
-This reduction is equivalent to 14\% of Irish power sector emissions.
-100\% annual renewable matching policy can also deliver system-level \co emissions reductions (left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, beyond 85\% CFE target, 24/7 hourly matching achieves greater emissions reductions than 100\% annual mathing.
-
-\begin{figure}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.95\columnwidth}
         \centering
+        \vspace{-0.2cm}
+        \caption{\co emissions in the local region (Ireland).}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \caption{\co emissions in the local region (Ireland).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \caption{\co emissions in the local region (Ireland).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \caption{\co emissions in the local region (Ireland).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \caption{\co emissions in the local region (Ireland).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \caption{\co emissions in the local region (Ireland).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \caption{\co emissions in the local region (Ireland).}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
+    \caption{\co emissions in the local region (Ireland).}
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
@@
         \label{fig:10-2025-IE-p1-zone_emissions}
+    \end{subfigure}
+    \caption{Impact of clean electricity procurement commitments on emissions of participating consumers (top panel) and the system-level emissions in a local region (bottom panel).}
+    \label{fig:10-2025-IE-p1-emissions}
 \end{figure}
 
-The following analysis reveals the modelled cost-optimal procurement strategies for each \gls{cfe} policy.
-\cref{fig:10-2025-IE-p1-ci_capacity} shows that for 10\% of \gls{ci} load in Ireland (220 MW), the 100\% annual matching policy is met by onshore wind and solar PV generators with combined capacity of 1.3~GW.
-Matching demand with clean generation on hourly basis requires a much bigger portfolio of wind and solar than the annual matching policy, up to 4.0~GW of combined capacity to reach the 100\%~CFE.
-Batteries are included in the cost-optimal portfolio mix when CFE targets are above 85\%.
-Note that for 80\% CFE target, 24/7 participating consumers procure less capacity than for 100\% annual matching policy, as they rely more on grid imports.
+The following analysis unveils the modelled cost-optimal procurement strategies for each each procurement policy (\cref{fig:10-2025-IE-p1-ci_capacity}).
+In Ireland, 10\% of the \gls{ci} sector's demand yields a load of 220~MW.
+The findings indicate that, to cover this load adhering to a 100\%~RES policy, participating consumers procure a combined capacity of 1.3~GW from onshore wind and solar PV generators.
+Ensuring demand is matched with \gls{cfe} on an hourly basis requires a considerably more substantial portfolio of wind and solar PV, up to 4.0~GW of combined capacity to reach the 100\%~CFE target.
+Batteries are integrated into the cost-optimal portfolio mix when CFE targets exceed 85\%.
+It is noteworthy that, for an 80\%~CFE target, participating consumers procure less capacity than under a 100\%~RES policy, as they rely more on grid imports.
 
@@
 Note that revenues from selling the excess electricity to the regional grid at market prices can be treated as ”negative costs” and subtracted from the net procurement cost.
-The results show that a CFE targets of 80\%--95\% can be achieved at a small cost premium to 100\% annual renewable matching with solar, wind and batteries.
+The results show that a CFE targets of 80\%--95\% can be achieved at a small cost premium to 100\%~RES policy with solar, wind and batteries.
 However, what stands out in the plot is the rapid increase of procurement costs for high 24/7 CFE targets. 
-For example, 98\% CFE target has cost premium of 54\% over 100\% the RES policy; while the last 2\% of hourly CFE matching more than doubles the costs.
+For example, 98\% CFE target has cost premium of 54\% over 100\% the annual matching policy; while the last 2\% of hourly matching more than doubles the costs.
 
@@
         \centering
-        \vspace{-0.5cm}
-        \caption{Costs of a procurement policy.}
+        \vspace{-0.2cm}
+        \caption{Cost breakdown of a procurement policy.}
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_costandrev.pdf}
@@
     \end{subfigure}
-    \caption{Procurement of clean resources and energy storage by \gls{ci} consumers participating in voluntary clean electricity procurement. 
-    \cref{fig:10-2025-IE-p1-ci_capacity} shows power capacity portfolio for each procurement policy.
-    \cref{fig:10-2025-IE-p1-ci_costandrev} shows the breakdown of costs associated with a procurement.}
+    \caption{Optimal capacity portfolios (top panel) and costs breakdown (bottom panel) per procurement strategy.}
     \label{fig:10-2025-IE-p1-ci_procurement}
@@
 
-The cost premium of 24/7 hourly \gls{cfe} procurement presented in \cref{subsec:base} is driven by the variability of renewable power supply.
+The cost premium of 24/7~CFE procurement presented in \cref{subsec:base} is driven by the variability of renewable power supply.
 Indeed, in the periods when not much wind or solar is available, matching every kWh of electricity consumption with carbon-free electricity on hourly basis is not an easy task.
@@
 
-\cref{fig:10-2025-IE-p2-ci_costandrev} (left panel) shows the breakdown of costs for a case when \gls{ci} consumers have an access to \textbf{palette~2} technologies, i.e., \gls{ldes} complements onshore wind, solar PV and battery storage.
-A \gls{ldes} system\footnote{Here we assume 2.5~\euro/kWh underground hydrogen storage in salt caverns.} helps to bridge hours with no renewable feed-in. 
+\cref{fig:10-2025-IE-p2-ci_costandrev} (left panel) shows the breakdown of costs for a case when participating consumers have an access to palette~2 technologies, i.e., long-duration storage complements onshore wind, solar PV and battery storage.
+Here we assume an underground hydrogen storage in salt caverns with energy storage cost of 2.5~\euro/kWh [\cref{tab:tech_costs}].
+A \gls{ldes} system helps to bridge hours with no renewable feed-in. 
 As a result, the required portfolio of renewable capacity and procurement costs are reduced, especially for high CFE targets.
-Thus, 100\% 24/7 hourly matching has a cost premium of 42\% above annual matching policy, which is significantly lower than w/o \gls{ldes}.
+Thus, 100\% 24/7~CFE policy has a cost premium of 42\% above 100\%~RES, which is significantly lower than w/o \gls{ldes}.
 
-\cref{fig:10-2025-IE-p3-ci_costandrev} (right panel) illustrates \textbf{palette~3} scenario, i.e., 24/7 participants have an access to all palette~2 technologies, as well as to clean firm generation technologies.
-Allam cycle generator with \gls{ccs} is now part of the optimal procurement strategy.
-As CFE targets increase, the cost-optimal share of clean firm technology increases.
-The clean firm technology helps to fill in the gaps in variable renewable generation to match demand and clean generation on an hourly basis.
-The cost premium for 24/7 CFE is further reduced in this case: the 100\% 24/7 CFE costs only 15\% over 100\% annual renewable matching.
+\cref{fig:10-2025-IE-p3-ci_costandrev} (right panel) depicts the technological palette~3 scenario, wherein participating consumers additionally gain access to clean firm generation technologies.
+The Allam cycle turbine with \gls{ccs} now enters into the optimal procurement strategy.
+The cost-optimal share of to clean firm technology increases as CFE targets rise.
+The clean dispatchable generator helps to fill in the gaps in variable renewable generation to match demand and \gls{cfe} supply on an hourly basis.
+The cost premium is further reduced: 100\% 24/7 CFE costs only 15\% above the 100\%~RES.
 
@@
         \centering
-        \caption{Costs of a procurement policy with LDES.}
+        \caption{Cost breakdown of a procurement policy (w/ \gls{ldes}).}
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p2/ci_costandrev.pdf}
@@
         \centering
-        \caption{Costs of a procurement policy with LDES and clean firm generators.}
+        \caption{Costs of a procurement policy \\ 
+        (w/ \gls{ldes} and advanced technologies).}
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p3/ci_costandrev.pdf}
@@
     \end{subfigure}
-    \caption{The breakdown of costs per procurement policy if \gls{ci} consumers located in Ireland have an access to a wider palette of technologies:
-    w/ \gls{ldes} (\cref{fig:10-2025-IE-p2-ci_costandrev});
-    w/ \gls{ldes} and clean firm generation technologies (\cref{fig:10-2025-IE-p3-ci_costandrev}).
+    \caption{The breakdown of costs per procurement policy if participating consumers have an access to a wider palette of technologies: w/ \gls{ldes} (left panel); w/ \gls{ldes} and advanced clean firm generators (right panel).
     }
@@
 
-While we have focused on base scenario reflecting the case of Ireland, the same modelling exercise can be repeated for other regions of the European electricity grid.
-Since each region has a unique set of characteristics that depend on local resources, renewable potentials, national energy and climate policies, and degree of interconnections, such sensitivity can allow for generalising the impact of 24/7 CFE procurement void regional differences.
+While the primary focus has been a base scenario exemplifying Ireland, analogous modelling can be applied to diverse regions within the European electricity grid, each exhibiting unique characteristics influenced by local resources, renewable potentials, \gls{necp}s, the degree of interconnections, and other factors.
 
-\cref{fig:10-2025-DEPL-p3-4plots} shows the results for the two selected regions: Germany and Poland. 
-Germany is selected because it is the largest electricity consumer in Europe and has a good connection to regions with relatively clean grids, like France and Denmark. 
-As an example of the contrast, Poland is chosen because of its historical reliance on coal resources, resistance from the coal industry, and lack of government support for renewable energy.
-The participation rate of 24/7~CFE consumers is set at 10\% of the \gls{ci} sector in each country, as in the base scenario.%
-\footnote{10\% participation rate of \gls{ci} sector yields load of 3.8~GW in Germany and 1.1~GW in Poland.}
+\cref{fig:10-2025-DEPL-p3-4plots} depicts outcomes for the selected regions of Germany and Poland. 
+Germany, is selected due to its substantial connections to regions with relatively clean grids, such as France and Denmark, and it is the largest electricity consumer in Europe.
+In contrast, Poland has a smaller electricity demand, as well as historical coal dependence, opposition from its coal industry, and a paucity of governmental support for renewables.
+The participation rate is maintained at 10\% of the \gls{ci} sector in both regions, aligning with the base scenario.\footnote{A 10\% participation rate within the \gls{ci} sector corresponds to loads of 3.8~GW in Germany and 1.1~GW in Poland.}
+Despite regional variances, the dynamics and system impacts of clean energy procurement, as observed in the base scenario, exhibit similarities.
 
-The dynamics of 24/7 CFE procurement, observed above, appear similar despite regional differences.
+German consumers experience lower average emissions rates, attributed to a cleaner grid, in contrast to those in Poland.
+In the reference cases, emission values stand at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.\footnote{For context, the emission intensity of electricity generation in 2021 was 402~g\co/kWh for Germany and 750~g\co/kWh for Poland \cite{EEA-GNGEmissionsEU}.}
+Echoing the Irish scenario, both \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} demonstrate that in both contexts, participating consumers attain reduced emissions rates with 24/7~CFE procurement compared to 100\%~RES, given sufficiently strict CFE targets.
 
-German consumers have lower average emissions rates due to a cleaner grid than Polish consumers, as one would expect.
-In the reference case of grid electricity procurement, the values are at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.%
-\footnote{For reference, 2021 data for emission intensity of electricity generation was at 402~g\co/kWh in Germany and 750~g\co/kWh Poland \cite{EEA-GNGEmissionsEU}.}
-Similar to the Irish results, \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} show that in both cases, \gls{ci} participants achieve lower emissions rates with 24/7 hourly CFE procurement than with 100\% annual matching with renewable energy once their CFE targets are tight enough.
+The impact of 24/7 hourly CFE procurement on system-level \co emissions is notable in both Germany and Poland, as depicted in \cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions}.
+In the absence of any procurement strategy, carbon emissions from the power sectors of Germany and Poland are projected to be 118.8~Mt\co and 83.8~Mt\co in 2025, respectively.%
+\footnote{Despite Germany consuming more electricity, the similar scale of power sector carbon emissions between the two countries can be attributed to Poland's significantly higher emission intensity in its electricity mix.}
+By engaging in voluntary clean energy procurement, \gls{ci} consumers can drive notable decarbonisation in the local regions, exceeding the benchmarks set by \gls{necp}s.
+For instance, in Germany, even a 10\% participation rate under a 100\%~RES policy can diminish national emissions by 11.1~Mt\co annually; remarkably, the 24/7~CFE approach can amplify this impact to up to 14~Mt\co/a, given a CFE target of 100\%.
 
-A result that stands out in the cases of Germany and Poland is the impact of the 24/7 hourly CFE procurement on the system-level \co emissions, as shown in \cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions}.
-Without any CFE procurement stategy, the German and Polish power sector carbon emissions are at 118.8~Mt\co and 83.8~Mt\co in 2025, respectively.%
-\footnote{Germany is a larger electricity consumer, while Polish electricity mix has much a higher emission intensity; thus, power sector carbon emissions are on a similar scale for these countries.} 
-If C\&I load commits to voluntary clean energy procurement beyond \gls{necp}s, a significant decarbonisation impact is achieved. 
-The modelling results provides insightful data.
-For example, in Germany, with just 10\% \gls{ci} participation rate, the 100\% annual matching with renewable energy can reduce national emissions by 11.1~Mt\co/a; the 24/7 hourly matching policy yields even greater impact, up to 14~Mt\co/a with CFE 100\% target.
-
-The results for the required portfolio capacity-/costs are shown in \cref{fig:10-2025-DE-p3-ci_costandrev} and \cref{fig:10-2025-PL-p3-ci_costandrev}.
-24/7 consumers in Germany and Poland complement procurement of renewable energy with electricity imports from grid for low CFE targets. 
-To achieve higher CFE targets, Allam cycle with \gls{ccs} and advanced clean firm generators enter the technology mix. 
-The fact that both advanced technologies enter the optimal solution space is different to Irish results, where only the Allam cycle is cost-optimal. 
-This likely due to a case that Germany and Poland are better interconnected with the rest of the European electrcity grid than Ireland. 
-A better interconnection makes possible to exhaust all arbitrage opportunities across time and space and maximise the dispatch value from an advanced dispatchable generator with low variable costs.
-Similarly to Irish results though, the cost premium of 24/7 hourly matching is small when the advanced technologies are available.
+The optimal capacities of energy technologies and associated costs are illustrated in \cref{fig:10-2025-DE-p3-ci_costandrev} and \cref{fig:10-2025-PL-p3-ci_costandrev}.
+Similar to the Irish scenario, participating consumers complement renewable energy procurement with electricity imports from the grid to meet lower CFE targets. 
+For the realization of strict CFE targets, both the Allam cycle with \gls{ccs} and advanced clean firm generators are incorporated into the technology mix. 
+This entry of two advanced technologies into the optimal solution space diverges from the Irish findings, where solely the Allam cycle turbine is deemed cost-optimal. 
+The difference is likely attributable to Germany and Poland being more extensively interconnected with the broader European electricity grid compared to Ireland. 
+Better interconnection allows exhausting all arbitrage opportunities across temporal and spatial dimensions, and maximising the dispatch value derived from an advanced dispatchable generator with high \gls{capex}.
+Mirroring the findings from Ireland, the cost premium of 24/7~CFE matching gets minimal when these advanced technologies are accessible.
 
@@
         \centering
-        \caption{Costs of a procurement policy (Germany).}
+        \caption{Cost breakdown of a procurement policy (Germany).}
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/ci_costandrev.pdf}
@@
         \centering
-        \caption{Costs of a procurement policy (Poland).}
+        \caption{Cost breakdown of a procurement policy (Poland).}
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/ci_costandrev.pdf}
@@
     \end{subfigure}
-
-    \caption{Results for cases when 10\% of \gls{ci} load in Germany \textbf{(left)} and Poland \textbf{(right)} follows 24/7 hourly clean electricity procurement.
-Selected scenario with technological palette~3.}
+    \caption{Selected results for scenarios when participating consumers are located in Germany (left) and Poland (right); all plots are for technological palette~3.} 
     \label{fig:10-2025-DEPL-p3-4plots}
@@
 
-We explored the means, costs, and impacts of clean electricity procurement in the European electricity system for the year 2025 in the sections above.
-In this section, we examine the results and implications of these procurement strategies for 2030.
-To recall the \nameref{sec:methods} section, the key trends of advancing five years forward are cleaner electricity grids and lower costs for energy technologies.
+Having explored the methods, costs, and impacts of clean electricity procurement in the European electricity system for the year 2025 in preceding sections, this section delves into the projected results and implications of these strategies for 2030.
+Referencing back to the \nameref{sec:methods} section, the key implications of advancing five years forward are cleaner electricity grids and decreased costs for energy  technologies.
+\cref{fig:10-2030-IE-6plots} illustrates the outcomes for the \textit{base scenario} transitioned to 2030, maintaining all other parameters constant.
 
-\cref{fig:10-2030-IE-6plots} illustrates the results for \textit{base scenario} moved five years to 2030, with all other factors held constant.
+Analyzing \cref{fig:10-2030-IE-p1-used}, which presents the fraction of hourly demand met by clean electricity under each procurement policy in 2030, two key insights emerge when compared to the base scenario.
+Firstly, 72\% of demand is met by \gls{cfe} in the reference case, marking an 18\% increase from 2025, indicating an enhancement in the cleanliness of the background electricity grid.
+Consequently, lower CFE targets (like 80\%) are met with higher share of electricity imports.
+Secondly, participanting consumers depend on their own procurement of \gls{cfe} resources and storage, limiting imports from the background grid to achieve strict CFE targets. 
+This effect stays consistent with the base scenario.
 
-\cref{fig:10-2030-IE-p1-used} shows the fraction of hourly demand met by clean electricity under each procurement policy in 2030.
-Two observations can be drawn from comparing these results with a base scenario.
-The first is that 72\% of demand is met by CFE in the reference case, which is 18\% greater than in 2025, i.e., there is a cleaner electricity grid on a background.
-Therefore, lower CFE targets (such as 80\%) are achieved by importing more electricity.
-Second, 24/7 participants continue to rely primarily on their own procurement of \gls{cfe} resources and storage, without importing much from the background grid to reach higher CFE targets.
+A cleaner background grid results in lower average emissions rates for participating consumers.
+\cref{fig:10-2030-IE-p1-ci_emisrate} shows that the emissions rate for consumers purchasing only grid electricity decreases from 240~g\co/kWh in 2025 to 107~g\co/kWh in 2030.
+The hourly matching policy enables the attainment of zero emissions linked to \gls{ci} participants' consumption.
+It is interesting to note that a CFE target of 90\% yields lower average emissions than a 100\% annual matching policy, even though these policies are equally costly (see \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p3-ci_costandrev}).
 
-A cleaner background grid results in lower average emissions rates for 24/7 participants. 
-As shown in \cref{fig:10-2030-IE-p1-ci_emisrate}, the reference case value is reduced from 240~g\co/kWh in 2025 to 107~g\co/kWh in 2030.
-The hourly matching policy allows achieving zero emissions associated with \gls{ci} participants consumption.
-It is interesting to note that a CFE target of 90\% yields lower average emissions than a 100\% annual matching policy, even though these policies are both equally costly (see \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p3-ci_costandrev}).
+In cleaner systems, both 100\%~RES and 24/7~CFE policies sustain their beneficial impact on system-level emissions. 
+As observed in \cref{fig:10-2030-IE-p1-zone_emissions}, 24/7~CFE with a sufficiently high CFE target, outperforms 100\%~RES policy in the decarbonisation impact: with 10\% participation rate, hourly matching reduces local emissions by up to 0.4~Mt\(\text{CO}_2\)/a, in contrast to the 0.2~Mt\(\text{CO}_2\)/a reduction achieved by annual matching.
+The 0.2~Mt\(\text{CO}_2\)/a differential equates to approximately 8\% of Irish power sector emissions.
+The mechanisms driving this impact are detailed in \cref{subsec:mechanisms}.
 
-In even cleaner systems, both 100\% annual matching with renewable energy and 24/7 hourly matching with \gls{cfe} keep their positive effect on system-level emissions.
-Similar to 2025, when a CFE target is high enough, a diverse portfolio of energy resources procured by 24/7 participating consumers impacts system-level emissions more than the annual matching policy, see \cref{fig:10-2030-IE-p1-zone_emissions}.
-The hourly matching policy nearly doubles the decarbonisation effect of renewable matching in 2030: with a 10\% participation rate, annual matching reduces local emissions by 0.2~Mt\co/a (approximately 8\% of Irish power section emissions).
-Hourly matching results in a reduction of 0.4~Mt\co/a at 100\% CFE target.
-The nature of this effect is explained in \cref{subsec:mechanisms}.
-
-The cost breakdown for Ireland 2030 shows that 24/7 hourly matching costs are decreasing for all technological pallets compared to 2025, see \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p3-ci_costandrev}.
-The reason is that 24/7 participating consumers benefit from lower prices for clean energy technologies and cleaner electricity grids. 
-The results show that cost-optimal portfolios procured by 24/7 participants for the 100\% hourly matching policy have a minor cost premium over the annual renewable matching, for scenarios when \gls{ldes} and advanced clean firm technologies are available.
-Through these low cost premiums, participating consumers achieve zero emissions associated with their consumption and have a great impact on system-level \co emissions.
+As illustrated in \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p3-ci_costandrev}, the cost breakdown of the procurement policy reveals a decline in 24/7~CFE costs across all technological pallets relative to 2025.
+Participating consumers benefit from lower prices for clean energy technologies and progressively cleaner electricity grids. 
+Remarkably, these participants not only achieve zero emissions associated with their consumption and exert a notable impact on system-level \(\text{CO}_2\) emissions but also do so while encountering smaller cost premiums, enhancing the accessibility of the voluntary clean energy procurement goals.
 
@@
     \begin{subfigure}{0.5\textwidth}
-        \caption{Costs of a procurement policy: technological palette~1.}
+        \caption{Cost breakdown of a procurement policy: technological palette~1.}
         \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_costandrev.pdf}
@@
         \centering
-        \caption{Costs of a procurement policy: technological palette~2.}
+        \caption{Cost breakdown of a procurement policy: technological palette~2.}
         \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p2/ci_costandrev.pdf}
@@
         \centering
-        \caption{Costs of a procurement policy: technological palette~3.}
+        \caption{Cost breakdown of a procurement policy: technological palette~3.}
         \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p3/ci_costandrev.pdf}
@@
 
-    \caption{Results for the case of Ireland 2030. 10\% participation rate. 
+    \caption{Results for the scenario of Ireland 2030; 10\% participation rate. 
     Figures \ref{fig:10-2030-IE-p1-used}--\ref{fig:10-2030-IE-p1-ci_costandrev} display the technological palette~1 scenario.}
@@
 
-In the following, we conduct an experiment to isolate the decarbonisation effects of the volume and profile mechanisms.
+We conduct an experiment to isolate the decarbonisation effects of the volume and profile mechanisms.
 In the experiment, we reran the optimization with fixing an excess electricity sold to the grid to zero (NB excess is still possible, but can either be stored or curtailed). 
@@
 We attribute the difference between emissions reduction in the experiment model setup and the base scenario to the volume mechanism.
-As a result, the reduction of \co emissions in a local zone can be attributed either to excess electricity sold to the grid (volume effect) or to better alignment of CFE generation with demand (profile effect).
+As a result, the reduction of emissions in a local zone can be attributed either to excess electricity sold to the grid (volume effect) or to better alignment of CFE generation with demand (profile effect).
 
@@
 
-Additional insights into decarbonisation mechanisms can be gained by examining the emission reductions achieved by 100\% renewables matching and 100\% 24/7 CFE matching policies.
-\cref{fig:10-hourly-annual.pdf} compares the decarbonisation impact in a local zone of the two procurement policies in relative terms (percent point p.a.); the counterfactual scenario is a case when no \gls{ci} consumers participate in voluntary clean electricity procurement.
-The figure shows that the relative impact of 24/7 CFE matching on system-level emissions \textit{increases over time}; this is despite the fact that the impact of procurement policies in absolute terms decreases over time, as shown above.
-Furthermore, the self-cannibalisation effect of non-dispatchable generators, such as wind and solar, decreases the value of additional renewable capacity.
-Thus, in the countries where governments commit to ambitious \gls{necp} targets, such as Ireland and Germany, 24/7 CFE matching has a stronger decarbonisation impact than 100\% annual matching with renewable energy.
-It is because the profile mechanism remains relevant even when renewable energy generators are self-cannibalizing; whereas the volume mechanism is amplified due to the diverse portfolio of procured resources, including batteries, long-term energy storage, and advanced clean firm technologies.
-As a result, clean electricity can be available during times when wind and solar generation is scarce system-wide.
+Additional insights into decarbonisation mechanisms can be gained by examining the emission reductions achieved through 100\%~RES and 100\% 24/7 CFE matching policies.
+\cref{fig:10-hourly-annual.pdf} compares the decarbonisation impact within a local zone of the two procurement policies in relative terms (percent point p.a.), with a counterfactual scenario where no consumers engage in voluntary clean electricity procurement.
+The figure demonstrates that, even though the absolute impact of procurement policies diminishes over time, the relative impact of 24/7 CFE on system-level emissions \textit{increases over time} when compared to 100\%~RES.
+This phenomenon is attributable to the self-cannibalisation effect of wind and solar that influences the value of additional renewable capacity.
+This is relevant in regions where governments adhere to ambitious \gls{necp} targets, like Ireland and Germany (NB Denmark is an outlier with an exceptional RES target exceeding 100\% of national electricity demand for 2030).
+The profile mechanism maintains its relevancy even when renewable energy generators undergo self-cannibalization.
+The volume mechanism retains, or even amplifies, its relevance, by leveraging a diversified portfolio of procured resources by 24/7 participants, including batteries, long-term energy storage, and advanced clean firm technologies.
+Consequently, clean electricity is not only available but can also be sold to the background grid during periods when system-wide wind and solar generation is scarce.
 

### 2023-10-11 manuscript/sections/introduction.tex
manuscript: polishing sections 1-3

@@
 Many public and private energy buyers join this effort by purchasing clean energy to demonstrate their sustainability credentials.
-The established schemes for voluntary clean energy procurement are the Guarantees of Origin (\gls{go}s) in Europe and the Renewable Energy Certificates (also known as Renewable Energy Credits) (\gls{rec}s) in the United States.
+The established schemes for voluntary clean energy procurement are the Guarantees of Origin (\gls{go}s) in Europe and the Renewable Energy Certificates (\gls{rec}s) in the United States.
 A common feature of these schemes is that renewable energy credits are \enquote{unbundled} from megawatt-hours of energy and can be traded numerous times on specialized markets before being retired.
@@
 The first to incorporate it into the electricity system planning model were Xu et al.
-(2022) \cite{xu-247CFE-SSRN}.\footnote{A working paper updates a prior public technical report published in November 2021 investigating the system-level impacts of 24/7~CFE in two regions of the U.S.
+(2022) \cite{xu-247CFE-SSRN}.\footnote{A working paper updates a prior report published in November 2021 investigating the system-level impacts of 24/7~CFE in two regions of the U.S.
 -- California and PJM \cite{xu-247CFE-report}.}
@@
 Additionally, we examine the underlying mechanisms that drive the system-level reduction of \co emissions, and examine how they perform over time and across regions. 
+This work is a follow-up to the earlier public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.
 

### 2023-10-11 manuscript/sections/methods.tex
manuscript: polishing sections 1-3

@@
 The objective of the model is to minimise the annualised system-wide costs of meeting energy demand within the modelled system, while adhering to all relevant engineering, reliability, and policy constraints.
+We use a brownfield investment approach, which means that we keep the existing power generation and storage assets in the model and only optimise the capacity expansion of new assets.
 The optimal solution of the model includes the location and capacity of new power generation and storage assets, as well as the hourly dispatch of all existing and new assets, including the linear optimal power flow on the transmission network for the planning year.
@@
 By incorporating these into the mathematical problem, we model a situation when a fraction of electricity demand in a particular bidding zone is committed to procuring additional clean energy with a desired strategy.
-The fraction is set at 10\% of the total \gls{ci} electricity demand in a particular bidding zone, unless otherwise stated (hereinafter referred to as \enquote{participating consumers}).
+The fraction is set at 10\% of the total \gls{ci} electricity demand in a particular bidding zone, hereinafter referred to as \enquote{participating consumers}.
+The participating consumers are modelled as a single entity with a baseload demand profile.
 Accordingly, the model co-optimises the procurement and operational decisions of the participating consumers to meet their electricity demand in accordance with the procurement strategy they have chosen.
@@
 The framework considers various \gls{cfe} supply options for the participating consumers, including procurement of own generation resources and storage assets, and electricity imports from the local grid.
-The framework also allows for controlling \textit{the quality score} of the 24/7~CFE procurement by setting the threshold for the minimum share of hours when the hourly \gls{cfe} supply meets the hourly electricity demand.
+The framework also allows for controlling \textit{the quality score} of the 24/7~CFE procurement by setting the target threshold for the minimum share of hours when the hourly \gls{cfe} supply meets the hourly electricity demand.
+The quality score is hereinafter referred to as \enquote{CFE target}, which takes values in percent points, e.g., 95\%, 99\%, 100\%.
+The higher the CFE target, the higher the quality of the 24/7~CFE supply; see equation [TODO] for details.
 
@@
     \item \textit{100\% annual matching}: participating buyers meet their annual energy demand on volumetric basis with additional renewable energy procurement;
-    \item \textit{24/7 hourly matching}: participating buyers optimise their investment and operational decisions mixing procurement of additional generation and storage resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality score;
-    \item For benchmarking, we also model \textit{a reference case}: participating buyers have no voluntary environmental commitments and get all their electricity from the local grid.
+    \item \textit{24/7 hourly matching}: participating buyers optimise their investment and operational decisions mixing procurement of additional generation and storage resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality target.
 \end{itemize}
@@
 In both cases (i) procurement is possible with generators from the same bidding zone only (i.e., we model the \enquote{best case} of the annual matching strategy); (ii) the same set of consumers participate; (iii) the same set of constraints is applied to the rest of the electricity system.
+For benchmarking, we also model \textit{a reference case}: participating buyers have no voluntary environmental commitments and purchase all their electricity from the local grid.
 

### 2023-10-11 manuscript/sections/results.tex
manuscript: polishing sections 1-3

@@
 The participating consumers can attain the 24/7~CFE procurement targets by co-optimizing local procurement using mature technologies, designated as \textit{palette~1}, and by importing electricity from the local grid.
-
 Afterward, we delve deeper into the scenario space, altering highlighted parameters to explore various alternatives and address the following questions:
@@
 Considering the large scenario space, this work presents results for a selection of scenario branches that generalise the system impacts of 24/7 CFE procurements.
-For interested readers, we publish an online dashboard with results for the entire scenario space, see \nameref{sec:code}.
+We publish an online dashboard with results for the entire scenario space alongside the paper, see \nameref{sec:code}.
 
@@
 %some parts of this paragraph may go to methods
-\cref{fig:10-2025-IE-p1-used} shows the fraction of the fraction of hourly demand met with carbon-free electricity depending on the procurement policy that participating consumers follow.
-We contrast two main cases, one where participating consumers commit to 100\% annual renewable matching policy (hereinafter -- \enquote{100\% RES}) and another case where the consumers commit to 24/7~CFE hourly matching policy (hereinafter -- \enquote{24/7~CFE}) with various \gls{cfe} targets in a range from 80\% to 100\%.
+\cref{fig:10-2025-IE-p1-used} shows the fraction of hourly demand met with \gls{cfe} depending on the procurement policy that participating consumers follow.
+We contrast two main cases, one where participants commit to 100\% annual renewable matching policy (hereinafter -- \enquote{100\% RES}) and another case where the consumers commit to 24/7~CFE hourly matching policy (hereinafter -- \enquote{24/7~CFE}) with various \gls{cfe} targets in a range from 80\% to 100\%.
 In the \textit{reference case}, participating consumers cover their load purely with grid purchases without any policy regarding the origin of electricity.
@@
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \caption{Average emissions rate of participating consumers.}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \caption{Average emissions rate of participating consumers.}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \caption{Average emissions rate of participating consumers.}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \caption{Average emissions rate of participating consumers.}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \caption{Average emissions rate of participating consumers.}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \caption{Average emissions rate of participating consumers.}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \caption{Average emissions rate of participating consumers.}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
-    \caption{Average emissions rate of participating consumers.}
         \label{fig:10-2025-IE-p1-ci_emisrate}
@@
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \caption{\co emissions in the local region (Ireland).}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \caption{\co emissions in the local region (Ireland).}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \caption{\co emissions in the local region (Ireland).}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \caption{\co emissions in the local region (Ireland).}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \caption{\co emissions in the local region (Ireland).}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \caption{\co emissions in the local region (Ireland).}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \caption{\co emissions in the local region (Ireland).}
-        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
-    \caption{\co emissions in the local region (Ireland).}
         \label{fig:10-2025-IE-p1-zone_emissions}

### 2023-10-13 manuscript/sections/discussion.tex
discussion: add perspective text

\textbf{Our results in perspective --} Our findings agree with the existing model-based studies on clean energy procurement \cite{xu-247CFE-SSRN,ieaAdvancingDecarbonisationClean2022,peninsula-report247}, as well as with the general understanding of the energy research community that \enquote{100\% renewable energy is not enough} \cite{chalendar-2019} in a context of electricity consumers claiming environmental sustainability. 
Specifically, we show that through hourly matching of demand with clean electricity, electricity consumers can both completely negate their carbon emissions and contribute to broader system-wide decarbonisation. 
100\% CFE matching is viable with commercially available technologies, albeit incurs a cost premium for participating consumers.
The cost premium can be substantially reduced if the advanced technologies, such as long-duration energy storage and clean firm generators are available, or if consumers opt for participating in the 24/7~CFE procurement with quality scores ranging from 90\% to 95\% instead of an absolute 100\%.

Another important finding of this work that confirms prevailing understanding is that 24/7 CFE matching creates an early market for advanced energy technologies. Citing an episode of the David Roberts' Volts podcast: \enquote{One reason energy nerds are excited about the 24/7 trend is that it's going to pull forward in time a bunch of questions (and investment decisions) that were going to face grids trying to reach 100 percent CFE anyway} \cite{roberts-intro247CFE}. Further research is needed to better understand how 24/7 CFE commitments push advanced energy technologies along their learning curves, and to estimate the potential economic impact on global decarbonisation costs.

% Where we add: Diverse grid locations and years
According to a comparison of the results over the modeled regions and time periods, voluntary clean energy procurement commitmetns appear to have consistent effects on both participating buyers and system-level decarbonisation.
Based on these findings, this work can provide a basis for generalising the implications of clean energy procurement strategies, while taking into account regional differences in electricity demand, renewable resource availability, legacy power plant fleets, degrees of interconnection, and energy policies, among other factors.

% Where we add: Decarbonisation story
A deeper look at the role of voluntary clean energy procurement commitments in grid decarbonisation reveals that the hourly matching strategy retains its significance in reducing system-level emissions, even as grids become cleaner over time.
We examined two distinct mechanisms through which 24/7 CFE procurement facilitates system decarbonization: "profile" and "volume".
As companies adapt their procurement strategies, it is important to understand how these mechanisms perform across different grid locations and years.
Interestingly, the disparity between the annual renewable (\enquote{volumentric}) matching and 24/7 CFE hourly matching strategies in decarbonisation outcomes becomes ever more evident as electricity grids become cleaner.
This phenomenon illustrates the effectiveness of 24/7 CFE procurement in supporting system decarbonisation within the context of evolving national energy and climate policies.

These results highlight that voluntary commitments to 24/7 hourly matching goals can create an early market for the advanced technologies.

Diverse grid locations:
The results highlight that the decarbonisation impact of 24/7 hourly procurement can be achieved with very little cost premium over the 100\% annual renewable matching, if the advanced technology is available.

### 2023-10-13 manuscript/sections/methods.tex
discussion: add perspective text

@@
 The participating consumers can be located in either of the four selected zones: Ireland, Denmark (zone DK1), Germany, or Poland.
-The comparison of results across these zones allows us to generalize the implications of of voluntary clean energy procurement, taking into account factors such as electricity demand, weather, availability of renewable resources, existing electricity generation capacity mix, and national energy policies, among other factors.
+The comparison of results across these zones allows us to generalize the implications of voluntary clean energy procurement, taking into account factors such as electricity demand, weather, availability of renewable resources, existing electricity generation capacity mix, and national energy policies, among other factors.
 

### 2023-10-13 manuscript/sections/discussion.tex
discussion: add features text

@@
 
-These results highlight that voluntary commitments to 24/7 hourly matching goals can create an early market for the advanced technologies.
+\textbf{Features of 24/7~CFE not covered in this work --} Some positive features of 24/7 CFE procurement fall beyond the scope of this manuscript.
+
+% on the impact on back up flexibility needs
+From a system-wide benefits perspective, voluntary commitments to 24/7 CFE reduce the need for flexibility in background electricity systems. 
+There will be less investment in gas-fired peaker generators, as well as less need for battery storage elsewhere in the system.
+This effect has been explored in Xu et al. (2022) and Riepin~\&~Brown (2022) \cite{riepin-zenodo-systemlevel247,xu-247CFE-report}
+
+% add a point on the price hedge
+From an electricity buyer perspective, 24/7 CFE procurement can provide a hedge against volatile wholesale market prices.
+Since 100\% CFE matching implies covering the entire electricity demand with clean energy from procured generators via power purchase agreements and operating storage, the buyer is not exposed to the wholesale market price risk (see \cref{fig:10-2025-IE-p1-used}).
+More information on the price hedge effect is provided by the 24/7 CFE Energy Compact \cite{gocarbonfree247}.
 

### 2023-10-14 manuscript/sections/discussion.tex
discussion: add limitations text

@@
 
-Diverse grid locations:
-The results highlight that the decarbonisation impact of 24/7 hourly procurement can be achieved with very little cost premium over the 100\% annual renewable matching, if the advanced technology is available.
+\textbf{Critical appraisal --} This work has simplifications and limitations that should be acknowledged.
+
+%Limitations: electricity sector only
+First, only the electricity sector is included in the mathematical model of the European energy system.
+The research focus of this study justifies it.
+However, it is important to acknowledge that the electricity sector is not an isolated system, but it is closely linked with other energy sectors, such as heat and transport.
+Brown et al. (2018) discuss the synergies of sector coupling in the integrated European energy system \cite{brownSynergiesSectorCoupling2018}.
+
+%Limitations: merged profiles of consumers
+Second, consumers participating in clean energy procurement are modelled as one entity.
+The real-world situation may involve a number of individual consumers participating in a voluntary clean energy procurement scheme.
+Our assumption is that all consumers that commit to 24/7 matching, form alliances, and enter into contracts with carbon-free energy generators so that their aggregated consumption can be matched with clean generation on an hourly basis to achieve a given CFE target.
+In reality, participating consumers can pursue hourly matching strategies independently based on their own load profiles.
+See Xu \& Jenkins (2022) investigating this case \cite{princeton-TEACs-2022}.
+
+% Limitations: consumption profiles
+Third, we assume that the participating consumers have a flat demand profile (i.e. baseload).
+As a matter of fact, consumer demand profiles vary based on their business activities.
+It has been shown by Riepin~\&~Brown (2022) that the shape of consumption profiles affects the cost-optimal technology mix required for achieving a certain CFE target; however, the shape of the profile has relatively little impact on procurement costs, emissionality of the portfolio, and system-level impacts of 24/7 procurement \cite{riepin-zenodo-systemlevel247}.
+
+% Limitations: a point on DSM
+Fourth, participating consumers have an inflexible demand, i.e., no demand-side management is considered.
+In reality, many \gls{ci} consumers have some degree of demand flexibility, which they can use to adjust their consumption as needed based on grid signals, such as the wholesale market price and the average emission rate of the local electricity mix.
+Moreover, some consumers, such as data centers and cloud computing providers, can shift their load also in space, i.e., to shift computing
+jobs and associated power loads across data center locations \cite{rosskoningsteinWeNowMore2021}.
+In the recent work, Riepin~\&~Brown (2023) explore how space-time load-shifting flexibility can be used to meet high 24/7 CFE targets, as well as what potential benefits it may offer to participating energy buyers and to the rest of the energy system \cite{riepin-zenodo-spacetime247CFE}.
+
+% Excess constraint problem
+One of the simplifications of mathematical models implementing 24/7 CFE procurement is how the excess carbon-free electricity is handled. 
+The \enquote{excess CFE} can be defined as the total amount of carbon-free electricity supply exceeding the demand of the participating consumers in a given period of time.
+Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices, until the excess constraint is reached (see \cref{sec:si_3} for detail).
+The problem with the uncostrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement.
+Similar \enquote{spillover effect} problem has been observed and discussed by Xu et al. (2022) \cite{xu-247CFE-SSRN}.
+In their white paper, Peninsula Clean Energy team also discuss the problems and implications of the excess supply.
+Citing their work: \enquote{We conclude that excess supply is a necessary aspect of a time-coincident renewable portfolio in the range of likely market conditions in California today} \cite{peninsula-report247}.
+Both studies perform sensitivity analyses on the excess supply and discuss the implications on their findings \cite{xu-247CFE-SSRN, peninsula-report247}.

### 2023-10-14 manuscript/sections/discussion.tex
discussion: add final part and complete section

@@
 
+% Where we converge: on advanced technologies
 Another important finding of this work that confirms prevailing understanding is that 24/7 CFE matching creates an early market for advanced energy technologies.
@@
 % Where we add: Diverse grid locations and years
-According to a comparison of the results over the modeled regions and time periods, voluntary clean energy procurement commitmetns appear to have consistent effects on both participating buyers and system-level decarbonisation.
+According to a comparison of the results over the modeled regions and time periods, voluntary clean energy procurement commitments appear to have consistent effects on both participating buyers and system-level decarbonisation.
 Based on these findings, this work can provide a basis for generalising the implications of clean energy procurement strategies, while taking into account regional differences in electricity demand, renewable resource availability, legacy power plant fleets, degrees of interconnection, and energy policies, among other factors.
@@
 There will be less investment in gas-fired peaker generators, as well as less need for battery storage elsewhere in the system.
-This effect has been explored in Xu et al. (2022) and Riepin~\&~Brown (2022) \cite{riepin-zenodo-systemlevel247,xu-247CFE-report}
+This effect has been explored by Xu et al. (2022) and Riepin~\&~Brown (2022) \cite{riepin-zenodo-systemlevel247,xu-247CFE-report}
 
@@
 Both studies perform sensitivity analyses on the excess supply and discuss the implications on their findings \cite{xu-247CFE-SSRN, peninsula-report247}.
+
+% On "emissionality" approach
+\textbf{Is 24/7~CFE the right strategy? --} Last but not least, it is worth mentioning an ongoing discussion whether 24/7 CFE is the right strategy for companies to reduce their carbon emissions.
+Some proponents of alternative strategies contend that 24/7 CFE, or \enquote{temporal matching}, may not represent the most effective approach to emissions reduction. 
+Instead, they suggest that companies, in their pursuit to reduce system-level carbon emissions, should focus on system-wide impact as measured via short-run marginal emissions accounting (\enquote{emissions matching}).
+This argument is based on the rationale that optimising procurement and deployment of carbon-free generators and batteries to cover 24/7 consumption will be different from optimising the assets to \enquote{offset emissions} based on the short-run marginal emission estimates of the grid.
+Xu~et~al.
+(2023) bring this discussion from the realm of arguments into quantitative analysis, discovering that \enquote{emissions matching strategies have zero or near-zero long-run impact on system-level \co emissions} \cite{princeton-247CFEvsEmissionality}.
+
+More work---encompassing the collective contributions of the research community, \gls{ngo}s, policy-makers, and corporate energy buyers---is needed to deepen our understanding of the implications, challenges, and opportunities inherent in various clean energy procurement strategies, guiding us all towards net-zero sustainable energy systems.

### 2023-10-14 manuscript/sections/results.tex
manuscript: add literature and final touches text

@@
 \cref{fig:10-2025-IE-p1-used} shows the fraction of hourly demand met with \gls{cfe} depending on the procurement policy that participating consumers follow.
-We contrast two main cases, one where participants commit to 100\% annual renewable matching policy (hereinafter -- \enquote{100\% RES}) and another case where the consumers commit to 24/7~CFE hourly matching policy (hereinafter -- \enquote{24/7~CFE}) with various \gls{cfe} targets in a range from 80\% to 100\%.
+We contrast two main cases, one where participants commit to 100\% annual renewable matching policy (hereinafter -- \enquote{100\% RES}) and another case where the consumers commit to 24/7~CFE hourly matching policy (hereinafter -- \enquote{24/7~CFE}) with various CFE targets in a range from 80\% to 100\%.
 In the \textit{reference case}, participating consumers cover their load purely with grid purchases without any policy regarding the origin of electricity.
@@
 
-In the reference case, only 54\% of demand is met with \gls{cfe} electricity.
+In the reference case, only 54\% of demand is met with \gls{cfe}.
 100\% RES---the best case for the annual renewable matching policy---results in 83\% fraction. 
@@
 
-Two mechanisms are responsible for reducing system-wide emissions:
+As originally identified by Xu et al. (2021) \cite{xu-247CFE-report}, two mechanisms are responsible for reducing system-wide emissions:
 
@@
 
-It can be seen in \cref{fig:10-profile-volume.pdf} that the overall impact of 24/7 CFE procurement is proportional to how clean the background grid on average is.
-Thus, the largest impact is at 571.6~kgCO$_2$/a·MWh$^{-1}$ takes place in the Poland 2025 zone, and the lowest one is 3.7~kgCO$_2$/a·MWh$^{-1}$ in Denmark 2030 (NB 10\% of \gls{ci} sector participation rate with CFE 100\% target).
+\cref{fig:10-profile-volume.pdf} shows that the impact of 24/7 CFE procurement in absolute terms is proportional to how clean the background grid on average is.
+Thus, the largest impact is at 571.6~kgCO$_2$/a·MWh$^{-1}$ takes place in the Poland 2025 zone, and the lowest one is 3.7~kgCO$_2$/a·MWh$^{-1}$ in Denmark 2030 (NB values for 10\% of \gls{ci} sector participation rate with CFE 100\% target).
 It is noteworthy that from 2025 to 2030, the decarbonisation effect of voluntary clean electricity procurement decreases over time in all zones since electricity grids become cleaner as a result of national climate policy programs and decomissioning of emitting power plants.
@@
 
-\begin{figure}
+\begin{figure}[H]
     \centering
@@
 \end{figure}
-
-% \subsection{System flexibility need reduction}
-% \label{subsec:flexibility}
-
-% \vspace{5pt}
-% \begin{res}
-%     24/7 CFE procurement reduces the needs for flexibility in the rest of the system.
-% \end{res}
-
-% The decarbonisation mechanisms discussed above suggest a displacement of fossil-fueled generators in the rest of the system in presense of voluntary clean electricity procurement.
-% We illustrate this effect in \cref{fig:10-2030-DE-p1-system_capacity_diff.pdf}, which shows the difference in the generation capacity expansion of the whole European electricity system (excluding resources procured by participating customers) with and without commitments to clean electrity procurement (an illustraive scenario for Germany, 2030, technological palette~1).
-% Hourly CFE procurement benefits the system by having a pronounced effect of flexibility needs reduction -- the system requires less battery storage and less peaker capacity in a form of \gls{ocgt}. 
-% In the selected example, 3.8~GW of load (10\% of \gls{ci} sectors in Germany) participate in the procurement.
-% In a case of hourly matching with 100\% CFE target, this reduces \gls{ocgt} investments by 4.6~GW and battery storage by 2.6~GW in the rest of the system.
-% The substitution of gas-fired capacity with clean resources procured by \gls{ci} consumers facilitates decarbonization of the entire system, as shown above.
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[width=0.95\columnwidth]{plots/10/2030/DE/p1/system_capacity_diff.pdf}
-%     \caption{
-%     Difference in generation capacity expansion in the whole European electricity system (including \gls{ci} resources) with and without clean energy procurement. 
-%     Selected scenario of Germany, 2030, technological palette~1.}
-%     \label{fig:10-2030-DE-p1-system_capacity_diff.pdf}
-% \end{figure}

### 2023-10-14 manuscript/sections/conclusion.tex
manuscript: add conclusions

@@
-Taken together, we show that 24/7-CFE commitment by corporate sector stakeholders is a step above and beyond the 100\% annual renewable matching in paving the path toward the carbon net-zero energy systems.
-This voluntary commitment also delivers a range of benefits to the society by 
-(i) triggering innovation, availability and earlier utilisation of advanced clean firm generation needed for the transformation of energy systems to a complete carbon net-zero state, 
-(ii) reducing system emissions, and (iii) reducing system flexibility needs.
+24/7 carbon-free energy matching is a viable and effective strategy for electricity buyers aiming to eliminate their own carbon footprint and contribute to wider system decarbonisation.
+Voluntary commitments to 24/7 CFE procurement have further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
+The evidence holds across geographical locations and time periods, and is robust to sensitivity analyses.
+The strategy retains its significance in reducing system-level emissions, even as grids become cleaner over time, which is essential in light of evolving national energy and climate policies.

### 2023-10-14 manuscript/sections/discussion.tex
manuscript: add conclusions

@@
 
-More work---encompassing the collective contributions of the research community, \gls{ngo}s, policy-makers, and corporate energy buyers---is needed to deepen our understanding of the implications, challenges, and opportunities inherent in various clean energy procurement strategies, guiding us all towards net-zero sustainable energy systems.
+More work---encompassing the collective contributions of the research community, \gls{ngo}s, policy-makers, and corporate energy buyers---is needed to deepen our understanding of the implications, challenges, and opportunities inherent in various clean energy accounting approaches and procurement strategies, guiding us all towards net-zero sustainable energy systems.

### 2023-10-15 manuscript/sections/abstract.tex
manuscript: add abstract

@@
-Traditional power purchase agreements for renewable energy have seen rapid growth in recent years, but they only match supply and demand on average over a longer period such as a year.
-There is increasing interest from leaders in voluntary clean electricity procurement to cover their consumption with clean energy supply on truly 24/7 basis. 
-Achieving 24/7 carbon-free energy means that every kilowatt-hour of electricity consumption is met with carbon-free electricity sources, every hour of every day.
-In this study, we investigate both the means and costs of pursuing different clean electricity procurement strategies for companies in a selection of European countries.
-We also explore how the 24/7 clean energy procurement affects the rest of the European electricity system.
+% The 5 things a good abstract needs:
 
-\bf{Dummy abstract - to refine}
+% 1. Introduce the topic: what we know 
+% 2. State the unknown: what we don't know
+% 3. Outline the methods: how we answer the questions
+% 4. Preview the findings: what we learned
+% 5. Tell us what your work teaches us: what we conclude and why this is important
+
+% aim ~200 words | 225 words used
+
+A growing number of public and private energy buyers are interested in 24/7 carbon-free energy (CFE) procurement, which means that every kilowatt-hour of electricity consumption is met by carbon-free sources at all times.
+It has the potential to overcome the limitations of established procurement schemes, such as the temporal mismatch between clean electricity supply and buyers' demand that is inherent to "volumetric" matching.
+Yet it is unclear whether 24/7 CFE procurement is only effective during the early stages of the energy transition, or if it has a system-level impact in a variety of regional contexts.
+We use a mathematical model to systematically examine different designs, optimal procurement strategies, costs, and impacts of the 24/7 CFE matching, both for participating buyers and for regions where voluntary procurement occurs.
+We examine the mechanisms driving system-level co emissions reduction and how they vary across regions and over time.
+Our results indicate that voluntary clean energy procurement commitments have consistent effects on participants and the electricity system.
+Even as grids become cleaner over time, the hourly matching strategy remains significant in reducing CO$_2$ emissions.
+In addition, voluntary commitments to 24/7 CFE have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
+This work generalises the implications of clean energy procurement strategies in the context of evolving national energy and climate policies.

### 2023-10-15 manuscript/manuscript.tex
manuscript: add acknowledgements

@@
 
-This paper is an independent project, which is based on the third-party funded research work \cite{riepin-zenodo-systemlevel247}.
-This research work was supported by a grant from Google Inc.
+This work is an independent follow-up to the prior public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.
+The prior public report was supported by a research grant from Google LLC.
+
+We thank the following people for fruitful discussions on the 24/7 carbon-free energy procurement and the art of energy system modelling: Fabian Neumann, Elisabeth Zeyen, Devon Swezey.
 

### 2023-10-15 manuscript/sections/methods.tex
manuscript: title, keywords, and final touches main text

@@
 
-\textbf{Technology assumptions --} Cost and other assumptions for energy technologies available for participating consumers were collected primarily from the Danish Energy Agency \cite{DEA-technologydata} for the respective years and are provided in Table S1.
+\textbf{Technology assumptions --} Cost and other assumptions for energy technologies available for participating consumers were collected primarily from the Danish Energy Agency \cite{DEA-technologydata} for the respective years and are provided in [\cref{tab:tech_costs}].
 For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion. 

### 2023-10-15 manuscript/manuscript.tex
manuscript: title, keywords, and final touches main text
manuscript: add data and code availability section

@@
 
-	\title{Navigating to a greener Europe with 24/7 hourly carbon-free electricity procurement}
+	\title{On the means, costs, and system-level impacts of the 24/7 carbon-free energy procurement}
 
@@
 	\begin{keyword}
-		TODO
+		24/7 carbon-free electricity, 
+		Clean electricity procurement, 
+		Energy modelling, 
+		Renewable energy
 	\end{keyword}
@@
 
-%\listoftodos[TODOs]
 \tableofcontents
@@
 
-This project is also developed as open-source. \url{https://github.com/PyPSA/247-cfe}
+The simulations were carried out with PyPSA --- an open-source software framework for simulating and optimising modern energy systems \cite{brownPyPSAPythonPower2018}.
 
-The data and code to reproduce the experiments is available at \href{https://github.com/repository}{GITHUB}.
+All code, input data and results are published under an open license.
+The code to reproduce the experiments is available at GitHub: \href{https://github.com/Irieo/247-procurement-paper}{github.com/Irieo/247-procurement-paper}.
 
-The online dashboard with the results for this study is available at \url{dashboard}.
+We publish an online dashboard with results for the entire scenario space alongside the paper \href{}{DASHBOARD}.
 

### 2023-10-15 manuscript/sections/supplementary_2.tex
si: add background system assumptions

@@
 %S2: Background system assumptions
-In all the modelled countries, renewable generation must meet the political targets as defined in the NECPs or by more recent national policy targets (such as the Easter package in Germany), see Table 1.
+
+The model performs \textit{a perfect-foresight optimisation} of investment and power dispatch decisions to meet electricity demand of the 24/7 consumers, as well as the demand of other consumers in the European electricity system for 2025 or 2030.
+
+In all the modelled countries, renewable generation \textit{must meet the political targets} as defined in the \gls{necp}s or by more recent national policy targets (such as the Easter package in Germany).
+In countries that not have a target for 2025, a linear increase from targets between 2020 and 2030 is assumed.
+The assumed renewable targets are available in the config file of the scientific workflow \cite{github-247CFEpaper}.
+
+We assume 2013 to be a representative climate year for renewable in-feed. The renewable feed-in profiles are computed with the atlite package \cite{atlite-github}.
+
+The country demand profiles for 2025 and 2030 are assumed to be the same as in 2013. Time-series data for electricity demand is based on the Open Power System Data project \cite{OPSD}.
+
+The existing power plant fleet data is based on the powerplantmatching package \cite{Powerplantmatching-github}.
+We consider national policies and decommissioning plans for coal and nuclear power plants based on data from the \enquote{beyondfossilfuels.org} and the \enquote{world-nuclear.org} projects \cite{FossilFuels, WorldNuclearAssociation}.
+
+We assume price for EU ETS allowances to be 80~\euro/t\co and 130~\euro/t\co  for 2025 and 2030, accordingly. 
+The price for natural gas is assumed to be 35~\euro/MWh.

### 2023-10-15 manuscript/sections/results.tex
manuscript: title, keywords, and final touches main text
manuscript: final literature items and formatting

@@
 
-\cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of participating consumers.
-Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case.
-If participating consumers follow 100\%~RES policy, the emission rate is reduced to 60~g\co/kWh.
-This yields a considerable emission rate reduction compared to the reference case.
-The 24/7~CFE procurement with targets above 85\% helps the participating consumers to reduce emissions further beyond the treshhold set by the 100\%~RES. 
-At the 100\% CFE target, participating consumers attain a zero emission rate associated with their electricity consumption, as they perfectly align demand and \gls{cfe} supply on an hourly basis.
-
-Voluntary procurement of clean electricity also helps decarbonise electricity system as a whole.
-We explore this effect by plotting \co emissions in the local region of the participating consumers, i.e. Ireland (\cref{fig:10-2025-IE-p1-zone_emissions}).
-Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2~Mt\co.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021.
-A strong decreasing trend is expected, since Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
-The modelling results indicate that a commitment to 100\% 24/7~CFE in 2025 from 10\% of the \gls{ci} electricity demand could yield a reduction in Irish emissions by 0.6~MtCO$_2$ annually, in contrast to a scenario absent voluntary procurement.
-This reduction equates to 14\% of the total emissions from the Irish power sector.
-100\%~RES can also facilitate system-level \co emissions reductions (as depicted by the left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, 24/7~CFE attains superior emissions reductions when the CFE target surpasses 85\%.
-
-\begin{figure}
+\begin{figure}[t]
     \centering
@@
 
-The following analysis unveils the modelled cost-optimal procurement strategies for each each procurement policy (\cref{fig:10-2025-IE-p1-ci_capacity}).
-In Ireland, 10\% of the \gls{ci} sector's demand yields a load of 220~MW.
-The findings indicate that, to cover this load adhering to a 100\%~RES policy, participating consumers procure a combined capacity of 1.3~GW from onshore wind and solar PV generators.
-Ensuring demand is matched with \gls{cfe} on an hourly basis requires a considerably more substantial portfolio of wind and solar PV, up to 4.0~GW of combined capacity to reach the 100\%~CFE target.
-Batteries are integrated into the cost-optimal portfolio mix when CFE targets exceed 85\%.
-It is noteworthy that, for an 80\%~CFE target, participating consumers procure less capacity than under a 100\%~RES policy, as they rely more on grid imports.
+\cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of participating consumers.
+Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case.
+If participating consumers follow 100\%~RES policy, the emission rate is reduced to 60~g\co/kWh.
+This yields a considerable emission rate reduction compared to the reference case.
+The 24/7~CFE procurement with targets above 85\% helps the participating consumers to reduce emissions further beyond the treshhold set by the 100\%~RES. 
+At the 100\% CFE target, participating consumers attain a zero emission rate associated with their electricity consumption, as they perfectly align demand and \gls{cfe} supply on an hourly basis.
 
-The breakdown of costs associated with a procurement policy that participating consumers choose is shown in \cref{fig:10-2025-IE-p1-ci_costandrev}.
-Note that revenues from selling the excess electricity to the regional grid at market prices can be treated as ”negative costs” and subtracted from the net procurement cost.
-The results show that a CFE targets of 80\%--95\% can be achieved at a small cost premium to 100\%~RES policy with solar, wind and batteries.
-However, what stands out in the plot is the rapid increase of procurement costs for high 24/7 CFE targets. 
-For example, 98\% CFE target has cost premium of 54\% over 100\% the annual matching policy; while the last 2\% of hourly matching more than doubles the costs.
+Voluntary procurement of clean electricity also helps decarbonise electricity system as a whole.
+We explore this effect by plotting \co emissions in the local region of the participating consumers, i.e. Ireland (\cref{fig:10-2025-IE-p1-zone_emissions}).
+Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2~Mt\co.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021.
+A strong decreasing trend is expected, since Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
+The modelling results indicate that a commitment to 100\% 24/7~CFE in 2025 from 10\% of the \gls{ci} electricity demand could yield a reduction in Irish emissions by 0.6~MtCO$_2$ annually, in contrast to a scenario absent voluntary procurement.
+This reduction equates to 14\% of the total emissions from the Irish power sector.
+100\%~RES can also facilitate system-level \co emissions reductions (as depicted by the left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, 24/7~CFE attains superior emissions reductions when the CFE target surpasses 85\%.
 
-\begin{figure}
+\begin{figure}[t]
     \centering
@@
 \end{figure}
+
+The following analysis unveils the modelled cost-optimal procurement strategies for each each procurement policy (\cref{fig:10-2025-IE-p1-ci_capacity}).
+In Ireland, 10\% of the \gls{ci} sector's demand yields a load of 220~MW.
+The findings indicate that, to cover this load adhering to a 100\%~RES policy, participating consumers procure a combined capacity of 1.3~GW from onshore wind and solar PV generators.
+Ensuring demand is matched with \gls{cfe} on an hourly basis requires a considerably more substantial portfolio of wind and solar PV, up to 4.0~GW of combined capacity to reach the 100\%~CFE target.
+Batteries are integrated into the cost-optimal portfolio mix when CFE targets exceed 85\%.
+It is noteworthy that, for an 80\%~CFE target, participating consumers procure less capacity than under a 100\%~RES policy, as they rely more on grid imports.
+
+The breakdown of costs associated with a procurement policy that participating consumers choose is shown in \cref{fig:10-2025-IE-p1-ci_costandrev}.
+Note that revenues from selling the excess electricity to the regional grid at market prices can be treated as ”negative costs” and subtracted from the net procurement cost.
+The results show that a CFE targets of 80\%--95\% can be achieved at a small cost premium to 100\%~RES policy with solar, wind and batteries.
+However, what stands out in the plot is the rapid increase of procurement costs for high 24/7 CFE targets. 
+For example, 98\% CFE target has cost premium of 54\% over 100\% the annual matching policy; while the last 2\% of hourly matching more than doubles the costs.
 
@@
     24/7 CFE procurement mitigates system-level \co \newline 
-    emissions through two distinct mechanisms: "profile" and "volume".
+    emissions through two distinct mechanisms: \enquote{profile} and \enquote{volume}.
 The mechanisms origin from distinct aspects of the interplay between the 24/7 CFE procurement and the background electricity grids.
@@
 Second, a \textit{volume} mechanism: even the cost-optimal procurement strategy for 24/7 hourly matching might include some amount of excess clean energy.
-If total \gls{cfe} generation of assets procured by 24/7 participants exceeds demand in a given hour and region, the “excess CFE” is not counted toward a CFE target; however, it is clean electricity that can potentially be stored (using batteries or LDES), or sold to the regional grid.
-As for the latter, "excess CFE" might displace emitting grid generators or reduce the need to import electricity from neighbouring areas.
+If total \gls{cfe} generation of assets procured by 24/7 participants exceeds demand in a given hour, the \enquote{excess CFE} is not counted toward a CFE target; however, it is clean electricity that can potentially be stored (using batteries or LDES), or sold to the regional grid.
+As for the latter, excess CFE might displace emitting grid generators or reduce the need to import electricity from neighbouring areas.
 
@@
 In particular, the profile mechanism contributes significantly to overall emissions reductions, with a major share across all zones regardless of their configuration.
-
-Additional insights into decarbonisation mechanisms can be gained by examining the emission reductions achieved through 100\%~RES and 100\% 24/7 CFE matching policies.
-\cref{fig:10-hourly-annual.pdf} compares the decarbonisation impact within a local zone of the two procurement policies in relative terms (percent point p.a.), with a counterfactual scenario where no consumers engage in voluntary clean electricity procurement.
-The figure demonstrates that, even though the absolute impact of procurement policies diminishes over time, the relative impact of 24/7 CFE on system-level emissions \textit{increases over time} when compared to 100\%~RES.
-This phenomenon is attributable to the self-cannibalisation effect of wind and solar that influences the value of additional renewable capacity.
-This is relevant in regions where governments adhere to ambitious \gls{necp} targets, like Ireland and Germany (NB Denmark is an outlier with an exceptional RES target exceeding 100\% of national electricity demand for 2030).
-The profile mechanism maintains its relevancy even when renewable energy generators undergo self-cannibalization.
-The volume mechanism retains, or even amplifies, its relevance, by leveraging a diversified portfolio of procured resources by 24/7 participants, including batteries, long-term energy storage, and advanced clean firm technologies.
-Consequently, clean electricity is not only available but can also be sold to the background grid during periods when system-wide wind and solar generation is scarce.
 
@@
 \end{figure}
+
+Additional insights into decarbonisation mechanisms can be gained by examining the emission reductions achieved through 100\%~RES and 100\% 24/7 CFE matching policies.
+\cref{fig:10-hourly-annual.pdf} compares the decarbonisation impact within a local zone of the two procurement policies in relative terms (percent point p.a.), with a counterfactual scenario where no consumers engage in voluntary clean electricity procurement.
+The figure demonstrates that, even though the absolute impact of procurement policies diminishes over time, the relative impact of 24/7 CFE on system-level emissions \textit{increases over time} when compared to 100\%~RES.
+This phenomenon is attributable to the self-cannibalisation effect of wind and solar that influences the value of additional renewable capacity.
+This is relevant in regions where governments adhere to ambitious \gls{necp} targets, like Ireland and Germany (NB Denmark is an outlier with an exceptional RES target exceeding 100\% of national electricity demand for 2030).
+The profile mechanism maintains its relevancy even when renewable energy generators undergo self-cannibalization.
+The volume mechanism retains, or even amplifies, its relevance, by leveraging a diversified portfolio of procured resources by 24/7 participants, including batteries, long-term energy storage, and advanced clean firm technologies.
+Consequently, clean electricity is not only available but can also be sold to the background grid during periods when system-wide wind and solar generation is scarce.

### 2023-10-15 manuscript/sections/supplementary_3.tex
si: add annex with the mathematical problem

@@
 %S3: Mathematical formulation of clean energy procurement
-\cite{srivastavCarbonCaptureUtilisation} %test supplementary references
+We introduce new model components (parameters, variables, constraints) into the PyPSA-Eur model to represent voluntary clean energy procurement.
+By incorporating these into the mathematical problem, we model a situation where a fraction of electricity demand in a particular bidding zone is voluntarily committed to procuring clean energy with a desired strategy.
+The fraction is hereinafter referred to as \enquote{participating consumers}.
+
+\textbf{100\% annual matching --} The annual (\enquote{volumetric}) renewable matching strategy is modelled with a constraint (\ref{eqn:RES100}). 
+The constraint requires participating consumers to purchase just enough renewable electricity to match all of their electricity consumption on an annual basis.
+
+More formally, the sum of all dispatch $g_{r,t}$ of contracted renewable generators $r\in RES$ over the year $t\in T$ is equal to the sum of the annual demand $d_t$ of participating consumers:
+\begin{equation}
+\sum_{r\in RES, t\in T} g_{r,t} = \sum_{t\in T} d_t
+\label{eqn:RES100}
+\end{equation}
+
+The contracted renewable generators must be new, i.e., they must be additional to the system.
+Procured generators can be sited only in the local bidding zone; thus, we model the \enquote{best case} of the annual matching strategy.
+
+\textbf{24/7 CFE hourly matching --} The hourly matching strategy is modelled with a constraint (\ref{eqn:CFE}).
+In this case, participating consumers commit to match their electricity demand with carbon-free electricity (CFE) throughout the year on an hourly basis.
+The 24/7~CFE procurement framework is based on the methodologies and metrics paper by Google~(2021) \cite{google-methodologies}.
+
+More formally, the hourly generation from the procured CFE generators $r\in CFE$, discharge and charge from the procured storage technologies $s\in STO$, plus imports of electricity from the regional grid $im_t$ multiplied by the grid's hourly CFE factor $CFE_t$ minus the excess of the CFE supply must be higher or equal than a certain CFE target $x$ multiplied by the total load of participating consumers:
+
+\begin{equation}
+    \begin{split}
+        \sum_{r\in CFE, t\in T} g_{r,t} &+ \sum_{s\in STO, t\in T} \left(\bar{g}_{s,t} - \underline{g}_{s,t}\right) \\
+        &- \sum_{t\in T} ex_t + \sum_{t\in T} CFE_t \cdot im_t \geq x \cdot \sum_{t\in T} d_t
+    \end{split}
+\label{eqn:CFE}
+\end{equation}
+
+% On CFE target
+\noindent where \textit{CFE target} $x$[\%] measures the degree to which hourly electricity consumption is matched with carbon-free electricity generation. 
+Equation (\ref{eqn:CFE}) thus allows for controlling \textit{the quality score} of the 24/7~CFE procurement by adjusting the parameter $x$.
+The best quality score---100\% CFE---means that every kilowatt-hour of electricity consumption is met by carbon-free sources at all times.
+
+% On locational matching and additionality
+Similarly to the hourly matching strategy, the contracted generators must be additional to the system and can be sited only in the local bidding zone.
+
+% On excess
+Note that if total electricity generation of assets procured by participating consumers exceeds demand in a given hour, the \enquote{excess} carbon-free electricity is not counted toward a CFE target.
+Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices.
+We set a constraint on the total amount of excess generation sold to the regional grid, setting the limit to 20\% of the total annual demand of participating consumers.
+The necessity of this limit is addressed in the \cref{sec:discussion}. The wholesale market prices are derived from dual variables of a nodal energy balance constraint.
+
+% On bilinear term due to grid CFE factor
+The grid CFE factor $CFE_t$ can be seen as the percentage of clean electricity in each MWh of imported electricity to supply demand of participating consumers in a given hour.
+Note that in equation (\ref{eqn:CFE}), $CFE_t$ is affected by additional CFE resources procured by the participating consumers. 
+This introduces a nonconvex term to the optimisation problem. 
+The nonconvexity can be avoided by treating the grid CFE factor as a parameter that is iteratively updated (starting with $CFE_t =0 \,~\forall t$).
+We find that one forward pass (i.e. 2 iterations) yields very good convergence.
+
+The methodology to calculate the grid hourly CFE factor is described in the prior work of the authors \cite{riepin-zenodo-systemlevel247}.

### 2023-10-17 manuscript/manuscript.tex
manuscript: final literature items and formatting
manuscript: internal revision

@@
 \newcommand{\N}{\mathbb{N} }
-\newcommand{\co}{\ce{CO2}~}
+\newcommand{\co}{\ce{CO2}}
 \def\el{${}_{\textrm{el}}$}
@@
 
-	\title{On the means, costs, and system-level impacts of the 24/7 carbon-free energy procurement}
+	\title{On the means, costs, and system-level impacts of 24/7 carbon-free energy procurement}
 
@@
 
-All code, input data and results are published under an open license.
-The code to reproduce the experiments is available at GitHub: \href{https://github.com/Irieo/247-procurement-paper}{github.com/Irieo/247-procurement-paper}.
+All code, input data and results are published under an open license. The code to reproduce the experiments is available at GitHub \cite{github-247CFEpaper}.
 

### 2023-10-17 manuscript/sections/abstract.tex
manuscript: title, keywords, and final touches main text
manuscript: internal revision

@@
 % The 5 things a good abstract needs:
-
 % 1. Introduce the topic: what we know 
@@
 % 5. Tell us what your work teaches us: what we conclude and why this is important
-
 % aim ~200 words | 225 words used
-
 A growing number of public and private energy buyers are interested in 24/7 carbon-free energy (CFE) procurement, which means that every kilowatt-hour of electricity consumption is met by carbon-free sources at all times.
-It has the potential to overcome the limitations of established procurement schemes, such as the temporal mismatch between clean electricity supply and buyers' demand that is inherent to "volumetric" matching.
-Yet it is unclear whether 24/7 CFE procurement is only effective during the early stages of the energy transition, or if it has a system-level impact in a variety of regional contexts.
+It has the potential to overcome the limitations of established procurement schemes, such as the temporal mismatch between clean electricity supply and buyers' demand that is inherent to \enquote{volumetric} matching.
+Yet it is unclear how 24/7 CFE procurement affects the rest of the power system, and whether this effect is consistent across regional contexts and different levels of system cleanness.
 We use a mathematical model to systematically examine different designs, optimal procurement strategies, costs, and impacts of the 24/7 CFE matching, both for participating buyers and for regions where voluntary procurement occurs.
-We examine the mechanisms driving system-level co emissions reduction and how they vary across regions and over time.
-Our results indicate that voluntary clean energy procurement commitments have consistent effects on participants and the electricity system.
-Even as grids become cleaner over time, the hourly matching strategy remains significant in reducing CO$_2$ emissions.
+We examine mechanisms driving system-level emissions reduction and how they vary across regions and over time.
+Our results indicate that clean energy procurement commitments have consistent beneficial effects on participants and the electricity system.
+Even as grids become cleaner over time, the hourly matching strategy contributes significantly to system-level emissions reduction.
 In addition, voluntary commitments to 24/7 CFE have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
-This work generalises the implications of clean energy procurement strategies in the context of evolving national energy and climate policies.

### 2023-10-17 manuscript/sections/discussion.tex
manuscript: internal revision

@@
 Another important finding of this work that confirms prevailing understanding is that 24/7 CFE matching creates an early market for advanced energy technologies.
-Citing an episode of the David Roberts' Volts podcast: \enquote{One reason energy nerds are excited about the 24/7 trend is that it's going to pull forward in time a bunch of questions (and investment decisions) that were going to face grids trying to reach 100 percent CFE anyway} \cite{roberts-intro247CFE}.
 Further research is needed to better understand how 24/7 CFE commitments push advanced energy technologies along their learning curves, and to estimate the potential economic impact on global decarbonisation costs.
@@
 A deeper look at the role of voluntary clean energy procurement commitments in grid decarbonisation reveals that the hourly matching strategy retains its significance in reducing system-level emissions, even as grids become cleaner over time.
-We examined two distinct mechanisms through which 24/7 CFE procurement facilitates system decarbonization: "profile" and "volume".
+We examined two distinct mechanisms through which 24/7 CFE procurement facilitates system decarbonization: \enquote{profile} and \enquote{volume}.
 As companies adapt their procurement strategies, it is important to understand how these mechanisms perform across different grid locations and years.
@@
 %Limitations: electricity sector only
-First, only the electricity sector is included in the mathematical model of the European energy system.
-The research focus of this study justifies it.
-However, it is important to acknowledge that the electricity sector is not an isolated system, but it is closely linked with other energy sectors, such as heat and transport.
+First, only the electricity sector is included in the mathematical model of the European energy system, which is justified by the research focus.
+However, it is important to acknowledge that the electricity sector is not an isolated system, but is increasingly becoming linked with other energy sectors, such as heat and transport.
 Brown et al. (2018) discuss the synergies of sector coupling in the integrated European energy system \cite{brownSynergiesSectorCoupling2018}.
@@
 Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices, until the excess constraint is reached (see \cref{sec:si_3} for detail).
-The problem with the uncostrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement.
+The problem with the uncostrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement; and if system-wide renewable expansion is constrained, the cost-optimal solution may be to use the excess CFE to \enquote{relax} the constraint, increasing the renewable portfolio of participating consumers.
 Similar \enquote{spillover effect} problem has been observed and discussed by Xu et al. (2022) \cite{xu-247CFE-SSRN}.
@@
 Some proponents of alternative strategies contend that 24/7 CFE, or \enquote{temporal matching}, may not represent the most effective approach to emissions reduction. 
-Instead, they suggest that companies, in their pursuit to reduce system-level carbon emissions, should focus on system-wide impact as measured via short-run marginal emissions accounting (\enquote{emissions matching}).
-This argument is based on the rationale that optimising procurement and deployment of carbon-free generators and batteries to cover 24/7 consumption will be different from optimising the assets to \enquote{offset emissions} based on the short-run marginal emission estimates of the grid.
+This argument is based on the rationale that optimising procurement and deployment of carbon-free generators and batteries to cover own consumption 24/7 with clean electricity is a different strategy to optimising the assets specifically to displace \enquote{as much emissions as possible}.
+
+One of the alternative strategies could be that companies, in their pursuit to reduce system-level carbon emissions, focus on system-wide impact as measured via short-run marginal emissions accounting (\enquote{emissions matching}).
 Xu~et~al.
-(2023) bring this discussion from the realm of arguments into quantitative analysis, discovering that \enquote{emissions matching strategies have zero or near-zero long-run impact on system-level \co emissions} \cite{princeton-247CFEvsEmissionality}.
+(2023) bring this discussion from the realm of arguments into quantitative analysis, concluding that \enquote{emissions matching strategies have zero or near-zero long-run impact on system-level \co emissions} \cite{princeton-247CFEvsEmissionality}.
+
+Another alternative strategy could be that companies do annual matching with \enquote{overprocurement}, i.e., covering own consumption on an annual volumentric basis plus procuring some more clean electricity on top.
+Such strategy could be implemented at low cost, e.g., with solar PV.
+However, as shown in \cref{subsec:mechanisms}, this strategy would not be as effective in reducing system-level emissions as 24/7 CFE matching, especially in the context of evolving national energy and climate policies.
+Further, such a strategy would not promote innovation and pull forward in time research and investment decisions in advanced energy technologies, such as long-duration energy storage and clean firm generators.
 

### 2023-10-17 manuscript/sections/introduction.tex
manuscript: internal revision

@@
 Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe. 
-The European Union (\gls{eu}) has committed to achieve net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}.
-National climate initiatives span the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have \co emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.
+The European Union (\gls{eu}) has committed to achieving net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}.
+National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have \co emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.
 
@@
 
-Many public and private energy buyers join this effort by purchasing clean energy to demonstrate their sustainability credentials.
-The established schemes for voluntary clean energy procurement are the Guarantees of Origin (\gls{go}s) in Europe and the Renewable Energy Certificates (\gls{rec}s) in the United States.
+Many public and private energy buyers have joined this effort by purchasing clean energy to demonstrate their sustainability credentials. 
+The established certification schemes for voluntary clean energy procurement are the Guarantees of Origin (\gls{go}s) in Europe and the Renewable Energy Certificates (\gls{rec}s) in the United States.
 A common feature of these schemes is that renewable energy credits are \enquote{unbundled} from megawatt-hours of energy and can be traded numerous times on specialized markets before being retired.
 The owner gets to claim environmental benefits when \enquote{retiring} (i.e. using) the certificate.
-The unbundled renewable energy credits, however, have been criticized for not ensuring a physical match between renewable energy generation and consumption, and for absence of evidence that such schemes drive build-out of additional renewable energy capacity \cite{bjorn-RECSnatcom-2022, gillenwater-2014, re100report-2020, spglobal-recs, bock-icelandGOproblem}.
+The unbundled renewable energy credits, however, have been criticized for not ensuring a physical match between renewable energy generation and consumption \cite{spglobal-recs, bock-icelandGOproblem, re100report-2020}, and for absence of evidence that such schemes drive build-out of additional renewable energy capacity \cite{bjorn-RECSnatcom-2022, gillenwater-2014}.
 
@@
 
-\textbf{The key problem --} When \gls{ci} consumers purchase renewable credits, either via unbundled schemes or via bundled \gls{ppa}s, renewable energy supply is typically matched over a long period of time with buyers' energy demands.
+\textbf{The key problem --} When \gls{ci} consumers purchase renewable credits, either via unbundled schemes or via bundled \gls{ppa}s, renewable energy supply is typically matched over a long period of time with buyers' energy demand.
 As an example, more than 400 members of the RE100 group \cite{re100report-2020} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
-Even the \enquote{best case} of the 100\% annual matching commitments, where energy buyers sign \gls{ppa}s with renewable energy generators located within a local grid, has a major problem -- the temporal mismatch between renewable energy supply and electricity demand.
+Even the \enquote{best case} of 100\% annual matching commitments, where energy buyers sign \gls{ppa}s with renewable energy generators located within a local grid, has a major problem: the temporal mismatch between renewable energy supply and electricity demand.
 In hours when wind and solar generation is low, energy buyers have to depend on carbon-emitting technologies, like coal and gas, available on local markets.
-As a result, the 100\% annual renewable matching approach does not entirely eliminate carbon emissions from the energy buyers portfolio.
-Furthermore, 100\% annual matching approach keeps electricity buyers exposed to price volatility, as the price of electricity on the wholesale markets can vary significantly from hour to hour.
+As a result, the 100\% annual renewable matching approach does not entirely eliminate carbon emissions from the energy buyer's portfolio.
+Furthermore, the 100\% annual matching approach keeps electricity buyers exposed to price volatility, as the price of electricity on the wholesale markets can vary significantly from hour to hour.
 
@@
 
-\textbf{Proposed solution: 24/7 CFE --} There is growing interest from the leaders in the clean energy procurement to move beyond the 100\% annual matching approach.
-The next frontier in the clean energy procurement is the 24/7 Carbon-Free Energy (\gls{cfe}) procurement, which aims to match clean energy supply with electricity demand on an \textit{hourly basis}.
-Thus, 24/7~CFE procurement has the potential to eliminate all greenhouse gas emissions associated with electricity use of the parciticpating companies.
-Furthermore, 24/7~CFE procurement is focused on \textit{carbon-free} rather than renewable energy, which opens up opportunities for a broad range of advanced energy technologies, such as long-duration energy storage (\gls{ldes}) or new clean firm power generators that are needed for deep decarbonisation of the energy systems.
+\textbf{One proposed solution: 24/7 CFE --} There is growing interest from the leaders in the clean energy procurement to move beyond the 100\% annual matching approach.
+One approach is called 24/7 Carbon-Free Energy (\gls{cfe}) procurement, which aims to match clean energy supply with electricity demand on an \textit{hourly basis}.
+Thus, 24/7~CFE procurement has the potential to eliminate all greenhouse gas emissions associated with electricity use of the participating companies.
+Furthermore, 24/7~CFE procurement is focused on \textit{carbon-free} rather than renewable energy, which opens up opportunities for a broad range of advanced energy technologies, such as long-duration energy storage (\gls{ldes}) or new clean firm power generators that are needed for deep decarbonisation of energy systems.
 
-Google broke the 24/7 ground in 2020 by announcing its commitment to entirely on the 24/7~CFE approach at all its data centres and campuses worldwide by 2030 \cite{google-247by2030}.
+Google led the 24/7 movement in 2020 by announcing its commitment to cover the demand at all its data centres and campuses worldwide using the 24/7 CFE approach by 2030 \cite{google-247by2030}.
 Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.
 Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. \enquote{100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases} \cite{Microsoft-vision}. 
-The list of entities that have committed to 24/7~CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}.
-In 2021, an international group of energy suppliers, buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact \cite{gocarbonfree247}.
+The list of entities that have committed to 24/7 CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}.
+In 2021, an international group of energy suppliers, electricity buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact \cite{gocarbonfree247}.
 With over 135 signatories, the group aims to \enquote{develop and scale high-impact technologies, energy policies, procurement practices, aand solutions to make 24/7 Carbon-Free Energy achievable for all}.
@@
 
-\textbf{Existing literature on 24/7 CFE --} The growing interest in the means, costs and the system-level impacts of hourly \gls{cfe} procurement created a need for a quantitative analysis of the approach.
-The existing model-based studies on 24/7~CFE approach are very recent.
+\textbf{Existing literature on 24/7 CFE --} The growing interest in the means, costs and the system-level impacts of hourly \gls{cfe} procurement has created a need for a quantitative analysis of the approach.
+There is relatively little research on the system-level impacts of 24/7~CFE procurement; and it is all fairly recent.
 The first to incorporate it into the electricity system planning model were Xu et al.
@@
 
-\textbf{Contribution --} The goal of this work is to systematically explore different designs, optimal procurement strategies, costs, benefits and impacts of the 24/7~CFE matching approach, both for participating buyers and for regions where voluntary procurement occurs.
+\textbf{Contribution --} The novelty of this study is to go beyond case studies and show in a systematic way, across many regions and levels of energy transition, how voluntary commitments to 24/7 CFE procurement impact participating buyers and regions where voluntary procurement occurs.
+We explore different designs, optimal procurement strategies, costs, benefits and system-level impacts of the 24/7~CFE matching approach.
 Our analysis focuses on four regions within the European energy system with unique characteristics, and we vary the analysis years to track the evolution of the energy system.

### 2023-10-17 manuscript/sections/methods.tex
manuscript: internal revision

@@
-The modelling workflow is based on the PyPSA --- an open-source software framework for simulating and optimising modern energy systems \cite{brownPyPSAPythonPower2018}.
-
-\textbf{Optimisation model --} The simulations were carried out with the modified version of the PyPSA-Eur model \cite{PyPSA-Eur-github}. 
+\textbf{Optimisation model --} The simulations were carried out with the modified version of the open European power system model PyPSA-Eur, built using the open framework PyPSA \cite{brownPyPSAPythonPower2018}.
 The objective of the model is to minimise the annualised system-wide costs of meeting energy demand within the modelled system, while adhering to all relevant engineering, reliability, and policy constraints.
@@
 The 24/7~CFE procurement framework is based on the methodologies and metrics paper by Google (2021) \cite{google-methodologies}.
-The framework considers various \gls{cfe} supply options for the participating consumers, including procurement of own generation resources and storage assets, and electricity imports from the local grid.
+The framework considers various \gls{cfe} supply options for the participating consumers, including procurement of their own generation resources and storage assets, and electricity imports from the local grid.
 The framework also allows for controlling \textit{the quality score} of the 24/7~CFE procurement by setting the target threshold for the minimum share of hours when the hourly \gls{cfe} supply meets the hourly electricity demand.
-The quality score is hereinafter referred to as \enquote{CFE target}, which takes values in percent points, e.g., 95\%, 99\%, 100\%.
+The quality score is hereinafter referred to as the \enquote{CFE target}, which takes values in percent points, e.g., 95\%, 99\%, 100\%.
 The higher the CFE target, the higher the quality of the 24/7~CFE supply; see equation [TODO] for details.
@@
 From a modelling perspective, a five-year step changes many system parameters.
-In particular, technology costs decline as a result of economies of scale and incremental innovation, \gls{necp}s become tighter, and some legacy power plants go out of business.
+In particular, technology costs decline as a result of economies of scale and incremental innovation, \gls{necp}s become tighter, \co prices increase, and some legacy power plants go out of business.
 The problem is solved with a temporal resolution of 2920 snapshots, representing a 3-hourly average of the hourly time-series data.
@@
 \begin{itemize}[-]
-    \item \textit{100\% annual matching}: participating buyers meet their annual energy demand on volumetric basis with additional renewable energy procurement;
+    \item \textit{100\% annual matching}: participating buyers meet their energy demand on an annual volumetric basis with additional renewable energy procurement;
     \item \textit{24/7 hourly matching}: participating buyers optimise their investment and operational decisions mixing procurement of additional generation and storage resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality target.
@@
 
-We setup the study design so that the procurement strategies are modelled under the same conditions.
-In both cases (i) procurement is possible with generators from the same bidding zone only (i.e., we model the \enquote{best case} of the annual matching strategy); (ii) the same set of consumers participate; (iii) the same set of constraints is applied to the rest of the electricity system.
+We set up the study design so that the procurement strategies are modelled under the same conditions.
+In both cases (i) procurement is only possible with generators from the same bidding zone (i.e., we model the \enquote{best case} of the annual matching strategy); (ii) the same set of consumers participate; (iii) the same set of constraints is applied to the rest of the electricity system.
 For benchmarking, we also model \textit{a reference case}: participating buyers have no voluntary environmental commitments and purchase all their electricity from the local grid.
@@
     \item \textit{Palette 2} -- all above plus a long-duration energy storage (\gls{ldes}) that is expected to be commercially available in the near future; 
-    \item \textit{Palette 3} -- all above plus promising advanced technologies that are in prototype stage today, but are expected to be commercially available in the future: Allam cycle power plant with \gls{ccs}\footnote{Allam cycle is a natural gas power plant with up to 100\% of carbon capture and sequestration}, and advanced dispatchable generators -- a stand-in for clean firm technologies, such as advanced geothermal or advanced nuclear systems.
+    \item \textit{Palette 3} -- all above plus promising advanced technologies that are in prototype stage today, but are expected to be commercially available in the future: (i) Allam cycle power plant with \gls{ccs}\footnote{Allam cycle is a natural gas power plant with up to 100\% of carbon capture and sequestration} to represent a technology option with higher operational expences (\gls{opex}), and (ii) \enquote{an advanced dispatchable generator}, a stand-in for clean firm technologies with higher capital expences (\gls{capex}), such as advanced geothermal or nuclear systems.
 \end{itemize}
@@
 For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion. 
-Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, use own indicative assumptions.
+Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, use our own indicative assumptions.
 

### 2023-10-17 manuscript/sections/results.tex
manuscript: internal revision

@@
 The participating consumers can attain the 24/7~CFE procurement targets by co-optimizing local procurement using mature technologies, designated as \textit{palette~1}, and by importing electricity from the local grid.
-Afterward, we delve deeper into the scenario space, altering highlighted parameters to explore various alternatives and address the following questions:
+Afterward, we delve deeper into the scenario space, altering selected parameters to explore various alternatives and address the following questions:
 
@@
 In the reference case, only 54\% of demand is met with \gls{cfe}.
-100\% RES---the best case for the annual renewable matching policy---results in 83\% fraction. 
+100\% RES---the best case for the annual renewable matching policy---results in a 83\% fraction.
 Consequently, CFE targets beyond 85\% yield higher share of hourly demand met with \gls{cfe} than 100\%~RES.
-Another notable trend in \cref{fig:10-2025-IE-p1-used} is that participanting consumers rely more on procured resources and less on grid imports with higher CFE targets.
-When targets approach 100\%, participanting consumers cannot rely on electricity imports from the grid, since the grid supply mix contains some carbon content in almost all hours.
+Another notable trend in \cref{fig:10-2025-IE-p1-used} is that participating consumers rely more on procured resources and less on grid imports with higher CFE targets.
+When targets approach 100\%, participating consumers cannot rely on electricity imports from the grid, since the grid supply mix contains some carbon content in almost all hours.
 
@@
 
-Voluntary procurement of clean electricity also helps decarbonise electricity system as a whole.
+Voluntary procurement of clean electricity also helps decarbonise the electricity system as a whole.
 We explore this effect by plotting \co emissions in the local region of the participating consumers, i.e. Ireland (\cref{fig:10-2025-IE-p1-zone_emissions}).
-Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2~Mt\co.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021.
-A strong decreasing trend is expected, since Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
-The modelling results indicate that a commitment to 100\% 24/7~CFE in 2025 from 10\% of the \gls{ci} electricity demand could yield a reduction in Irish emissions by 0.6~MtCO$_2$ annually, in contrast to a scenario absent voluntary procurement.
+Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2 Mt\co/a.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021.
+A strong decreasing trend is expected, since the Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
+The modelling results indicate that a commitment to 100\% 24/7~CFE in 2025 from 10\% of the \gls{ci} electricity demand could yield a reduction in Irish emissions by 0.6~Mt\co/a, in contrast to a scenario absent voluntary procurement.
 This reduction equates to 14\% of the total emissions from the Irish power sector.
@@
 
-The following analysis unveils the modelled cost-optimal procurement strategies for each each procurement policy (\cref{fig:10-2025-IE-p1-ci_capacity}).
+The following analysis unveils the modelled cost-optimal procurement strategies for each procurement policy (\cref{fig:10-2025-IE-p1-ci_capacity}).
 In Ireland, 10\% of the \gls{ci} sector's demand yields a load of 220~MW.
@@
 The breakdown of costs associated with a procurement policy that participating consumers choose is shown in \cref{fig:10-2025-IE-p1-ci_costandrev}.
-Note that revenues from selling the excess electricity to the regional grid at market prices can be treated as ”negative costs” and subtracted from the net procurement cost.
+Note that revenues from selling the excess electricity to the regional grid at market prices can be treated as \enquote{negative costs} and subtracted from the net procurement cost.
 The results show that a CFE targets of 80\%--95\% can be achieved at a small cost premium to 100\%~RES policy with solar, wind and batteries.
@@
 \begin{res}
-    The cost premium of 24/7 procurement with high CFE targets may substantially decrease if advanced energy technologies available for commercial scale-up. 
+    The cost premium of 24/7 procurement with high CFE targets may substantially decrease if advanced energy technologies are available for commercial scale-up. 
 \end{res}
@@
 Indeed, in the periods when not much wind or solar is available, matching every kWh of electricity consumption with carbon-free electricity on hourly basis is not an easy task.
-Battery storage technology is cost-optimal for shifting surplus a power supply by a couple of hours.
+Battery storage technology is cost-optimal for shifting surplus power supply by a couple of hours.
 However, bridging extended periods of low wind and sun with battery storage is expensive.
@@
 
-The results in \cref{fig:10-2025-IE-p23-ci_procurement} reflect a case when 24/7~CFE participants have an access to a wider palette of technologies, including \gls{ldes} and advanced clean firm generators, such as advanced geothermal systems, advanced nuclear or Allam cycle generators with \gls{ccs}.
+The results in \cref{fig:10-2025-IE-p23-ci_procurement} reflect a case when 24/7~CFE participants have access to a wider palette of technologies, including \gls{ldes} and advanced clean firm generators, such as advanced geothermal systems, advanced nuclear or Allam cycle generators with \gls{ccs}.
 
@@
 Here we assume an underground hydrogen storage in salt caverns with energy storage cost of 2.5~\euro/kWh [\cref{tab:tech_costs}].
-A \gls{ldes} system helps to bridge hours with no renewable feed-in. 
+An \gls{ldes} system helps to bridge hours with no renewable feed-in. 
 As a result, the required portfolio of renewable capacity and procurement costs are reduced, especially for high CFE targets.
-Thus, 100\% 24/7~CFE policy has a cost premium of 42\% above 100\%~RES, which is significantly lower than w/o \gls{ldes}.
+Thus, 100\% 24/7~CFE policy has a cost premium of 42\% above 100\%~RES, which is significantly lower than without \gls{ldes}.
 
@@
 \cref{fig:10-2025-DEPL-p3-4plots} depicts outcomes for the selected regions of Germany and Poland. 
-Germany, is selected due to its substantial connections to regions with relatively clean grids, such as France and Denmark, and it is the largest electricity consumer in Europe.
-In contrast, Poland has a smaller electricity demand, as well as historical coal dependence, opposition from its coal industry, and a paucity of governmental support for renewables.
+Germany is selected due to its extensive interconnections with neighbouring regions with relatively clean grids, such as France and Denmark, and its status as the largest electricity consumer in Europe.
+In contrast, Poland has a smaller electricity demand. 
+Moreover, the Polish energy system typically has higher carbon intensity, largely due to its historical dependence on coal resources.
 The participation rate is maintained at 10\% of the \gls{ci} sector in both regions, aligning with the base scenario.\footnote{A 10\% participation rate within the \gls{ci} sector corresponds to loads of 3.8~GW in Germany and 1.1~GW in Poland.}
@@
 For the realization of strict CFE targets, both the Allam cycle with \gls{ccs} and advanced clean firm generators are incorporated into the technology mix. 
-This entry of two advanced technologies into the optimal solution space diverges from the Irish findings, where solely the Allam cycle turbine is deemed cost-optimal. 
+This entry of two advanced technologies into the optimal solution space diverges from the Irish findings, where solely the \gls{opex}-heavy Allam cycle turbine is deemed cost-optimal. 
 The difference is likely attributable to Germany and Poland being more extensively interconnected with the broader European electricity grid compared to Ireland. 
@@
 Consequently, lower CFE targets (like 80\%) are met with higher share of electricity imports.
-Secondly, participanting consumers depend on their own procurement of \gls{cfe} resources and storage, limiting imports from the background grid to achieve strict CFE targets. 
+Secondly, participating consumers depend on their own procurement of \gls{cfe} resources and storage, limiting imports from the background grid to achieve strict CFE targets. 
 This effect stays consistent with the base scenario.
@@
 
-\subsection{Unpacking 24/7 CFE procurement's role in grid decarbonisation}
+\subsection{Understanding the mechanism of 24/7 CFE procurement in grid decarbonisation}
 \label{subsec:mechanisms}
@@
 First, a \textit{profile} mechanism: participants doing 24/7 hourly matching procure clean energy resources that better match their demand patterns. 
-As certain consumers timely align their demand with \gls{cfe} supply, the need for dispatchable generation that can firm intermittent renewable supply is lower in the rest of the system. 
+As certain consumers align their demand with \gls{cfe} supply on hourly basis, the need for dispatchable generation that can firm intermittent renewable supply is lower in the rest of the system. 
 This mechanism can reduce the utilisation of fossil-based generators, such as \gls{ocgt} power plants, which typically ramp up when wind and solar resources are scarce.
@@
 We conduct an experiment to isolate the decarbonisation effects of the volume and profile mechanisms.
-In the experiment, we reran the optimization with fixing an excess electricity sold to the grid to zero (NB excess is still possible, but can either be stored or curtailed). 
+In the experiment, we reran the optimization while fixing an excess electricity sold to the grid to zero (NB excess is still possible, but must be either stored or curtailed). 
 Such a model setup includes only a profile decarbonisation mechanism. 

### 2023-10-18 manuscript/sections/methods.tex
manuscript: move CFE problem from SI to methods

@@
 
-\textbf{Clean energy procurement --} We introduce new model components (parameters, variables, constraints) to model voluntary clean energy procurement.
-By incorporating these into the mathematical problem, we model a situation when a fraction of electricity demand in a particular bidding zone is committed to procuring additional clean energy with a desired strategy.
+\textbf{Clean energy procurement model --} We introduce new model components (parameters, variables, constraints) into the PyPSA-Eur model to represent voluntary clean energy procurement.
+By incorporating these into the mathematical problem, we model a situation where a fraction of electricity demand in a particular bidding zone is voluntarily committed to procuring clean energy with a desired strategy.
 The fraction is set at 10\% of the total \gls{ci} electricity demand in a particular bidding zone, hereinafter referred to as \enquote{participating consumers}.
-The participating consumers are modelled as a single entity with a baseload demand profile.
-Accordingly, the model co-optimises the procurement and operational decisions of the participating consumers to meet their electricity demand in accordance with the procurement strategy they have chosen.
-The mathematical formulation of the clean energy procurement strategies is provided in the supplementary material [\labelcref{sec:si_3}].
+The model co-optimises procurement and operational decisions of the participating consumers to meet their electricity demand in accordance with the procurement strategy they have chosen.
 
-The 24/7~CFE procurement framework is based on the methodologies and metrics paper by Google (2021) \cite{google-methodologies}.
+We model and compare two procurement strategies:
+
+\begin{itemize}[-]
+    \item \textit{100\% annual matching}: participating buyers meet their energy demand on an annual volumetric basis with additional renewable energy procurement;
+    \item \textit{24/7 hourly matching}: participating buyers optimise their investment and operational decisions mixing procurement of additional generation and storage resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality score.
+    \item For benchmarking, we also model \textit{a reference case}: participating buyers have no voluntary environmental commitments and purchase all their electricity from the local grid.
+\end{itemize}
+
+\textit{100\% annual matching --} The annual volumetric renewable matching strategy is modelled with a constraint (\ref{eqn:RES100}). 
+More formally, the sum of all dispatch $g_{r,t}$ of contracted renewable generators $r\in RES$ over the year $t\in T$ is equal to the sum of the annual demand $d_t$ of participating consumers:
+\begin{equation}
+\sum_{r\in RES, t\in T} g_{r,t} = \sum_{t\in T} d_t
+\label{eqn:RES100}
+\end{equation}
+
+The contracted renewable generators must be new, i.e., they must be additional to the system.
+Procured generators can be sited only in the local bidding zone; thus, we model the \enquote{best case} of the annual matching strategy.
+
+\textit{24/7 CFE hourly matching --} The hourly matching strategy is modelled with a constraint (\ref{eqn:CFE}).
+The 24/7~CFE procurement framework is based on the methodologies and metrics paper by Google~(2021) \cite{google-methodologies}.
 The framework considers various \gls{cfe} supply options for the participating consumers, including procurement of their own generation resources and storage assets, and electricity imports from the local grid.
-The framework also allows for controlling \textit{the quality score} of the 24/7~CFE procurement by setting the target threshold for the minimum share of hours when the hourly \gls{cfe} supply meets the hourly electricity demand.
-The quality score is hereinafter referred to as the \enquote{CFE target}, which takes values in percent points, e.g., 95\%, 99\%, 100\%.
-The higher the CFE target, the higher the quality of the 24/7~CFE supply; see equation [TODO] for details.
+
+More formally, the hourly generation from the procured CFE generators $r\in CFE$, discharge and charge from the procured storage technologies $s\in STO$, plus imports of electricity from the regional grid $im_t$ multiplied by the grid's hourly CFE factor $CFE_t$ minus the excess of the CFE supply must be higher or equal than a certain CFE score $x$ multiplied by the total load of participating consumers:
+
+\begin{equation}
+    \begin{split}
+        \sum_{r\in CFE, t\in T} g_{r,t} &+ \sum_{s\in STO, t\in T} \left(\bar{g}_{s,t} - \underline{g}_{s,t}\right) \\
+        &- \sum_{t\in T} ex_t + \sum_{t\in T} CFE_t \cdot im_t \geq x \cdot \sum_{t\in T} d_t
+    \end{split}
+\label{eqn:CFE}
+\end{equation}
+
+% On CFE target
+\noindent where \textit{CFE score} $x$[\%] measures the degree to which hourly electricity consumption is matched with carbon-free electricity generation. 
+Equation (\ref{eqn:CFE}) thus allows for controlling \textit{the quality score} of the 24/7~CFE procurement by adjusting the parameter $x$.
+The best quality score---100\% CFE---means that every kilowatt-hour of electricity consumption is met by carbon-free sources at all times.
+
+% On locational matching and additionality
+Similarly to the hourly matching strategy, the contracted generators must be additional to the system and can be sited only in the local bidding zone.
+
+% On excess
+Note that if total electricity generation of assets procured by participating consumers exceeds demand in a given hour, the \enquote{excess} carbon-free electricity is not counted toward a CFE score.
+Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices.
+We set a constraint on the total amount of excess generation sold to the regional grid, setting the limit to 20\% of the total annual demand of participating consumers.\footnote{In \nameref{sec:discussion}, we explain the rationale behind this limit and discuss the implications of this assumption.}
+The wholesale market prices are derived from dual variables of a nodal energy balance constraint.
+
+% On bilinear term due to grid CFE factor
+The CFE factor of the regional grid ($CFE_t$) can be seen as the percentage of clean electricity in each MWh of imported electricity to supply demand of participating consumers in a given hour. 
+To compute $CFE_t$, we consider both the hourly electricity mix in the local bidding zone and the emissionality of imported electricity from the neighbouring zones.
+The methodology to calculate the grid CFE factor is described in the prior work of the authors \cite{riepin-zenodo-systemlevel247}.
+
+Note that in equation (\ref{eqn:CFE}), $CFE_t$ is affected by additional CFE resources procured by the participating consumers. 
+This introduces a nonconvex term to the optimisation problem. 
+The nonconvexity can be avoided by treating the grid CFE factor as a parameter that is iteratively updated (starting with $CFE_t =0 \,~\forall t$).
+We find that one forward pass (i.e. 2 iterations) yields very good convergence.
 
 \textbf{Model scope --} Geographically, the model encompasses the entire \gls{entsoe} area, which covers the entire European electricity system.\footnote{Islands that are not connected to the main European system, such as Malta, Crete and Cyprus, are excluded from the model.}
-In this study, electricity demand, supply and power transmission infrastructure\footnote{Alternating current lines at and above 220kV voltage level and all high voltage direct current lines.} are clustered to 37 individual bidding zones \cite{PyPSAEur-docs-spatialresolution}.
+In this study, electricity demand, supply and power transmission infrastructure (alternating current lines at and above 220~kV voltage level and all high voltage direct current lines) are clustered to 37 individual bidding zones \cite{PyPSAEur-docs-spatialresolution}.
 Thus, each zone represents a country; some countries straddling different synchronous areas are split into individual bidding zones, such as DK1 (West) and DK2 (East).
-The participating consumers can be located in either of the four selected zones: Ireland, Denmark (zone DK1), Germany, or Poland.
+
+Participating consumers can be located in either of the four selected zones: Ireland, Denmark (zone DK1), Germany, or Poland.
 The comparison of results across these zones allows us to generalize the implications of voluntary clean energy procurement, taking into account factors such as electricity demand, weather, availability of renewable resources, existing electricity generation capacity mix, and national energy policies, among other factors.
@@
 From a modelling perspective, a five-year step changes many system parameters.
-In particular, technology costs decline as a result of economies of scale and incremental innovation, \gls{necp}s become tighter, \co prices increase, and some legacy power plants go out of business.
+In particular, technology costs decline as a result of economies of scale and incremental innovation, \gls{necp}s become tighter, \co~prices increase, and some legacy power plants go out of business.
 The problem is solved with a temporal resolution of 2920 snapshots, representing a 3-hourly average of the hourly time-series data.
-
-\textbf{Procurement strategies in scope --} We model and compare two procurement strategies:
-
-\begin{itemize}[-]
-    \item \textit{100\% annual matching}: participating buyers meet their energy demand on an annual volumetric basis with additional renewable energy procurement;
-    \item \textit{24/7 hourly matching}: participating buyers optimise their investment and operational decisions mixing procurement of additional generation and storage resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality target.
-\end{itemize}
-
-We set up the study design so that the procurement strategies are modelled under the same conditions.
-In both cases (i) procurement is only possible with generators from the same bidding zone (i.e., we model the \enquote{best case} of the annual matching strategy); (ii) the same set of consumers participate; (iii) the same set of constraints is applied to the rest of the electricity system.
-For benchmarking, we also model \textit{a reference case}: participating buyers have no voluntary environmental commitments and purchase all their electricity from the local grid.
 

### 2023-10-18 manuscript/manuscript.tex
manuscript: move CFE problem from SI to methods
manuscript: internal revision, final minor improvements

@@
 
-We thank the following people for fruitful discussions on the 24/7 carbon-free energy procurement and the art of energy system modelling: Fabian Neumann, Elisabeth Zeyen, Devon Swezey.
+We thank the following people for fruitful discussions on the 24/7 carbon-free energy procurement and the art of energy system modelling: Fabian Neumann, Elisabeth Zeyen, Devon Swezey, Brian Denvir, Marc Oman, Jesse Jenkins and research staff of the Zero carbon Energy systems Research and Optimization Laboratory (ZERO Lab) at Princeton University.
 
@@
 All code, input data and results are published under an open license. The code to reproduce the experiments is available at GitHub \cite{github-247CFEpaper}.
-
-We publish an online dashboard with results for the entire scenario space alongside the paper \href{}{DASHBOARD}.
 
@@
 
-\section{Mathematical formulation of clean energy procurement}
-\label{sec:si_3}
-\input{sections/supplementary_3.tex}
-
 % \addcontentsline{toc}{section}{Supplementary References}

### 2023-10-18 manuscript/sections/conclusion.tex
manuscript: internal revision, final minor improvements

--- 2023-04-04 manuscript/sections/conclusion.tex
@@
-Taken together, we show that 24/7-CFE commitment by corporate sector stakeholders is a step above and beyond the 100\% annual renewable matching in paving the path toward the carbon net-zero energy systems.
-This voluntary commitment also delivers a range of benefits to the society by 
-(i) triggering innovation, availability and earlier utilisation of advanced clean firm generation needed for the transformation of energy systems to a complete carbon net-zero state, 
-(ii) reducing system emissions, and (iii) reducing system flexibility needs.
+In this work, we systematically examined the means, costs, and the system-level impacts of the 24/7 carbon-free energy matching. 
+We find that 24/7 matching is a viable and effective strategy for electricity buyers aiming to eliminate their own carbon footprint and contribute to wider system decarbonisation.
+Voluntary commitments to the hourly matching strategy have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
+The evidence holds across geographical locations and is robust to sensitivity analyses.
+Even as grids become cleaner over time, the 24/7 matching strategy retains its significance in reducing system-level emissions, which is essential in light of evolving national energy and climate policies.

### 2023-10-18 manuscript/sections/discussion.tex
manuscript: internal revision, final minor improvements

@@
 As companies adapt their procurement strategies, it is important to understand how these mechanisms perform across different grid locations and years.
-Interestingly, the disparity between the annual renewable (\enquote{volumentric}) matching and 24/7 CFE hourly matching strategies in decarbonisation outcomes becomes ever more evident as electricity grids become cleaner.
+Interestingly, the disparity between the annual (\enquote{volumetric}) matching with renewable energy and 24/7 CFE hourly matching strategies in decarbonisation outcomes becomes ever more evident as electricity grids become cleaner.
 This phenomenon illustrates the effectiveness of 24/7 CFE procurement in supporting system decarbonisation within the context of evolving national energy and climate policies.
@@
 % on the impact on back up flexibility needs
-From a system-wide benefits perspective, voluntary commitments to 24/7 CFE reduce the need for flexibility in background electricity systems. 
+From a system-wide perspective, voluntary commitments to 24/7 CFE reduce the need for flexibility in background electricity systems. 
 There will be less investment in gas-fired peaker generators, as well as less need for battery storage elsewhere in the system.
@@
 The \enquote{excess CFE} can be defined as the total amount of carbon-free electricity supply exceeding the demand of the participating consumers in a given period of time.
-Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices, until the excess constraint is reached (see \cref{sec:si_3} for detail).
-The problem with the uncostrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement; and if system-wide renewable expansion is constrained, the cost-optimal solution may be to use the excess CFE to \enquote{relax} the constraint, increasing the renewable portfolio of participating consumers.
+Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices, until the excess constraint is reached. 
+The constraint restricts the volume of excess electricity sold to the regional grid, ensuring it does not surpass 20\% of the annual demand from participating consumers.
+The problem with the uncostrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement; and if system-wide renewable expansion is constrained, the cost-optimal solution may be to use the excess clean electricity to \enquote{relax} the constraint, increasing the renewable portfolio of participating consumers.
 Similar \enquote{spillover effect} problem has been observed and discussed by Xu et al. (2022) \cite{xu-247CFE-SSRN}.
@@
 Xu~et~al.
-(2023) bring this discussion from the realm of arguments into quantitative analysis, concluding that \enquote{emissions matching strategies have zero or near-zero long-run impact on system-level \co emissions} \cite{princeton-247CFEvsEmissionality}.
+(2023) bring this discussion from the realm of arguments into quantitative analysis, concluding that \enquote{emissions matching strategies have zero or near-zero long-run impact on system-level CO$_2$ emissions} \cite{princeton-247CFEvsEmissionality}.
+The reason for this, citing the authors, is that voluntary carbon-free energy procurement under this strategy almost exclusively displaces other carbon-free energy rather than fossil fuels.
 

### 2023-10-18 manuscript/sections/introduction.tex
manuscript: internal revision, final minor improvements

@@
 Our analysis focuses on four regions within the European energy system with unique characteristics, and we vary the analysis years to track the evolution of the energy system.
-Additionally, we examine the underlying mechanisms that drive the system-level reduction of \co emissions, and examine how they perform over time and across regions. 
+Additionally, we examine the underlying mechanisms that drive the system-level reduction of CO$_2$ emissions, and examine how they perform over time and across regions. 
 This work is a follow-up to the earlier public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.
@@
 
-The remainder of the paper is structured as follows: \cref{sec:methods} gives a brief summary of methodology, sources of model input data, and the experimental setup. 
+The remainder of the paper is structured as follows: \cref{sec:methods} introduces a mathematical model of clean energy procurement strategies and gives a brief summary of the methodology, sources of model input data, and the experimental setup.
 The results are presented and discussed in \cref{sec:results} and put in perspective in \cref{sec:discussion}. 
 The work is concluded in \cref{sec:conclusion}. 
-\nameref{sec:si} provides further details about model assumptions, background energy system parametrisation, and the clean energy procurement mathematical model.
+\nameref{sec:si} provides further details about model assumptions and parametrisation of the background energy system.

### 2023-10-18 manuscript/sections/methods.tex
manuscript: internal revision, final minor improvements

@@
 \textit{100\% annual matching --} The annual volumetric renewable matching strategy is modelled with a constraint (\ref{eqn:RES100}). 
-More formally, the sum of all dispatch $g_{r,t}$ of contracted renewable generators $r\in RES$ over the year $t\in T$ is equal to the sum of the annual demand $d_t$ of participating consumers:
+More formally, the sum of all dispatch $g_{r,t}$ of contracted renewable generators $r\in RES$ over the year $t\in T$ is equal to the annual electricity demand of participating consumers:
 \begin{equation}

### 2023-10-18 manuscript/sections/results.tex
manuscript: internal revision, final minor improvements

@@
 From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
-From a system perspective, we analyze how voluntary clean energy procurement impacts \co emissions in the region and the \enquote{demand pull} for advanced energy technologies.
+From a system perspective, we analyze how voluntary clean energy procurement impacts CO$_2$ emissions in the region and the \enquote{demand pull} for advanced energy technologies.
 
@@
 
-Considering the large scenario space, this work presents results for a selection of scenario branches that generalise the system impacts of 24/7 CFE procurements.
-We publish an online dashboard with results for the entire scenario space alongside the paper, see \nameref{sec:code}.
+Considering the large scenario space, this work presents results for a selection of scenario branches that generalise the system impacts of the 24/7 carbon-free energy procurement.
+We publish all code to reproduce the experiments under open license alongside the paper. 
+See \nameref{sec:code}.
 
@@
 
+\cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of participating consumers.
+The average emissions rate is derived by dividing the total CO$_2$ emissions linked to the electricity consumption of participating consumers by the total kilowatt-hours (kWh) consumed.
+Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case.
+If participating consumers follow 100\%~RES policy, the emission rate is reduced to 60~g\co/kWh.
+This yields a considerable emission rate reduction compared to the reference case.
+The 24/7~CFE procurement with targets above 85\% helps the participating consumers to reduce emissions further beyond the treshhold set by the 100\%~RES. 
+At the 100\% CFE target, participating consumers attain a zero emission rate associated with their electricity consumption, as they perfectly align demand and \gls{cfe} supply on an hourly basis.
+
+Voluntary procurement of clean electricity also helps decarbonise the electricity system as a whole.
+We explore this effect by plotting CO$_2$ emissions in the local region of the participating consumers, i.e. Ireland (\cref{fig:10-2025-IE-p1-zone_emissions}).
+Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2 Mt\co/a.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~MtCO$_2$ in 2021.
+A strong decreasing trend is expected, since the Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
+The modelling results indicate that a commitment to 100\% 24/7~CFE in 2025 from 10\% of the \gls{ci} electricity demand could yield a reduction in Irish emissions by 0.6~Mt\co/a, in contrast to a scenario absent voluntary procurement.
+This reduction equates to 14\% of the total emissions from the Irish power sector.
+100\%~RES can also facilitate system-level CO$_2$ emissions reductions (as depicted by the left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, 24/7~CFE attains superior emissions reductions when the CFE target surpasses 85\%.
+
 \begin{figure}[t]
@@
         \vspace{-0.2cm}
-        \caption{\co emissions in the local region (Ireland).}
+        \caption{CO$_2$ emissions in the local region (Ireland).}
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
@@
 \end{figure}
-
-\cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of participating consumers.
-Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case.
-If participating consumers follow 100\%~RES policy, the emission rate is reduced to 60~g\co/kWh.
-This yields a considerable emission rate reduction compared to the reference case.
-The 24/7~CFE procurement with targets above 85\% helps the participating consumers to reduce emissions further beyond the treshhold set by the 100\%~RES. 
-At the 100\% CFE target, participating consumers attain a zero emission rate associated with their electricity consumption, as they perfectly align demand and \gls{cfe} supply on an hourly basis.
-
-Voluntary procurement of clean electricity also helps decarbonise the electricity system as a whole.
-We explore this effect by plotting \co emissions in the local region of the participating consumers, i.e. Ireland (\cref{fig:10-2025-IE-p1-zone_emissions}).
-Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2 Mt\co/a.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~Mt\co in 2021.
-A strong decreasing trend is expected, since the Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
-The modelling results indicate that a commitment to 100\% 24/7~CFE in 2025 from 10\% of the \gls{ci} electricity demand could yield a reduction in Irish emissions by 0.6~Mt\co/a, in contrast to a scenario absent voluntary procurement.
-This reduction equates to 14\% of the total emissions from the Irish power sector.
-100\%~RES can also facilitate system-level \co emissions reductions (as depicted by the left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, 24/7~CFE attains superior emissions reductions when the CFE target surpasses 85\%.
 
@@
 
-The impact of 24/7 hourly CFE procurement on system-level \co emissions is notable in both Germany and Poland, as depicted in \cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions}.
-In the absence of any procurement strategy, carbon emissions from the power sectors of Germany and Poland are projected to be 118.8~Mt\co and 83.8~Mt\co in 2025, respectively.%
+The impact of 24/7 hourly CFE procurement on system-level CO$_2$ emissions is notable in both Germany and Poland, as depicted in \cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions}.
+In the absence of any procurement strategy, carbon emissions from the power sectors of Germany and Poland are projected to be 118.8~MtCO$_2$ and 83.8~MtCO$_2$ in 2025, respectively.%
 \footnote{Despite Germany consuming more electricity, the similar scale of power sector carbon emissions between the two countries can be attributed to Poland's significantly higher emission intensity in its electricity mix.}
 By engaging in voluntary clean energy procurement, \gls{ci} consumers can drive notable decarbonisation in the local regions, exceeding the benchmarks set by \gls{necp}s.
-For instance, in Germany, even a 10\% participation rate under a 100\%~RES policy can diminish national emissions by 11.1~Mt\co annually; remarkably, the 24/7~CFE approach can amplify this impact to up to 14~Mt\co/a, given a CFE target of 100\%.
+For instance, in Germany, even a 10\% participation rate under a 100\%~RES policy can diminish national emissions by 11.1~MtCO$_2$ annually; remarkably, the 24/7~CFE approach can amplify this impact to up to 14~Mt\co/a, given a CFE target of 100\%.
 
@@
         \centering
-        \caption{\co emissions in the local region (Germany).}
+        \caption{CO$_2$ emissions in the local region (Germany).}
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/zone_emissions.pdf}
@@
         \centering
-        \caption{\co emissions in the local region (Poland).}
+        \caption{CO$_2$ emissions in the local region (Poland).}
         \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/zone_emissions.pdf}
@@
         \centering
-        \caption{\co emissions in the local region (Ireland).}
+        \caption{CO$_2$ emissions in the local region (Ireland).}
         \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/zone_emissions.pdf}
@@
 \begin{res}
-    24/7 CFE procurement mitigates system-level \co \newline 
+    24/7 CFE procurement mitigates system-level CO$_2$ \newline 
     emissions through two distinct mechanisms: \enquote{profile} and \enquote{volume}.
@@
 
-In the previous sections, we demonstrated that 24/7 clean energy procurement results in a substantial reduction of \co emissions in local electricity grids (Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions}).
+In the previous sections, we demonstrated that 24/7 clean energy procurement results in a substantial reduction of CO$_2$ emissions in local electricity grids (Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions}).
 In this section, we examine the underlying mechanisms that drive these observed reductions, so as to better understand how clean energy procurement and emissions reduction interrelate.

### 2023-10-20 manuscript/sections/discussion.tex
manuscript: arXiv version

@@
 Some proponents of alternative strategies contend that 24/7 CFE, or \enquote{temporal matching}, may not represent the most effective approach to emissions reduction. 
-This argument is based on the rationale that optimising procurement and deployment of carbon-free generators and batteries to cover own consumption 24/7 with clean electricity is a different strategy to optimising the assets specifically to displace \enquote{as much emissions as possible}.
+This argument is based on the rationale that optimising procurement and deployment of carbon-free generators and batteries to cover consumption 24/7 with clean electricity is a different strategy to optimising the assets specifically to displace \enquote{as much emissions as possible}.
 
@@
 
-Another alternative strategy could be that companies do annual matching with \enquote{overprocurement}, i.e., covering own consumption on an annual volumentric basis plus procuring some more clean electricity on top.
+Another alternative strategy could be that companies do annual matching with \enquote{overprocurement}, i.e., covering their own consumption on an annual volumentric basis plus procuring some more clean electricity on top.
 Such strategy could be implemented at low cost, e.g., with solar PV.

### 2023-10-20 manuscript/sections/introduction.tex
manuscript: arXiv version

@@
 The European Union (\gls{eu}) has committed to achieving net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}.
-National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have \co emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.
+National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have CO$_2$ emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.
 

### 2023-10-23 scripts/copy_config.py
scripts: consistent (Black) formatting

@@ -1,18 +1,19 @@
-
 from shutil import copy
 
 import os
 
-files = [
-    "config.yaml",
-    "Snakefile",
-    "scripts/solve_network.py"
-]
+files = ["config.yaml", "Snakefile", "scripts/solve_network.py"]
 
-if __name__ == '__main__':
-    if 'snakemake' not in globals():
+if __name__ == "__main__":
+    if "snakemake" not in globals():
         from helper import mock_snakemake
-        snakemake = mock_snakemake('copy_config')
+
+        snakemake = mock_snakemake("copy_config")
 
     for f in files:
-        copy(f,os.path.join(snakemake.config['results_dir'], snakemake.config['run'], 'configs'))
+        copy(
+            f,
+            os.path.join(
+                snakemake.config["results_dir"], snakemake.config["run"], "configs"
+            ),
+        )

### 2023-10-23 scripts/make_summary.py

@@ -5,29 +5,42 @@ import yaml
 
 
 def summarise_scalars():
-
     df = pd.DataFrame()
 
-    fns = list(filter(lambda k: ('{}'.format(participation+'/'+year+'/'+zone+'/'+tech_palette)) in k, snakemake.input))
+    fns = list(
+        filter(
+            lambda k: (
+                "{}".format(
+                    participation + "/" + year + "/" + zone + "/" + tech_palette
+                )
+            )
+            in k,
+            snakemake.input,
+        )
+    )
 
     for fn in fns:
-        policy = fn[fn.rfind("/")+1:-5]
+        policy = fn[fn.rfind("/") + 1 : -5]
         print(policy)
-        with open(fn,'r') as f:
+        with open(fn, "r") as f:
             results = yaml.safe_load(f)
 
-        float_keys = [k for k in results.keys() if isinstance(results[k],float)]
+        float_keys = [k for k in results.keys() if isinstance(results[k], float)]
 
-        df[policy] = pd.Series({k : results[k] for k in float_keys})
+        df[policy] = pd.Series({k: results[k] for k in float_keys})
 
     df.to_csv(snakemake.output["summary"])
 
+
 if __name__ == "__main__":
     # Detect running outside of snakemake and mock snakemake for testing
-    if 'snakemake' not in globals():
+    if "snakemake" not in globals():
         from _helpers import mock_snakemake
-        snakemake = mock_snakemake('make_summary', palette='p1', zone='IE', year='2025',  participation='10')    
-    
+
+        snakemake = mock_snakemake(
+            "make_summary", palette="p1", zone="IE", year="2025", participation="10"
+        )
+
     # When running via snakemake
     tech_palette = snakemake.wildcards.palette
     zone = snakemake.wildcards.zone
@@ -35,4 +48,3 @@ if __name__ == "__main__":
     participation = snakemake.wildcards.participation
 
     summarise_scalars()
-

### 2023-10-23 scripts/merge_plots.py

@@ -5,9 +5,12 @@ from PyPDF2 import PdfMerger, PdfReader
 
 if __name__ == "__main__":
     # Detect running outside of snakemake and mock snakemake for testing
-    if 'snakemake' not in globals():
+    if "snakemake" not in globals():
         from _helpers import mock_snakemake
-        snakemake = mock_snakemake('merge_plots', palette='p1', zone='IE', year='2025', participation='10') 
+
+        snakemake = mock_snakemake(
+            "merge_plots", palette="p1", zone="IE", year="2025", participation="10"
+        )
 
 # Call the PdfFileMerger
 mergedObject = PdfMerger()
@@ -15,7 +18,7 @@ path = snakemake.output[0][:-11]
 
 # Loop through existing plots in output repository and append them
 for file in os.listdir(path):
-    mergedObject.append(PdfReader(path+f'{file}', 'rb'))
+    mergedObject.append(PdfReader(path + f"{file}", "rb"))
 
 # Write merged pdf
-mergedObject.write(path+"/"+"SUMMARY.pdf")
+mergedObject.write(path + "/" + "SUMMARY.pdf")

### 2023-10-23 scripts/plot_maps.py

@@ -1,4 +1,3 @@
-
 """
 Function for plotting a generation capacity fleet and transmission infrastructure
 considering pypsa-eur-sec component structure
@@ -26,24 +25,30 @@ import cartopy.mpl.ticker as cticker
 
 
 def assign_location(n):
-    '''
+    """
     Assign bus location per each individual component
     From pypsa-eur-sec/plot_network.py
-    '''
+    """
     for c in n.iterate_components(n.one_port_components | n.branch_components):
         ifind = pd.Series(c.df.index.str.find(" ", start=4), c.df.index)
         for i in ifind.value_counts().index:
             # these have already been assigned defaults
-            if i == -1: continue
+            if i == -1:
+                continue
             names = ifind.index[ifind == i]
-            c.df.loc[names, 'location'] = names.str[:i]
+            c.df.loc[names, "location"] = names.str[:i]
 
 
-def plot_map(network, components=["links", "stores", "storage_units", "generators"],
-             bus_size_factor=6e4, transmission=True, with_legend=True):
-    '''Plotting function for stages 1 and 2'''
+def plot_map(
+    network,
+    components=["links", "stores", "storage_units", "generators"],
+    bus_size_factor=6e4,
+    transmission=True,
+    with_legend=True,
+):
+    """Plotting function for stages 1 and 2"""
 
-    tech_colors = snakemake.config['tech_colors']
+    tech_colors = snakemake.config["tech_colors"]
 
     n = network.copy()
     assign_location(n)
@@ -53,12 +58,12 @@ def plot_map(network, components=["links", "stores", "storage_units", "generator
 
     # Drop virtual stores
     n.stores.drop(n.stores[n.stores.index.str.contains("EU")].index, inplace=True)
-    
-    # For now simple drop -> to add 2/3/4 stage difference
-    if 'google' in n.buses.index:
-        n.mremove('Bus', ['google'])
 
-    # Empty dataframe indexed with electrical buses 
+    # For now simple drop -> to add 2/3/4 stage difference
+    if "datacenter" in n.buses.index:
+        n.mremove("Bus", ["datacenter"])
+
+    # Empty dataframe indexed with electrical buses
     index = pd.DataFrame(index=n.buses.index)
     df = pd.DataFrame(index=n.buses.index)
 
[…]

### 2023-10-23 scripts/plot_summary.py

@@ -1,108 +1,148 @@
-
 import pandas as pd
 import matplotlib.pyplot as plt
 from matplotlib.ticker import FormatStrFormatter
 import numpy as np
-#allow plotting without Xwindows
+
+# allow plotting without Xwindows
 import matplotlib
 from pyrsistent import s
 from xarray import align
-matplotlib.use('Agg')
+
+matplotlib.use("Agg")
 
 from solve_network import palette, geoscope
 
 
 def used():
-
     fig, ax = plt.subplots()
-    fig.set_size_inches((6,4.5))
+    fig.set_size_inches((6, 4.5))
 
-    typ = ["local","grid"]
+    typ = ["local", "grid"]
 
-    ldf = df.loc[[f"ci_fraction_clean_used_{t}" for t in typ]].rename({f"ci_fraction_clean_used_{t}" : t for t in typ})
+    ldf = df.loc[[f"ci_fraction_clean_used_{t}" for t in typ]].rename(
+        {f"ci_fraction_clean_used_{t}": t for t in typ}
+    )
     ldf.columns = ldf.columns.map(rename_scen)
-    ldf.rename({"local" : "PPA", "grid" : "grid imports"}, inplace=True)
-    ldf = (100. * ldf).round(1)
+    ldf.rename({"local": "PPA", "grid": "grid imports"}, inplace=True)
+    ldf = (100.0 * ldf).round(1)
 
-    yl_ref = ldf.loc[:,'no\npolicy'].sum()
-    yl_100RES = ldf.loc[:,'100%\nRES'].sum()
-    plt.axhline(y = yl_ref, color = 'gray', linestyle="--", linewidth=0.8)
-    plt.axhline(y = yl_100RES, color = 'gray', linestyle="--", linewidth=0.8)
-    plt.axvline(x = 0.5, color = 'gray', linestyle="--")
-    plt.text(4, yl_ref-6,f'Reference case: {int(round(yl_ref,0))}'+'%', 
-            horizontalalignment='left', bbox=dict(facecolor='w', alpha=0.5)) 
-    
-    #Drop reference scenario before plotting
+    yl_ref = ldf.loc[:, "no\npolicy"].sum()
+    yl_100RES = ldf.loc[:, "100%\nRES"].sum()
+    plt.axhline(y=yl_ref, color="gray", linestyle="--", linewidth=0.8)
+    plt.axhline(y=yl_100RES, color="gray", linestyle="--", linewidth=0.8)
+    plt.axvline(x=0.5, color="gray", linestyle="--")
[…]

### 2023-10-23 scripts/solve_network.py

@@ -1,7 +1,6 @@
-
 import pypsa, numpy as np, pandas as pd
-
 import logging
+
 logger = logging.getLogger(__name__)
 import sys
 import os
@@ -14,249 +13,389 @@ from _helpers import override_component_attrs
 
 
 def palette(tech_palette):
-    '''
+    """
     Define technology palette at CI node based on wildcard value
-    '''
+    """
 
-    if tech_palette == 'p1':
+    if tech_palette == "p1":
         clean_techs = ["onwind", "solar"]
         storage_techs = ["battery"]
         storage_chargers = ["battery charger"]
         storage_dischargers = ["battery discharger"]
 
-    elif tech_palette == 'p2':
+    elif tech_palette == "p2":
         clean_techs = ["onwind", "solar"]
         storage_techs = ["battery", "hydrogen"]
         storage_chargers = ["battery charger", "H2 Electrolysis"]
         storage_dischargers = ["battery discharger", "H2 Fuel Cell"]
 
-    elif tech_palette == 'p3':
-        clean_techs = ["onwind", "solar", "allam_ccs", "adv_geothermal"]  #"adv_nuclear", "adv_geothermal"
+    elif tech_palette == "p3":
+        clean_techs = [
+            "onwind",
+            "solar",
+            "allam_ccs",
+            "adv_geothermal",
+        ]  # "adv_nuclear", "adv_geothermal"
         storage_techs = ["battery", "hydrogen"]
         storage_chargers = ["battery charger", "H2 Electrolysis"]
         storage_dischargers = ["battery discharger", "H2 Fuel Cell"]
-        
-    else: 
-        print(f"'palette' wildcard must be one of 'p1', 'p2' or 'p3'. Now is {tech_palette}.")
+
+    else:
+        print(
+            f"'palette' wildcard must be one of 'p1', 'p2' or 'p3'. Now is {tech_palette}."
+        )
         sys.exit()
 
     return clean_techs, storage_techs, storage_chargers, storage_dischargers
 
 
 def geoscope(zone, area):
-    '''
+    """
     basenodes_to_keep -> geographical scope of the model
     country_nodes -> scope for national RES policy constraint
     node -> zone where C&I load is located
-    '''
[…]

### 2023-10-23 scripts/summarise_network.py

@@ -1,5 +1,3 @@
-
-
 import pypsa, numpy as np, pandas as pd
 import yaml
 from solve_network import palette, geoscope, timescope
@@ -7,8 +5,7 @@ from _helpers import override_component_attrs
 
 
 def summarise_network(n, policy, tech_palette):
-
-    #tech_palette options
+    # tech_palette options
     clean_techs = palette(tech_palette)[0]
     storage_techs = palette(tech_palette)[1]
     storage_chargers = palette(tech_palette)[2]
@@ -19,317 +16,505 @@ def summarise_network(n, policy, tech_palette):
     elif policy == "res":
         n_iterations = 2
     elif policy == "cfe":
-        n_iterations = snakemake.config['solving']['options']['n_iterations']
+        n_iterations = snakemake.config["solving"]["options"]["n_iterations"]
 
-    name = snakemake.config['ci']['name']
-    node = geoscope(zone, area)['node']
+    name = snakemake.config["ci"]["name"]
+    node = geoscope(zone, area)["node"]
 
     clean_gens = [name + " " + g for g in clean_techs]
     clean_dischargers = [name + " " + g for g in storage_dischargers]
     clean_chargers = [name + " " + g for g in storage_chargers]
 
-
     # for calculation of system expansion beyond CI node in pypsa-eur-sec brownfield network for {year}
-    exp_generators = ['offwind-ac-%s' % year, 
-                    'offwind-dc-%s' % year, 
-                    'onwind-%s' % year, 
-                    'solar-%s' % year, 
-                    'solar rooftop-%s' % year]
-    exp_links = ['OCGT-%s' % year]
-    exp_chargers = ['battery charger-%s' % year, 'H2 Electrolysis-%s' % year]
-    exp_dischargers = ['battery discharger-%s' % year, 'H2 Fuel Cell-%s' % year]
-
+    exp_generators = [
+        "offwind-ac-%s" % year,
+        "offwind-dc-%s" % year,
+        "onwind-%s" % year,
+        "solar-%s" % year,
+        "solar rooftop-%s" % year,
+    ]
+    exp_links = ["OCGT-%s" % year]
+    exp_chargers = ["battery charger-%s" % year, "H2 Electrolysis-%s" % year]
+    exp_dischargers = ["battery discharger-%s" % year, "H2 Fuel Cell-%s" % year]
 
[…]

### 2023-10-25 scripts/copy_config.py
license: add reuse compatibility

@@ -1,3 +1,7 @@
+# SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
+#
+# SPDX-License-Identifier: MIT
+
 from shutil import copy
 
 import os

### 2023-10-25 scripts/plot_maps.py

@@ -1,3 +1,7 @@
+# SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
+#
+# SPDX-License-Identifier: MIT
+
 """
 Function for plotting a generation capacity fleet and transmission infrastructure
 considering pypsa-eur-sec component structure

### 2023-10-25 scripts/plot_summary.py

@@ -1,3 +1,7 @@
+# SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
+#
+# SPDX-License-Identifier: MIT
+
 import pandas as pd
 import matplotlib.pyplot as plt
 from matplotlib.ticker import FormatStrFormatter

### 2023-10-25 scripts/solve_network.py

@@ -1,3 +1,7 @@
+# SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
+#
+# SPDX-License-Identifier: MIT
+
 import pypsa, numpy as np, pandas as pd
 import logging
 

### 2023-10-25 scripts/summarise_network.py

@@ -1,3 +1,7 @@
+# SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
+#
+# SPDX-License-Identifier: MIT
+
 import pypsa, numpy as np, pandas as pd
 import yaml
 from solve_network import palette, geoscope, timescope

### 2023-10-25 scripts/_helpers.py
project: initial run pre-commit against all files

@@ -1,4 +1,4 @@
-# Snakemake mocking function 
+# Snakemake mocking function
 # see: https://github.com/PyPSA/pypsa-eur/blob/master/scripts/_helpers.py
 
 # SPDX-FileCopyrightText: 2017-2020 The PyPSA-Eur Authors
@@ -9,18 +9,73 @@ from pathlib import Path
 
 
 def override_component_attrs():
-
     # from https://github.com/PyPSA/pypsa-eur-sec/blob/93eb86eec87d34832ebc061697e289eabb38c105/scripts/solve_network.py
-    override_component_attrs = pypsa.descriptors.Dict({k : v.copy() for k,v in pypsa.components.component_attrs.items()})
-    override_component_attrs["Link"].loc["bus2"] = ["string",np.nan,np.nan,"2nd bus","Input (optional)"]
-    override_component_attrs["Link"].loc["bus3"] = ["string",np.nan,np.nan,"3rd bus","Input (optional)"]
-    override_component_attrs["Link"].loc["bus4"] = ["string",np.nan,np.nan,"4th bus","Input (optional)"]
-    override_component_attrs["Link"].loc["efficiency2"] = ["static or series","per unit",1.,"2nd bus efficiency","Input (optional)"]
-    override_component_attrs["Link"].loc["efficiency3"] = ["static or series","per unit",1.,"3rd bus efficiency","Input (optional)"]
-    override_component_attrs["Link"].loc["efficiency4"] = ["static or series","per unit",1.,"4th bus efficiency","Input (optional)"]
-    override_component_attrs["Link"].loc["p2"] = ["series","MW",0.,"2nd bus output","Output"]
-    override_component_attrs["Link"].loc["p3"] = ["series","MW",0.,"3rd bus output","Output"]
-    override_component_attrs["Link"].loc["p4"] = ["series","MW",0.,"4th bus output","Output"]
+    override_component_attrs = pypsa.descriptors.Dict(
+        {k: v.copy() for k, v in pypsa.components.component_attrs.items()}
+    )
+    override_component_attrs["Link"].loc["bus2"] = [
+        "string",
+        np.nan,
+        np.nan,
+        "2nd bus",
+        "Input (optional)",
+    ]
+    override_component_attrs["Link"].loc["bus3"] = [
+        "string",
+        np.nan,
+        np.nan,
+        "3rd bus",
+        "Input (optional)",
+    ]
[…]

### 2023-10-25 scripts/plot_maps.py

@@ -8,7 +8,7 @@ considering pypsa-eur-sec component structure
 
 Keep note that in this project each network has four stages:
 1) An input network (existing capacities)
-2) Regionally- and component-wise stripped input network (existing capacities) 
+2) Regionally- and component-wise stripped input network (existing capacities)
 3) (2) with policy adjustments for nuclear/lignite/etc.
    That yields a brownfield fleet for the target year -- an input for the optimization.
 4) Solved network

### 2023-10-25 scripts/plot_summary.py
pre-commit: add reuse license check

@@ -5,12 +5,7 @@
 import pandas as pd
 import matplotlib.pyplot as plt
 from matplotlib.ticker import FormatStrFormatter
-import numpy as np
-
-# allow plotting without Xwindows
 import matplotlib
-from pyrsistent import s
-from xarray import align
 
 matplotlib.use("Agg")
 

### 2023-10-25 scripts/solve_network.py

@@ -542,7 +542,7 @@ def add_ci(n, participation, year):
         p_set=load_profile(n, zone, profile_shape),
     )
 
-    # C&I following 24/7 approach is a share of all C&I load -> thus substract it from node's profile
+    # C&I following 24/7 approach is a share of all C&I load -> thus subtract it from node's profile
     n.loads_t.p_set[f"{node}"] -= n.loads_t.p_set[f"{name}" + " load"]
 
     # Add generators

### 2023-10-27 manuscript/manuscript.tex
license: add reuse compatibility
project: initial run pre-commit against all files
manuscript: update acknowledgements

@@
+% SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
+%
+% SPDX-License-Identifier: CC-BY-4.0
+
 \documentclass[11pt, 5p, nopreprintline]{elsarticle}
@@
 
-This work is an independent follow-up to the prior public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.
-The prior public report was supported by a research grant from Google LLC.
+We thank the following people for fruitful discussions on the 24/7 carbon-free energy procurement and the art of energy system modelling: Fabian Neumann, Elisabeth Zeyen, Devon Swezey, Brian Denvir, Marc Oman, Jesse Jenkins and research staff of the Zero carbon Energy systems Research and Optimization Laboratory (ZERO Lab) at Princeton University.
 
-We thank the following people for fruitful discussions on the 24/7 carbon-free energy procurement and the art of energy system modelling: Fabian Neumann, Elisabeth Zeyen, Devon Swezey, Brian Denvir, Marc Oman, Jesse Jenkins and research staff of the Zero carbon Energy systems Research and Optimization Laboratory (ZERO Lab) at Princeton University.
+Iegor Riepin was supported by the research grant from Google LLC.
+
+This work is a follow-up to the prior public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.
 

### 2023-10-29 manuscript/manuscript.tex
manuscript: prepare submission, single tex

@@
 \graphicspath{ 						% Allows for multiple directories
-	{../results/paper/},
+	{},
 	}
@@
 	\begin{abstract}
-		\input{sections/abstract.tex}
+		% The 5 things a good abstract needs:
+		% 1. Introduce the topic: what we know
+		% 2. State the unknown: what we don't know
+		% 3. Outline the methods: how we answer the questions
+		% 4. Preview the findings: what we learned
+		% 5. Tell us what your work teaches us: what we conclude and why this is important
+		% aim ~200 words | 225 words used
+		A growing number of public and private energy buyers are interested in 24/7 carbon-free energy (CFE) procurement, which means that every kilowatt-hour of electricity consumption is met by carbon-free sources at all times.
+		It has the potential to overcome the limitations of established procurement schemes, such as the temporal mismatch between clean electricity supply and buyers' demand that is inherent to \enquote{volumetric} matching.
+		Yet it is unclear how 24/7 CFE procurement affects the rest of the power system, and whether this effect is consistent across regional contexts and different levels of system cleanness.
+		We use a mathematical model to systematically examine different designs, optimal procurement strategies, costs, and impacts of the 24/7 CFE matching, both for participating buyers and for regions where voluntary procurement occurs.
+		We examine mechanisms driving system-level emissions reduction and how they vary across regions and over time.
+		Our results indicate that clean energy procurement commitments have consistent beneficial effects on participants and the electricity system.
+		Even as grids become cleaner over time, the hourly matching strategy contributes significantly to system-level emissions reduction.
+		In addition, voluntary commitments to 24/7 CFE have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
 	\end{abstract}
@@
 \label{sec:intro}
-\input{sections/introduction.tex}
+% Introduction Structure
+
+% 1. **Opening & Introduce the global momentum towards renewable energy adoption.**
+
+Climate change is driving a global effort to rapidly decarbonise electricity systems across the globe.
+The European Union (\gls{eu}) has committed to achieving net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}.
+National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have CO$_2$ emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.
+
+% 2. **Evolution, approaches and challenges of voluntary clean energy procurement**
+
+Many public and private energy buyers have joined this effort by purchasing clean energy to demonstrate their sustainability credentials.
+The established certification schemes for voluntary clean energy procurement are the Guarantees of Origin (\gls{go}s) in Europe and the Renewable Energy Certificates (\gls{rec}s) in the United States.
+A common feature of these schemes is that renewable energy credits are \enquote{unbundled} from megawatt-hours of energy and can be traded numerous times on specialized markets before being retired.
+The owner gets to claim environmental benefits when \enquote{retiring} (i.e. using) the certificate.
+The unbundled renewable energy credits, however, have been criticized for not ensuring a physical match between renewable energy generation and consumption \cite{spglobal-recs, bock-icelandGOproblem, re100report-2020}, and for absence of evidence that such schemes drive build-out of additional renewable energy capacity \cite{bjorn-RECSnatcom-2022, gillenwater-2014}.
+
+Some corporate and industrial (\gls{ci}) buyers recongnised the problems associated with the unbundled certificates and turned towards Power Purchase Agreements (\gls{ppa}s).
+When signing a \gls{ppa}, energy buyers pledge to buy both the energy and the environmental credits \enquote{bundled} to megawatt-hours.
+Market-driven procurement of renewable energy has become one of the major drivers of the energy transition: \gls{ppa}s are expected to account for one-fifth of utility solar PV and wind capacity expansion in 2023--2024, and almost twice as much (36\%) when China is excluded \cite{iea-REppa2023}.
+In some countries, such as Spain and Sweden, market-driven procurement of renewable energy capacity surpasses policy-driven capacity expansion \cite{iea-REppa2023}.
+
+\textbf{The key problem --} When \gls{ci} consumers purchase renewable credits, either via unbundled schemes or via bundled \gls{ppa}s, renewable energy supply is typically matched over a long period of time with buyers' energy demand.
+As an example, more than 400 members of the RE100 group \cite{re100report-2020} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
+Even the \enquote{best case} of 100\% annual matching commitments, where energy buyers sign \gls{ppa}s with renewable energy generators located within a local grid, has a major problem: the temporal mismatch between renewable energy supply and electricity demand.
+In hours when wind and solar generation is low, energy buyers have to depend on carbon-emitting technologies, like coal and gas, available on local markets.
+As a result, the 100\% annual renewable matching approach does not entirely eliminate carbon emissions from the energy buyer's portfolio.
+Furthermore, the 100\% annual matching approach keeps electricity buyers exposed to price volatility, as the price of electricity on the wholesale markets can vary significantly from hour to hour.
+
+% 3. **24/7 Carbon-free Energy Procurement**
+% Introduce the 24/7 CFE idea
+% Initiatives corporate and NGO interest in 24/7 Carbon-free Energy Procurement
+
+\textbf{One proposed solution: 24/7 CFE --} There is growing interest from the leaders in the clean energy procurement to move beyond the 100\% annual matching approach.
+One approach is called 24/7 Carbon-Free Energy (\gls{cfe}) procurement, which aims to match clean energy supply with electricity demand on an \textit{hourly basis}.
+Thus, 24/7~CFE procurement has the potential to eliminate all greenhouse gas emissions associated with electricity use of the participating companies.
+Furthermore, 24/7~CFE procurement is focused on \textit{carbon-free} rather than renewable energy, which opens up opportunities for a broad range of advanced energy technologies, such as long-duration energy storage (\gls{ldes}) or new clean firm power generators that are needed for deep decarbonisation of energy systems.
+
+Google led the 24/7 movement in 2020 by announcing its commitment to cover the demand at all its data centres and campuses worldwide using the 24/7 CFE approach by 2030 \cite{google-247by2030}.
+Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.
+Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. \enquote{100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases} \cite{Microsoft-vision}.
+The list of entities that have committed to 24/7 CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}.
+In 2021, an international group of energy suppliers, electricity buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact \cite{gocarbonfree247}.
+With over 135 signatories, the group aims to \enquote{develop and scale high-impact technologies, energy policies, procurement practices, aand solutions to make 24/7 Carbon-Free Energy achievable for all}.
+
+% 5. **24/7 model-based studies review**
+
+\textbf{Existing literature on 24/7 CFE --} The growing interest in the means, costs and the system-level impacts of hourly \gls{cfe} procurement has created a need for a quantitative analysis of the approach.
+There is relatively little research on the system-level impacts of 24/7~CFE procurement; and it is all fairly recent.
+The first to incorporate it into the electricity system planning model were Xu et al.
+(2022) \cite{xu-247CFE-SSRN}.\footnote{A working paper updates a prior report published in November 2021 investigating the system-level impacts of 24/7~CFE in two regions of the U.S.
+-- California and PJM \cite{xu-247CFE-report}.}
+The authors study the system-level impacts of 24/7~CFE procurement based on an example of California in the year 2030.
+In November 2022, IEA also released a model-based study on the 24/7~CFE, focusing on India and Indonesia \cite{ieaAdvancingDecarbonisationClean2022}.
+In early 2023, Peninsula Clean Energy published an own white paper introducing their modeling tool---MATCH (Matching Around-the-Clock Hourly energy)---and the results of the modeling indicating feasibility of the company's \enquote{24/7 renewable energy by 2025} goal \cite{peninsula-report247}.
+
+The first studies indicate that voluntary 24/7~CFE commitments reduce the emissions of participating buyers as well as emissions in the electricity grids they operate.
+What has been missing is a comprehensive analysis of 24/7~CFE procurement over multiple regions and years, since electricity system characteristics, National Climate and Energy Plans (\gls{necp}s), renewable resource quality, and the cost of clean energy vary significantly across regions and over time.
+Furthermore, it is unclear whether decarbonisation effect of 24/7 CFE procurement remains relevant when electricity grids are progressively decarbonised, as is the case in many countries and jurisdictions, or if the 24/7~CFE procurement is only impactful in the early stages of the energy transition.
+
+% 6. **Relevance of this paper**
+
+\textbf{Contribution --} The novelty of this study is to go beyond case studies and show in a systematic way, across many regions and levels of energy transition, how voluntary commitments to 24/7 CFE procurement impact participating buyers and regions where voluntary procurement occurs.
+We explore different designs, optimal procurement strategies, costs, benefits and system-level impacts of the 24/7~CFE matching approach.
+Our analysis focuses on four regions within the European energy system with unique characteristics, and we vary the analysis years to track the evolution of the energy system.
+Additionally, we examine the underlying mechanisms that drive the system-level reduction of CO$_2$ emissions, and examine how they perform over time and across regions.
+This work is a follow-up to the earlier public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.
+
+% 7. **Prologue**
+
+The remainder of the paper is structured as follows: \cref{sec:methods} introduces a mathematical model of clean energy procurement strategies and gives a brief summary of the methodology, sources of model input data, and the experimental setup.
+The results are presented and discussed in \cref{sec:results} and put in perspective in \cref{sec:discussion}.
+The work is concluded in \cref{sec:conclusion}.
+\nameref{sec:si} provides further details about model assumptions and parametrisation of the background energy system.
 
@@
 \label{sec:methods}
-\input{sections/methods.tex}
+
+\textbf{Optimisation model --} The simulations were carried out with the modified version of the open European power system model PyPSA-Eur, built using the open framework PyPSA \cite{brownPyPSAPythonPower2018}.
+The objective of the model is to minimise the annualised system-wide costs of meeting energy demand within the modelled system, while adhering to all relevant engineering, reliability, and policy constraints.
+We use a brownfield investment approach, which means that we keep the existing power generation and storage assets in the model and only optimise the capacity expansion of new assets.
+The optimal solution of the model includes the location and capacity of new power generation and storage assets, as well as the hourly dispatch of all existing and new assets, including the linear optimal power flow on the transmission network for the planning year.
+This is standard for the PyPSA-Eur model \cite{horschPyPSAEurOpenOptimisation2018} and the long-term energy planning models of this class \cite{jenkinsGenX2022, howellsOSeMOSYSOpenSource2011}.
+
+\textbf{Clean energy procurement model --} We introduce new model components (parameters, variables, constraints) into the PyPSA-Eur model to represent voluntary clean energy procurement.
+By incorporating these into the mathematical problem, we model a situation where a fraction of electricity demand in a particular bidding zone is voluntarily committed to procuring clean energy with a desired strategy.
+The fraction is set at 10\% of the total \gls{ci} electricity demand in a particular bidding zone, hereinafter referred to as \enquote{participating consumers}.
+The model co-optimises procurement and operational decisions of the participating consumers to meet their electricity demand in accordance with the procurement strategy they have chosen.
+
+We model and compare two procurement strategies:
+
+\begin{itemize}[-]
+    \item \textit{100\% annual matching}: participating buyers meet their energy demand on an annual volumetric basis with additional renewable energy procurement;
+    \item \textit{24/7 hourly matching}: participating buyers optimise their investment and operational decisions mixing procurement of additional generation and storage resources and electricity imports so that \gls{cfe} supply meets electricity demand 24/7 throughout the year with the desired quality score.
+    \item For benchmarking, we also model \textit{a reference case}: participating buyers have no voluntary environmental commitments and purchase all their electricity from the local grid.
+\end{itemize}
+
+\textit{100\% annual matching --} The annual volumetric renewable matching strategy is modelled with a constraint (\ref{eqn:RES100}).
+More formally, the sum of all dispatch $g_{r,t}$ of contracted renewable generators $r\in RES$ over the year $t\in T$ is equal to the annual electricity demand of participating consumers:
+\begin{equation}
+\sum_{r\in RES, t\in T} g_{r,t} = \sum_{t\in T} d_t
+\label{eqn:RES100}
+\end{equation}
+
+The contracted renewable generators must be new, i.e., they must be additional to the system.
+Procured generators can be sited only in the local bidding zone; thus, we model the \enquote{best case} of the annual matching strategy.
+
+\textit{24/7 CFE hourly matching --} The hourly matching strategy is modelled with a constraint (\ref{eqn:CFE}).
+The 24/7~CFE procurement framework is based on the methodologies and metrics paper by Google~(2021) \cite{google-methodologies}.
+The framework considers various \gls{cfe} supply options for the participating consumers, including procurement of their own generation resources and storage assets, and electricity imports from the local grid.
+
+More formally, the hourly generation from the procured CFE generators $r\in CFE$, discharge and charge from the procured storage technologies $s\in STO$, plus imports of electricity from the regional grid $im_t$ multiplied by the grid's hourly CFE factor $CFE_t$ minus the excess of the CFE supply must be higher or equal than a certain CFE score $x$ multiplied by the total load of participating consumers:
+
+\begin{equation}
+    \begin{split}
+        \sum_{r\in CFE, t\in T} g_{r,t} &+ \sum_{s\in STO, t\in T} \left(\bar{g}_{s,t} - \underline{g}_{s,t}\right) \\
+        &- \sum_{t\in T} ex_t + \sum_{t\in T} CFE_t \cdot im_t \geq x \cdot \sum_{t\in T} d_t
+    \end{split}
+\label{eqn:CFE}
+\end{equation}
+
+% On CFE target
+\noindent where \textit{CFE score} $x$[\%] measures the degree to which hourly electricity consumption is matched with carbon-free electricity generation.
+Equation (\ref{eqn:CFE}) thus allows for controlling \textit{the quality score} of the 24/7~CFE procurement by adjusting the parameter $x$.
+The best quality score---100\% CFE---means that every kilowatt-hour of electricity consumption is met by carbon-free sources at all times.
+
+% On locational matching and additionality
+Similarly to the hourly matching strategy, the contracted generators must be additional to the system and can be sited only in the local bidding zone.
+
+% On excess
+Note that if total electricity generation of assets procured by participating consumers exceeds demand in a given hour, the \enquote{excess} carbon-free electricity is not counted toward a CFE score.
+Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices.
+We set a constraint on the total amount of excess generation sold to the regional grid, setting the limit to 20\% of the total annual demand of participating consumers.\footnote{In \nameref{sec:discussion}, we explain the rationale behind this limit and discuss the implications of this assumption.}
+The wholesale market prices are derived from dual variables of a nodal energy balance constraint.
+
+% On bilinear term due to grid CFE factor
+The CFE factor of the regional grid ($CFE_t$) can be seen as the percentage of clean electricity in each MWh of imported electricity to supply demand of participating consumers in a given hour.
+To compute $CFE_t$, we consider both the hourly electricity mix in the local bidding zone and the emissionality of imported electricity from the neighbouring zones.
+The methodology to calculate the grid CFE factor is described in the prior work of the authors \cite{riepin-zenodo-systemlevel247}.
+
+Note that in equation (\ref{eqn:CFE}), $CFE_t$ is affected by additional CFE resources procured by the participating consumers.
+This introduces a nonconvex term to the optimisation problem.
+The nonconvexity can be avoided by treating the grid CFE factor as a parameter that is iteratively updated (starting with $CFE_t =0 \,~\forall t$).
+We find that one forward pass (i.e. 2 iterations) yields very good convergence.
+
+\textbf{Model scope --} Geographically, the model encompasses the entire \gls{entsoe} area, which covers the entire European electricity system.\footnote{Islands that are not connected to the main European system, such as Malta, Crete and Cyprus, are excluded from the model.}
+In this study, electricity demand, supply and power transmission infrastructure (alternating current lines at and above 220~kV voltage level and all high voltage direct current lines) are clustered to 37 individual bidding zones \cite{PyPSAEur-docs-spatialresolution}.
+Thus, each zone represents a country; some countries straddling different synchronous areas are split into individual bidding zones, such as DK1 (West) and DK2 (East).
+
+Participating consumers can be located in either of the four selected zones: Ireland, Denmark (zone DK1), Germany, or Poland.
+The comparison of results across these zones allows us to generalize the implications of voluntary clean energy procurement, taking into account factors such as electricity demand, weather, availability of renewable resources, existing electricity generation capacity mix, and national energy policies, among other factors.
+
+We model two individual years: 2025 and 2030.
+From a modelling perspective, a five-year step changes many system parameters.
+In particular, technology costs decline as a result of economies of scale and incremental innovation, \gls{necp}s become tighter, \co~prices increase, and some legacy power plants go out of business.
+The problem is solved with a temporal resolution of 2920 snapshots, representing a 3-hourly average of the hourly time-series data.
+
+\textbf{Carbon-free energy technologies in scope --} Depending on the scenario, participating consumers can choose from a variety of energy technologies available on the European market.
+By grouping technologies according to their maturity levels and availability on the market, we formulate three scenarios:
+
+\begin{itemize}[-]
+    \item \textit{Palette 1} -- technologies that are commercially available today: onshore wind, utility scale solar photovoltaics (\gls{PV}), and battery storage;
+    \item \textit{Palette 2} -- all above plus a long-duration energy storage (\gls{ldes}) that is expected to be commercially available in the near future;
+    \item \textit{Palette 3} -- all above plus promising advanced technologies that are in prototype stage today, but are expected to be commercially available in the future: (i) Allam cycle power plant with \gls{ccs}\footnote{Allam cycle is a natural gas power plant with up to 100\% of carbon capture and sequestration} to represent a technology option with higher operational expences (\gls{opex}), and (ii) \enquote{an advanced dispatchable generator}, a stand-in for clean firm technologies with higher capital expences (\gls{capex}), such as advanced geothermal or nuclear systems.
+\end{itemize}
+
+\textbf{Technology assumptions --} Cost and other assumptions for energy technologies available for participating consumers were collected primarily from the Danish Energy Agency \cite{DEA-technologydata} for the respective years and are provided in [\cref{tab:tech_costs}].
+For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion.
+Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, use our own indicative assumptions.
+
+\textbf{Other assumptions --} Other model inputs and key background system assumptions are provided in [\labelcref{sec:si_2}].
+For a full list of technology assumptions, see the GitHub repository \cite{github-247CFEpaper}.
 
@@
 \label{sec:results}
-\input{sections/results.tex}
+
+Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
+From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
+From a system perspective, we analyze how voluntary clean energy procurement impacts CO$_2$ emissions in the region and the \enquote{demand pull} for advanced energy technologies.
+
+Our experimental setup incorporates a wide range of scenarios, allowing us to generalise our results beyond individual assumptions.
+For convenience, we start with a \textit{base scenario} presented in \cref{subsec:base}.
+The base scenario reflects a case when 10\% (on volumetric basis) of \gls{ci} consumers in \textit{Ireland} in \textit{2025} are committed to procuring additional clean energy with a desired strategy.
+The participating consumers can attain the 24/7~CFE procurement targets by co-optimizing local procurement using mature technologies, designated as \textit{palette~1}, and by importing electricity from the local grid.
+Afterward, we delve deeper into the scenario space, altering selected parameters to explore various alternatives and address the following questions:
+
+\begin{enumerate}[-]
+\item \cref{subsec:palette}: What if a wider palette of carbon-free technologies were available to participating buyers?
+\item \cref{subsec:location}: What if participating buyers are located in areas of the European electricity grid that differ significantly from the base scenario?
+\item \cref{subsec:time}: What are the implications if we move the timeframe ahead five years to 2030?
+\item Finally, in \cref{subsec:mechanisms}, we get a closer look at how 24/7 CFE commitments can help decarbonize local grids and reveal the individual mechanisms involved.
+\end{enumerate}
+
+Considering the large scenario space, this work presents results for a selection of scenario branches that generalise the system impacts of the 24/7 carbon-free energy procurement.
+We publish all code to reproduce the experiments under open license alongside the paper.
+See \nameref{sec:code}.
+
+\subsection{Base scenario}
+\label{subsec:base}
+
+\begin{res}
+    Through 24/7 CFE procurement, participating consumers can eliminate carbon emissions associated with their electricity consumption and help to decarbonise the entire electricity system.
+\end{res}
+
+\begin{res}
+    90\%--95\% 24/7 CFE targets have only a small cost premium over 100\% annual renewable matching.
+100\%~CFE target can be achieved with solar PV, wind and battery storage, but at a high cost premium for participating consumers.
+\end{res}
+
+%some parts of this paragraph may go to methods
+\cref{fig:10-2025-IE-p1-used} shows the fraction of hourly demand met with \gls{cfe} depending on the procurement policy that participating consumers follow.
+We contrast two main cases, one where participants commit to 100\% annual renewable matching policy (hereinafter -- \enquote{100\% RES}) and another case where the consumers commit to 24/7~CFE hourly matching policy (hereinafter -- \enquote{24/7~CFE}) with various CFE targets in a range from 80\% to 100\%.
+In the \textit{reference case}, participating consumers cover their load purely with grid purchases without any policy regarding the origin of electricity.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-used.pdf}
+    \caption{Fraction of hourly demand met with carbon-free electricity.}
+    \label{fig:10-2025-IE-p1-used}
+\end{figure}
+
+In the reference case, only 54\% of demand is met with \gls{cfe}.
+100\% RES---the best case for the annual renewable matching policy---results in a 83\% fraction.
+Consequently, CFE targets beyond 85\% yield higher share of hourly demand met with \gls{cfe} than 100\%~RES.
+Another notable trend in \cref{fig:10-2025-IE-p1-used} is that participating consumers rely more on procured resources and less on grid imports with higher CFE targets.
+When targets approach 100\%, participating consumers cannot rely on electricity imports from the grid, since the grid supply mix contains some carbon content in almost all hours.
+
+\cref{fig:10-2025-IE-p1-ci_emisrate} shows how choice of a procurement policy affects the average emissions rate of participating consumers.
+The average emissions rate is derived by dividing the total CO$_2$ emissions linked to the electricity consumption of participating consumers by the total kilowatt-hours (kWh) consumed.
+Already in 2025, Ireland has a moderately clean electricity system: the emission rate is at 177~g\co/kWh in the reference case.
+If participating consumers follow 100\%~RES policy, the emission rate is reduced to 60~g\co/kWh.
+This yields a considerable emission rate reduction compared to the reference case.
+The 24/7~CFE procurement with targets above 85\% helps the participating consumers to reduce emissions further beyond the treshhold set by the 100\%~RES.
+At the 100\% CFE target, participating consumers attain a zero emission rate associated with their electricity consumption, as they perfectly align demand and \gls{cfe} supply on an hourly basis.
+
+Voluntary procurement of clean electricity also helps decarbonise the electricity system as a whole.
+We explore this effect by plotting CO$_2$ emissions in the local region of the participating consumers, i.e. Ireland (\cref{fig:10-2025-IE-p1-zone_emissions}).
+Without voluntary procurement, the model estimates Irish power sector carbon emissions to be at the level of 4.2 Mt\co/a.\footnote{For comparison, \href{https://www.seai.ie/data-and-insights/seai-statistics/key-publications/co2-emissions-report/}{seai.ie} reports this value to be at 10.3~MtCO$_2$ in 2021.
+A strong decreasing trend is expected, since the Irish government has set ambitious targets to achieve a low-carbon energy system \cite{seaiCOEmissionsReport2020}.}
+The modelling results indicate that a commitment to 100\% 24/7~CFE in 2025 from 10\% of the \gls{ci} electricity demand could yield a reduction in Irish emissions by 0.6~Mt\co/a, in contrast to a scenario absent voluntary procurement.
+This reduction equates to 14\% of the total emissions from the Irish power sector.
+100\%~RES can also facilitate system-level CO$_2$ emissions reductions (as depicted by the left bar in \cref{fig:10-2025-IE-p1-zone_emissions}); however, 24/7~CFE attains superior emissions reductions when the CFE target surpasses 85\%.
+
+\begin{figure}[t]
+    \centering
+    \begin{subfigure}[t]{0.95\columnwidth}
+        \centering
+        \caption{Average emissions rate of participating consumers.}
+        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_emisrate.pdf}
+        \label{fig:10-2025-IE-p1-ci_emisrate}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.95\columnwidth}
+        \centering
+        \vspace{-0.2cm}
+        \caption{CO$_2$ emissions in the local region (Ireland).}
+        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-zone_emissions.pdf}
+        \label{fig:10-2025-IE-p1-zone_emissions}
+    \end{subfigure}
+    \caption{Impact of clean electricity procurement commitments on emissions of participating consumers (top panel) and the system-level emissions in a local region (bottom panel).}
+    \label{fig:10-2025-IE-p1-emissions}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \begin{subfigure}[t]{0.95\columnwidth}
+        \centering
+        \caption{Portfolio capacity procured by participating consumers.}
+        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_capacity.pdf}
+        \label{fig:10-2025-IE-p1-ci_capacity}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.95\columnwidth}
+        \centering
+        \vspace{-0.2cm}
+        \caption{Cost breakdown of a procurement policy.}
+        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_costandrev.pdf}
+        \label{fig:10-2025-IE-p1-ci_costandrev}
+    \end{subfigure}
+    \caption{Optimal capacity portfolios (top panel) and costs breakdown (bottom panel) per procurement strategy.}
+    \label{fig:10-2025-IE-p1-ci_procurement}
+\end{figure}
+
+The following analysis unveils the modelled cost-optimal procurement strategies for each procurement policy (\cref{fig:10-2025-IE-p1-ci_capacity}).
+In Ireland, 10\% of the \gls{ci} sector's demand yields a load of 220~MW.
+The findings indicate that, to cover this load adhering to a 100\%~RES policy, participating consumers procure a combined capacity of 1.3~GW from onshore wind and solar PV generators.
+Ensuring demand is matched with \gls{cfe} on an hourly basis requires a considerably more substantial portfolio of wind and solar PV, up to 4.0~GW of combined capacity to reach the 100\%~CFE target.
+Batteries are integrated into the cost-optimal portfolio mix when CFE targets exceed 85\%.
+It is noteworthy that, for an 80\%~CFE target, participating consumers procure less capacity than under a 100\%~RES policy, as they rely more on grid imports.
+
+The breakdown of costs associated with a procurement policy that participating consumers choose is shown in \cref{fig:10-2025-IE-p1-ci_costandrev}.
+Note that revenues from selling the excess electricity to the regional grid at market prices can be treated as \enquote{negative costs} and subtracted from the net procurement cost.
+The results show that a CFE targets of 80\%--95\% can be achieved at a small cost premium to 100\%~RES policy with solar, wind and batteries.
+However, what stands out in the plot is the rapid increase of procurement costs for high 24/7 CFE targets.
+For example, 98\% CFE target has cost premium of 54\% over 100\% the annual matching policy; while the last 2\% of hourly matching more than doubles the costs.
+
+\subsection{Technology access}
+\label{subsec:palette}
+
+\begin{res}
+    24/7 CFE procurement creates an early market for advanced energy technologies the system will need later: long-duration energy storage and clean firm generators.
+\end{res}
+
+\begin{res}
+    The cost premium of 24/7 procurement with high CFE targets may substantially decrease if advanced energy technologies are available for commercial scale-up.
+\end{res}
+
+The cost premium of 24/7~CFE procurement presented in \cref{subsec:base} is driven by the variability of renewable power supply.
+Indeed, in the periods when not much wind or solar is available, matching every kWh of electricity consumption with carbon-free electricity on hourly basis is not an easy task.
+Battery storage technology is cost-optimal for shifting surplus power supply by a couple of hours.
+However, bridging extended periods of low wind and sun with battery storage is expensive.
+Also, the results above show that 24/7 participating consumers rely little on grid supply to reach CFE targets of 98\%--100\%, since a local grid's electricity mix almost always includes some fossil-fueled generation.
+
+The results in \cref{fig:10-2025-IE-p23-ci_procurement} reflect a case when 24/7~CFE participants have access to a wider palette of technologies, including \gls{ldes} and advanced clean firm generators, such as advanced geothermal systems, advanced nuclear or Allam cycle generators with \gls{ccs}.
+
+\cref{fig:10-2025-IE-p2-ci_costandrev} (left panel) shows the breakdown of costs for a case when participating consumers have an access to palette~2 technologies, i.e., long-duration storage complements onshore wind, solar PV and battery storage.
+Here we assume an underground hydrogen storage in salt caverns with energy storage cost of 2.5~\euro/kWh [\cref{tab:tech_costs}].
+An \gls{ldes} system helps to bridge hours with no renewable feed-in.
+As a result, the required portfolio of renewable capacity and procurement costs are reduced, especially for high CFE targets.
+Thus, 100\% 24/7~CFE policy has a cost premium of 42\% above 100\%~RES, which is significantly lower than without \gls{ldes}.
+
+\cref{fig:10-2025-IE-p3-ci_costandrev} (right panel) depicts the technological palette~3 scenario, wherein participating consumers additionally gain access to clean firm generation technologies.
+The Allam cycle turbine with \gls{ccs} now enters into the optimal procurement strategy.
+The cost-optimal share of to clean firm technology increases as CFE targets rise.
+The clean dispatchable generator helps to fill in the gaps in variable renewable generation to match demand and \gls{cfe} supply on an hourly basis.
+The cost premium is further reduced: 100\% 24/7 CFE costs only 15\% above the 100\%~RES.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Cost breakdown of a procurement policy (w/ \gls{ldes}).}
+        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p2-ci_costandrev.pdf}
+        \label{fig:10-2025-IE-p2-ci_costandrev}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Costs of a procurement policy \\
+        (w/ \gls{ldes} and advanced technologies).}
+        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p3-ci_costandrev.pdf}
+        \label{fig:10-2025-IE-p3-ci_costandrev}
+    \end{subfigure}
+    \caption{The breakdown of costs per procurement policy if participating consumers have an access to a wider palette of technologies: w/ \gls{ldes} (left panel); w/ \gls{ldes} and advanced clean firm generators (right panel).
+    }
+    \label{fig:10-2025-IE-p23-ci_procurement}
+\end{figure*}
+
+\subsection{Diverse grid locations}
+\label{subsec:location}
+
+\begin{res}
+    Despite the inherent variability in regional charac\-teristics---ranging from renewable resources and national policies to degrees of interconnection---the model shows a consistent effects of 24/7 clean energy procurement on both participating buyers and overarching system-level impacts across all analyzed regions.
+\end{res}
+
+While the primary focus has been a base scenario exemplifying Ireland, analogous modelling can be applied to diverse regions within the European electricity grid, each exhibiting unique characteristics influenced by local resources, renewable potentials, \gls{necp}s, the degree of interconnections, and other factors.
+
+\cref{fig:10-2025-DEPL-p3-4plots} depicts outcomes for the selected regions of Germany and Poland.
+Germany is selected due to its extensive interconnections with neighbouring regions with relatively clean grids, such as France and Denmark, and its status as the largest electricity consumer in Europe.
+In contrast, Poland has a smaller electricity demand.
+Moreover, the Polish energy system typically has higher carbon intensity, largely due to its historical dependence on coal resources.
+The participation rate is maintained at 10\% of the \gls{ci} sector in both regions, aligning with the base scenario.\footnote{A 10\% participation rate within the \gls{ci} sector corresponds to loads of 3.8~GW in Germany and 1.1~GW in Poland.}
+Despite regional variances, the dynamics and system impacts of clean energy procurement, as observed in the base scenario, exhibit similarities.
+
+German consumers experience lower average emissions rates, attributed to a cleaner grid, in contrast to those in Poland.
+In the reference cases, emission values stand at 240~g\co/kWh and 549~g\co/kWh for Germany and Poland, respectively.\footnote{For context, the emission intensity of electricity generation in 2021 was 402~g\co/kWh for Germany and 750~g\co/kWh for Poland \cite{EEA-GNGEmissionsEU}.}
+Echoing the Irish scenario, both \cref{fig:10-2025-DE-p3-ci_emisrate} and \cref{fig:10-2025-PL-p3-ci_emisrate} demonstrate that in both contexts, participating consumers attain reduced emissions rates with 24/7~CFE procurement compared to 100\%~RES, given sufficiently strict CFE targets.
+
+The impact of 24/7 hourly CFE procurement on system-level CO$_2$ emissions is notable in both Germany and Poland, as depicted in \cref{fig:10-2025-DE-p3-zone_emissions} and \cref{fig:10-2025-PL-p3-zone_emissions}.
+In the absence of any procurement strategy, carbon emissions from the power sectors of Germany and Poland are projected to be 118.8~MtCO$_2$ and 83.8~MtCO$_2$ in 2025, respectively.%
+\footnote{Despite Germany consuming more electricity, the similar scale of power sector carbon emissions between the two countries can be attributed to Poland's significantly higher emission intensity in its electricity mix.}
+By engaging in voluntary clean energy procurement, \gls{ci} consumers can drive notable decarbonisation in the local regions, exceeding the benchmarks set by \gls{necp}s.
+For instance, in Germany, even a 10\% participation rate under a 100\%~RES policy can diminish national emissions by 11.1~MtCO$_2$ annually; remarkably, the 24/7~CFE approach can amplify this impact to up to 14~Mt\co/a, given a CFE target of 100\%.
+
+The optimal capacities of energy technologies and associated costs are illustrated in \cref{fig:10-2025-DE-p3-ci_costandrev} and \cref{fig:10-2025-PL-p3-ci_costandrev}.
+Similar to the Irish scenario, participating consumers complement renewable energy procurement with electricity imports from the grid to meet lower CFE targets.
+For the realization of strict CFE targets, both the Allam cycle with \gls{ccs} and advanced clean firm generators are incorporated into the technology mix.
+This entry of two advanced technologies into the optimal solution space diverges from the Irish findings, where solely the \gls{opex}-heavy Allam cycle turbine is deemed cost-optimal.
+The difference is likely attributable to Germany and Poland being more extensively interconnected with the broader European electricity grid compared to Ireland.
+Better interconnection allows exhausting all arbitrage opportunities across temporal and spatial dimensions, and maximising the dispatch value derived from an advanced dispatchable generator with high \gls{capex}.
+Mirroring the findings from Ireland, the cost premium of 24/7~CFE matching gets minimal when these advanced technologies are accessible.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Average emissions rate of participating consumers (Germany).}
+        \includegraphics[width=0.95\columnwidth]{10-2025-DE-p3-ci_emisrate.pdf}
+        \label{fig:10-2025-DE-p3-ci_emisrate}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Average emissions rate of participating consumers (Poland).}
+        \includegraphics[width=0.95\columnwidth]{10-2025-PL-p3-ci_emisrate.pdf}
+        \label{fig:10-2025-PL-p3-ci_emisrate}
+    \end{subfigure}
+
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{CO$_2$ emissions in the local region (Germany).}
+        \includegraphics[width=0.95\columnwidth]{10-2025-DE-p3-zone_emissions.pdf}
+        \label{fig:10-2025-DE-p3-zone_emissions}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{CO$_2$ emissions in the local region (Poland).}
+        \includegraphics[width=0.95\columnwidth]{10-2025-PL-p3-zone_emissions.pdf}
+        \label{fig:10-2025-PL-p3-zone_emissions}
+    \end{subfigure}%
+
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Cost breakdown of a procurement policy (Germany).}
+        \includegraphics[width=0.95\columnwidth]{10-2025-DE-p3-ci_costandrev.pdf}
+        \label{fig:10-2025-DE-p3-ci_costandrev}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Cost breakdown of a procurement policy (Poland).}
+        \includegraphics[width=0.95\columnwidth]{10-2025-PL-p3-ci_costandrev.pdf}
+        \label{fig:10-2025-PL-p3-ci_costandrev}
+    \end{subfigure}
+    \caption{Selected results for scenarios when participating consumers are located in Germany (left) and Poland (right); all plots are for technological palette~3.}
+    \label{fig:10-2025-DEPL-p3-4plots}
+\end{figure*}
+
+\subsection{Advancing five years forward}
+\label{subsec:time}
+
+\begin{res}
+    Over time, participating consumers reap benefits from the gradual decline in clean technology costs and a progressively cleaner state of the electricity grids, enhancing the affordability of 24/7 CFE procurement.
+\end{res}
+
+\begin{res}
+    Voluntary commitments to 24/7 CFE procurement retain their significance in enhancing system value, even as grids become cleaner.
+Analogous to the base scenario, hourly matching commitments facilitate a more profound decarbonisation compared to 100\% annual renewable matching, provided that CFE targets surpass a particular threshold.
+\end{res}
+
+Having explored the methods, costs, and impacts of clean electricity procurement in the European electricity system for the year 2025 in preceding sections, this section delves into the projected results and implications of these strategies for 2030.
+Referencing back to the \nameref{sec:methods} section, the key implications of advancing five years forward are cleaner electricity grids and decreased costs for energy  technologies.
+\cref{fig:10-2030-IE-6plots} illustrates the outcomes for the \textit{base scenario} transitioned to 2030, maintaining all other parameters constant.
+
+Analyzing \cref{fig:10-2030-IE-p1-used}, which presents the fraction of hourly demand met by clean electricity under each procurement policy in 2030, two key insights emerge when compared to the base scenario.
+Firstly, 72\% of demand is met by \gls{cfe} in the reference case, marking an 18\% increase from 2025, indicating an enhancement in the cleanliness of the background electricity grid.
+Consequently, lower CFE targets (like 80\%) are met with higher share of electricity imports.
+Secondly, participating consumers depend on their own procurement of \gls{cfe} resources and storage, limiting imports from the background grid to achieve strict CFE targets.
+This effect stays consistent with the base scenario.
+
+A cleaner background grid results in lower average emissions rates for participating consumers.
+\cref{fig:10-2030-IE-p1-ci_emisrate} shows that the emissions rate for consumers purchasing only grid electricity decreases from 240~g\co/kWh in 2025 to 107~g\co/kWh in 2030.
+The hourly matching policy enables the attainment of zero emissions linked to \gls{ci} participants' consumption.
+It is interesting to note that a CFE target of 90\% yields lower average emissions than a 100\% annual matching policy, even though these policies are equally costly (see \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p3-ci_costandrev}).
+
+In cleaner systems, both 100\%~RES and 24/7~CFE policies sustain their beneficial impact on system-level emissions.
+As observed in \cref{fig:10-2030-IE-p1-zone_emissions}, 24/7~CFE with a sufficiently high CFE target, outperforms 100\%~RES policy in the decarbonisation impact: with 10\% participation rate, hourly matching reduces local emissions by up to 0.4~Mt\(\text{CO}_2\)/a, in contrast to the 0.2~Mt\(\text{CO}_2\)/a reduction achieved by annual matching.
+The 0.2~Mt\(\text{CO}_2\)/a differential equates to approximately 8\% of Irish power sector emissions.
+The mechanisms driving this impact are detailed in \cref{subsec:mechanisms}.
+
+As illustrated in \cref{fig:10-2030-IE-p1-ci_costandrev}--\cref{fig:10-2030-IE-p3-ci_costandrev}, the cost breakdown of the procurement policy reveals a decline in 24/7~CFE costs across all technological pallets relative to 2025.
+Participating consumers benefit from lower prices for clean energy technologies and progressively cleaner electricity grids.
+Remarkably, these participants not only achieve zero emissions associated with their consumption and exert a notable impact on system-level \(\text{CO}_2\) emissions but also do so while encountering smaller cost premiums, enhancing the accessibility of the voluntary clean energy procurement goals.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Fraction of hourly demand met with carbon-free electricity.}
+        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-used.pdf}
+        \label{fig:10-2030-IE-p1-used}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Average emissions rate of participating consumers.}
+        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-ci_emisrate.pdf}
+        \label{fig:10-2030-IE-p1-ci_emisrate}
+    \end{subfigure}
+
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{CO$_2$ emissions in the local region (Ireland).}
+        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-zone_emissions.pdf}
+        \label{fig:10-2030-IE-p1-zone_emissions}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \caption{Cost breakdown of a procurement policy: technological palette~1.}
+        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-ci_costandrev.pdf}
+        \label{fig:10-2030-IE-p1-ci_costandrev}
+    \end{subfigure}%
+
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Cost breakdown of a procurement policy: technological palette~2.}
+        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p2-ci_costandrev.pdf}
+        \label{fig:10-2030-IE-p2-ci_costandrev}
+    \end{subfigure}%
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \caption{Cost breakdown of a procurement policy: technological palette~3.}
+        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p3-ci_costandrev.pdf}
+        \label{fig:10-2030-IE-p3-ci_costandrev}
+    \end{subfigure}
+
+    \caption{Results for the scenario of Ireland 2030; 10\% participation rate.
+    Figures \ref{fig:10-2030-IE-p1-used}--\ref{fig:10-2030-IE-p1-ci_costandrev} display the technological palette~1 scenario.}
+    \label{fig:10-2030-IE-6plots}
+\end{figure*}
+
+\subsection{Understanding the mechanism of 24/7 CFE procurement in grid decarbonisation}
+\label{subsec:mechanisms}
+
+\begin{res}
+    24/7 CFE procurement mitigates system-level CO$_2$ \newline
+    emissions through two distinct mechanisms: \enquote{profile} and \enquote{volume}.
+The mechanisms origin from distinct aspects of the interplay between the 24/7 CFE procurement and the background electricity grids.
+\end{res}
+
+\begin{res}
+    The disparity in decarbonisation outcomes between 24/7 CFE hourly and 100\% annual renewable matching policies becomes increasingly pronounced as local grids transition to cleaner states.
+This phenomenon underscores the effectiveness of 24/7 CFE procurement in supporting system decarbonisation in the context of evolving national energy and climate policies.
+\end{res}
+
+In the previous sections, we demonstrated that 24/7 clean energy procurement results in a substantial reduction of CO$_2$ emissions in local electricity grids (Figures \ref{fig:10-2025-IE-p1-zone_emissions}, \ref{fig:10-2025-DE-p3-zone_emissions}, \ref{fig:10-2025-PL-p3-zone_emissions} and \ref{fig:10-2030-IE-p1-zone_emissions}).
+In this section, we examine the underlying mechanisms that drive these observed reductions, so as to better understand how clean energy procurement and emissions reduction interrelate.
+
+As originally identified by Xu et al. (2021) \cite{xu-247CFE-report}, two mechanisms are responsible for reducing system-wide emissions:
+
+First, a \textit{profile} mechanism: participants doing 24/7 hourly matching procure clean energy resources that better match their demand patterns.
+As certain consumers align their demand with \gls{cfe} supply on hourly basis, the need for dispatchable generation that can firm intermittent renewable supply is lower in the rest of the system.
+This mechanism can reduce the utilisation of fossil-based generators, such as \gls{ocgt} power plants, which typically ramp up when wind and solar resources are scarce.
+
+Second, a \textit{volume} mechanism: even the cost-optimal procurement strategy for 24/7 hourly matching might include some amount of excess clean energy.
+If total \gls{cfe} generation of assets procured by 24/7 participants exceeds demand in a given hour, the \enquote{excess CFE} is not counted toward a CFE target; however, it is clean electricity that can potentially be stored (using batteries or LDES), or sold to the regional grid.
+As for the latter, excess CFE might displace emitting grid generators or reduce the need to import electricity from neighbouring areas.
+
+Several factors influence the degree to which profile and volume mechanisms contribute to decarbonising the local grids, such as the composition of the 24/7 portfolio, the volume of excess generation sold to the grid, and the electricity generation (and import) mix in the local zone.
+
+We conduct an experiment to isolate the decarbonisation effects of the volume and profile mechanisms.
+In the experiment, we reran the optimization while fixing an excess electricity sold to the grid to zero (NB excess is still possible, but must be either stored or curtailed).
+Such a model setup includes only a profile decarbonisation mechanism.
+We attribute the difference between emissions reduction in the experiment model setup and the base scenario to the volume mechanism.
+As a result, the reduction of emissions in a local zone can be attributed either to excess electricity sold to the grid (volume effect) or to better alignment of CFE generation with demand (profile effect).
+
+\cref{fig:10-profile-volume.pdf} illustrates the reduction in local zone emissions attributed to each of the two decarbonisation mechanisms.
+In the plot, the x-axis shows the different states of electricity grids in which \gls{ci} consumers participate in 24/7 procurement.
+The eight 'background grids' are generated from the combination of modelled wildcards: four zones and two years.
+
+\cref{fig:10-profile-volume.pdf} shows that the impact of 24/7 CFE procurement in absolute terms is proportional to how clean the background grid on average is.
+Thus, the largest impact is at 571.6~kgCO$_2$/a·MWh$^{-1}$ takes place in the Poland 2025 zone, and the lowest one is 3.7~kgCO$_2$/a·MWh$^{-1}$ in Denmark 2030 (NB values for 10\% of \gls{ci} sector participation rate with CFE 100\% target).
+It is noteworthy that from 2025 to 2030, the decarbonisation effect of voluntary clean electricity procurement decreases over time in all zones since electricity grids become cleaner as a result of national climate policy programs and decomissioning of emitting power plants.
+A comparison of the volume and profile mechanisms reveals that both contribute to the decarbonization of the local grids.
+In particular, the profile mechanism contributes significantly to overall emissions reductions, with a major share across all zones regardless of their configuration.
+
+\begin{figure}[H]
+    \centering
+
+    \begin{subfigure}[t]{\columnwidth}
+        \centering
+        \caption{Emissions reduction in a local zone with profile and volume mechanisms isolated. Data is normalised per MWh of demand participating in 24/7 procurement.}
+        \includegraphics[width=0.95\columnwidth]{normalized_effects.pdf}
+        \label{fig:10-profile-volume.pdf}
+    \end{subfigure}
+
+    \begin{subfigure}[t]{\columnwidth}
+        \centering
+        \caption{Percentage of emissions reductions in a local zone as a result of a procurement policy compared with the no procurement policy case.}
+        \includegraphics[width=0.95\columnwidth]{emissions_reduction_comparison.pdf}
+        \label{fig:10-hourly-annual.pdf}
+    \end{subfigure}
+
+    \caption{
+        System-level emission reduction: comparison of procurement policies and isolation of decarbonisation mechanisms.
+        \cref{fig:10-profile-volume.pdf} shows breakdown of emissions reduction in a local zone if 10\% of \gls{ci} load follows 24/7 hourly procurement with CFE 100\% target.
+The profile are volume mechanisms are isolated.
+        \cref{fig:10-hourly-annual.pdf} compares reductions in annual zone emissions in percent points achieved through 100\% annual renewable matching and 100\% 24/7 CFE matching; no procurement policy is assumed in the counterfactual scenario.}
+        \label{fig:decarbonisation_story}
+
+\end{figure}
+
+Additional insights into decarbonisation mechanisms can be gained by examining the emission reductions achieved through 100\%~RES and 100\% 24/7 CFE matching policies.
+\cref{fig:10-hourly-annual.pdf} compares the decarbonisation impact within a local zone of the two procurement policies in relative terms (percent point p.a.), with a counterfactual scenario where no consumers engage in voluntary clean electricity procurement.
+The figure demonstrates that, even though the absolute impact of procurement policies diminishes over time, the relative impact of 24/7 CFE on system-level emissions \textit{increases over time} when compared to 100\%~RES.
+This phenomenon is attributable to the self-cannibalisation effect of wind and solar that influences the value of additional renewable capacity.
+This is relevant in regions where governments adhere to ambitious \gls{necp} targets, like Ireland and Germany (NB Denmark is an outlier with an exceptional RES target exceeding 100\% of national electricity demand for 2030).
+The profile mechanism maintains its relevancy even when renewable energy generators undergo self-cannibalization.
+The volume mechanism retains, or even amplifies, its relevance, by leveraging a diversified portfolio of procured resources by 24/7 participants, including batteries, long-term energy storage, and advanced clean firm technologies.
+Consequently, clean electricity is not only available but can also be sold to the background grid during periods when system-wide wind and solar generation is scarce.
 
@@
 \label{sec:discussion}
-\input{sections/discussion.tex}
+
+\textbf{Our results in perspective --} Our findings agree with the existing model-based studies on clean energy procurement \cite{xu-247CFE-SSRN,ieaAdvancingDecarbonisationClean2022,peninsula-report247}, as well as with the general understanding of the energy research community that \enquote{100\% renewable energy is not enough} \cite{chalendar-2019} in a context of electricity consumers claiming environmental sustainability.
+Specifically, we show that through hourly matching of demand with clean electricity, electricity consumers can both completely negate their carbon emissions and contribute to broader system-wide decarbonisation.
+100\% CFE matching is viable with commercially available technologies, albeit incurs a cost premium for participating consumers.
+The cost premium can be substantially reduced if the advanced technologies, such as long-duration energy storage and clean firm generators are available, or if consumers opt for participating in the 24/7~CFE procurement with quality scores ranging from 90\% to 95\% instead of an absolute 100\%.
+
+% Where we converge: on advanced technologies
+Another important finding of this work that confirms prevailing understanding is that 24/7 CFE matching creates an early market for advanced energy technologies.
+Further research is needed to better understand how 24/7 CFE commitments push advanced energy technologies along their learning curves, and to estimate the potential economic impact on global decarbonisation costs.
+
+% Where we add: Diverse grid locations and years
+According to a comparison of the results over the modeled regions and time periods, voluntary clean energy procurement commitments appear to have consistent effects on both participating buyers and system-level decarbonisation.
+Based on these findings, this work can provide a basis for generalising the implications of clean energy procurement strategies, while taking into account regional differences in electricity demand, renewable resource availability, legacy power plant fleets, degrees of interconnection, and energy policies, among other factors.
+
+% Where we add: Decarbonisation story
+A deeper look at the role of voluntary clean energy procurement commitments in grid decarbonisation reveals that the hourly matching strategy retains its significance in reducing system-level emissions, even as grids become cleaner over time.
+We examined two distinct mechanisms through which 24/7 CFE procurement facilitates system decarbonization: \enquote{profile} and \enquote{volume}.
+As companies adapt their procurement strategies, it is important to understand how these mechanisms perform across different grid locations and years.
+Interestingly, the disparity between the annual (\enquote{volumetric}) matching with renewable energy and 24/7 CFE hourly matching strategies in decarbonisation outcomes becomes ever more evident as electricity grids become cleaner.
+This phenomenon illustrates the effectiveness of 24/7 CFE procurement in supporting system decarbonisation within the context of evolving national energy and climate policies.
+
+\textbf{Features of 24/7~CFE not covered in this work --} Some positive features of 24/7 CFE procurement fall beyond the scope of this manuscript.
+
+% on the impact on back up flexibility needs
+From a system-wide perspective, voluntary commitments to 24/7 CFE reduce the need for flexibility in background electricity systems.
+There will be less investment in gas-fired peaker generators, as well as less need for battery storage elsewhere in the system.
+This effect has been explored by Xu et al. (2022) and Riepin~\&~Brown (2022) \cite{riepin-zenodo-systemlevel247,xu-247CFE-report}
+
+% add a point on the price hedge
+From an electricity buyer perspective, 24/7 CFE procurement can provide a hedge against volatile wholesale market prices.
+Since 100\% CFE matching implies covering the entire electricity demand with clean energy from procured generators via power purchase agreements and operating storage, the buyer is not exposed to the wholesale market price risk (see \cref{fig:10-2025-IE-p1-used}).
+More information on the price hedge effect is provided by the 24/7 CFE Energy Compact \cite{gocarbonfree247}.
+
+\textbf{Critical appraisal --} This work has simplifications and limitations that should be acknowledged.
+
+%Limitations: electricity sector only
+First, only the electricity sector is included in the mathematical model of the European energy system, which is justified by the research focus.
+However, it is important to acknowledge that the electricity sector is not an isolated system, but is increasingly becoming linked with other energy sectors, such as heat and transport.
+Brown et al. (2018) discuss the synergies of sector coupling in the integrated European energy system \cite{brownSynergiesSectorCoupling2018}.
+
+%Limitations: merged profiles of consumers
+Second, consumers participating in clean energy procurement are modelled as one entity.
+The real-world situation may involve a number of individual consumers participating in a voluntary clean energy procurement scheme.
+Our assumption is that all consumers that commit to 24/7 matching, form alliances, and enter into contracts with carbon-free energy generators so that their aggregated consumption can be matched with clean generation on an hourly basis to achieve a given CFE target.
+In reality, participating consumers can pursue hourly matching strategies independently based on their own load profiles.
+See Xu \& Jenkins (2022) investigating this case \cite{princeton-TEACs-2022}.
+
+% Limitations: consumption profiles
+Third, we assume that the participating consumers have a flat demand profile (i.e. baseload).
+As a matter of fact, consumer demand profiles vary based on their business activities.
+It has been shown by Riepin~\&~Brown (2022) that the shape of consumption profiles affects the cost-optimal technology mix required for achieving a certain CFE target; however, the shape of the profile has relatively little impact on procurement costs, emissionality of the portfolio, and system-level impacts of 24/7 procurement \cite{riepin-zenodo-systemlevel247}.
+
+% Limitations: a point on DSM
+Fourth, participating consumers have an inflexible demand, i.e., no demand-side management is considered.
+In reality, many \gls{ci} consumers have some degree of demand flexibility, which they can use to adjust their consumption as needed based on grid signals, such as the wholesale market price and the average emission rate of the local electricity mix.
+Moreover, some consumers, such as data centers and cloud computing providers, can shift their load also in space, i.e., to shift computing
+jobs and associated power loads across data center locations \cite{rosskoningsteinWeNowMore2021}.
+In the recent work, Riepin~\&~Brown (2023) explore how space-time load-shifting flexibility can be used to meet high 24/7 CFE targets, as well as what potential benefits it may offer to participating energy buyers and to the rest of the energy system \cite{riepin-zenodo-spacetime247CFE}.
+
+% Excess constraint problem
+One of the simplifications of mathematical models implementing 24/7 CFE procurement is how the excess carbon-free electricity is handled.
+The \enquote{excess CFE} can be defined as the total amount of carbon-free electricity supply exceeding the demand of the participating consumers in a given period of time.
+Here we assume that the excess can either be curtailed or sold to the regional electricity market at wholesale market prices, until the excess constraint is reached.
+The constraint restricts the volume of excess electricity sold to the regional grid, ensuring it does not surpass 20\% of the annual demand from participating consumers.
+The problem with the uncostrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement; and if system-wide renewable expansion is constrained, the cost-optimal solution may be to use the excess clean electricity to \enquote{relax} the constraint, increasing the renewable portfolio of participating consumers.
+Similar \enquote{spillover effect} problem has been observed and discussed by Xu et al. (2022) \cite{xu-247CFE-SSRN}.
+In their white paper, Peninsula Clean Energy team also discuss the problems and implications of the excess supply.
+Citing their work: \enquote{We conclude that excess supply is a necessary aspect of a time-coincident renewable portfolio in the range of likely market conditions in California today} \cite{peninsula-report247}.
+Both studies perform sensitivity analyses on the excess supply and discuss the implications on their findings \cite{xu-247CFE-SSRN, peninsula-report247}.
+
+% On "emissionality" approach
+\textbf{Is 24/7~CFE the right strategy? --} Last but not least, it is worth mentioning an ongoing discussion whether 24/7 CFE is the right strategy for companies to reduce their carbon emissions.
+Some proponents of alternative strategies contend that 24/7 CFE, or \enquote{temporal matching}, may not represent the most effective approach to emissions reduction.
+This argument is based on the rationale that optimising procurement and deployment of carbon-free generators and batteries to cover consumption 24/7 with clean electricity is a different strategy to optimising the assets specifically to displace \enquote{as much emissions as possible}.
+
+One of the alternative strategies could be that companies, in their pursuit to reduce system-level carbon emissions, focus on system-wide impact as measured via short-run marginal emissions accounting (\enquote{emissions matching}).
+Xu~et~al.
+(2023) bring this discussion from the realm of arguments into quantitative analysis, concluding that \enquote{emissions matching strategies have zero or near-zero long-run impact on system-level CO$_2$ emissions} \cite{princeton-247CFEvsEmissionality}.
+The reason for this, citing the authors, is that voluntary carbon-free energy procurement under this strategy almost exclusively displaces other carbon-free energy rather than fossil fuels.
+
+Another alternative strategy could be that companies do annual matching with \enquote{overprocurement}, i.e., covering their own consumption on an annual volumentric basis plus procuring some more clean electricity on top.
+Such strategy could be implemented at low cost, e.g., with solar PV.
+However, as shown in \cref{subsec:mechanisms}, this strategy would not be as effective in reducing system-level emissions as 24/7 CFE matching, especially in the context of evolving national energy and climate policies.
+Further, such a strategy would not promote innovation and pull forward in time research and investment decisions in advanced energy technologies, such as long-duration energy storage and clean firm generators.
+
+More work---encompassing the collective contributions of the research community, \gls{ngo}s, policy-makers, and corporate energy buyers---is needed to deepen our understanding of the implications, challenges, and opportunities inherent in various clean energy accounting approaches and procurement strategies, guiding us all towards net-zero sustainable energy systems.
 
@@
 \label{sec:conclusion}
-\input{sections/conclusion.tex}
+
+In this work, we systematically examined the means, costs, and the system-level impacts of the 24/7 carbon-free energy matching.
+We find that 24/7 matching is a viable and effective strategy for electricity buyers aiming to eliminate their own carbon footprint and contribute to wider system decarbonisation.
+Voluntary commitments to the hourly matching strategy have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
+The evidence holds across geographical locations and is robust to sensitivity analyses.
+Even as grids become cleaner over time, the 24/7 matching strategy retains its significance in reducing system-level emissions, which is essential in light of evolving national energy and climate policies.
 
@@
 \label{sec:si_1}
-\input{sections/supplementary_1.tex}
+
+%S1: Technology assumptions
+Cost and other assumptions for energy technologies available for participating consumers were collected primarily from the Danish Energy Agency \cite{DEA-technologydata}.
+These assumptions are listed in \cref{tab:tech_costs}.
+A full list of technology assumptions, including the data for energy technologies in the background energy system, is available via the reproducible scientific workflow in the GitHub repository \cite{github-247CFEpaper}.
+
+\begin{table*}[]
+    \centering
+    \resizebox{0.95\textwidth}{!}{%
+        \begin{tabular}{lccccccc}
+            \hline\hline
+            \textbf{Technology} &
+            \textbf{Year} &
+            \textbf{\begin{tabular}[c]{@{}c@{}}CAPEX\\ (overnight cost)\end{tabular}} &
+            \textbf{\begin{tabular}[c]{@{}c@{}}FOM\\ {[}\%/year{]}\end{tabular}} &
+            \textbf{\begin{tabular}[c]{@{}c@{}}VOM\\ {[}Eur/MWh{]}\end{tabular}} &
+            \textbf{\begin{tabular}[c]{@{}c@{}}Efficiency\\ {[}per unit{]}\end{tabular}} &
+            \textbf{\begin{tabular}[c]{@{}c@{}}Lifetime\\ {[}years{]}\end{tabular}} &
+            \textbf{Source} \\ \hline\hline
+            Utility solar PV & 2025 & 612 \officialeuro/kW & 1.7 & 0.01 & - & 37.5 & \cite{DEA-technologydata} \\
+            & 2030 & 492 \officialeuro/kW & 2.0 & 0.01 & - & 40.0 & \cite{DEA-technologydata}  \\ \hline
+            Onshore wind & 2025 & 1077 \officialeuro/kW & 1.2 & 0.015 & - & 28.5 & \cite{DEA-technologydata} \\
+            & 2030 & 1035 \officialeuro/kW & 1.2 & 0.015 & - & 30 & \cite{DEA-technologydata} \\ \hline
+            Battery storage & 2025 & 187 \officialeuro/kWh & - & - & - & 22.5 & \cite{DEA-technologydata}  \\
+            & 2030 & 142 \officialeuro/kWh & - & - & - & 25 & \cite{DEA-technologydata} \\ \hline
+            Battery inverter & 2025 & 215 \officialeuro/kW & 0.3 & - & 0.96 & 10 & \cite{DEA-technologydata} \\
+            & 2030 & 160 \officialeuro/kW & 0.3 & - & 0.96 & 10 & \cite{DEA-technologydata} \\ \hline
+            Hydrogen storage$^1$ & 2025 & 2.5 \officialeuro/kWh$_{\text{H}_2}$ & - & - & - & 100 & \cite{DEA-technologydata}  \\
+            & 2030 & 2.0 \officialeuro/kWh$_{\text{H}_2}$ & - & - & - & 100 & \cite{DEA-technologydata} \\ \hline
+            Hydrogen electrolysis & 2025 & 550 \officialeuro/kW$_{\text{el}}$ & 2.0 & - & 0.67 & 27.5 & \cite{DEA-technologydata} \\
+            & 2030 & 450 \officialeuro/kW$_{\text{el}}$ & 2.0 & - & 0.68 & 30 & \cite{DEA-technologydata} \\ \hline
+            Hydrogen fuel cell & 2025 & 1200 \officialeuro/kW  & 5.0 & - & 0.50 & 10.0 & \cite{DEA-technologydata} \\
+            & 2030 & 1100 \officialeuro/kW & 5.0 & - & 0.50 & 10.0 & \cite{DEA-technologydata} \\ \hline
+            Allam cycle generator$^2$ & 2025 & 2760 \officialeuro/kW  & 14.8 & 3.2 & 0.54 & 30 & \cite{navigant-report, NetZeroAmerica-report} \\
+            & 2030 & 2600 \officialeuro/kW & 14.8 & 3.2 & 0.54 & 30 & \cite{navigant-report, NetZeroAmerica-report} \\ \hline
+            Clean firm generator$^3$ & 2025 & 10000 \officialeuro/kW & 0 & 0 & 1.00 & 30.0 & [-]\\
+            & 2030 & 10000 \officialeuro/kW & 0 & 0 & 1.00 & 30.0 & [-]\\ \hline \hline
+        \end{tabular}%
+    }
+\begin{tablenotes}
+    {\footnotesize
+    \item[] Notes: All costs are in 2020 euros; $^1$assumed to be underground hydrogen storage in salt caverns; $^2$costs also include estimate of 40 \officialeuro/t\co for carbon transport and sequestration; $^3$a stand-in for clean dispatchable technologies, such as advanced geothermal or advanced nuclear systems; own indicative assumptions.
+\item[] CAPEX = capital expenditure; FOM = fixed operations and maintenance costs; VOM = variable operations and maintenance costs.
+    }
+\end{tablenotes}
+    \vspace{0.2cm}
+    \caption{Technology assumptions.}
+    \label{tab:tech_costs}
+\end{table*}
 
@@
 \label{sec:si_2}
-\input{sections/supplementary_2.tex}
 
-% \addcontentsline{toc}{section}{Supplementary References}
-% \renewcommand{\ttdefault}{\sfdefault}
-% \bibliographyS{paper_247CFE}
+%S2: Background system assumptions
+
+The model performs \textit{a perfect-foresight optimisation} of investment and power dispatch decisions to meet electricity demand of the 24/7 consumers, as well as the demand of other consumers in the European electricity system for 2025 or 2030.
+
+In all the modelled countries, renewable generation \textit{must meet the political targets} as defined in the \gls{necp}s or by more recent national policy targets (such as the Easter package in Germany).
+In countries that not have a target for 2025, a linear increase from targets between 2020 and 2030 is assumed.
+The assumed renewable targets are available in the config file of the scientific workflow \cite{github-247CFEpaper}.
+
+We assume 2013 to be a representative climate year for renewable generation. The renewable feed-in profiles are computed with the atlite package \cite{atlite-github}.
+
+The country demand profiles for 2025 and 2030 are assumed to be the same as in 2013. Time-series data for electricity demand is based on the Open Power System Data project \cite{OPSD}.
+
+The existing power plant fleet data is based on the powerplantmatching package \cite{Powerplantmatching-github}.
+We consider national policies and decommissioning plans for coal and nuclear power plants based on data from the \enquote{beyondfossilfuels.org} and the \enquote{world-nuclear.org} projects \cite{FossilFuels, WorldNuclearAssociation}.
+
+We assume price for EU ETS allowances to be 80~\euro/t\co and 130~\euro/t\co  for 2025 and 2030, accordingly.
+The price for natural gas is assumed to be 35~\euro/MWh.
 

### 2024-01-05 manuscript/manuscript.tex
fix last typos, add citation and corresponding author

@@
 
-	\author[tubaddress]{Iegor Riepin}
+	\author[tubaddress]{Iegor Riepin\fnref{fn1}}
 	\ead{iegor.riepin@tu-berlin.de}
+
 	\author[tubaddress]{Tom Brown}
@@
 	\address[tubaddress]{Department of Digital Transformation in Energy Systems, TU Berlin, Germany}
+
+    \fntext[fn1]{Corresponding author: Iegor Riepin, Technical University of Berlin, Einsteinufer 25, 10587 Berlin, Germany}
 
@@
 		In addition, voluntary commitments to 24/7 CFE have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
+
 	\end{abstract}
@@
 The European Union (\gls{eu}) has committed to achieving net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}.
-National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have CO$_2$ emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.
+National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have CO$_2$ emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA, liuEconomicCostEnergy2023}.
 
@@
 
-Some corporate and industrial (\gls{ci}) buyers recongnised the problems associated with the unbundled certificates and turned towards Power Purchase Agreements (\gls{ppa}s).
+Some corporate and industrial (\gls{ci}) buyers recognised the problems associated with the unbundled certificates and turned towards Power Purchase Agreements (\gls{ppa}s).
 When signing a \gls{ppa}, energy buyers pledge to buy both the energy and the environmental credits \enquote{bundled} to megawatt-hours.
@@
 
-Google led the 24/7 movement in 2020 by announcing its commitment to cover the demand at all its data centres and campuses worldwide using the 24/7 CFE approach by 2030 \cite{google-247by2030}.
-Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.
+Google initiated the 24/7 movement in 2020 by announcing its commitment to cover the demand at all its data centres and campuses worldwide using the 24/7 CFE approach by 2030 \cite{google-247by2030}.
+Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap} and methodologies paper for how to measure the progress \cite{google-methodologies}.
 Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. \enquote{100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases} \cite{Microsoft-vision}.
@@
 In 2021, an international group of energy suppliers, electricity buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact \cite{gocarbonfree247}.
-With over 135 signatories, the group aims to \enquote{develop and scale high-impact technologies, energy policies, procurement practices, aand solutions to make 24/7 Carbon-Free Energy achievable for all}.
+With over 135 signatories, the group aims to \enquote{develop and scale high-impact technologies, energy policies, procurement practices, and solutions to make 24/7 Carbon-Free Energy achievable for all}.
 
@@
 The CFE factor of the regional grid ($CFE_t$) can be seen as the percentage of clean electricity in each MWh of imported electricity to supply demand of participating consumers in a given hour.
-To compute $CFE_t$, we consider both the hourly electricity mix in the local bidding zone and the emissionality of imported electricity from the neighbouring zones.
-The methodology to calculate the grid CFE factor is described in the prior work of the authors \cite{riepin-zenodo-systemlevel247}.
+To compute $CFE_t$, we consider both the hourly electricity mix in the local bidding zone and emission intensity of imported electricity from the neighbouring zones.
+The methodology to calculate the CFE factor of the regional grid is described in detail in the prior work of the authors \cite{riepin-zenodo-systemlevel247}.
 
@@
 For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion.
-Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, use our own indicative assumptions.
+Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, we use our own indicative assumptions.
 
@@
         \cref{fig:10-profile-volume.pdf} shows breakdown of emissions reduction in a local zone if 10\% of \gls{ci} load follows 24/7 hourly procurement with CFE 100\% target.
-The profile are volume mechanisms are isolated.
+The profile and volume mechanisms are isolated.
         \cref{fig:10-hourly-annual.pdf} compares reductions in annual zone emissions in percent points achieved through 100\% annual renewable matching and 100\% 24/7 CFE matching; no procurement policy is assumed in the counterfactual scenario.}
@@
 
-\textbf{Our results in perspective --} Our findings agree with the existing model-based studies on clean energy procurement \cite{xu-247CFE-SSRN,ieaAdvancingDecarbonisationClean2022,peninsula-report247}, as well as with the general understanding of the energy research community that \enquote{100\% renewable energy is not enough} \cite{chalendar-2019} in a context of electricity consumers claiming environmental sustainability.
+\textbf{Our results in perspective --} Our findings agree with the existing model-based studies on clean energy procurement \cite{xu-247CFE-SSRN,ieaAdvancingDecarbonisationClean2022,peninsula-report247}, as well as with the general understanding of the energy research community that \enquote{100\% renewable energy is not enough} \cite{chalendar-2019} in a context of electricity consumers claiming complete environmental sustainability.
 Specifically, we show that through hourly matching of demand with clean electricity, electricity consumers can both completely negate their carbon emissions and contribute to broader system-wide decarbonisation.
@@
 As a matter of fact, consumer demand profiles vary based on their business activities.
-It has been shown by Riepin~\&~Brown (2022) that the shape of consumption profiles affects the cost-optimal technology mix required for achieving a certain CFE target; however, the shape of the profile has relatively little impact on procurement costs, emissionality of the portfolio, and system-level impacts of 24/7 procurement \cite{riepin-zenodo-systemlevel247}.
+It has been shown by Riepin~\&~Brown (2022) that the shape of consumption profiles affects the cost-optimal technology mix required for achieving a certain CFE target; however, the shape of the profile has relatively little impact on procurement costs, cost-optimal portfolio of technologies, and system-level impacts of 24/7 procurement \cite{riepin-zenodo-systemlevel247}.
 
@@
 The constraint restricts the volume of excess electricity sold to the regional grid, ensuring it does not surpass 20\% of the annual demand from participating consumers.
-The problem with the uncostrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement; and if system-wide renewable expansion is constrained, the cost-optimal solution may be to use the excess clean electricity to \enquote{relax} the constraint, increasing the renewable portfolio of participating consumers.
+The problem with the unconstrained export of excess CFE to the regional market could be a situation where excess electricity from the renewable generators procured by 24/7 consumers displaces electricity from other renewable generators in the market, which in turn may challenge additionality of the 24/7 procurement; and if system-wide renewable expansion is constrained, the cost-optimal solution may be to use the excess clean electricity to \enquote{relax} the constraint, increasing the renewable portfolio of participating consumers.
 Similar \enquote{spillover effect} problem has been observed and discussed by Xu et al. (2022) \cite{xu-247CFE-SSRN}.
@@
 
-Another alternative strategy could be that companies do annual matching with \enquote{overprocurement}, i.e., covering their own consumption on an annual volumentric basis plus procuring some more clean electricity on top.
+Another alternative strategy could be that companies do annual matching with \enquote{overprocurement}, i.e., covering their own consumption on an annual volumetric basis plus procuring some more clean electricity on top.
 Such strategy could be implemented at low cost, e.g., with solar PV.

### 2024-06-19 manuscript/manuscript.tex
manuscript: working paper version

--- 2023-10-27 manuscript/manuscript.tex
@@
 
-	\author[tubaddress]{Iegor Riepin}
+	\author[tubaddress]{Iegor Riepin\fnref{fn1}}
 	\ead{iegor.riepin@tu-berlin.de}
@@
 	\address[tubaddress]{Department of Digital Transformation in Energy Systems, TU Berlin, Germany}
+	\fntext[fn1]{Corresponding author: Iegor Riepin, Technical University of Berlin, Einsteinufer 25, 10587 Berlin, Germany}
 
@@
 
-\tableofcontents
+% \tableofcontents
 
@@
 
+Iegor Riepin was supported by the research grant from Google LLC.
 We thank the following people for fruitful discussions on the 24/7 carbon-free energy procurement and the art of energy system modelling: Fabian Neumann, Elisabeth Zeyen, Devon Swezey, Brian Denvir, Marc Oman, Jesse Jenkins and research staff of the Zero carbon Energy systems Research and Optimization Laboratory (ZERO Lab) at Princeton University.
-
-Iegor Riepin was supported by the research grant from Google LLC.
-
-This work is a follow-up to the prior public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.
 

### 2024-06-19 manuscript/sections/discussion.tex
license: add reuse compatibility
project: initial run pre-commit against all files
manuscript: working paper version

@@
-\textbf{Our results in perspective --} Our findings agree with the existing model-based studies on clean energy procurement \cite{xu-247CFE-SSRN,ieaAdvancingDecarbonisationClean2022,peninsula-report247}, as well as with the general understanding of the energy research community that \enquote{100\% renewable energy is not enough} \cite{chalendar-2019} in a context of electricity consumers claiming environmental sustainability.
+% SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
+%
+% SPDX-License-Identifier: CC-BY-4.0
+
+\textbf{Our results in perspective --} Our findings agree with the existing model-based studies on clean energy procurement \cite{xu-247CFE-SSRN,ieaAdvancingDecarbonisationClean2022,peninsula-report247}, as well as with the general understanding of the energy research community that \enquote{100\% renewable energy is not enough} \cite{chalendar-2019} in a context of electricity consumers claiming complete environmental sustainability.
 Specifically, we show that through hourly matching of demand with clean electricity, electricity consumers can both completely negate their carbon emissions and contribute to broader system-wide decarbonisation.
@@
 Moreover, some consumers, such as data centers and cloud computing providers, can shift their load also in space, i.e., to shift computing
-jobs and associated power loads across data center locations \cite{rosskoningsteinWeNowMore2021}.
+jobs and associated power loads across data center locations \cite{koningsteinWeNowMore2021}.
 In the recent work, Riepin~\&~Brown (2023) explore how space-time load-shifting flexibility can be used to meet high 24/7 CFE targets, as well as what potential benefits it may offer to participating energy buyers and to the rest of the energy system \cite{riepin-zenodo-spacetime247CFE}.

### 2024-06-19 manuscript/sections/introduction.tex
license: add reuse compatibility
project: initial run pre-commit against all files
manuscript: working paper version

@@
+% SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
+%
+% SPDX-License-Identifier: CC-BY-4.0
+
 % Introduction Structure
@@
 
-Some corporate and industrial (\gls{ci}) buyers recongnised the problems associated with the unbundled certificates and turned towards Power Purchase Agreements (\gls{ppa}s). 
+Some corporate and industrial (\gls{ci}) buyers recognised the problems associated with the unbundled certificates and turned towards Power Purchase Agreements (\gls{ppa}s).
 When signing a \gls{ppa}, energy buyers pledge to buy both the energy and the environmental credits \enquote{bundled} to megawatt-hours.
@@
 
-Google led the 24/7 movement in 2020 by announcing its commitment to cover the demand at all its data centres and campuses worldwide using the 24/7 CFE approach by 2030 \cite{google-247by2030}.
-Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.
+Google initiated the 24/7 CFE movement in 2020 by announcing its commitment to cover the demand at all its data centres and campuses worldwide using the 24/7 CFE approach by 2030 \cite{google-247by2030}.
+Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.	Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap} and methodologies paper for how to measure the progress \cite{google-methodologies}.
 Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. \enquote{100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases} \cite{Microsoft-vision}.

### 2024-06-19 manuscript/sections/methods.tex
license: add reuse compatibility
project: initial run pre-commit against all files
manuscript: working paper version

@@
+% SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
+%
+% SPDX-License-Identifier: CC-BY-4.0
+
 \textbf{Optimisation model --} The simulations were carried out with the modified version of the open European power system model PyPSA-Eur, built using the open framework PyPSA \cite{brownPyPSAPythonPower2018}.
@@
 The CFE factor of the regional grid ($CFE_t$) can be seen as the percentage of clean electricity in each MWh of imported electricity to supply demand of participating consumers in a given hour.
-To compute $CFE_t$, we consider both the hourly electricity mix in the local bidding zone and the emissionality of imported electricity from the neighbouring zones.
-The methodology to calculate the grid CFE factor is described in the prior work of the authors \cite{riepin-zenodo-systemlevel247}.
+To compute $CFE_t$, we consider both the hourly electricity mix in the local bidding zone and emission intensity of imported electricity from the neighbouring zones.
+The methodology to calculate the CFE factor of the grid is described in the prior work of the authors \cite{riepin-zenodo-systemlevel247}.
 
@@
 For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion.
-Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, use our own indicative assumptions.
+Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, we use own indicative assumptions.
 

### 2024-06-23 manuscript/sections/introduction.tex
manuscript: revision

@@
 \textbf{Contribution --} The novelty of this study is to go beyond case studies and show in a systematic way, across many regions and levels of energy transition, how voluntary commitments to 24/7 CFE procurement impact participating buyers and regions where voluntary procurement occurs.
-We explore different designs, optimal procurement strategies, costs, benefits and system-level impacts of the 24/7~CFE matching approach.
+We explore different optimal procurement strategies for 24/7 CFE matching, costs associated with them, benefits for participating buyers, and impacts on system-level emissions.
 Our analysis focuses on four regions within the European energy system with unique characteristics, and we vary the analysis years to track the evolution of the energy system.
 Additionally, we examine the underlying mechanisms that drive the system-level reduction of CO$_2$ emissions, and examine how they perform over time and across regions.
-This work is a follow-up to the earlier public report by the authors \cite{riepin-zenodo-systemlevel247} with an updated model, updated system-wide assumptions, and additional analysis of the results.
 

### 2024-06-24 manuscript/manuscript.tex
revision: move sections into master tex

--- 2024-01-05 manuscript/manuscript.tex
@@
 \graphicspath{ 						% Allows for multiple directories
-	{},
+	{../results/paper/},
 	}
@@
 	\ead{iegor.riepin@tu-berlin.de}
-
 	\author[tubaddress]{Tom Brown}
@@
 	\address[tubaddress]{Department of Digital Transformation in Energy Systems, TU Berlin, Germany}
-
 	\fntext[fn1]{Corresponding author: Iegor Riepin, Technical University of Berlin, Einsteinufer 25, 10587 Berlin, Germany}
@@
 % 5. Tell us what your work teaches us: what we conclude and why this is important
-		% aim ~200 words | 225 words used
+% aim ~200 words | working paper: 205 words | revision: 230 words
+
 A growing number of public and private energy buyers are interested in 24/7 carbon-free energy (CFE) procurement, which means that every kilowatt-hour of electricity consumption is met by carbon-free sources at all times.
@@
 Our results indicate that clean energy procurement commitments have consistent beneficial effects on participants and the electricity system.
+Utilizing an hourly matching strategy, energy buyers can eliminate all carbon emissions linked to their electricity consumption, while also reducing system-level emissions by up to 572~kgCO$_2$/a per MWh of participating load.
 Even as grids become cleaner over time, the hourly matching strategy contributes significantly to system-level emissions reduction.
@@
 \label{sec:intro}
-% Introduction Structure
 
@@
 The European Union (\gls{eu}) has committed to achieving net-zero emissions by 2050, and the European Commission has adopted the European Climate Law with a target of reducing net greenhouse gas emissions by at least 55\% by 2030, compared to 1990 levels \cite{EuropeanClimateLaw2020}.
-National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have CO$_2$ emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA, liuEconomicCostEnergy2023}.
+National climate initiatives are gaining ground across the globe, including the United States with the Biden administration's goal of reducing emissions by 50-52\% by 2030, compared to 2005 levels \cite{BidenClimatePlan2021}, and China's commitment to have CO$_2$ emissions peak before 2030 and achieve carbon neutrality before 2060 \cite{ChinaNetZero-IEA}.
 
@@
 
-Google initiated the 24/7 movement in 2020 by announcing its commitment to cover the demand at all its data centres and campuses worldwide using the 24/7 CFE approach by 2030 \cite{google-247by2030}.
-Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap} and methodologies paper for how to measure the progress \cite{google-methodologies}.
+Google initiated the 24/7 CFE movement in 2020 by announcing its commitment to cover the demand at all its data centres and campuses worldwide using the 24/7 CFE approach by 2030 \cite{google-247by2030}.
+Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.	Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap} and methodologies paper for how to measure the progress \cite{google-methodologies}.
 Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. \enquote{100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases} \cite{Microsoft-vision}.
@@
 This is standard for the PyPSA-Eur model \cite{horschPyPSAEurOpenOptimisation2018} and the long-term energy planning models of this class \cite{jenkinsGenX2022, howellsOSeMOSYSOpenSource2011}.
+The mathematical formulation of the model is available in PyPSA documentation \cite{pypsadocs}.
+The code to reproduce the optimisation problem behind this analysis is available at GitHub \cite{github-247CFEpaper}.
 
@@
 By incorporating these into the mathematical problem, we model a situation where a fraction of electricity demand in a particular bidding zone is voluntarily committed to procuring clean energy with a desired strategy.
-The fraction is set at 10\% of the total \gls{ci} electricity demand in a particular bidding zone, hereinafter referred to as \enquote{participating consumers}.
-The model co-optimises procurement and operational decisions of the participating consumers to meet their electricity demand in accordance with the procurement strategy they have chosen.
+The fraction is set at 10\% of the total \gls{ci} electricity demand in a particular bidding zone, representing a hypotetical group of electricity consumers (e.g.
+datacentres, industrial facilities, or municipalities) committed to clean energy procurement, hereinafter referred to as \enquote{participating consumers}.
+The model seeks to find cost-optimal procurement strategy and operational decisions for the participating consumers to meet their electricity demand in accordance with the chosen clean electricity matching strategy.
 
@@
 To compute $CFE_t$, we consider both the hourly electricity mix in the local bidding zone and emission intensity of imported electricity from the neighbouring zones.
-The methodology to calculate the CFE factor of the regional grid is described in detail in the prior work of the authors \cite{riepin-zenodo-systemlevel247}.
+The methodology to calculate the CFE factor of the grid is described in the prior work of the authors \cite{riepin-zenodo-systemlevel247}.
 
@@
 \textbf{Model scope --} Geographically, the model encompasses the entire \gls{entsoe} area, which covers the entire European electricity system.\footnote{Islands that are not connected to the main European system, such as Malta, Crete and Cyprus, are excluded from the model.}
-In this study, electricity demand, supply and power transmission infrastructure (alternating current lines at and above 220~kV voltage level and all high voltage direct current lines) are clustered to 37 individual bidding zones \cite{PyPSAEur-docs-spatialresolution}.
+In this study, electricity demand, supply and power transmission infrastructure (alternating current lines at and above 220~kV voltage level and all high voltage direct current lines) are clustered to 37 individual bidding zones \cite{PyPSAEur-docs}.
 Thus, each zone represents a country; some countries straddling different synchronous areas are split into individual bidding zones, such as DK1 (West) and DK2 (East).
@@
 Participating consumers can be located in either of the four selected zones: Ireland, Denmark (zone DK1), Germany, or Poland.
-The comparison of results across these zones allows us to generalize the implications of voluntary clean energy procurement, taking into account factors such as electricity demand, weather, availability of renewable resources, existing electricity generation capacity mix, and national energy policies, among other factors.
+The comparison of results across these zones allows us to generalize the implications of voluntary clean energy procurement, taking into account individual characteristics of each zone, such as electricity demand, weather, availability of renewable resources, existing electricity generation capacity mix, and national energy policies, among other factors.
 
@@
 For the \gls{ldes}, we assume an underground hydrogen storage in salt caverns with an electolyzer and a fuel cell for hydrogen conversion.
-Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, we use our own indicative assumptions.
+Data for advanced clean firm technologies is less reliable due to technological uncertainty and lack of commercial experience; therefore, we use own indicative assumptions.
 
@@
 Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
-From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
-From a system perspective, we analyze how voluntary clean energy procurement impacts CO$_2$ emissions in the region and the \enquote{demand pull} for advanced energy technologies.
+From the \gls{ci} buyers' perspective, we examine optimal procurement strategies for both annual and hourly matching strategies (i.e., a cost-optimal mix of locally procured energy generation, storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
+From a system perspective, we analyze how voluntary clean energy procurement impacts CO$_2$ emissions in the background grid and the \enquote{demand pull} for advanced energy technologies.
 
@@
 \begin{res}
-    The disparity in decarbonisation outcomes between 24/7 CFE hourly and 100\% annual renewable matching policies becomes increasingly pronounced as local grids transition to cleaner states.
-This phenomenon underscores the effectiveness of 24/7 CFE procurement in supporting system decarbonisation in the context of evolving national energy and climate policies.
+    The disparity in decarbonisation outcomes between 24/7 CFE hourly and 100\% annual renewable matching policies becomes increasingly pronounced as local grids transition to cleaner states over time.
 \end{res}
@@
 In reality, many \gls{ci} consumers have some degree of demand flexibility, which they can use to adjust their consumption as needed based on grid signals, such as the wholesale market price and the average emission rate of the local electricity mix.
-Moreover, some consumers, such as data centers and cloud computing providers, can shift their load also in space, i.e., to shift computing
-jobs and associated power loads across data center locations \cite{rosskoningsteinWeNowMore2021}.
-In the recent work, Riepin~\&~Brown (2023) explore how space-time load-shifting flexibility can be used to meet high 24/7 CFE targets, as well as what potential benefits it may offer to participating energy buyers and to the rest of the energy system \cite{riepin-zenodo-spacetime247CFE}.
+Moreover, some consumers, such as data centers and cloud computing providers, can shift their load also in space, i.e., to shift computing jobs and associated power loads across data center locations \cite{koningsteinWeNowMore2021}.
+The ability to shift power loads in time and space can play a significant role in achieving hourly carbon-free energy matching by 2030, as more applications and engineering solutions become available \cite{radovanovicCarbonAwareComputingDatacenters2021,radovanovicIEEE2023,koningsteinWeNowMore2021}.
+In the recent work, Riepin~\&~Brown (2023) explore how space-time load-shifting flexibility can be used to meet high 24/7 CFE targets. \cite{riepin-zenodo-spacetime247CFE}.
 
@@
 In this work, we systematically examined the means, costs, and the system-level impacts of the 24/7 carbon-free energy matching.
-We find that 24/7 matching is a viable and effective strategy for electricity buyers aiming to eliminate their own carbon footprint and contribute to wider system decarbonisation.
-Voluntary commitments to the hourly matching strategy have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
-The evidence holds across geographical locations and is robust to sensitivity analyses.
+We find that 24/7 matching is a viable and effective strategy for clean electricity buyers aiming to eliminate their own carbon footprint and contribute to wider system decarbonisation.
+The evidence holds across different geographical locations.
 Even as grids become cleaner over time, the 24/7 matching strategy retains its significance in reducing system-level emissions, which is essential in light of evolving national energy and climate policies.
+Voluntary commitments to the hourly matching strategy have a further transformative effect on electricity systems by creating an early market for advanced energy technologies, such as long-duration energy storage and clean firm power generators.
 
@@
 
-%S2: Background system assumptions
-
 The model performs \textit{a perfect-foresight optimisation} of investment and power dispatch decisions to meet electricity demand of the 24/7 consumers, as well as the demand of other consumers in the European electricity system for 2025 or 2030.
@@
 
+% \addcontentsline{toc}{section}{Supplementary References}
+% \renewcommand{\ttdefault}{\sfdefault}
+% \bibliographyS{paper_247CFE}
+
 \end{document}

### 2024-07-17 manuscript/manuscript-si.tex
si: create separate si.tex for elsevier typesetting

--- 2024-06-19 manuscript/manuscript.tex
@@
 \usepackage{csquotes} 				 % For handling inline and display quotations
-\usepackage[acronym, automake, nonumberlist]{glossaries-extra}
 
@@
 
-% acronyms
-\makeglossaries
-
-% Proper nouns
-\newacronym{eu}{EU}{European Union}
-\newacronym{bdew}{BDEW}{Bundesverband der Energie- und Wasserwirtschaft}
-\newacronym{dea}{DEA}{Danish Energy Agency}
-\newacronym{jrc}{JRC}{Joint Research Center}
-\newacronym{tyndp}{TYNDP}{Ten-Year Network Development Plan}
-\newacronym{entsoe}{ENTSO-E}{European Network for Transmission System Operators for Electricity}
-\newacronym{entsog}{ENTSO-G}{European Network of Transmission System Operators for Gas}
-
-% Enegy tech concepts
-\newacronym{tes}{TES}{Thermal Energy Storage (in form of water tanks)}
-\newacronym{chp}{CHP}{Combined Heat and Power plant}
-\newacronym{cop}{COP}{Coefficient of Performance}
-\newacronym{PV}{PV}{Solar photovoltaics}
-\newacronym{ghg}{GHG}{Greenhouse gas}
-\newacronym{helmeth}{HELMETH}{Integrated High-Temperature Electrolysis and Methanation for Effective Power to Gas Conversion}
-\newacronym{ocgt}{OCGT}{Open Cycle Gas Turbine}
-\newacronym{v2g}{V2G}{Vehicle to Grid}
-\newacronym{dsm}{DSM}{Demand Side Management}
-\newacronym{hvdc}{HVDC}{High Voltage Direct Current}
-\newacronym{phs}{PHS}{Pumped Hydro Storage}
-\newacronym{dac}{DAC}{Direct Air Capture}
-\newacronym{sng}{SNG}{Synthetic Natural Gas}
-\newacronym{res}{RES}{Renewable Energy Sources}
-\newacronym{cfe}{CFE}{Carbon-Free Electricity}
-\newacronym{ldes}{LDES}{Long Duration Energy Storage}
-\newacronym{ccs}{CCS}{Carbon Capture and Sequestration}
-
-% Energy economics and finance concepts
-\newacronym{fom}{FOM}{Fixed Operation and Maintenance costs}
-\newacronym{vom}{VOM}{Variable Operation and Maintenance costs}
-\newacronym{capex}{CAPEX}{Capital expenditures}
-\newacronym{opex}{OPEX}{Operational expenditures}
-\newacronym{ppa}{PPA}{Power Purchase Agreement}
-\newacronym{ptc}{PTC}{Production Tax Credit}
-\newacronym{necp}{NECP}{National Energy and Climate Plan}
-\newacronym{ets}{ETS}{Emissions Trading System}
-\newacronym{cfd}{CfD}{Contract for Difference}
-\newacronym{go}{GO}{Guarantees of Origin}
-\newacronym{rec}{REC}{Renewable Energy Certificate}
-
-% Other
-\newacronym{pypsa}{PyPSA}{Python for Power System Analysis}
-\newacronym{nuts}{NUTS}{Nomenclature of Territorial Units for Statistics}
-\newacronym{ci}{C\&I}{Corporate and Industry (sectors)}
-\newacronym{ngo}{NGO}{Non-Governmental Organization}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{document}
-
-\begin{frontmatter}
-
-	\title{On the means, costs, and system-level impacts of 24/7 carbon-free energy procurement}
-
-	\author[tubaddress]{Iegor Riepin\fnref{fn1}}
-	\ead{iegor.riepin@tu-berlin.de}
-	\author[tubaddress]{Tom Brown}
-	\ead{t.brown@tu-berlin.de}
-
-	\address[tubaddress]{Department of Digital Transformation in Energy Systems, TU Berlin, Germany}
-	\fntext[fn1]{Corresponding author: Iegor Riepin, Technical University of Berlin, Einsteinufer 25, 10587 Berlin, Germany}
-
-	\begin{abstract}
-		\input{sections/abstract.tex}
-	\end{abstract}
-
-	\begin{keyword}
-		24/7 carbon-free electricity,
-		Clean electricity procurement,
-		Energy modelling,
-		Renewable energy
-	\end{keyword}
-
-	% \begin{graphicalabstract}
-	% \end{graphicalabstract}
-
-\end{frontmatter}
-
-% \tableofcontents
-
-\section{Introduction}
-\label{sec:intro}
-\input{sections/introduction.tex}
-
-\section{Methods and experimental design}
-\label{sec:methods}
-\input{sections/methods.tex}
-
-\section{Results}
-\label{sec:results}
-\input{sections/results.tex}
-
-\section{Discussion}
-\label{sec:discussion}
-\input{sections/discussion.tex}
-
-\section{Conclusion}
-\label{sec:conclusion}
-\input{sections/conclusion.tex}
-
-\section*{Acknowledgements}
-
-Iegor Riepin was supported by the research grant from Google LLC.
-We thank the following people for fruitful discussions on the 24/7 carbon-free energy procurement and the art of energy system modelling: Fabian Neumann, Elisabeth Zeyen, Devon Swezey, Brian Denvir, Marc Oman, Jesse Jenkins and research staff of the Zero carbon Energy systems Research and Optimization Laboratory (ZERO Lab) at Princeton University.
-
-\section*{Author Contributions}
-
-% following https://casrai.org/credit/
-
-\textbf{Iegor Riepin}:
-Conceptualization --
-Data curation --
-Formal Analysis --
-Investigation --
-Methodology --
-Software --
-Validation --
-Visualization --
-Writing - original draft
-
-\textbf{Tom Brown}:
-Conceptualization --
-Methodology --
-Software --
-Supervision --
-Writing - review \& editing
-
-\section*{Data and Code Availability}
-\label{sec:code}
-
-The simulations were carried out with PyPSA --- an open-source software framework for simulating and optimising modern energy systems \cite{brownPyPSAPythonPower2018}.
-
-All code, input data and results are published under an open license. The code to reproduce the experiments is available at GitHub \cite{github-247CFEpaper}.
-
-\printglossary[type=\acronymtype]
-
-% tidy with https://flamingtempura.github.io/bibtex-tidy/
-\addcontentsline{toc}{section}{References}
-\renewcommand{\ttdefault}{\sfdefault}
-\bibliography{paper_247CFE}
 
@@
 \label{sec:si_2}
-\input{sections/supplementary_2.tex}
+
+The model performs \textit{a perfect-foresight optimisation} of investment and power dispatch decisions to meet electricity demand of the 24/7 consumers, as well as the demand of other consumers in the European electricity system for 2025 or 2030.
+
+In all the modelled countries, renewable generation \textit{must meet the political targets} as defined in the National Energy and Climate Plans or by more recent national policy targets (such as the Easter package in Germany).
+In countries that not have a target for 2025, a linear increase from targets between 2020 and 2030 is assumed.
+The assumed renewable targets are available in the config file of the scientific workflow \cite{github-247CFEpaper}.
+
+We assume 2013 to be a representative climate year for renewable generation. The renewable feed-in profiles are computed with the atlite package \cite{atlite-github}.
+
+The country demand profiles for 2025 and 2030 are assumed to be the same as in 2013. Time-series data for electricity demand is based on the Open Power System Data project \cite{OPSD}.
+
+The existing power plant fleet data is based on the powerplantmatching package \cite{Powerplantmatching-github}.
+We consider national policies and decommissioning plans for coal and nuclear power plants based on data from the \enquote{beyondfossilfuels.org} and the \enquote{world-nuclear.org} projects \cite{FossilFuels, WorldNuclearAssociation}.
+
+We assume price for EU ETS allowances to be 80~\euro/t\co and 130~\euro/t\co  for 2025 and 2030, accordingly.
+The price for natural gas is assumed to be 35~\euro/MWh.
 
@@
 % \renewcommand{\ttdefault}{\sfdefault}
-% \bibliographyS{paper_247CFE}
+\bibliography{paper_247CFE}
 

### 2024-07-17 manuscript/manuscript.tex
tex: update graphicspath for reproducibility

@@
     \centering
-    \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-used.pdf}
+    \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/used.pdf}
     \caption{Fraction of hourly demand met with carbon-free electricity.}
@@
         \caption{Average emissions rate of participating consumers.}
-        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_emisrate.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_emisrate.pdf}
         \label{fig:10-2025-IE-p1-ci_emisrate}
@@
         \caption{CO$_2$ emissions in the local region (Ireland).}
-        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-zone_emissions.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/zone_emissions.pdf}
         \label{fig:10-2025-IE-p1-zone_emissions}
@@
         \caption{Portfolio capacity procured by participating consumers.}
-        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_capacity.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_capacity.pdf}
         \label{fig:10-2025-IE-p1-ci_capacity}
@@
         \caption{Cost breakdown of a procurement policy.}
-        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p1-ci_costandrev.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p1/ci_costandrev.pdf}
         \label{fig:10-2025-IE-p1-ci_costandrev}
@@
         \caption{Cost breakdown of a procurement policy (w/ \gls{ldes}).}
-        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p2-ci_costandrev.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p2/ci_costandrev.pdf}
         \label{fig:10-2025-IE-p2-ci_costandrev}
@@
         (w/ \gls{ldes} and advanced technologies).}
-        \includegraphics[width=0.95\columnwidth]{10-2025-IE-p3-ci_costandrev.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/IE/p3/ci_costandrev.pdf}
         \label{fig:10-2025-IE-p3-ci_costandrev}
@@
         \caption{Average emissions rate of participating consumers (Germany).}
-        \includegraphics[width=0.95\columnwidth]{10-2025-DE-p3-ci_emisrate.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/ci_emisrate.pdf}
         \label{fig:10-2025-DE-p3-ci_emisrate}
@@
         \caption{Average emissions rate of participating consumers (Poland).}
-        \includegraphics[width=0.95\columnwidth]{10-2025-PL-p3-ci_emisrate.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/ci_emisrate.pdf}
         \label{fig:10-2025-PL-p3-ci_emisrate}
@@
         \caption{CO$_2$ emissions in the local region (Germany).}
-        \includegraphics[width=0.95\columnwidth]{10-2025-DE-p3-zone_emissions.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/zone_emissions.pdf}
         \label{fig:10-2025-DE-p3-zone_emissions}
@@
         \caption{CO$_2$ emissions in the local region (Poland).}
-        \includegraphics[width=0.95\columnwidth]{10-2025-PL-p3-zone_emissions.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/zone_emissions.pdf}
         \label{fig:10-2025-PL-p3-zone_emissions}
@@
         \caption{Cost breakdown of a procurement policy (Germany).}
-        \includegraphics[width=0.95\columnwidth]{10-2025-DE-p3-ci_costandrev.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/DE/p3/ci_costandrev.pdf}
         \label{fig:10-2025-DE-p3-ci_costandrev}
@@
         \caption{Cost breakdown of a procurement policy (Poland).}
-        \includegraphics[width=0.95\columnwidth]{10-2025-PL-p3-ci_costandrev.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2025/PL/p3/ci_costandrev.pdf}
         \label{fig:10-2025-PL-p3-ci_costandrev}
@@
         \caption{Fraction of hourly demand met with carbon-free electricity.}
-        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-used.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/used.pdf}
         \label{fig:10-2030-IE-p1-used}
@@
         \caption{Average emissions rate of participating consumers.}
-        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-ci_emisrate.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_emisrate.pdf}
         \label{fig:10-2030-IE-p1-ci_emisrate}
@@
         \caption{CO$_2$ emissions in the local region (Ireland).}
-        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-zone_emissions.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/zone_emissions.pdf}
         \label{fig:10-2030-IE-p1-zone_emissions}
@@
         \caption{Cost breakdown of a procurement policy: technological palette~1.}
-        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p1-ci_costandrev.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p1/ci_costandrev.pdf}
         \label{fig:10-2030-IE-p1-ci_costandrev}
@@
         \caption{Cost breakdown of a procurement policy: technological palette~2.}
-        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p2-ci_costandrev.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p2/ci_costandrev.pdf}
         \label{fig:10-2030-IE-p2-ci_costandrev}
@@
         \caption{Cost breakdown of a procurement policy: technological palette~3.}
-        \includegraphics[width=0.95\columnwidth]{10-2030-IE-p3-ci_costandrev.pdf}
+        \includegraphics[width=0.95\columnwidth]{plots/10/2030/IE/p3/ci_costandrev.pdf}
         \label{fig:10-2030-IE-p3-ci_costandrev}

### 2024-07-17 manuscript/sections/conclusion.tex
license: add reuse compatibility
project: initial run pre-commit against all files

@@
+% SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
+%
+% SPDX-License-Identifier: CC-BY-4.0
+
 In this work, we systematically examined the means, costs, and the system-level impacts of the 24/7 carbon-free energy matching.
-We find that 24/7 matching is a viable and effective strategy for electricity buyers aiming to eliminate their own carbon footprint and contribute to wider system decarbonisation.
-Voluntary commitments to the hourly matching strategy have a further transformative effect on electricity systems through accelerated innovation and early deployment of advanced energy technologies.
-The evidence holds across geographical locations and is robust to sensitivity analyses.
+We find that 24/7 matching is a viable and effective strategy for clean electricity buyers aiming to eliminate their own carbon footprint and contribute to wider system decarbonisation.
+The evidence holds across different geographical locations.
 Even as grids become cleaner over time, the 24/7 matching strategy retains its significance in reducing system-level emissions, which is essential in light of evolving national energy and climate policies.
+Voluntary commitments to the hourly matching strategy have a further transformative effect on electricity systems by creating an early market for advanced energy technologies, such as long-duration energy storage and clean firm power generators.

### 2024-07-17 manuscript/sections/discussion.tex

@@
 In reality, many \gls{ci} consumers have some degree of demand flexibility, which they can use to adjust their consumption as needed based on grid signals, such as the wholesale market price and the average emission rate of the local electricity mix.
-Moreover, some consumers, such as data centers and cloud computing providers, can shift their load also in space, i.e., to shift computing
-jobs and associated power loads across data center locations \cite{koningsteinWeNowMore2021}.
-In the recent work, Riepin~\&~Brown (2023) explore how space-time load-shifting flexibility can be used to meet high 24/7 CFE targets, as well as what potential benefits it may offer to participating energy buyers and to the rest of the energy system \cite{riepin-zenodo-spacetime247CFE}.
+Moreover, some consumers, such as data centers and cloud computing providers, can shift their load also in space, i.e., to shift computing jobs and associated power loads across data center locations \cite{koningsteinWeNowMore2021}.
+The ability to shift power loads in time and space can play a significant role in achieving hourly carbon-free energy matching by 2030, as more applications and engineering solutions become available \cite{radovanovicCarbonAwareComputingDatacenters2021,radovanovicIEEE2023,koningsteinWeNowMore2021}.
+In the recent work, Riepin~\&~Brown (2023) explore how space-time load-shifting flexibility can be used to meet high 24/7 CFE targets. \cite{riepin-zenodo-spacetime247CFE}.
 

### 2024-07-17 manuscript/sections/results.tex
license: add reuse compatibility
project: initial run pre-commit against all files
manuscript: working paper version

@@
+% SPDX-FileCopyrightText: 2023 Iegor Riepin, Tom Brown
+%
+% SPDX-License-Identifier: CC-BY-4.0
+
 Throughout the analysis, we examine how voluntary clean electricity procurement strategies affect both buyers and the electricity system as a whole.
-From the \gls{ci} buyers' perspective, we examine optimal procurement strategies (i.e., a mix of locally procured energy generation and storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
-From a system perspective, we analyze how voluntary clean energy procurement impacts CO$_2$ emissions in the region and the \enquote{demand pull} for advanced energy technologies.
+From the \gls{ci} buyers' perspective, we examine optimal procurement strategies for both annual and hourly matching strategies (i.e., a cost-optimal mix of locally procured energy generation, storage assets and electricity imports), the average cost of procured electricity and the carbon emissions associated with electricity usage, also known as Scope 2 emissions \cite{GHGProtocolScope2}.
+From a system perspective, we analyze how voluntary clean energy procurement impacts CO$_2$ emissions in the background grid and the \enquote{demand pull} for advanced energy technologies.
 
